```{r, include=F}
library(here)
source(file = here::here("functions/fun.R"))
f_load_libraries_colors()
```

# Experimental design construction for mixture effect on reproduction

## General method

Mixture effects were evaluated using two classical reference models: concentration addition (CA) and independent action (IA) also known as response addition, both of which assume that the effects of two substances are predictable from their individual dose–response functions without any interaction. These models do not introduce additional parameters and serve as the null hypothesis. CA assumes that chemicals behave as dilutions of one another and is most appropriate when compounds share a similar mode of action. CA is generally considered conservative, often predicting stronger mixture effects even when modes of action differ (Drescher & Boedeker, 1995). IA assumes that chemicals act through independent modes of action. It predicts the probability of effect based on the individual dose–response functions and is typically less conservative than CA. Using both CA and IA provides a complementary, widely used framework to detect potential synergistic or antagonistic deviations from additivity (see @sec-howmix for more detail). The use of IA is warranted given the mechanistic dissimilarity between the two compounds: imidacloprid functions as a nicotinic acetylcholine receptor agonist, while epoxiconazole disrupts sterol biosynthesis.

If the CA model or the IA model adequately describe the mixture data, no interaction is inferred. However, when deviations occur, the framework introduces three interaction models that extend CA and IA with one or two additional parameters (see @sec-howmix for details). In the simple interaction model (SA), a single parameter $a$, quantifies a constant shift from the CA or IA prediction, regardless of the dose level or mixture ratio. Here, $a>0$ indicates a systematic synergistic deviation, \$ indicates antagonism, and \$ corresponds to strict additivity (the CA model). In the dose-level dependent model (DL), the parameter $b$ modifies the predicted effect depending on the magnitude of the response. This allows interactions to strengthen or weaken at higher effect levels, capturing scenarios where, for example, synergy emerges only at high concentrations. In the dose-ratio dependent model (DR), the parameter b links the strength of the interaction to the relative proportions of the two compounds. This formulation captures cases where mixture toxicity depends strongly on whether one compound dominates the mixture composition.

To enable proper fitting of the response-surface models, we designed our mixture experiment (MIX experiment) using a ray-design approach [@gessner_1995; @greco_1995], which involves testing predefined mixture ratios based on toxic units derived from individual compound potencies. This experimental design ensures adequate coverage of the dose-response surface while providing the necessary data structure for reliable model calibration and interaction assessment. Although this design is built to ensure optimal detection and visualisation of deviations from concentration additivity, it also allows detection of deviations from the independence of action model. This design assesses binary mixtures at predefined ratios based on Toxic Units.

Ratios of Toxic Units tested were: 1:0, 3:1, 1:1, 1:3, and 0:1. For example, a ratio of 3:1 at TUmix = 1 means that the mixture corresponds to 0.75 TU of imidacloprid and 0.25 TU of epoxiconazole. In other words, mixture ratios were selected to distribute the contribution to the joint effect between the two pesticides in fixed proportions, from single-compound exposures (1:0 and 0:1) to equitoxic and non-equitoxic combinations (3:1, 1:1, 1:3). This design allows evaluation of whether deviations from concentration addition occur across the whole gradient of relative contributions. The concentrations of each pesticide required to achieve these effect-based mixture ratios were calculated from EC50 values derived from individual dose-response curves fitted to the UNI experiment data.

The individual dose-response curves derived from the UNI experiment data were constrained to have common baseline and maximal response levels ($Y_{min}$, $Y_{max}$), and slope parameters for both pesticides, as assumed in the [@jonker_2005] interaction models. The suitability of the three equal dose-response parameters for both pesticides was tested using likelihood ratio tests comparing models with compound-specific parameters against models with constrained equal parameters. The EC$_{50}$ values from these constrained dose-response curves were then used to design the MIX experiment, ensuring that tested concentrations would theoretically match effect isoboles under the concentration addition (CA) hypothesis.

Because we were not able to produce complete dose-response curves for juvenile growth with the UNI experiment (see @sec-expUNI), mixture interaction assessment was only performed on cocoon production from reproduction tests. For the MIX experiment design, seven theoretical effect levels (effect isoboles) spanning the full response range were selected and calculated under the CA hypothesis (more detail available @sec-howmix). These effect isoboles are defined by @eq-isoboles.

$$\frac{C_{IMD}}{f^{-1}_{IMD}(Y)}+\frac{C_{EPX}}{f^{-1}_{EPX}(Y)}=1$$ {#eq-isoboles}

With $Y$ the observed effect for an exposition to the mixture with a concentration $C_{IMD}$ of imidacloprid and a concentration $C_{EPX}$ of epoxiconazole, and $f^{-1}_{IMD}$ and $f^{-1}_{EPX}$ the inverse function of the dose-response relationship.

Including the five mixture ratios and the controls, a total of 36 experimental conditions were assessed, with each condition replicated four times to ensure statistical robustness and account for biological variability in earthworm responses.

For logistical reasons, the MIX experiment was conducted in two batches in the Spring of 2025, with each batch representing two replicates of all treatment conditions using earthworms randomly selected from the same culture pool. The reproduction tests followed the same protocol as the UNI experiment but with individual weight measurements facilitated by tagging earthworms with Visible Implant Elastomers (VIE, Northwest Marine Technology Inc.) two weeks prior to the experiment using the method described by Butt & Lowe, (2007). Cocoon hatching was monitored daily during working days for 8 weeks for the first three replicates to assess reproductive success beyond cocoon production.

The steps leading to the experimental design are described in the following sections.

## Tests of different joint dose-response model for EPX and IMD

```{r data, warning=F, message=F}
data_expA_repro    <- f_read_data_expA_repro()
df_expA_repro_tot  <- data_expA_repro$df_expA_repro
df_expA_repro      <- data_expA_repro$df_expA_repro_alive
df_expA_repro_mean <- data_expA_repro$df_expA_repro_alive_mean

Val_Ctrl <- 1e-4
Label_Ctrl <- "0 (Ctrl)"

path_mixture <- here::here("fig/Mixture/Design")
```

### Definition of the different models

```{r drccomp, warning=F, message=F}
# No common parameter
drc.1<- drm(
  r_Nb_cocoons~Dose, Molecule, 
  data = df_expA_repro,
  type="continuous",
  fct=LL.4(
    names = c("slope", "Ymin", "Ymax", "EC50"),
    fixed=c(NA, 0, NA, NA)
    ), 
    # Reproduction is expected to reach 0 for large concentrations
    pmodels=data.frame(Molecule, Molecule, Molecule)
  )
# summary(drc.1)

Dose_x <- expand.grid(
  exp(
    seq(
      log(0.0001),log(5000),
      by=(log(5000)-log(0.0001))/100
      )
    )
  )

CI.1 <- data.frame(
  Dose=c(Dose_x$Var1, Dose_x$Var1),
  Molecule = c(rep("EPX", length(Dose_x$Var1)), rep("IMD", length(Dose_x$Var1)))
  )

pm.1 <- predict(drc.1, newdata=CI.1, interval="confidence")
CI.1$p <- pm.1[,1]
CI.1$pmin <- pm.1[,2]
CI.1$pmax <- pm.1[,3]

# Common Ymax
drc.2<- drm(
  r_Nb_cocoons~Dose, Molecule, 
  data = df_expA_repro,
  type="continuous",
  fct=LL.4(
    names = c("slope", "Ymin", "Ymax", "EC50"),
    fixed=c(NA, 0, NA, NA)
    ), 
  # Reproduction is expected to reach 0 for large concentrations
  pmodels=data.frame(Molecule, 1, Molecule)
  )
# summary(drc.2)

CI.2 <- data.frame(
  Dose=c(Dose_x$Var1, Dose_x$Var1),
  Molecule = c(rep("EPX", length(Dose_x$Var1)), rep("IMD", length(Dose_x$Var1)))
  )

pm.2 <- predict(drc.2, newdata=CI.2, interval="confidence")
CI.2$p <- pm.2[,1]
CI.2$pmin <- pm.2[,2]
CI.2$pmax <- pm.2[,3]

# Common slope
drc.3<- drm(
  r_Nb_cocoons~Dose, Molecule, 
  data = df_expA_repro,
  type="continuous",
  fct=LL.4(
    names = c("slope", "Ymin", "Ymax", "EC50"),
    fixed=c(NA, 0, NA, NA)
    ), 
  # Reproduction is expected to reach 0 for large concentrations
  pmodels=data.frame(1, Molecule, Molecule)
  )
# summary(drc.3)

CI.3 <- data.frame(
  Dose = c(Dose_x$Var1, Dose_x$Var1),
  Molecule = c(rep("EPX", length(Dose_x$Var1)), rep("IMD", length(Dose_x$Var1)))
  )

pm.3 <- predict(drc.3, newdata=CI.3, interval="confidence")
CI.3$p <- pm.3[,1]
CI.3$pmin <- pm.3[,2]
CI.3$pmax <- pm.3[,3]

# Common Ymax and slope
drc.4<- drm(
  r_Nb_cocoons~Dose, Molecule, 
  data = df_expA_repro,
  type="continuous",
  fct=LL.4(
    names = c("slope", "Ymin", "Ymax", "EC50"),
    fixed = c(NA, 0, NA, NA)
    ), 
  # Reproduction is expected to reach 0 for large concentrations
  pmodels=data.frame(1, 1, Molecule)
  )
# summary(drc.4)

CI.4 <- data.frame(
  Dose = c(Dose_x$Var1, Dose_x$Var1),
  Molecule = c(rep("EPX", length(Dose_x$Var1)), rep("IMD", length(Dose_x$Var1)))
  )

pm.4 <- predict(drc.4, newdata=CI.4, interval="confidence")
CI.4$p <- pm.4[,1]
CI.4$pmin <- pm.4[,2]
CI.4$pmax <- pm.4[,3]

```

```{r, warning=F, message=F}
#| fig-cap: Dose-response curves for production of cocoons according to different models. EPX in represented in light blue and IMD in blue. Each point correspond to the number of cocoons produced in one cosm (with 2 earthworms). Thick lines represent the estimated dose-response curves. 
#| label: fig-drcsplot
#| fig-width: 12
#| fig-height: 8

line_width <- 1.2

x <- seq(0.000001, 5000, 0.01)

plot_drc_1 <- ggplot()+
  
  geom_ribbon(
    data=CI.1, 
    aes(
      x=Dose, 
      y=p, 
      ymin=pmin, ymax=pmax, 
      group=Molecule, 
      fill=Molecule
      ), 
    alpha=0.2
    )+
  geom_line(
    data=CI.1, 
    aes(
      x=Dose, 
      y=p, 
      group=Molecule, 
      color=Molecule
      ), 
    linewidth=line_width
    )+
  geom_point(
    data=df_expA_repro, 
    aes(
      x=Dose_plot, 
      y=r_Nb_cocoons, 
      color=Molecule, 
      shape=Molecule
      ), 
    cex=2, 
    alpha=0.4
    )+
  geom_point(
    data=df_expA_repro_mean, 
    aes(
      x=Dose_plot, 
      y=r_Nb_cocoons, 
      color=Molecule, 
      shape=Molecule
      ), 
    cex=3, 
    alpha=1
    )+
  #geom_ribbon(data=CI.1, aes(x=x, y=p, ymin=pmin, ymax=pmax), alpha=0.2)+
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100),  
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100")
  )+
  
  scale_color_manual(name="Dose (mg/kg)",values=c(col_molec, col_molec))+
  scale_shape_manual(name="Dose (mg/kg)",values=c(shape_molec, shape_molec))+
  scale_fill_manual(name="Dose (mg/kg)",values=c(col_molec, col_molec))+
  
  theme_minimal()+
  
  labs(
    x="Dose (mg/kg)", 
    y=expression(paste("Relative number of cocoons produced per cosm")), 
    title = "No common parameter"
    )+
  theme(
    legend.position = "right", 
    legend.title=element_text(size=sizetitle-2,face="bold"), 
    
    title=element_text(size=sizetitle, face="bold"), 
    
    axis.title.x = element_text(size=sizetitle,face="plain"), 
    axis.title.y = element_text(size=sizetitle,face="plain")
    )

plot_drc_2 <- ggplot()+
  
  geom_ribbon(
    data=CI.2, 
    aes(
      x=Dose, 
      y=p, 
      ymin=pmin, ymax=pmax, 
      group=Molecule, 
      fill=Molecule
      ), 
    alpha=0.2
    )+
  geom_line(
    data=CI.2, 
    aes(
      x=Dose, 
      y=p, 
      group=Molecule, 
      color=Molecule
      ), 
    linewidth=line_width
    )+
  geom_point(
    data=df_expA_repro, 
    aes(
      x=Dose_plot, 
      y=r_Nb_cocoons, 
      color=Molecule, 
      shape=Molecule
      ), 
    cex=2, 
    alpha=0.4
    )+
  geom_point(
    data=df_expA_repro_mean, 
    aes(
      x=Dose_plot, 
      y=r_Nb_cocoons, 
      color=Molecule, 
      shape=Molecule
      ), 
    cex=3, 
    alpha=1
    )+
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100),  
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100")
  )+
  
  scale_color_manual(name="Dose (mg/kg)",values=c(col_molec, col_molec))+
  scale_shape_manual(name="Dose (mg/kg)",values=c(shape_molec, shape_molec))+
  scale_fill_manual(name="Dose (mg/kg)",values=c(col_molec, col_molec))+
  
  theme_minimal()+
  
  labs(
    x="Dose (mg/kg)", 
    y=expression(paste("Relative number of cocoons produced per cosm")), 
    title = "Common Ymax"
    )+
  theme(
    legend.position = "right", 
    legend.title=element_text(size=sizetitle-2,face="bold"), 
    
    title=element_text(size=sizetitle, face="bold"), 
    
    axis.title.x = element_text(size=sizetitle,face="plain"), 
    axis.title.y = element_text(size=sizetitle,face="plain")
    )

plot_drc_3 <- ggplot()+
  
  geom_ribbon(
    data=CI.3, 
    aes(
      x=Dose, 
      y=p, 
      ymin=pmin, ymax=pmax, 
      group=Molecule, 
      fill=Molecule
      ), 
    alpha=0.2
    )+
  geom_line(
    data=CI.3, 
    aes(
      x=Dose, 
      y=p, 
      group=Molecule, 
      color=Molecule
      ), 
    linewidth=line_width
    )+
  geom_point(
    data=df_expA_repro, 
    aes(
      x=Dose_plot, 
      y=r_Nb_cocoons, 
      color=Molecule, 
      shape=Molecule
      ), 
    cex=2, 
    alpha=0.4
    )+
  geom_point(
    data=df_expA_repro_mean, 
    aes(
      x=Dose_plot, 
      y=r_Nb_cocoons, 
      color=Molecule, 
      shape=Molecule
      ), 
    cex=3, 
    alpha=1
    )+
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100),  
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100")
  )+
  
  scale_color_manual(name="Dose (mg/kg)",values=c(col_molec, col_molec))+
  scale_shape_manual(name="Dose (mg/kg)",values=c(shape_molec, shape_molec))+
  scale_fill_manual(name="Dose (mg/kg)",values=c(col_molec, col_molec))+
  
  theme_minimal()+
  
  labs(
    x="Dose (mg/kg)", 
    y=expression(paste("Relative number of cocoons produced per cosm")), 
    title = "Common slope"
    )+
  theme(
    legend.position = "right", 
    legend.title=element_text(size=sizetitle-2,face="bold"), 
    
    title=element_text(size=sizetitle, face="bold"), 
    
    axis.title.x = element_text(size=sizetitle,face="plain"), 
    axis.title.y = element_text(size=sizetitle,face="plain")
    )

plot_drc_4 <- ggplot()+
  
  geom_ribbon(
    data=CI.4, 
    aes(
      x=Dose, 
      y=p, 
      ymin=pmin, ymax=pmax, 
      group=Molecule, 
      fill=Molecule
      ), 
    alpha=0.2
    )+
  geom_line(
    data=CI.4, 
    aes(
      x=Dose, 
      y=p, 
      group=Molecule, 
      color=Molecule
      ), 
    linewidth=line_width
    )+
  geom_point(
    data=df_expA_repro, 
    aes(
      x=Dose_plot, 
      y=r_Nb_cocoons, 
      color=Molecule, 
      shape=Molecule
      ), 
    cex=2, 
    alpha=0.4
    )+
  geom_point(
    data=df_expA_repro_mean, 
    aes(
      x=Dose_plot, 
      y=r_Nb_cocoons, 
      color=Molecule, 
      shape=Molecule
      ), 
    cex=3, 
    alpha=1
    )+
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100),  
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100")
  )+
  
  scale_color_manual(name="Dose (mg/kg)",values=c(col_molec, col_molec))+
  scale_shape_manual(name="Dose (mg/kg)",values=c(shape_molec, shape_molec))+
  scale_fill_manual(name="Dose (mg/kg)",values=c(col_molec, col_molec))+
  
  theme_minimal()+
  
  labs(
    x="Dose (mg/kg)", 
    y=expression(paste("Relative number of cocoons produced per cosm")), 
    title = "Common slope and Ymax"
    )+
  theme(
    legend.position = "right", 
    legend.title=element_text(size=sizetitle-2,face="bold"), 
    
    title=element_text(size=sizetitle, face="bold"), 
    
    axis.title.x = element_text(size=sizetitle,face="plain"), 
    axis.title.y = element_text(size=sizetitle,face="plain")
    )

plot_save <- plot_drc_1 + plot_drc_2 + plot_drc_3 + plot_drc_4 + 
  plot_layout(ncol=2, guides="collect") & 
  theme(
    legend.position = "bottom", 
    title=element_text(size=12, face="bold"), 
    axis.title.x = element_text(face="plain"), 
    axis.title.y = element_text(face="plain")
    )

plot_save

```

```{r, include=F}
ggsave(
  filename="ExpA_repro_comp_drc_models.png", 
  plot=plot_save, 
  width=12, height = 8, 
  path=path_mixture
  )
ggsave(
  filename="ExpA_repro_comp_drc_models.svg", 
  plot=plot_save, 
  width=12, height = 8, 
  path=path_mixture
  )
```

```{r, include=F}
plot_drc.4.show <- ggplot()+
  geom_ribbon(
    data=CI.4, 
    aes(
      x=Dose, 
      y=p, 
      ymin=pmin, 
      ymax=pmax, 
      group=Molecule, 
      fill=Molecule
      ), 
    alpha=0.2
    )+
  geom_line(
    data=CI.4, 
    aes(
      x=Dose, 
      y=p, 
      color=Molecule
    ), 
    linewidth=line_width
    )+
  geom_point(
    data=df_expA_repro, 
    aes(
      x=Dose_plot, 
      y=r_Nb_cocoons, 
      color=Molecule, 
      shape=Molecule
      ), 
    cex=2, 
    alpha=0.4
    )+
    geom_point(
     data=df_expA_repro_mean, 
     aes(
       x=Dose_plot, 
       y=r_Nb_cocoons, 
       color=Molecule, 
       shape=Molecule
       ), 
     cex=3, 
     alpha=1
     )+
  
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100),  
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100")
  )+

  scale_color_manual(values=col_molec)+
  scale_fill_manual(values=col_molec)+
  scale_shape_manual(values=shape_molec)+
  
  labs(
    x="Dose (mg/kg)", 
    y=expression(paste("Number of cocoons produced per cosm"))
    )+
  
  theme_minimal()+
  theme(
    legend.position = "bottom", 
    legend.title=element_blank(),
    
    title=element_text(size=sizetitle, face="bold"),
    
    axis.title.x = element_text(size=sizetitle,face="plain"), 
    axis.title.y = element_text(size=sizetitle,face="plain")
    )
```

```{r, include=F}
ggsave(
  filename="ExpA_repro_drc_mixmodel.png", 
  plot=plot_drc.4.show, 
  width=5, 
  height = 4, 
  path=path_mixture
  )
ggsave(
  filename="ExpA_repro_drc_mixmodel.svg", 
  plot=plot_drc.4.show, 
  width=5, 
  height = 4, 
  path=path_mixture
  )
```

### Comparison of the models

We can the compare the models.

```{r AIC, warning=F, message=F}
AIC <- AIC(
  drc.1, 
  drc.2, 
  drc.3, 
  drc.4
  )
AIC

delta_AIC_24 <- round(abs(AIC$AIC[2]-AIC$AIC[4]), 2)

```

The drc.1 model is not the best biologically speaking because Ymax should be the same (in each case controls should produce the same number of cocoons in average). So there is only a AIC difference of `r delta_AIC_24` between the drc.2 model (common extremums) and the model drc.4 (common slopes and extremums).

```{r anova12, warning=F, message=F}
anova(
  drc.1, 
  drc.2, 
  test="Chisq"
  )
```

```{r anova13, warning=F, message=F}
anova(
  drc.1, 
  drc.3, 
  test="Chisq"
  )
```

```{r anova14, warning=F, message=F}
anova(
  drc.1, 
  drc.4, 
  test="Chisq"
  )
```

```{r anova24, warning=F, message=F}
anova(
  drc.2, 
  drc.4, 
  test="Chisq"
  )
```

There is no significative difference between the four models. We can then consider that both dose-response curves have the same extremums and slopes (model drc.4).

### Hypothesis testing for the drc.4 model

```{r, warning=F, message=F}
#| fig-cap: Diagnostic graphs for the model with common extremums and slope (drc.4)
#| label: fig-drc4diag
#| fig-width: 8
#| fig-height: 4

col_diag <- Nord_polar[4]

plot_QQ <- ggplot(mapping=aes(sample=residuals(drc.4)))+
  
  stat_qq(alpha=0.3)+
  stat_qq_line(color=col_diag)+
  
  labs(
    x="Normal quantiles", 
    y="Residuals"
    )+
  
  theme_minimal()

plot_resfit <- ggplot()+
  geom_point(
    mapping=aes(
      x=fitted(drc.4), 
      y=residuals(drc.4)
      ), 
    alpha=0.3, 
    color=col_diag
    )+
  labs(
    x="Fitted", 
    y="Residuals"
    )+
  
  scale_x_log10()+
  
  theme_minimal()

plot <- plot_resfit + plot_QQ + 
  plot_layout(ncol=2)
plot
```

Normality test and homogeneity of variance test for the drc.4 model.

```{r shapbart, warning=F, message=F}
# Residus normality
shapiro.test(residuals(drc.4))
# Residus variance homogeneity
bartlett.test(residuals(drc.4), as.factor(subset(df_expA_repro, t==28)$Dose))
```

### Summary of the drc.4 model

```{r drc4res, warning=F, message=F}
summary(drc.4)
confint(object = drc.4, level=0.95)
```

```{r EC50, warning=F, message=F}
Ratio_EC50 <- EDcomp(drc.4, c(50, 50),interval="delta") # Estimate of the EC50 ratio
Ratio_EC50_print <- round(Ratio_EC50[1],2)
```

This model gives us an EC$_{50}$ ratio of `r Ratio_EC50_print`.

```{r resdrcsave, warning=F, message=F}
res <- as.data.frame(coef(drc.4))
#write.csv(x= res, file=here::here("data/DRC_parameters_cocoons.csv"))
```

## Construction of the experimental design

```{r drcdef, warning=F, message=F}
drc_res <- read.csv(here::here("data/DRC_parameters_cocoons_really_used.csv"), sep=",")

Y_max <- drc_res[2, 2]
Y_min <- 0
slope <- drc_res[1, 2]
EPX_EC50 <- drc_res[3, 2]
IMD_EC50 <- drc_res[4, 2]

EPX_drc <- function(dose){
  return(Y_min+(Y_max-Y_min)/(1+exp(slope*(log(dose)-log(EPX_EC50)))))
}

IMD_drc <- function(dose){
  Y_max <- drc_res[2, 2]
  Y_min <- 0
  slope <- drc_res[1, 2]
  EPX_EC50 <- drc_res[3, 2]
  IMD_EC50 <- drc_res[4, 2]
  return(Y_min+(Y_max-Y_min)/(1+exp(slope*(log(dose)-log(IMD_EC50)))))
}

```

```{r defratios, warning=F, message=F}
# Ratios considered
ratios = c(0, 1/4, 1/2, 3/4, 1)

EPX_x = NULL
IMD_x = NULL

ratio_EC50 <- IMD_EC50/EPX_EC50

for(i in ratios){
  EPX_x=rbind(EPX_x,EPX_EC50*i)
  IMD_x=rbind(IMD_x,IMD_EC50*(1-i))
}

factor_design <- 10^(1/4)

```

```{r defdesign, warning=F, message=F}

EPX_x <- c(
  EPX_x,
  EPX_x/(factor_design^9),
  EPX_x/(factor_design^5), 
  EPX_x/(factor_design^2), 
  EPX_x/factor_design,
  factor_design*EPX_x, 
  factor_design^2*EPX_x
  )
IMD_x <- c(
  IMD_x,
  IMD_x/(factor_design^9),
  IMD_x/(factor_design^5), 
  IMD_x/(factor_design^2), 
  IMD_x/factor_design,
  factor_design*IMD_x, 
  factor_design^2*IMD_x
  )


df_design <- data.frame(EPX=EPX_x,
                        IMD=IMD_x,
                        Ratio=EPX_x/IMD_x*IMD_EC50/EPX_EC50)

write.csv(df_design, file=here::here("data/Design_mixture.csv"))

```

```{r, message=F, warning=F}
#| fig-cap: Experimental design for mixture effects on reproduction
#| label: fig-mixdesign
#| fig-width: 5
#| fig-height: 5

width_iso <- 1.1
size_points <- 3

df_design_plot <- df_design |> 
  mutate(
    label=paste(
      "[IMD] = ", 
      signif(IMD, 3), 
      "mg/kg\n [EPX] = ", 
      signif(EPX,3), "mg/kg"
      )
    )

plot_design <- ggplot()+
  xlim(min(EPX_x), max(EPX_x))+
  ylim(min(IMD_x), max(IMD_x))+
  # Ligne des ratios
  geom_abline(
    intercept=0, 
    slope=ratio_EC50/3, 
    color=pal_col[2]
    )+
  geom_abline(
    intercept=0, 
    slope=ratio_EC50*3, 
    color=pal_col[2]
    )+
  geom_abline(
    intercept=0, 
    slope=ratio_EC50, 
    color=pal_col[2]
    )+
  geom_abline(
    intercept=0, 
    slope=0, 
    color=pal_col[2]
    )+
  geom_vline(
    xintercept = 0, 
    color=pal_col[2]
    )+
  
  # Effect isoboles
  geom_abline(
    intercept=IMD_EC50*factor_design^2, 
    slope=-ratio_EC50, 
    color=pal_col[1], 
    lwd=width_iso
    )+
  geom_abline(
    intercept=IMD_EC50*factor_design, 
    slope=-ratio_EC50, 
    color=pal_col[1], 
    lwd=width_iso
    )+
  geom_abline(
    intercept=IMD_EC50, 
    slope=-ratio_EC50, 
    color=pal_col[1], 
    lwd=width_iso
    )+
  geom_abline(
    intercept=IMD_EC50/factor_design, 
    slope=-ratio_EC50, 
    color=pal_col[1], 
    lwd=width_iso
    )+
  geom_abline(
    intercept=IMD_EC50/(factor_design^2), 
    slope=-ratio_EC50, 
    color=pal_col[1], 
    lwd=width_iso
    )+
  geom_abline(
    intercept=IMD_EC50/(factor_design^5), 
    slope=-ratio_EC50, 
    color=pal_col[1], 
    lwd=width_iso
    )+
  geom_abline(
    intercept=IMD_EC50/(factor_design^9), 
    slope=-ratio_EC50, 
    color=pal_col[1], 
    lwd=width_iso
    )+
  
  # Ratios annotations
  annotate(
    geom="text", 
    x=30, 
    y=max(IMD_x), 
    label="0:1", 
    color=pal_col[2], 
    fontface="bold"
    )+
  annotate(
    geom="text", 
    x=200, 
    y=max(IMD_x), 
    label="3:1", 
    color=pal_col[2], 
    fontface="bold"
    )+
  annotate(
    geom="text", 
    x=max(EPX_x)-30, 
    y=max(IMD_x), 
    label="1:1", 
    color=pal_col[2], 
    fontface="bold"
    )+
  annotate(
    geom="text",
    x=max(EPX_x),
    y=0.8,
    label="1:3", 
    color=pal_col[2], 
    fontface="bold"
    )+
  annotate(
    geom="text", 
    x=max(EPX_x), 
    y=0.1, 
    label="1:0", 
    color=pal_col[2], 
    fontface="bold"
    )+
  
  # Design points
  geom_point_interactive(
    data=df_design_plot, 
    aes(
      x=EPX, 
      y=IMD,
      tooltip = label), 
    size=size_points, 
    color=Nord_polar[1]
    )+
  
  labs(
    x="Epoxiconazole (mg/kg)",
    y="Imidacloprid (mg/kg)"
    )+
  
  theme_minimal(12)



tooltip_css <- "
  border-radius: 12px;
  color: #333;
  background-color: white;
  padding: 10px;
  font-size: 14px;
  transition: all 0.5s ease-out;
"

hover_css <- "
  filter: brightness(75%);
  cursor: pointer;
  transition: all 0.5s ease-out;
  filter: brightness(1.15);
"

interactive_plot <- girafe(
  ggobj=plot_design,
  height_svg = 5,
  width_svg = 5
  ) |> 
  girafe_options(opts_sizing(rescale = FALSE))

# Add interactivity
interactive_plot <- interactive_plot %>%
  girafe_options(
    opts_hover(css = hover_css),
    opts_tooltip(css = tooltip_css),
    opts_hover_inv(css = "opacity:0.3; transition: all 0.2s ease-out;")
  )

interactive_plot

```

```{r, include=F}
ggsave(
  filename="Mixture_design_exp.png", 
  plot=plot_design, 
  width=5, 
  height = 4, 
  path=path_mixture
  )

ggsave(
  filename="Mixture_design_exp.jpg", 
  plot=plot_design, 
  width=5, 
  height = 4, 
  path=path_mixture
  )

ggsave(
  filename="Mixture_design_exp.svg", 
  plot=plot_design, 
  width=5, 
  height = 4, 
  path=path_mixture
  )
```

Each effect isobole is supposed to give us a range of effects given by @fig-leveleffectdesign.

```{r, warning=F, message=F}
IMD_point_design <- subset(df_design, EPX==0)$IMD
EPX_point_design <- subset(df_design, IMD==0)$EPX

CI.design <- data.frame(
  Dose=c(EPX_point_design, IMD_point_design),
  Molecule = c(rep("EPX", length(EPX_point_design)), rep("IMD", length(IMD_point_design)))
)

pm.design <- predict(drc.1, newdata=CI.design, interval="confidence")
CI.design$p <- pm.design[,1]
CI.design$pmin <- pm.design[,2]
CI.design$pmax <- pm.design[,3]
```

```{r, message=F, warning=F}
#| fig-cap: Corresponding theorical range of effect tested with this design. Effects are calculated with the dose-response curves without common parameters (drc.1). Small points correspond to data from the single exposition experiment. Bold points are the predicted effect of the tested isobols. 
#| label: fig-leveleffectdesign
#| fig-width: 8
#| fig-height: 6

# y_min <- 0
# y_max <- 35

plot_drc_th <- ggplot()+
  geom_ribbon(
    data=CI.1, 
    aes(
      x=Dose, 
      y=p, 
      ymin=pmin, 
      ymax=pmax,
      fill = Molecule
      ), 
    alpha=0.2
    )+
  geom_line(
    data=CI.1, 
    aes(
      x=Dose, 
      y=p,
      color=Molecule
      )
    )+
  geom_point(
    data=df_expA_repro, 
    aes(
      x=Dose_plot, 
      y=r_Nb_cocoons,
      color=Molecule, 
      shape=Molecule, 
      ), 
    cex=2, 
    alpha=0.4
    )+
  
  geom_point(
    data = CI.design,
    aes(
      x=Dose, 
      y=p,
      shape = Molecule
      ), 
    color=col_red,
    cex=3,
    alpha = 1
    )+
  
  scale_color_manual(values=col_molec)+
  scale_fill_manual(values=col_molec)+
  scale_shape_manual(values=shape_molec)+
  
  facet_wrap(~Molecule, ncol=2)+
  
  scale_x_log10(
     breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100),  
     labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100")
   )+
  # ylim(y_min, y_max)+
  
  theme_minimal()+
  
  labs(
    x="Dose (mg/kg)", 
    y=expression(paste("Relative cocoon production"))
    )+
  theme(
    legend.position = "right", 
    legend.title=element_text(size=sizetitle-2,face="bold"), 
    
    title=element_text(size=sizetitle, face="bold"), 
    
    axis.title.x = element_text(size=sizetitle,face="plain"), 
    axis.title.y = element_text(size=sizetitle,face="plain")
    )

plot_drc_th
```

```{r, include=F}
ggsave(
  filename="Mixture_design_effect_range.png", 
  plot=plot_drc_th, 
  width=8, 
  height = 4, 
  path=path_mixture
  )
ggsave(
  filename="Mixture_design_effect_range.svg", 
  plot=plot_drc_th, 
  width=8, 
  height = 4, 
  path=path_mixture
  )
```

```{r logistics, include=F}
Q_clx_cosm <- 200 # g
Nb_rep <- 5
Q_sample <- 200 # g

Q_EPX <- Nb_rep*Q_clx_cosm/1000*sum(df_design$EPX)

df_Q <- df_design%>%
  mutate(
    Q_clx_conc = (Q_clx_cosm*Nb_rep+Q_sample)/1000, # kg
    Q_EPX_conc = EPX*Q_clx_conc, 
    Q_IMD_conc = IMD*Q_clx_conc
    )

Q_EPX_tot <- sum(df_Q$Q_EPX_conc)
Q_IMD_tot <- sum(df_Q$Q_IMD_conc)
Q_EPX_tot # 3.3 g
Q_IMD_tot # 9.3 mg
```

<button class="accordion-button" type="button" data-bs-toggle="collapse" data-bs-target="#collapseOne">

<b> Session Information </b>

</button>

:::: {#collapseOne .accordion-collapse .collapse}
<div>

```{r}
sessionInfo()
```

</div>
::::
