```{r, include=F}
library(here)
source(file = here::here("functions/fun.R"))
f_load_libraries_colors()

color_red <- c(
  "#F2DADB",  # Very light  
  "#E8B6B9",  # Lighter  
  "#D88C91",  # Light  
  "#BF616A",  # Base color  
  "#9F4E56",  # Darker  
  "#7F3D44",  # Even darker  
  "#5F2C32"   # Very dark  
)

color_green <- c(
  "#EEF4E6",  # Very light  
  "#D4E2C1",  # Lighter  
  "#B8CC9E",  # Light  
  "#A3BE8C",  # Base color  
  "#86A06F",  # Darker  
  "#6B8356",  # Even darker  
  "#4F663D"   # Very dark  
)

color_blue <- c(
  "#E3E9F1",  # Very light  
  "#B8C7DC",  # Lighter  
  "#8FA5C7",  # Light  
  "#5E81AC",  # Base color  
  "#48648A",  # Darker  
  "#354B6B",  # Even darker  
  "#22324D"   # Very dark  
)


```

# Power analysis

We want to investiguate what is the minimal interaction that can be estimated with a maximum error of 10% with such experimental design with 4 replicates and with simulated data following a Poisson distribution (reproduction data are count data).

```{r paramdef, message=F, warning=F}
Nb_rep <- 4
# Simulated interaction
interaction_a <- -1
```

We get the information about the experimental design.

```{r datadesign, message=F, warning=F}
#| code-show: show

df_design <- read.csv(here::here("data/Design_mixture.csv"))
df_drc_param <- read.csv(here::here("data/DRC_parameters_cocoons_really_used.csv"))

slope <- df_drc_param$coef.drc.4.[1]
Y_max <- df_drc_param$coef.drc.4.[2]
EPX_EC50 <- df_drc_param$coef.drc.4.[3]
IMD_EC50 <- df_drc_param$coef.drc.4.[4]
y_min <- 0

C_mat = cbind(df_design$EPX,df_design$IMD)
Max = Y_max
Slopes = c(slope, slope)
Ec50s = c(EPX_EC50, IMD_EC50)

```

## Example for a given interaction value

### Data simulation

We first calculate the theorical effect for each concentration combinations of our design.

```{r resCAthdesign, message=F, warning=F}
#| code-show: show
# Calculation of effects for the design concentrations 
res_CA_theorical_design <- CA_complete2(
  C_mat, 
  Max, Slopes, Ec50s, 
  interact="SA", 
  a=interaction_a
  )

# We add the corresponding response to our design
df_dose_rep <- df_design%>%
  mutate(rep_Y=res_CA_theorical_design)

df_dose_rep <- df_dose_rep[,-c(1, 4)]
```

```{r resCAthdesignsurf, message=F, warning=F}
#| code-show: show
# Graphic preparation : Construction of the surface mesh

min_dose_EPX <- min(subset(df_design, !EPX==0)$EPX)
max_dose_EPX <- max(subset(df_design, !EPX==0)$EPX)

min_dose_IMD <- min(subset(df_design, !IMD==0)$IMD)
max_dose_IMD <- max(subset(df_design, !IMD==0)$IMD)

by_EPX <- (log(max_dose_EPX)-log(min_dose_EPX))/100
by_IMD <- (log(max_dose_IMD)-log(min_dose_IMD))/100

# Grid creation
grid_C1 <- exp(seq(log(min_dose_EPX), log(max_dose_EPX), by = by_EPX))
grid_C2 <- exp(seq(log(min_dose_IMD), log(max_dose_IMD), by = by_IMD))

grid <- expand.grid(
  x = grid_C1, 
  y = grid_C2
  )

# Calculation of the response in the case of additivity (CA model - null hypothesis)

df_theorical_surf_CA <- CA_complete2(
  C_mat=grid, 
  Max, Slopes, Ec50s, 
  interact="none",
  multicore = TRUE
  )

df_theorical_surf_CA_ordered <- df_theorical_surf_CA[order(grid[,2])]

z_CA <- matrix(
    df_theorical_surf_CA_ordered, 
    nrow = length(grid_C1), 
    ncol = length(grid_C2), 
    byrow = FALSE
    )

grid_CA <- expand.grid(x = grid_C1, y = grid_C2)
grid_CA$z <- as.vector(z_CA)

# Calculation of the response for all our mesh
df_theorical_surf_SA <- CA_complete2(
  C_mat=grid, 
  Max, Slopes, Ec50s, 
  interact="SA", 
  a=interaction_a,
  multicore = TRUE
  )

df_theorical_surf_SA_ordered <- df_theorical_surf_SA[order(grid[,2])]

z_SA <- matrix(
    df_theorical_surf_SA_ordered, 
    nrow = length(grid_C1), 
    ncol = length(grid_C2), 
    byrow = FALSE
    )

grid_ThSurface_SA <- expand.grid(x = grid_C1, y = grid_C2)
grid_ThSurface_SA$z <- as.vector(z_SA)

```

```{r, warning=F, message=F}
#| fig-cap: Theorical surface (blue lines). Dotted grey lines represent the additivity case. 
#| label: fig-ThSurf2D
#| fig-width: 5
#| fig-height: 4

target_effect <- 50
bin_contour <- 1

p <- ggplot() +
  geom_contour(
    data = grid_CA,
    aes(x = x, y = y, z = z),
    color = Nord_polar[4],
    linewidth = 0.8,
    linetype = "dotted",
    binwidth = bin_contour
  ) +
  geom_contour(
    data = grid_ThSurface_SA,
    aes(x = x, y = y, z = z),
    color = Nord_frost[4], 
    linewidth = 1,
    binwidth = bin_contour
  ) +
  metR::geom_text_contour(
    data = grid_ThSurface_SA,
    aes(x = x, y = y, z = z), 
    stroke = 0.2,
    size = 4,
    color = Nord_frost[4],
    skip = 1,
    label.placer = label_placer_flattest(),
    binwidth = bin_contour
  ) +
  labs(
    x = expression("[EPX] (mg·kg"^-1*")"),
    y = expression("[IMD] (mg·kg"^-1*")")
  ) +
  theme_minimal(base_size = 13) +
  theme(
    axis.title = element_text(face = "bold"),
    axis.text = element_text(color = "black"),
    plot.margin = margin(10, 10, 10, 10)
  )

p

```


We can now simulate our data.

```{r simdata, message=F, warning=F}
#| code-show: show

df_sim_data <- data.frame(
  Y=c(),
  EPX=c(),
  IMD=c()
  )

set.seed(12)
for(i in 1:length(df_dose_rep$EPX)){
  
  Y_th <- df_dose_rep$rep_Y[i] # Theorical response for a given condition
  Y_sim <- rpois(Nb_rep, Y_th) # <1> # Simulated responses for a given condition
  
  EPX <- rep(df_dose_rep$EPX[i], Nb_rep)
  IMD <- rep(df_dose_rep$IMD[i], Nb_rep)
  
  df_sim_data_i <- data.frame(
    Y_th=rep(Y_th, Nb_rep),       
    Y_sim=Y_sim,                  
    EPX=EPX,
    IMD=IMD
    )
  df_sim_data <- rbind(df_sim_data, df_sim_data_i)
}
```

1.  Addition of individual variation in the response through a Poisson distribution

### Fit of the model on our data

```{r resCAfit, message=F, warning=F}
#| code-show: show

param <- data.frame(Slopes=Slopes, Max=Max, Ec50s=Ec50s)

df_data_fit<-CA_complete2_fit_speed(
  C_mat=cbind(                     
    df_sim_data$EPX,               
    df_sim_data$IMD                 
    ),                            
  Response=df_sim_data$Y_sim,        
  interact="SA",                    
  param=param,                    
  multicore = TRUE               
  )                                 

# Log-likelihood of the model
LL_data_fit_SA <- df_data_fit$Error

res_a <- round(df_data_fit$a, 3)                          # <1>
ratio_interaction_a=round(df_data_fit$a/interaction_a, 3) # <2>

```

1.  Estimated value of $a$
2.  Ratio between the estimated and simulated value of $a$

The estimated interaction parameter $a$ is `r res_a`.

```{r, warning=F, message=F}
#| tbl-cap: Result of the interaction estimation.
#| label: tbl-resSAinter

df_res <- data.frame(`Simulated interaction parameter`=interaction_a,
                     `Estimated interaction parameter`=round(df_data_fit$a,3),
                     Ratio=ratio_interaction_a,
                     LL = LL_data_fit_SA)
df_res |> datatable(options = list(dom = 't'), class="hover") 
```

Step 3 - Graphical representation

```{r simdataCAfit, message=F, warning=F}
df_data_solved_surf <- CA_complete2( # <1> 
  C_mat=grid,                            # <1> 
  Max=Max,                               # <1> 
  Slopes=Slopes,                         # <1> 
  Ec50s=Ec50s,                           # <1> 
  a=df_data_fit$a, interact="SA"       # <1> 
  )                                      # <1> 

df_data_solved_surf_ordered <- df_data_solved_surf[order(grid[,2])]

z_SA_Est <- matrix(
  df_data_solved_surf_ordered,
  nrow=length(grid_C1),
  ncol=length(grid_C2),
  byrow=FALSE
  )

grid_EstSurface_SA <- expand.grid(x = grid_C1, y = grid_C2)
grid_EstSurface_SA$z <- as.vector(z_SA_Est)
```

1.  Modeling of the dose-response surface with the estimated value of $a$

```{r, warning=F, message=F}
#| fig-cap: Estimated surface (blue lines). Dotted grey lines represent the additivity case. 
#| label: fig-EstSurf2D
#| fig-width: 5
#| fig-height: 4

target_effect <- 50
bin_contour <- 1

p <- ggplot() +
  geom_contour(
    data = grid_CA,
    aes(x = x, y = y, z = z),
    color = Nord_polar[4],
    linewidth = 0.8,
    linetype = "dotted",
    binwidth = bin_contour
  ) +
  geom_contour(
    data = grid_ThSurface_SA,
    aes(x = x, y = y, z = z),
    color = Nord_frost[4], 
    linewidth = 1,
    binwidth = bin_contour
  ) +
  metR::geom_text_contour(
    data = grid_ThSurface_SA,
    aes(x = x, y = y, z = z), 
    stroke = 0.2,
    size = 4,
    color = Nord_frost[4],
    skip = 1,
    label.placer = label_placer_flattest(),
    binwidth = bin_contour
  ) +
  labs(
    x = expression("[EPX] (mg·kg"^-1*")"),
    y = expression("[IMD] (mg·kg"^-1*")")
  ) +
  theme_minimal(base_size = 13) +
  theme(
    axis.title = element_text(face = "bold"),
    axis.text = element_text(color = "black"),
    plot.margin = margin(10, 10, 10, 10)
  )

p

```

## Determination of the lowest interaction detectable with an error of 10%

We create a function that will simulate the response of `Nb_pop` experiments consisting of our experimental design with `Nb_rep` replicates for an exposure to a mixture with each of the interaction parameter value ($a$) contained in the list `l_interaction_a` and will estimate the interaction with the Jonker simple interaction model. 

```{r fpower}
#| code-show: show

f_power_design <- function(Nb_rep, l_interaction_a, Nb_pop, param){
  
  res <- data.frame()

  for (Nb_rep_j in Nb_rep){
    for (interaction_a_i in l_interaction_a){
    
      print(interaction_a_i)
      
      a_i <- interaction_a_i
      
      # Calculation of the theorical response
      res_CA_theorical_design_i <- CA_complete2(
        C_mat, 
        Max, Slopes, Ec50s, 
        interact="SA", 
        a=a_i
      )
    
      # We add the corresponding response to our design
      df_dose_rep_i <- df_design%>%
        mutate(rep_Y=res_CA_theorical_design_i)
    
      df_dose_rep_i <- df_dose_rep_i[,-c(1, 4)]
      
      for(k in 1:Nb_pop){
        
        set.seed(121212+k)
        ID_pop <- k
        # Population simulation 
        df_sim_data_k <- data.frame(
          Y=c(),
          EPX=c(),
          IMD=c()
          )
        
        for(i in 1:length(df_dose_rep_i$EPX)){
          
          Y_th <- df_dose_rep_i$rep_Y[i]
          Y_sim <- rnorm(Nb_rep_j, Y_th, IV*Y_th) # <1>
          
          EPX <- rep(df_dose_rep_i$EPX[i], Nb_rep_j)
          IMD <- rep(df_dose_rep_i$IMD[i], Nb_rep_j)
          
          df_sim_data_j <- data.frame(
            Y_th=rep(Y_th, Nb_rep_j),
            Y_sim=Y_sim,
            EPX=EPX,
            IMD=IMD
            )
          df_sim_data_k <- rbind(df_sim_data_k, df_sim_data_j)
        }
        # Fit of the model 
        res_CA_SA_fit_k<-CA_complete2_fit_speed(
          C_mat=cbind(                      
            df_sim_data_k$EPX,                
            df_sim_data_k$IMD                 
            ),                              
          Response=df_sim_data_k$Y_sim,       
          interact="SA",                      
          param=param                         
          )
        res_a_k <- res_CA_SA_fit_k$a
      
        res_k <- data.frame(
          Simulated_interaction = a_i,
          Estimated_interaction = res_a_k,
          ID_pop = ID_pop,
          Nb_rep = Nb_rep_j
          )
        res <- rbind(res, res_k)
      }
      
      
      print("Calculations done for given interaction")
      
    }
    print("Calculations done for given Nb_rep")
  }
  
  return(res)
}

```

```{r defparampower}
#| code-show: show
Nb_rep <- c(4)
tmp <- c(10, 7, 5, 2, 1)
l_interaction_a <- c(tmp, -rev(tmp))
Nb_pop <- 1000
df_boot_res <- f_power_design(Nb_rep, l_interaction_a, Nb_pop, param)
save(df_boot_res,file = here::here("mod/MIX/Res_boot_design_new.RData"))
#load(file = here::here("mod/MIX/Res_boot_design_new.RData"))
```

```{r respower}
df_boot_res_print <- df_boot_res |> mutate(
  Per_error = round((Estimated_interaction - Simulated_interaction) / Simulated_interaction*100, 5),
  Estimated_interaction = round(Estimated_interaction, 5),
  Error = Estimated_interaction - Simulated_interaction
)
df_boot_res_line <- data.frame(Simulated_interaction = l_interaction_a,
                              Line = l_interaction_a)
# regarder erreur sur le signe
```

```{r fpdirection}
library(bayestestR)

f_pdir <- function(df){
  Nb_rep_unique = unique(df$Nb_rep)
  Simulated_interaction_unique = unique(df$Simulated_interaction)
  
  res <- data.frame(
    Nb_rep = c(),
    Simulated_interaction = c(),
    P_direction = c())
  
  for(Nb_rep_i in Nb_rep_unique){
    for(Simulated_interaction_i in Simulated_interaction_unique){
      
      p_dir <- p_direction(subset(df, Nb_rep == Nb_rep_i & Simulated_interaction == Simulated_interaction_i)$Estimated_interaction)
      
      res_i <- data.frame(
    Nb_rep = Nb_rep_i,
    Simulated_interaction = Simulated_interaction_i,
    P_direction = p_dir[2])
      
      res <- rbind(res, res_i)
    }
  }
  return(res)
}

df_boot_res_line <- df_boot_res_line |> 
  left_join(f_pdir(df_boot_res_print), by = join_by(Simulated_interaction))

```

Thanks to this algorithm, we can estimate the density of error of estimation and the probability of direction of the model for each interaction level. 

```{r, warning=F, message=F}
#| fig-cap: Density of errors of estimation and probability of direction. 
#| label: fig-pererrorpdir
#| fig-width: 12
#| fig-height: 8
alpha_dens <- 0.5
p <- ggplot(
  data = df_boot_res_print, 
  aes(x = Estimated_interaction)
  )+
  stat_halfeye(
    adjust=0.5,
    alpha=alpha_dens,
    fill = Nord_polar[1]
    )+
  geom_vline(
    data = df_boot_res_line,
    aes(xintercept = Line),
    color = Nord_frost[2],
    size = 1.2
  )+
  geom_vline(
    xintercept = 0,
    color = Nord_frost[4],
    size = 1.2
  )+
  geom_text(
    data = df_boot_res_line,
    aes(
      x = Simulated_interaction-0.25,
      y = 0.8,
      label = paste("Pdirection = ", pd)
      )
  )+
  facet_grid(
    rows = vars(Simulated_interaction),
    cols = vars(Nb_rep),
    scales="free"
    )+
  # facet_wrap(
  #   ~ Nb_rep+Simulated_interaction,
  #   scales = "free"
  #   )+
  #xlim(xmin=-50, xmax=50)+
  labs(
    x = "Estimated interaction",
    y = "Density"
  )+
  #theme_minimal()+
  theme(
    strip.background = element_rect(fill=Nord_polar[1]),
    strip.text = element_text(color="white", size = 14)
  )
p
```
@fig-pererrorpdir shows that at least when the interaction is above 1, there is a very low probability of being wrong about the direction of the interaction with our experimental design. 

```{r, warning=F, message=F}
#| fig-cap: Density of percentage of estimation errors
#| label: fig-pererror
#| fig-width: 12
#| fig-height: 8

alpha_dens <- 0.5
p <- ggplot(
  data = df_boot_res_print, 
  aes(
    x = Per_error
    )
  )+
  stat_halfeye(
    adjust=0.5,
    alpha=alpha_dens,
    fill = Nord_polar[1]
    )+
  facet_grid(
    rows = vars(Simulated_interaction),
    cols = vars(Nb_rep),
    scales="free"
    )+
  xlim(xmin=-50, xmax=50)+
  labs(
    x = "Percentage of error compared to the simulated value",
    y = "Density"
  )+
  #theme_minimal()+
  theme(
    strip.background = element_rect(fill=Nord_polar[1]),
    strip.text = element_text(color="white", size = 14)
  )
p
```

```{r, message=F, warning=F}

df_boot_res_print_summary <- df_boot_res_print %>%
  group_by(Simulated_interaction) %>%
  summarise(
    Per_error_above_10 = signif(mean(abs(Per_error) > 10) * 100, 3),
    Per_error_above_25 = signif(mean(abs(Per_error) > 25) * 100, 3),
    Per_error_above_50 = signif(mean(abs(Per_error) > 50) * 100, 3),
    .groups = "drop"
  )

df_boot_res_print_summary |> datatable(
  options = list(
    dom = 't',
    autoWidth = TRUE,
    columnDefs = list(
      list(className = 'dt-left', targets = "_all")
      )
    ), 
  class="hover"
  ) 

```

With our design, we can quantify absolute interaction value above 5 reasonnably well.

<button class="accordion-button" type="button" data-bs-toggle="collapse" data-bs-target="#collapseOne">

<b> Session Information </b>

</button>

:::: {#collapseOne .accordion-collapse .collapse}
<div>

```{r}
sessionInfo()
```

</div>
::::
