```{r, include=F}
library(tidyverse); library(here); library(ggthemes)
library(viridis); library(tidybayes); library(wesanderson)
library(ggdist); library(patchwork); library(extrafont)
library(scales); library(ggdist); library(ggsci)
library(parallel); library(deSolve); library(tmvtnorm)
library(fdrtool); library(readxl); library(here); library(car)
library(RColorBrewer); library(devtools) ; library(drc)
library(knitr); library(Hmisc); library(nlstools); library(lsmeans)
library(ggpubr);library(brglm2);library(marginaleffects)
library(performance);library(rethinking); library(nord); library(ggiraph)

Nord_frost <- nord(palette = "frost")
Nord_aurora <- nord(palette = "aurora")
Nord_polar <- nord(palette = "polarnight")
Nord_snow <- nord(palette = "snowstorm")

pal_col <- c(Nord_aurora[1], Nord_frost[4])
col_EPX <- Nord_frost[2]
col_IMD <- Nord_frost[4]
shape_IMD <- 16
shape_EPX <- 15
col_molec <- c(col_EPX, col_IMD)
sizetitle <- 12

shape_molec <- c(shape_EPX, shape_IMD)

set.seed(121212)
col_red <- "#f42404"

pal_lot <- c(Nord_frost[4], Nord_aurora[3], Nord_aurora[2], Nord_aurora[4]) # blue, yellow, orange

```

# Results of the mixture experiments : Results of the first round of the mixture experiment

## Data importation

Importation of the mixture experiement data.

```{r datamix}
# Data mix

df_repro_mix <- read_excel(here::here("data/Data_Mix.xlsx"), sheet="ReproAutumn2024") |> 
  mutate(
    w=w_tot/Nb_ind,
    L=w^(1/3),
    Condition = paste(Ratio, Line, sep = ""),
    Nb_rep = as.factor(Nb_rep),
    Dose_IMD = Dose_IMD / 2
    )

df_repro_mix_mean <- df_repro_mix |> 
  aggregate(Nb_cocoons ~ Condition+Dose_EPX+Dose_IMD+Ratio, mean)
```

## Initial state

We can first take a look at the initial weights of individuals (@fig-init).

```{r D0, warning=F, message=F}
#| fig-cap: Initial weights of earthworms according to batches. 
#| label: fig-init
#| fig-width: 8
#| fig-height: 4

# Weights at t=0
p <- ggplot(
  data=subset(df_repro_mix,t==0), 
  aes(
    x=Condition, 
    y=w
    )
  )+

  geom_boxplot(
    alpha=0.2,
    color = Nord_polar[1]
    )+
  geom_dotplot(
    aes(
    color=Lot, 
    fill=Lot
    ),
    binaxis='y', 
    stackdir='center', 
    dotsize=0.5, 
    alpha=0.7
    )+
  
  scale_color_manual(values=pal_lot)+
  scale_fill_manual(values=pal_lot)+

  labs(x="Condition", y="Weight (mg)")+
  

  theme_classic(12)+
  theme(
    legend.position = "none", 
    legend.title=element_text(size=sizetitle-2,face="bold"),
    legend.text = element_text(size=sizetitle-2,face="plain"),
    
    title=element_text(size=sizetitle, face="bold"), 
    
    axis.title.x = element_blank(),
    axis.title.y = element_text(size=sizetitle,face="plain"),
    
    #axis.text.x = element_blank(),
    axis.line.x=element_blank(),
    axis.ticks.x=element_blank(),
    
    
    strip.background = element_rect(
      color="black", 
      fill="grey95", 
      size=0, 
      linetype="solid"
      )
    )
p
```

```{r, include=F}
ggsave(
  filename="Mix_initial_weights.png",
  plot=p, 
  width=8, 
  height = 4, 
  path=here::here("fig/Mixture")
  )
ggsave(
  filename="Mix_initial_weights.svg",
  plot=p, 
  width=8, 
  height = 4, 
  path=here::here("fig/Mixture")
  )
```

## Growth of individuals

Mean growth curves of each cosm and per condition.

```{r, warning=F}
#| fig-cap: Mean growth curves of each cosme and per condition. 
#| label: fig-growthcurves
#| fig-width: 8
#| fig-height: 12

p <- ggplot(
  data = df_repro_mix, 
  aes(
    x = t, 
    y = w, 
    group = paste(Nb_rep,Lot), 
    color = Lot
    )
  )+
  geom_point()+
  geom_line()+
  facet_wrap(~Condition, ncol = 7)+
  scale_color_manual(values = pal_lot)+
  theme_bw()
p

```

```{r, include=F}
ggsave(
  filename="Mix_1_growth_curves.png", 
  plot=p, 
  width=8, height = 12, 
  path=here::here("fig/Mixture")
  )
ggsave(
  filename="Mix_1_growth_curves.svg", 
  plot=p, 
  width=8, height = 12, 
  path=here::here("fig/Mixture")
  )
```

Calculation of growth rates :

```{r}
f_growth_rate <- function(data){
  a_init <- 0.1
  a_i <- c()
  
  # Calculation of the growth rate for each individual
  for(i in subset(data, t==0)$ID_cosm){
    data_i <- data.frame(L = subset(data, ID_cosm==i)$L,
                         t = subset(data, ID_cosm==i)$t)
    L0_i <- subset(data, ID_cosm==i & t==0)$L
    if(length(na.omit(data_i$L))==2){ # If only 2 data points
      a.Est <- (subset(data_i, !t==0)$L-subset(data_i, t==0)$L)/
        subset(data_i, !t==0)$t
    }else{
      a.Est <- NA
    }
    a_i <- rbind(a_i, a.Est)
  }
  return(a_i)
}

a_i <- f_growth_rate(df_repro_mix)

df_repro_mix_grate <- cbind(subset(df_repro_mix, t == 0), a_i)
df_repro_mix_grate_mean <- df_repro_mix_grate |> 
  aggregate(a_i ~ Condition + Dose_EPX + Dose_IMD+Ratio, FUN = "mean")

```

```{r, warning=F, message=F}
#| fig-cap: Mean growth rates of each cosm and per condition. 
#| label: fig-growthrates
#| fig-width: 8
#| fig-height: 10

p <- ggplot(
  data = df_repro_mix_grate, 
  aes(
    x = Lot, 
    y = a_i, 
    #group = Nb_rep, 
    color = Lot
  )
)+
  geom_boxplot()+
  geom_dotplot(
    binaxis='y', 
    stackdir='center', 
    dotsize=0.7, 
    alpha=0.7
  )+
  facet_wrap(
    ~Condition, 
    ncol = 7, 
    #scales = "free"
    )+
  scale_color_manual(values = pal_lot)+
  theme_bw()
p
```

```{r, include=F}
ggsave(
  filename="Mix_1_growth_rates.png", 
  plot=p, 
  width=8, height = 10, 
  path=here::here("fig/Mixture")
  )
ggsave(
  filename="Mix_1_growth_rates.svg", 
  plot=p, 
  width=8, height = 10, 
  path=here::here("fig/Mixture")
  )
```

## First look at cocoons production

```{r, warning=F, message=F}
#| fig-cap: Cocoons produced by each cosme and per condition. 
#| label: fig-cocbox
#| fig-width: 8
#| fig-height: 4

p <- ggplot(
  data = df_repro_mix, 
  aes(
    x = Condition, 
    y = Nb_cocoons, 
    )
  )+
  geom_boxplot()+
  geom_dotplot(
    binaxis='y', 
    stackdir='center', 
    dotsize=0.7, 
    alpha=0.7,
    aes(color = Lot, fill = Lot)
  )+
  #facet_wrap(~Condition, ncol = 7)+
  scale_color_manual(values = pal_lot)+
  scale_fill_manual(values = pal_lot)+
  theme_bw()
p

```

```{r, include=F}
ggsave(
  filename="Mix_1_cocoons_boxplot.png", 
  plot=p, 
  width=12, height = 8, 
  path=here::here("fig/Mixture")
  )
ggsave(
  filename="Mix_1_cocoons_boxplot.svg", 
  plot=p, 
  width=12, height = 8, 
  path=here::here("fig/Mixture")
  )
```

The results for imidacloprid only do not seem to correspond to the expected effect. We will compare the ratio I and E to the previously obtained dose response curves.

## Retrieving of the previously obtained dose-response curves

Importation of the EC50 experiment data.

```{r dataEC50}
# Data EC50

df_repro_tot <- read_excel(here::here("data/Data_EC50.xlsx"), sheet="Repro") |> 
  mutate(Dose = as.numeric(Dose)) |> 
  mutate(Dose_f = as.factor(round(Dose, 4))) |> 
  mutate(w=w_tot/Nb_ind) |> 
  mutate(L=w^(1/3))

# Data for EPX
df_repro_EPX <- subset(df_repro_tot, Molec %in% c("Ctrl_2", "EPX")) |> 
  mutate(Molecule = "EPX")
# We only keep earthworms still alive at then end of the experiment
ID_alive_EPX <- subset(df_repro_EPX, t==28 & (!Status=="D"))$ID_cosm
df_repro_EPX_alive <- subset(df_repro_EPX, ID_cosm %in% ID_alive_EPX)

# Data for IMD
df_repro_IMD <- subset(df_repro_tot, Molec %in% c("Ctrl_1", "Ctrl_2", "IMD")) |> 
  mutate(Molecule = "IMD")
# We only keep earthworms still alive at then end of the experiment
ID_alive_IMD <- subset(df_repro_IMD, t==28 & (!Status=="D"))$ID_cosm
df_repro_IMD_alive <- subset(df_repro_IMD, ID_cosm %in% ID_alive_IMD)

df_repro <- rbind(df_repro_EPX, df_repro_IMD)
df_repro_alive <- rbind(df_repro_EPX_alive, df_repro_IMD_alive)
df_repro_alive_mean <- df_repro_alive |> 
  aggregate(Nb_cocoons~Dose+Molecule, mean)

```

```{r drc, warning=F, message=F}

Dose_x <- expand.grid(
  exp(
    seq(
      log(0.000001),log(5000), 
      by=(log(5000)-log(0.000001))/100
    )
  )
)

# Common Ymax and slope
drc.4<- drm(
  Nb_cocoons~Dose, Molecule, 
  data = df_repro_alive,
  type="Poisson",
  fct=LL.4(
    names = c("slope", "Ymin", "Ymax", "EC50"),
    fixed = c(NA, 0, NA, NA)
  ), 
  # Reproduction is expected to reach 0 for large concentrations
  pmodels=data.frame(1, 1, Molecule)
)
# summary(drc.4)

CI.4 <- data.frame(
  Dose = c(Dose_x$Var1, Dose_x$Var1),
  Molecule = c(rep("EPX", length(Dose_x$Var1)), rep("IMD", length(Dose_x$Var1)))
)

pm.4 <- predict(drc.4, newdata=CI.4, interval="confidence")
CI.4$p <- pm.4[,1]
CI.4$pmin <- pm.4[,2]
CI.4$pmax <- pm.4[,3]

Hill.4 <- function(Dose, Molecule){
  
  i <- 0
  if(Molecule == "IMD"){i <- 1}
  
  Y_min <- 0
  slope <- coef(drc.4)[1]
  Y_max <- coef(drc.4)[2]
  EC50 <- coef(drc.4)[3+i]
  
  return(Y_min+(Y_max-Y_min)/(1+exp(slope*(log(Dose)-log(EC50)))))
}
EPX_EC50 <- coef(drc.4)[4]
IMD_EC50 <- coef(drc.4)[4]
```

```{r}
x <- seq(0.000001, 5000, 0.01)

df_repro_mix_IMD <- subset(df_repro_mix, Ratio %in% c("I", "N"))
df_repro_mix_EPX <- subset(df_repro_mix, Ratio  %in% c("E", "N"))
df_repro_mix_IMD_mean <- df_repro_mix_IMD |> 
  aggregate(Nb_cocoons ~ Condition+Dose_IMD, mean)
df_repro_mix_EPX_mean <- df_repro_mix_EPX |> 
  aggregate(Nb_cocoons ~ Condition+Dose_EPX, mean)
```

```{r, warning=F}
#| fig-cap: Comparaison of the results obtained in the mixture experiment (red) with the results of the EC50 experiments (blues).  The line represents the dose-response curve obtained with the EC50 experiments (with common $Y_{max}$ and slope for the 2 active substances). Crosses correspond to the number of cocoons produced by one cosm and the bold points represents the mean per dose.
#| label: fig-drcIMDEPX
#| fig-width: 6
#| fig-height: 6

line_width <- 1.2

p_I <- ggplot()+
  geom_ribbon(
    data = subset(CI.4, Molecule == "IMD"), 
    aes(
      x = Dose, 
      y = p, 
      ymin = pmin, 
      ymax = pmax
      ), 
    alpha=0.2,
    fill = col_IMD,
    #color = col_IMD
    )+
  geom_line(
    aes(
      x=x, 
      y=Hill.4(Dose=x, Molecule="IMD")
    ), 
    color=col_IMD, 
    linewidth=line_width
  )+
  geom_point(
    data = subset(df_repro_mix_IMD, Lot == "T"), 
    aes(x = Dose_IMD, y = Nb_cocoons),
    color = col_red,
    alpha = 0.6,
    shape = 4
  )+
  geom_point(
    data = df_repro_IMD_alive,
    aes(x = Dose, y = Nb_cocoons),
    color = col_IMD,
    alpha = 0.5,
    shape = 4
  )+
  geom_point(
    data = df_repro_mix_IMD_mean, 
    aes(x = Dose_IMD, y = Nb_cocoons),
    color = col_red,
    size = 3
  )+
  geom_point(
    data = subset(df_repro_alive_mean, Molecule == "IMD"),
    aes(x = Dose, y = Nb_cocoons),
    color = col_IMD,
    size = 3
  )+
  annotate(
    geom = "text",
    x = 1500,
    y = 30,
    label = "I",
    fontface = "bold"
  )+
  
  scale_x_log10()+
  labs(
    x = "Concentration en IMD (mg/kg)",
    y = "Nombre de cocons produits"
  )+
  theme_bw()

p_E <- ggplot()+
  geom_ribbon(
    data = subset(CI.4, Molecule == "EPX"), 
    aes(
      x = Dose, 
      y = p, 
      ymin = pmin, 
      ymax = pmax
    ), 
    alpha=0.2,
    fill = col_EPX,
    #color = col_IMD
  )+
  geom_line(
    aes(
      x=x, 
      y=Hill.4(Dose=x, Molecule="EPX")
    ), 
    color=col_EPX, 
    linewidth=line_width
  )+
  geom_point(
    data = df_repro_mix_EPX, 
    aes(x = Dose_EPX, y = Nb_cocoons),
    color = col_red,
    alpha = 0.6,
    shape = 4
  )+
  geom_point(
    data = df_repro_EPX_alive,
    aes(x = Dose, y = Nb_cocoons),
    color = col_EPX,
    alpha = 0.5,
    shape = 4
  )+
  geom_point(
    data = subset(df_repro_alive_mean, Molecule == "EPX"),
    aes(x = Dose, y = Nb_cocoons),
    color = col_EPX,
    size = 3
  )+
  geom_point(
    data = df_repro_mix_EPX_mean, 
    aes(x = Dose_EPX, y = Nb_cocoons),
    color = col_red,
    size = 3
  )+
  annotate(
    geom = "text",
    x = 1500,
    y = 30,
    label = "E",
    fontface = "bold"
  )+
  
  scale_x_log10()+
  labs(
    x = "Concentration en EPX (mg/kg)",
    y = "Nombre de cocons produits"
  )+
  theme_bw()

p <- p_I / p_E
p
```

```{r, include=F}
ggsave(
  filename="Mix_1_cocoons_compEC50.png", 
  plot=p, 
  width=6, height = 6, 
  path=here::here("fig/Mixture")
  )
ggsave(
  filename="Mix_1_cocoons_compEC50.svg", 
  plot=p, 
  width=6, height = 6, 
  path=here::here("fig/Mixture")
  )
```

## Comparison of the other ratio with the EPX dose-response curve

```{r, warning=F}
#| fig-cap: Comparaison of the results obtained in the mixture experiment (red) with the results of the EC50 experiment for EPX (blues).  The line represents the dose-response curve obtained with the EC50 experiment (with common $Y_{max}$ and slope for the 2 active substances). Crosses correspond to the number of cocoons produced by one cosm and the bold points represents the mean per dose. The results of the mixture experiment are plotted a if only EPX was added to the soil. 
#| label: fig-drcEPXratio
#| fig-width: 10
#| fig-height: 8

p_F <- ggplot()+
  geom_ribbon(
    data = subset(CI.4, Molecule == "EPX"), 
    aes(
      x = Dose, 
      y = p, 
      ymin = pmin, 
      ymax = pmax
    ), 
    alpha=0.2,
    fill = col_EPX,
    #color = col_IMD
  )+
  geom_line(
    aes(
      x=x, 
      y=Hill.4(Dose=x, Molecule="EPX")
    ), 
    color=col_EPX, 
    linewidth=line_width
  )+
  geom_point(
    data = subset(df_repro_mix, Ratio %in% c("N", "F")), 
    aes(
      x = Dose_EPX, 
      y = Nb_cocoons
      ),
    alpha = 0.6,
    shape = 4,
    color = col_red
  )+
  geom_point(
    data = df_repro_EPX_alive,
    aes(x = Dose, y = Nb_cocoons),
    color = col_EPX,
    alpha = 0.5,
    shape = 4
  )+
  geom_point(
    data = subset(df_repro_alive_mean, Molecule == "EPX"),
    aes(x = Dose, y = Nb_cocoons),
    color = col_EPX,
    size = 3
  )+
  geom_point(
    data = subset(df_repro_mix_mean, Ratio %in% c("N", "F")),
    aes(
      x = Dose_EPX,
      y = Nb_cocoons
      ),
    size = 3,
    color = col_red
  )+
  annotate(
    geom = "text",
    x = 1500,
    y = 30,
    label = "F",
    fontface = "bold"
  )+
  scale_x_log10()+
  labs(
    x = "Concentration en EPX (mg/kg)",
    y = "Nombre de cocons produits"
  )+
  theme_bw()

p_G <- ggplot()+
  geom_ribbon(
    data = subset(CI.4, Molecule == "EPX"), 
    aes(
      x = Dose, 
      y = p, 
      ymin = pmin, 
      ymax = pmax
    ), 
    alpha=0.2,
    fill = col_EPX,
  )+
  geom_line(
    aes(
      x=x, 
      y=Hill.4(Dose=x, Molecule="EPX")
    ), 
    color=col_EPX, 
    linewidth=line_width
  )+
  geom_point(
    data = subset(df_repro_mix, Ratio %in% c("N", "G")), 
    aes(
      x = Dose_EPX, 
      y = Nb_cocoons
      ),
    alpha = 0.6,
    shape = 4,
    color = col_red
  )+
  geom_point(
    data = df_repro_EPX_alive,
    aes(x = Dose, y = Nb_cocoons),
    color = col_EPX,
    alpha = 0.5,
    shape = 4
  )+
  geom_point(
    data = subset(df_repro_alive_mean, Molecule == "EPX"),
    aes(x = Dose, y = Nb_cocoons),
    color = col_EPX,
    size = 3
  )+
  geom_point(
    data = subset(df_repro_mix_mean, Ratio %in% c("N", "G")),
    aes(
      x = Dose_EPX,
      y = Nb_cocoons
      ),
    size = 3,
    color = col_red
  )+
  annotate(
    geom = "text",
    x = 1500,
    y = 30,
    label = "G",
    fontface = "bold"
  )+
  #facet_wrap(~Ratio, ncol = 2)+
  scale_color_manual(values = c(Nord_frost[2],Nord_frost[2]))+
  scale_x_log10()+
  labs(
    x = "Concentration en EPX (mg/kg)",
    y = "Nombre de cocons produits"
  )+
  theme_bw()

p_H <- ggplot()+
  geom_ribbon(
    data = subset(CI.4, Molecule == "EPX"), 
    aes(
      x = Dose, 
      y = p, 
      ymin = pmin, 
      ymax = pmax
    ), 
    alpha=0.2,
    fill = col_EPX,
    #color = col_IMD
  )+
  geom_line(
    aes(
      x=x, 
      y=Hill.4(Dose=x, Molecule="EPX")
    ), 
    color=col_EPX, 
    linewidth=line_width
  )+
  geom_point(
    data = subset(df_repro_mix, Ratio %in% c("N", "H")), 
    aes(
      x = Dose_EPX, 
      y = Nb_cocoons
      ),
    alpha = 0.6,
    shape = 4,
    color = col_red
  )+
  geom_point(
    data = df_repro_EPX_alive,
    aes(x = Dose, y = Nb_cocoons),
    color = col_EPX,
    alpha = 0.5,
    shape = 4
  )+
  geom_point(
    data = subset(df_repro_alive_mean, Molecule == "EPX"),
    aes(x = Dose, y = Nb_cocoons),
    color = col_EPX,
    size = 3
  )+
  geom_point(
    data = subset(df_repro_mix_mean, Ratio %in% c("N", "H")),
    aes(
      x = Dose_EPX,
      y = Nb_cocoons
      ),
    size = 3,
    color = col_red
  )+
  annotate(
    geom = "text",
    x = 1500,
    y = 30,
    label = "H",
    fontface = "bold"
  )+
  #facet_wrap(~Ratio, ncol = 2)+
  scale_color_manual(values = c(Nord_frost[2],Nord_frost[2]))+
  scale_x_log10()+
  labs(
    x = "Concentration en EPX (mg/kg)",
    y = "Nombre de cocons produits"
  )+
  theme_bw()

p <- p_E + p_F + p_G + p_H + plot_layout(ncol=2)
p

```

```{r, include=F}
ggsave(
  filename="Mix_1_cocoons_compEC50_EPX.png", 
  plot=p, 
  width=10, height = 8, 
  path=here::here("fig/Mixture")
  )
ggsave(
  filename="Mix_1_cocoons_compEC50_EPX.svg", 
  plot=p, 
  width=10, height = 8, 
  path=here::here("fig/Mixture")
  )
```

Everything happened a if no IMD was added to the soil.

## Comparison of growth rates with data from dose-response curves

```{r}
f_growth_rate <- function(data){
  a_init <- 0.1
  a_i <- c()
  
  # Calculation of the growth rate for each individual
  for(i in subset(data, t==0)$ID_cosm){
    data_i <- data.frame(L = subset(data, ID_cosm==i)$L,
                         t = subset(data, ID_cosm==i)$t)
    L0_i <- subset(data, ID_cosm==i & t==0)$L
    if(length(na.omit(data_i$L))==2){ # If only 2 data points
      a.Est <- (subset(data_i, !t==0)$L-subset(data_i, t==0)$L)/
        subset(data_i, !t==0)$t
    }else{
      a.Est <- NA
    }
    a_i <- rbind(a_i, a.Est)
  }
  return(a_i)
}

a_i <- f_growth_rate(df_repro)

df_repro_grate <- cbind(subset(df_repro, t == 0), a_i)
df_repro_grate_mean <- df_repro_grate |> 
  aggregate(a_i ~ Molecule + Dose, FUN = "mean")
```

```{r, warning=F, message=F}
#| fig-cap: Mean growth rates of each cosm and per condition. 
#| label: fig-growthratescomp
#| fig-width: 6
#| fig-height: 8


p_IMD <- ggplot()+
  # Dose-response curves expriements
  geom_point(
    data = subset(df_repro_grate, Molecule == "IMD"), 
    aes(
      x = Dose, 
      y = a_i
    ),
    alpha=0.5,
    color = col_IMD
  )+
  geom_point(
    data = subset(df_repro_grate_mean, Molecule == "IMD"), 
    aes(
      x = Dose, 
      y = a_i
    ),
    alpha=1,
    size = 3,
    color = col_IMD
  )+
  # Mixture experiment
  geom_point(
    data = subset(df_repro_mix_grate, Dose_EPX ==0), # IMD data (Ratio I)
    aes(
      x = Dose_IMD, 
      y = a_i
    ),
    alpha=0.5,
    color = col_red
  )+
  geom_point(
    data = subset(df_repro_mix_grate_mean, Dose_EPX ==0), 
    aes(
      x = Dose_IMD, 
      y = a_i
    ),
    alpha=1,
    size = 3,
    color = col_red
  )+
  labs(
    x = "Dose (mg/kg)",
    y = "Growth rate",
    title = "Effect on adult growth for IMD"
  )+
  scale_x_log10()+
  theme_bw(12)

p_EPX <- ggplot()+
  # Dose-response curves experiments
  geom_point(
    data = subset(df_repro_grate, Molecule == "EPX"), 
    aes(
      x = Dose, 
      y = a_i
    ),
    alpha=0.5,
    color = col_EPX
  )+
  geom_point(
    data = subset(df_repro_grate_mean, Molecule == "EPX"), 
    aes(
      x = Dose, 
      y = a_i
    ),
    alpha=1,
    size = 3,
    color = col_EPX
  )+
  # Mixture experiement
  geom_point(
    data = subset(df_repro_mix_grate, Dose_IMD ==0), # IMD data (Ratio I)
    aes(
      x = Dose_EPX, 
      y = a_i
    ),
    alpha=0.5,
    color = col_red
  )+
  geom_point(
    data = subset(df_repro_mix_grate_mean, Dose_IMD ==0), 
    aes(
      x = Dose_EPX, 
      y = a_i
    ),
    alpha=1,
    size = 3,
    color = col_red
  )+
  scale_x_log10()+
  labs(
    x = "Dose (mg/kg)",
    y = "Growth rate",
    title = "Effect on adult growth for EPX"
  )+
  theme_bw(12)

p <- p_IMD/p_EPX
p_IMD/p_EPX
```

```{r, include=F}
ggsave(
  filename="Mix_1_growth_compEC50.png", 
  plot=p, 
  width=8, height = 6, 
  path=here::here("fig/Mixture")
  )
ggsave(
  filename="Mix_1_growth_compEC50.svg", 
  plot=p, 
  width=8, height = 6, 
  path=here::here("fig/Mixture")
  )
```

## Design comparisons

```{r}
#| fig-cap: Comparison of the theorical design and the actual design. 
#| label: fig-compdesign
#| fig-width: 5
#| fig-height: 5

# Ratios considered
ratios = c(0, 1/4, 1/2, 3/4, 1)

EPX_x = NULL
IMD_x = NULL

ratio_EC50 <- IMD_EC50/EPX_EC50

for(i in ratios){
  EPX_x=rbind(EPX_x,EPX_EC50*i)
  IMD_x=rbind(IMD_x,IMD_EC50*(1-i))
}

factor_design <- 10^(1/4)

EPX_x <- c(
  EPX_x,
  EPX_x/(factor_design^9),
  EPX_x/(factor_design^5), 
  EPX_x/(factor_design^2), 
  EPX_x/factor_design,
  factor_design*EPX_x, 
  factor_design^2*EPX_x
  )
IMD_x <- c(
  IMD_x,
  IMD_x/(factor_design^9),
  IMD_x/(factor_design^5), 
  IMD_x/(factor_design^2), 
  IMD_x/factor_design,
  factor_design*IMD_x, 
  factor_design^2*IMD_x
  )


df_design <- data.frame(EPX=EPX_x,
                        IMD=IMD_x,
                        Ratio=EPX_x/IMD_x*IMD_EC50/EPX_EC50)

width_iso <- 1.1
size_points <- 3
alpha_true = 0.5

df_design_plot <- df_design |> 
  mutate(
    label=paste(
      "[IMD] = ", 
      signif(IMD, 3), 
      "mg/kg\n [EPX] = ", 
      signif(EPX,3), "mg/kg"
      )
    )

plot_design <- ggplot()+
  xlim(min(EPX_x), max(EPX_x))+
  ylim(min(IMD_x), max(IMD_x))+
  # Ligne des ratios
  geom_abline(
    intercept=0, 
    slope=ratio_EC50/3, 
    color=pal_col[2],
    alpha=alpha_true
    )+
  geom_abline(
    intercept=0, 
    slope=ratio_EC50*3, 
    color=pal_col[2],
    alpha=alpha_true
    )+
  geom_abline(
    intercept=0, 
    slope=ratio_EC50, 
    color=pal_col[2],
    alpha=alpha_true
    )+
  geom_abline(
    intercept=0, 
    slope=0, 
    color=pal_col[2],
    alpha=alpha_true
    )+
  geom_vline(
    xintercept = 0, 
    color=pal_col[2],
    alpha=alpha_true
    )+
  
  # Effect isoboles
  geom_abline(
    intercept=IMD_EC50*factor_design^2, 
    slope=-ratio_EC50, 
    color=pal_col[1], 
    lwd=width_iso,
    alpha=alpha_true
    )+
  geom_abline(
    intercept=IMD_EC50*factor_design, 
    slope=-ratio_EC50, 
    color=pal_col[1], 
    lwd=width_iso,
    alpha=alpha_true
    )+
  geom_abline(
    intercept=IMD_EC50, 
    slope=-ratio_EC50, 
    color=pal_col[1], 
    lwd=width_iso,
    alpha=alpha_true
    )+
  geom_abline(
    intercept=IMD_EC50/factor_design, 
    slope=-ratio_EC50, 
    color=pal_col[1], 
    lwd=width_iso,
    alpha=alpha_true
    )+
  geom_abline(
    intercept=IMD_EC50/(factor_design^2), 
    slope=-ratio_EC50, 
    color=pal_col[1], 
    lwd=width_iso,
    alpha=alpha_true
    )+
  geom_abline(
    intercept=IMD_EC50/(factor_design^5), 
    slope=-ratio_EC50, 
    color=pal_col[1], 
    lwd=width_iso,
    alpha=alpha_true
    )+
  geom_abline(
    intercept=IMD_EC50/(factor_design^9), 
    slope=-ratio_EC50, 
    color=pal_col[1], 
    lwd=width_iso,
    alpha=alpha_true
    )+
  
  # Effect isoboles
  geom_abline(
    intercept=IMD_EC50*factor_design^2/2, 
    slope=-ratio_EC50/2, 
    color=pal_col[1], 
    lwd=width_iso
    )+
  geom_abline(
    intercept=IMD_EC50*factor_design/2, 
    slope=-ratio_EC50/2, 
    color=pal_col[1], 
    lwd=width_iso
    )+
  geom_abline(
    intercept=IMD_EC50/2, 
    slope=-ratio_EC50/2, 
    color=pal_col[1], 
    lwd=width_iso
    )+
  geom_abline(
    intercept=IMD_EC50/factor_design/2, 
    slope=-ratio_EC50/2, 
    color=pal_col[1], 
    lwd=width_iso
    )+
  geom_abline(
    intercept=IMD_EC50/(factor_design^2)/2, 
    slope=-ratio_EC50/2, 
    color=pal_col[1], 
    lwd=width_iso
    )+
  geom_abline(
    intercept=IMD_EC50/(factor_design^5)/2, 
    slope=-ratio_EC50/2, 
    color=pal_col[1], 
    lwd=width_iso
    )+
  geom_abline(
    intercept=IMD_EC50/(factor_design^9)/2, 
    slope=-ratio_EC50/2, 
    color=pal_col[1], 
    lwd=width_iso
    )+
  
  # Ratios annotations
  annotate(
    geom="text", 
    x=30, 
    y=max(IMD_x), 
    label="0:1", 
    color=pal_col[2], 
    fontface="bold"
    )+
  annotate(
    geom="text", 
    x=200, 
    y=max(IMD_x), 
    label="3:1", 
    color=pal_col[2], 
    fontface="bold"
    )+
  annotate(
    geom="text", 
    x=max(EPX_x)-30, 
    y=max(IMD_x), 
    label="1:1", 
    color=pal_col[2], 
    fontface="bold"
    )+
  annotate(
    geom="text",
    x=max(EPX_x),
    y=0.8,
    label="1:3", 
    color=pal_col[2], 
    fontface="bold"
    )+
  annotate(
    geom="text", 
    x=max(EPX_x), 
    y=0.1, 
    label="1:0", 
    color=pal_col[2], 
    fontface="bold"
    )+
  
  # Design points
  geom_point_interactive(
    data=df_design_plot, 
    aes(
      x=EPX, 
      y=IMD,
      tooltip = label), 
    size=size_points, 
    color=Nord_polar[1],
    alpha=alpha_true
    )+
    # Design points
  geom_point_interactive(
    data=df_design_plot, 
    aes(
      x=EPX, 
      y=IMD/2,
      tooltip = label), 
    size=size_points, 
    color=Nord_polar[1]
    )+
  
  labs(
    x="Epoxiconazole (mg/kg)",
    y="Imidacloprid (mg/kg)"
    )+
  
  theme_minimal(12)



tooltip_css <- "
  border-radius: 12px;
  color: #333;
  background-color: white;
  padding: 10px;
  font-size: 14px;
  transition: all 0.5s ease-out;
"

hover_css <- "
  filter: brightness(75%);
  cursor: pointer;
  transition: all 0.5s ease-out;
  filter: brightness(1.15);
"

interactive_plot <- girafe(
  ggobj=plot_design,
  height_svg = 5,
  width_svg = 5
  ) |> 
  girafe_options(opts_sizing(rescale = FALSE))

# Add interactivity
interactive_plot <- interactive_plot %>%
  girafe_options(
    opts_hover(css = hover_css),
    opts_tooltip(css = tooltip_css),
    opts_hover_inv(css = "opacity:0.3; transition: all 0.2s ease-out;")
  )

interactive_plot

```

```{r, include=F}
ggsave(
  filename="Mix_1_design_comp.png", 
  plot=plot_design, 
  width=5, height = 5, 
  path=here::here("fig/Mixture")
  )
ggsave(
  filename="Mix_1_design_comp.svg", 
  plot=plot_design, 
  width=5, height = 5, 
  path=here::here("fig/Mixture")
  )
```

<button class="accordion-button" type="button" data-bs-toggle="collapse" data-bs-target="#collapseOne">

<b> Session Information </b>

</button>

:::: {#collapseOne .accordion-collapse .collapse}
<div>

```{r}
sessionInfo()
```

</div>
::::
