```{r lib, include=F}
library(here)
source(file = here::here("functions/fun.R"))

f_load_libraries_colors()

palette <- colorRampPalette(c("#5E81AC", "#88C0D0"))
col_mix <- Nord_polar[4]
pal_ratio <- c("#88C0D0", col_mix, col_mix, col_mix, "#5E81AC", col_mix)

pal_lot <- c(Nord_aurora[1], Nord_aurora[3], Nord_aurora[4], Nord_frost[4])

path_fig <- here::here("fig/Mixture/Autumn")
```

# Results of the mixture experiments : Results of the first round of the mixture experiment {#sec-MIXAutumn2024}

A first try of the MIX experiment was performed in three batches in the Autumn of 2024. However, the contamination in imidacloprid failed and everything happened as if only epoxiconazole was added to the soil. More details are provided in this section.

## Data importation

Importation of the mixture experiement data.

```{r datamix}
# Data mix
df_expB_autumn <- read_excel(here::here("data/Data_Mix.xlsx"), sheet = "ReproAutumn2024") |>
  mutate(
    w = w_tot / Nb_ind,
    L = w^(1 / 3),
    Condition = paste(Ratio, Line, sep = ""),
    Nb_rep = as.factor(Nb_rep),
    Dose_IMD = Dose_IMD / 2
  )

df_expB_autumn_mean <- df_expB_autumn |>
  aggregate(Nb_cocoons ~ Condition + Dose_EPX + Dose_IMD + Ratio, mean)
```

## Initial state

We can first take a look at the initial weights of individuals (@fig-initExpBAutumn).

```{r, warning=F, message=F}
#| fig-cap: Initial weights of earthworms according to batches.
#| label: fig-initExpBAutumn
#| fig-width: 8
#| fig-height: 4

# Weights at t=0
p <- ggplot(
  data = subset(df_expB_autumn, t == 0),
  aes(
    x = Condition,
    y = w
  )
) +
  geom_boxplot(
    alpha = 0.2,
    color = Nord_polar[1]
  ) +
  geom_dotplot(
    aes(
      color = Lot,
      fill = Lot
    ),
    binaxis = "y",
    stackdir = "center",
    dotsize = 0.5,
    alpha = 0.7
  ) +
  scale_color_manual(values = pal_lot) +
  scale_fill_manual(values = pal_lot) +
  labs(x = "Condition", y = "Weight (mg)") +
  theme_classic(12) +
  theme(
    legend.position = "top",
    legend.title = element_text(size = sizetitle - 2, face = "bold"),
    legend.text = element_text(size = sizetitle - 2, face = "plain"),
    title = element_text(size = sizetitle, face = "bold"),
    axis.title.x = element_blank(),
    axis.title.y = element_text(size = sizetitle, face = "plain"),

    # axis.text.x = element_blank(),
    axis.line.x = element_blank(),
    axis.ticks.x = element_blank(),
    strip.background = element_rect(
      color = "black",
      fill = "grey95",
      size = 0,
      linetype = "solid"
    )
  )
p
```

```{r saveinit, include=F}
ggsave(
  filename = "ExpB_initial_weights.png",
  plot = p,
  width = 8,
  height = 4,
  path = path_fig
)
ggsave(
  filename = "ExpB_initial_weights.svg",
  plot = p,
  width = 8,
  height = 4,
  path = path_fig
)
```

## Growth of individuals

Mean growth curves of each cosm and per condition.

```{r, warning=F}
#| fig-cap: Mean growth curves of each cosme and per condition.
#| label: fig-growthcurves
#| fig-width: 8
#| fig-height: 12

p <- ggplot(
  data = df_expB_autumn,
  aes(
    x = t,
    y = w,
    group = paste(Nb_rep, Lot),
    color = Lot
  )
) +
  geom_point() +
  geom_line() +
  facet_wrap(~Condition, ncol = 7) +
  scale_color_manual(values = pal_lot) +
  theme_bw()
p
```

```{r savegrowthcurve, include=F}
ggsave(
  filename = "ExpB_growth_curves.png",
  plot = p,
  width = 8, height = 12,
  path = path_fig
)
ggsave(
  filename = "ExpB_growth_curves.svg",
  plot = p,
  width = 8, height = 12,
  path = path_fig
)
```

Calculation of growth rates :

```{r gratescalc}
f_growth_rate <- function(data) {
  a_init <- 0.1
  a_i <- c()

  # Calculation of the growth rate for each individual
  for (i in subset(data, t == 0)$ID_cosm) {
    data_i <- data.frame(
      L = subset(data, ID_cosm == i)$L,
      t = subset(data, ID_cosm == i)$t
    )
    L0_i <- subset(data, ID_cosm == i & t == 0)$L
    if (length(na.omit(data_i$L)) == 2) { # If only 2 data points
      a.Est <- (subset(data_i, !t == 0)$L - subset(data_i, t == 0)$L) /
        subset(data_i, !t == 0)$t
    } else {
      a.Est <- NA
    }
    a_i <- rbind(a_i, a.Est)
  }
  return(a_i)
}

a_i <- f_growth_rate(df_expB_autumn)

df_expB_autumn_grate <- cbind(subset(df_expB_autumn, t == 0), a_i)
df_expB_autumn_grate_mean <- df_expB_autumn_grate |>
  aggregate(a_i ~ Condition + Dose_EPX + Dose_IMD + Ratio, FUN = "mean")
```

```{r, warning=F, message=F}
#| fig-cap: Mean growth rates of each cosm and per condition.
#| label: fig-growthrates
#| fig-width: 8
#| fig-height: 10

p <- ggplot(
  data = df_expB_autumn_grate,
  aes(
    x = Lot,
    y = a_i,
    # group = Nb_rep,
    color = Lot
  )
) +
  geom_boxplot() +
  geom_dotplot(
    binaxis = "y",
    stackdir = "center",
    dotsize = 0.7,
    alpha = 0.7
  ) +
  facet_wrap(
    ~Condition,
    ncol = 7,
    # scales = "free"
  ) +
  scale_color_manual(values = pal_lot) +
  theme_bw()
p
```

```{r savegrates, include=F}
ggsave(
  filename = "ExpB_growth_rates.png",
  plot = p,
  width = 8, height = 10,
  path = path_fig
)
ggsave(
  filename = "ExpB_growth_rates.svg",
  plot = p,
  width = 8, height = 10,
  path = path_fig
)
```

## First look at cocoons production

```{r, warning=F, message=F}
#| fig-cap: Cocoons produced by each cosme and per condition.
#| label: fig-cocbox
#| fig-width: 8
#| fig-height: 4

p <- ggplot(
  data = df_expB_autumn,
  aes(
    x = Condition,
    y = Nb_cocoons,
  )
) +
  geom_boxplot() +
  geom_dotplot(
    binaxis = "y",
    stackdir = "center",
    dotsize = 0.7,
    alpha = 0.7,
    aes(color = Lot, fill = Lot)
  ) +
  # facet_wrap(~Condition, ncol = 7)+
  scale_color_manual(values = pal_lot) +
  scale_fill_manual(values = pal_lot) +
  theme_bw()
p
```

```{r savecocbox, include=F}
ggsave(
  filename = "ExpB_cocoons_boxplot.png",
  plot = p,
  width = 12, height = 8,
  path = path_fig
)
ggsave(
  filename = "ExpB_cocoons_boxplot.svg",
  plot = p,
  width = 12, height = 8,
  path = path_fig
)
```

The results for imidacloprid only do not seem to correspond to the expected effect. We will compare the ratio I and E to the previously obtained dose response curves.

## Retrieving of the previously obtained dose-response curves

Importation of the EC50 experiment data.

```{r dataEC50}
# Data EC50
# Value given to controls for plot
Val_Ctrl <- 1e-4
Label_Ctrl <- "0 (Ctrl)"
# Data from experiment A (Single substances experiement)
data_expA_repro    <- f_read_data_expA_repro()
df_expA_repro_tot  <- data_expA_repro$df_expA_repro
df_expA_repro      <- data_expA_repro$df_expA_repro_alive
df_expA_repro_mean <- data_expA_repro$df_expA_repro_alive_mean

data_expA_growth   <- f_read_data_expA_growth()
df_expA_growth     <- data_expA_growth$df_expA_growth
```

```{r drc, warning=F, message=F}
# Common Ymax and slope
drc.4 <- drm(
  Nb_cocoons ~ Dose, Molecule,
  data = df_expA_repro,
  type = "Poisson",
  fct = LL.4(
    names = c("slope", "Ymin", "Ymax", "EC50"),
    fixed = c(NA, 0, NA, NA)
  ),
  # Reproduction is expected to reach 0 for large concentrations
  pmodels = data.frame(1, 1, Molecule)
)
# summary(drc.4)

data_CI_drc.4 <- f_CI_drc(
  Dose_min = Val_Ctrl,
  Dose_max = 5000,
  Molecules = c("EPX", "IMD"),
  drc.model = drc.4,
  signif_param = 3
)

df_CI_drc.4 <- data_CI_drc.4$df_CI
df_param.drc.4 <- data_CI_drc.4$df_param

EPX_EC50_expA <- coef(drc.4)[4]
IMD_EC50_expA <- coef(drc.4)[4]
```

```{r dfarr}
x <- seq(0.000001, 5000, 0.01)

df_expA_repro_IMD <- subset(df_expA_repro, Molecule == "IMD")
df_expA_repro_EPX <- subset(df_expA_repro, Molecule == "EPX")

df_expA_repro_IMD_mean <- subset(df_expA_repro_mean, Molecule == "IMD")
df_expA_repro_EPX_mean <- subset(df_expA_repro_mean, Molecule == "IMD")

df_expB_autumn_IMD <- subset(df_expB_autumn, Ratio %in% c("I", "N"))
df_expB_autumn_EPX <- subset(df_expB_autumn, Ratio %in% c("E", "N"))
df_expB_autumn_IMD_mean <- df_expB_autumn_IMD |>
  aggregate(Nb_cocoons ~ Condition + Dose_IMD, mean)
df_expB_autumn_EPX_mean <- df_expB_autumn_EPX |>
  aggregate(Nb_cocoons ~ Condition + Dose_EPX, mean)
```

```{r, warning=F}
#| fig-cap: Comparaison of the results obtained in the mixture experiment (red) with the results of the EC50 experiments (blues).  The line represents the dose-response curve obtained with the EC50 experiments (with common $Y_{max}$ and slope for the 2 active substances). Crosses correspond to the number of cocoons produced by one cosm and the bold points represents the mean per dose.
#| label: fig-drcIMDEPX
#| fig-width: 6
#| fig-height: 6

line_width <- 1.2

p_I <- ggplot() +
  geom_ribbon(
    data = subset(df_CI_drc.4, Molecule == "IMD"),
    aes(
      x = Dose,
      y = p,
      ymin = pmin,
      ymax = pmax
    ),
    alpha = 0.2,
    fill = col_IMD
  ) +
  geom_line(
    data = subset(df_CI_drc.4, Molecule == "IMD"),
    aes(
      x = Dose,
      y = p
    ),
    color = col_IMD,
    linewidth = line_width
  ) +
  geom_point(
    data = df_expA_repro_IMD,
    aes(x = Dose, y = Nb_cocoons),
    color = col_IMD,
    alpha = 0.5,
    shape = 4
  ) +
  geom_point(
    data = subset(df_expB_autumn_IMD, Lot == "T"),
    aes(x = Dose_IMD, y = Nb_cocoons),
    color = col_red,
    alpha = 0.6,
    shape = 4
  ) +
  geom_point(
    data = df_expB_autumn_IMD_mean,
    aes(x = Dose_IMD, y = Nb_cocoons),
    color = col_red,
    size = 3
  ) +
  geom_point(
    data = subset(df_expA_repro_IMD_mean, Molecule == "IMD"),
    aes(x = Dose, y = Nb_cocoons),
    color = col_IMD,
    size = 3
  ) +
  annotate(
    geom = "text",
    x = 1500,
    y = 30,
    label = "I",
    fontface = "bold"
  ) +
  scale_x_log10() +
  labs(
    x = "Concentration en IMD (mg/kg)",
    y = "Nombre de cocons produits"
  ) +
  theme_bw()

p_E <- ggplot() +
  geom_ribbon(
    data = subset(df_CI_drc.4, Molecule == "EPX"),
    aes(
      x = Dose,
      y = p,
      ymin = pmin,
      ymax = pmax
    ),
    alpha = 0.2,
    fill = col_EPX
  ) +
  geom_line(
    data = subset(df_CI_drc.4, Molecule == "EPX"),
    aes(
      x = Dose,
      y = p
    ),
    color = col_EPX,
    linewidth = line_width
  ) +
  geom_point(
    data = df_expA_repro_EPX,
    aes(x = Dose, y = Nb_cocoons),
    color = col_EPX,
    alpha = 0.5,
    shape = 4
  ) +
  geom_point(
    data = df_expB_autumn_EPX,
    aes(x = Dose_EPX, y = Nb_cocoons),
    color = col_red,
    alpha = 0.6,
    shape = 4
  ) +
  geom_point(
    data = subset(df_expA_repro_EPX_mean, Molecule == "EPX"),
    aes(x = Dose, y = Nb_cocoons),
    color = col_EPX,
    size = 3
  ) +
  geom_point(
    data = df_expB_autumn_EPX_mean,
    aes(x = Dose_EPX, y = Nb_cocoons),
    color = col_red,
    size = 3
  ) +
  annotate(
    geom = "text",
    x = 1500,
    y = 30,
    label = "E",
    fontface = "bold"
  ) +
  scale_x_log10() +
  labs(
    x = "Concentration en EPX (mg/kg)",
    y = "Nombre de cocons produits"
  ) +
  theme_bw()

p <- p_I / p_E
p
```

```{r savecompdrc, include=F}
ggsave(
  filename = "ExpB_cocoon_compdrc.png",
  plot = p,
  width = 6, height = 6,
  path = path_fig
)
ggsave(
  filename = "ExpB_cocoons_compdrc.svg",
  plot = p,
  width = 6, height = 6,
  path = path_fig
)
```

## Comparison of the other ratio with the EPX dose-response curve

```{r, warning=F}
#| fig-cap: Comparaison of the results obtained in the mixture experiment (red) with the results of the EC50 experiment for EPX (blues).  The line represents the dose-response curve obtained with the EC50 experiment (with common $Y_{max}$ and slope for the 2 active substances). Crosses correspond to the number of cocoons produced by one cosm and the bold points represents the mean per dose. The results of the mixture experiment are plotted a if only EPX was added to the soil.
#| label: fig-drcEPXratio
#| fig-width: 10
#| fig-height: 8

p_F <- ggplot() +
  geom_ribbon(
    data = subset(df_CI_drc.4, Molecule == "EPX"),
    aes(
      x = Dose,
      y = p,
      ymin = pmin,
      ymax = pmax
    ),
    alpha = 0.2,
    fill = col_EPX,
    # color = col_IMD
  ) +
  geom_line(
    data = subset(df_CI_drc.4, Molecule == "EPX"),
    aes(
      x = Dose,
      y = p
    ),
    color = col_EPX,
    linewidth = line_width
  ) +
  geom_point(
    data = subset(df_expB_autumn, Ratio %in% c("N", "F")),
    aes(
      x = Dose_EPX,
      y = Nb_cocoons
    ),
    alpha = 0.6,
    shape = 4,
    color = col_red
  ) +
  geom_point(
    data = df_expA_repro_EPX,
    aes(x = Dose, y = Nb_cocoons),
    color = col_EPX,
    alpha = 0.5,
    shape = 4
  ) +
  geom_point(
    data = subset(df_expA_repro_mean, Molecule == "EPX"),
    aes(x = Dose, y = Nb_cocoons),
    color = col_EPX,
    size = 3
  ) +
  geom_point(
    data = subset(df_expB_autumn_mean, Ratio %in% c("N", "F")),
    aes(
      x = Dose_EPX,
      y = Nb_cocoons
    ),
    size = 3,
    color = col_red
  ) +
  annotate(
    geom = "text",
    x = 1500,
    y = 30,
    label = "F",
    fontface = "bold"
  ) +
  scale_x_log10() +
  labs(
    x = "Concentration en EPX (mg/kg)",
    y = "Nombre de cocons produits"
  ) +
  theme_bw()

p_G <- ggplot() +
  geom_ribbon(
    data = subset(df_CI_drc.4, Molecule == "EPX"),
    aes(
      x = Dose,
      y = p,
      ymin = pmin,
      ymax = pmax
    ),
    alpha = 0.2,
    fill = col_EPX,
  ) +
  geom_line(
    data = subset(df_CI_drc.4, Molecule == "EPX"),
    aes(
      x = Dose,
      y = p
    ),
    color = col_EPX,
    linewidth = line_width
  ) +
  geom_point(
    data = subset(df_expB_autumn, Ratio %in% c("N", "G")),
    aes(
      x = Dose_EPX,
      y = Nb_cocoons
    ),
    alpha = 0.6,
    shape = 4,
    color = col_red
  ) +
  geom_point(
    data = df_expA_repro_EPX,
    aes(x = Dose, y = Nb_cocoons),
    color = col_EPX,
    alpha = 0.5,
    shape = 4
  ) +
  geom_point(
    data = subset(df_expA_repro_mean, Molecule == "EPX"),
    aes(x = Dose, y = Nb_cocoons),
    color = col_EPX,
    size = 3
  ) +
  geom_point(
    data = subset(df_expB_autumn_mean, Ratio %in% c("N", "G")),
    aes(
      x = Dose_EPX,
      y = Nb_cocoons
    ),
    size = 3,
    color = col_red
  ) +
  annotate(
    geom = "text",
    x = 1500,
    y = 30,
    label = "G",
    fontface = "bold"
  ) +
  # facet_wrap(~Ratio, ncol = 2)+
  scale_color_manual(values = c(Nord_frost[2], Nord_frost[2])) +
  scale_x_log10() +
  labs(
    x = "Concentration en EPX (mg/kg)",
    y = "Nombre de cocons produits"
  ) +
  theme_bw()

p_H <- ggplot() +
  geom_ribbon(
    data = subset(df_CI_drc.4, Molecule == "EPX"),
    aes(
      x = Dose,
      y = p,
      ymin = pmin,
      ymax = pmax
    ),
    alpha = 0.2,
    fill = col_EPX,
    # color = col_IMD
  ) +
  geom_line(
    data = subset(df_CI_drc.4, Molecule == "EPX"),
    aes(
      x = Dose,
      y = p
    ),
    color = col_EPX,
    linewidth = line_width
  ) +
  geom_point(
    data = subset(df_expB_autumn, Ratio %in% c("N", "H")),
    aes(
      x = Dose_EPX,
      y = Nb_cocoons
    ),
    alpha = 0.6,
    shape = 4,
    color = col_red
  ) +
  geom_point(
    data = df_expA_repro_EPX,
    aes(x = Dose, y = Nb_cocoons),
    color = col_EPX,
    alpha = 0.5,
    shape = 4
  ) +
  geom_point(
    data = subset(df_expA_repro_mean, Molecule == "EPX"),
    aes(x = Dose, y = Nb_cocoons),
    color = col_EPX,
    size = 3
  ) +
  geom_point(
    data = subset(df_expB_autumn_mean, Ratio %in% c("N", "H")),
    aes(
      x = Dose_EPX,
      y = Nb_cocoons
    ),
    size = 3,
    color = col_red
  ) +
  annotate(
    geom = "text",
    x = 1500,
    y = 30,
    label = "H",
    fontface = "bold"
  ) +
  # facet_wrap(~Ratio, ncol = 2)+
  scale_color_manual(values = c(Nord_frost[2], Nord_frost[2])) +
  scale_x_log10() +
  labs(
    x = "Concentration en EPX (mg/kg)",
    y = "Nombre de cocons produits"
  ) +
  theme_bw()

p <- p_E + p_F + p_G + p_H + plot_layout(ncol = 2)
p
```

```{r savecompdrcepx, include=F}
ggsave(
  filename = "ExpB_cocoons_compdrc_EPX.png",
  plot = p,
  width = 10, height = 8,
  path = path_fig
)
ggsave(
  filename = "ExpB_cocoons_compdrc_EPX.svg",
  plot = p,
  width = 10, height = 8,
  path = path_fig
)
```

Everything happened a if no IMD was added to the soil.

## Comparison of growth rates with data from dose-response curves

```{r gratescalc2}
f_growth_rate <- function(data) {
  a_init <- 0.1
  a_i <- c()

  # Calculation of the growth rate for each individual
  for (i in subset(data, t == 0)$ID_cosm) {
    data_i <- data.frame(
      L = subset(data, ID_cosm == i)$L,
      t = subset(data, ID_cosm == i)$t
    )
    L0_i <- subset(data, ID_cosm == i & t == 0)$L
    if (length(na.omit(data_i$L)) == 2) { # If only 2 data points
      a.Est <- (subset(data_i, !t == 0)$L - subset(data_i, t == 0)$L) /
        subset(data_i, !t == 0)$t
    } else {
      a.Est <- NA
    }
    a_i <- rbind(a_i, a.Est)
  }
  return(a_i)
}

a_i <- f_growth_rate(df_expA_repro)

df_expA_repro_grate <- cbind(subset(df_expA_repro, t == 0), a_i)
df_expA_repro_grate_mean <- df_expA_repro_grate |>
  aggregate(a_i ~ Molecule + Dose, FUN = "mean")
```

```{r, warning=F, message=F}
#| fig-cap: Mean growth rates of each cosm and per condition.
#| label: fig-growthratescomp
#| fig-width: 6
#| fig-height: 8


p_IMD <- ggplot() +
  # Dose-response curves expriements
  geom_point(
    data = subset(df_expA_repro_grate, Molecule == "IMD"),
    aes(
      x = Dose,
      y = a_i
    ),
    alpha = 0.5,
    color = col_IMD
  ) +
  geom_point(
    data = subset(df_expA_repro_grate_mean, Molecule == "IMD"),
    aes(
      x = Dose,
      y = a_i
    ),
    alpha = 1,
    size = 3,
    color = col_IMD
  ) +
  # Mixture experiment
  geom_point(
    data = subset(df_expB_autumn_grate, Dose_EPX == 0), # IMD data (Ratio I)
    aes(
      x = Dose_IMD,
      y = a_i
    ),
    alpha = 0.5,
    color = col_red
  ) +
  geom_point(
    data = subset(df_expB_autumn_grate_mean, Dose_EPX == 0),
    aes(
      x = Dose_IMD,
      y = a_i
    ),
    alpha = 1,
    size = 3,
    color = col_red
  ) +
  labs(
    x = "Dose (mg/kg)",
    y = "Growth rate",
    title = "Effect on adult growth for IMD"
  ) +
  scale_x_log10() +
  theme_bw(12)

p_EPX <- ggplot() +
  # Dose-response curves experiments
  geom_point(
    data = subset(df_expA_repro_grate, Molecule == "EPX"),
    aes(
      x = Dose,
      y = a_i
    ),
    alpha = 0.5,
    color = col_EPX
  ) +
  geom_point(
    data = subset(df_expA_repro_grate_mean, Molecule == "EPX"),
    aes(
      x = Dose,
      y = a_i
    ),
    alpha = 1,
    size = 3,
    color = col_EPX
  ) +
  # Mixture experiement
  geom_point(
    data = subset(df_expB_autumn_grate, Dose_IMD == 0), # IMD data (Ratio I)
    aes(
      x = Dose_EPX,
      y = a_i
    ),
    alpha = 0.5,
    color = col_red
  ) +
  geom_point(
    data = subset(df_expB_autumn_grate_mean, Dose_IMD == 0),
    aes(
      x = Dose_EPX,
      y = a_i
    ),
    alpha = 1,
    size = 3,
    color = col_red
  ) +
  scale_x_log10() +
  labs(
    x = "Dose (mg/kg)",
    y = "Growth rate",
    title = "Effect on adult growth for EPX"
  ) +
  theme_bw(12)

p <- p_IMD / p_EPX
p_IMD / p_EPX
```

```{r savegrowthcompdrc, include=F}
ggsave(
  filename = "ExpB_growth_compdrc.png",
  plot = p,
  width = 8, height = 6,
  path = path_fig
)
ggsave(
  filename = "ExpB_growth_compdrc.svg",
  plot = p,
  width = 8, height = 6,
  path = path_fig
)
```

## Design comparisons

```{r}
#| fig-cap: Comparison of the theorical design and the actual design.
#| label: fig-compdesign
#| fig-width: 5
#| fig-height: 5

# Ratios considered
ratios <- c(0, 1 / 4, 1 / 2, 3 / 4, 1)

EPX_x <- NULL
IMD_x <- NULL

ratio_EC50 <- IMD_EC50_expA / EPX_EC50_expA

for (i in ratios) {
  EPX_x <- rbind(EPX_x, EPX_EC50_expA * i)
  IMD_x <- rbind(IMD_x, IMD_EC50_expA * (1 - i))
}

factor_design <- 10^(1 / 4)

EPX_x <- c(
  EPX_x,
  EPX_x / (factor_design^9),
  EPX_x / (factor_design^5),
  EPX_x / (factor_design^2),
  EPX_x / factor_design,
  factor_design * EPX_x,
  factor_design^2 * EPX_x
)
IMD_x <- c(
  IMD_x,
  IMD_x / (factor_design^9),
  IMD_x / (factor_design^5),
  IMD_x / (factor_design^2),
  IMD_x / factor_design,
  factor_design * IMD_x,
  factor_design^2 * IMD_x
)


df_design <- data.frame(
  EPX = EPX_x,
  IMD = IMD_x,
  Ratio = EPX_x / IMD_x * IMD_EC50_expA / EPX_EC50_expA
)

width_iso <- 1.1
size_points <- 3
alpha_true <- 0.5

df_design_plot <- df_design |>
  mutate(
    label = paste(
      "[IMD] = ",
      signif(IMD, 3),
      "mg/kg\n [EPX] = ",
      signif(EPX, 3), "mg/kg"
    )
  )

plot_design <- ggplot() +
  xlim(min(EPX_x), max(EPX_x)) +
  ylim(min(IMD_x), max(IMD_x)) +
  # Ligne des ratios
  geom_abline(
    intercept = 0,
    slope = ratio_EC50 / 3,
    color = pal_col[2],
    alpha = alpha_true
  ) +
  geom_abline(
    intercept = 0,
    slope = ratio_EC50 * 3,
    color = pal_col[2],
    alpha = alpha_true
  ) +
  geom_abline(
    intercept = 0,
    slope = ratio_EC50,
    color = pal_col[2],
    alpha = alpha_true
  ) +
  geom_abline(
    intercept = 0,
    slope = 0,
    color = pal_col[2],
    alpha = alpha_true
  ) +
  geom_vline(
    xintercept = 0,
    color = pal_col[2],
    alpha = alpha_true
  ) +

  # Effect isoboles
  geom_abline(
    intercept = IMD_EC50_expA * factor_design^2,
    slope = -ratio_EC50,
    color = pal_col[1],
    lwd = width_iso,
    alpha = alpha_true
  ) +
  geom_abline(
    intercept = IMD_EC50_expA * factor_design,
    slope = -ratio_EC50,
    color = pal_col[1],
    lwd = width_iso,
    alpha = alpha_true
  ) +
  geom_abline(
    intercept = IMD_EC50_expA,
    slope = -ratio_EC50,
    color = pal_col[1],
    lwd = width_iso,
    alpha = alpha_true
  ) +
  geom_abline(
    intercept = IMD_EC50_expA / factor_design,
    slope = -ratio_EC50,
    color = pal_col[1],
    lwd = width_iso,
    alpha = alpha_true
  ) +
  geom_abline(
    intercept = IMD_EC50_expA / (factor_design^2),
    slope = -ratio_EC50,
    color = pal_col[1],
    lwd = width_iso,
    alpha = alpha_true
  ) +
  geom_abline(
    intercept = IMD_EC50_expA / (factor_design^5),
    slope = -ratio_EC50,
    color = pal_col[1],
    lwd = width_iso,
    alpha = alpha_true
  ) +
  geom_abline(
    intercept = IMD_EC50_expA / (factor_design^9),
    slope = -ratio_EC50,
    color = pal_col[1],
    lwd = width_iso,
    alpha = alpha_true
  ) +

  # Effect isoboles
  geom_abline(
    intercept = IMD_EC50_expA * factor_design^2 / 2,
    slope = -ratio_EC50 / 2,
    color = pal_col[1],
    lwd = width_iso
  ) +
  geom_abline(
    intercept = IMD_EC50_expA * factor_design / 2,
    slope = -ratio_EC50 / 2,
    color = pal_col[1],
    lwd = width_iso
  ) +
  geom_abline(
    intercept = IMD_EC50_expA / 2,
    slope = -ratio_EC50 / 2,
    color = pal_col[1],
    lwd = width_iso
  ) +
  geom_abline(
    intercept = IMD_EC50_expA / factor_design / 2,
    slope = -ratio_EC50 / 2,
    color = pal_col[1],
    lwd = width_iso
  ) +
  geom_abline(
    intercept = IMD_EC50_expA / (factor_design^2) / 2,
    slope = -ratio_EC50 / 2,
    color = pal_col[1],
    lwd = width_iso
  ) +
  geom_abline(
    intercept = IMD_EC50_expA / (factor_design^5) / 2,
    slope = -ratio_EC50 / 2,
    color = pal_col[1],
    lwd = width_iso
  ) +
  geom_abline(
    intercept = IMD_EC50_expA / (factor_design^9) / 2,
    slope = -ratio_EC50 / 2,
    color = pal_col[1],
    lwd = width_iso
  ) +

  # Ratios annotations
  annotate(
    geom = "text",
    x = 30,
    y = max(IMD_x),
    label = "0:1",
    color = pal_col[2],
    fontface = "bold"
  ) +
  annotate(
    geom = "text",
    x = 200,
    y = max(IMD_x),
    label = "3:1",
    color = pal_col[2],
    fontface = "bold"
  ) +
  annotate(
    geom = "text",
    x = max(EPX_x) - 30,
    y = max(IMD_x),
    label = "1:1",
    color = pal_col[2],
    fontface = "bold"
  ) +
  annotate(
    geom = "text",
    x = max(EPX_x),
    y = 0.8,
    label = "1:3",
    color = pal_col[2],
    fontface = "bold"
  ) +
  annotate(
    geom = "text",
    x = max(EPX_x),
    y = 0.1,
    label = "1:0",
    color = pal_col[2],
    fontface = "bold"
  ) +

  # Design points
  geom_point_interactive(
    data = df_design_plot,
    aes(
      x = EPX,
      y = IMD,
      tooltip = label
    ),
    size = size_points,
    color = Nord_polar[1],
    alpha = alpha_true
  ) +
  # Design points
  geom_point_interactive(
    data = df_design_plot,
    aes(
      x = EPX,
      y = IMD / 2,
      tooltip = label
    ),
    size = size_points,
    color = Nord_polar[1]
  ) +
  labs(
    x = "Epoxiconazole (mg/kg)",
    y = "Imidacloprid (mg/kg)"
  ) +
  theme_minimal(12)



tooltip_css <- "
  border-radius: 12px;
  color: #333;
  background-color: white;
  padding: 10px;
  font-size: 14px;
  transition: all 0.5s ease-out;
"

hover_css <- "
  filter: brightness(75%);
  cursor: pointer;
  transition: all 0.5s ease-out;
  filter: brightness(1.15);
"

interactive_plot <- girafe(
  ggobj = plot_design,
  height_svg = 5,
  width_svg = 5
) |>
  girafe_options(opts_sizing(rescale = FALSE))

# Add interactivity
interactive_plot <- interactive_plot %>%
  girafe_options(
    opts_hover(css = hover_css),
    opts_tooltip(css = tooltip_css),
    opts_hover_inv(css = "opacity:0.3; transition: all 0.2s ease-out;")
  )

interactive_plot
```

```{r, include=F}
ggsave(
  filename = "ExpB_design_comp.png",
  plot = plot_design,
  width = 5, height = 5,
  path = path_fig
)
ggsave(
  filename = "ExpB_design_comp.svg",
  plot = plot_design,
  width = 5, height = 5,
  path = path_fig
)
```

<button class="accordion-button" type="button" data-bs-toggle="collapse" data-bs-target="#collapseOne">

<b> Session Information </b>

</button>

:::: {#collapseOne .accordion-collapse .collapse}
<div>

```{r}
sessionInfo()
```

</div>
::::
