```{r lib, include=F}
library(here)
source(file = here::here("functions/fun.R"))
f_load_libraries_colors()

palette <- colorRampPalette(c("#5E81AC", "#88C0D0"))
col_mix <- Nord_polar[4]
pal_ratio <- c("#88C0D0", col_mix, col_mix, col_mix, "#5E81AC",col_mix)

path_fig <- here::here("fig/Mixture/Comp_expA_expB")

```

# Comparison of the single substances experiment with the mixture experiment ? {#sec-MIXSpringComp}

Because the single substances were tested again during the mixture experiment, the goal here is to compare the observed effects in both experiments and therefore to judge the reproducibility between the experiments. We then need to compare the dose-response curves for EPX & IMD obtained with the experiment UNI and the experiment MIX (Autumn 2024 vs. Spring 2025).

## Data importation

```{r datamix, message = F, warning=F}

# Value given to controls for plot
Val_Ctrl <- 1e-4
Label_Ctrl <- "0 (Ctrl)"


# Data from experiment A (Single substances experiement)
data_expA_repro    <- f_read_data_expA_repro()
df_expA_repro_tot  <- data_expA_repro$df_expA_repro
df_expA_repro      <- data_expA_repro$df_expA_repro_alive
df_expA_repro_mean <- data_expA_repro$df_expA_repro_alive_mean

# Retriving EC50 
df_drc_param <- read.csv(here::here("data/DRC_parameters_cocoons_really_used.csv"))
EPX_EC50_drc <- df_drc_param$coef.drc.4.[3]
IMD_EC50_drc <- df_drc_param$coef.drc.4.[4]

# Data from experiment B (Mixture experiment)
data_expB                 <- f_read_data_expB()
df_expB_growth            <- data_expB$df_expB_growth
df_expB_repro             <- data_expB$df_expB_repro
df_expB_repro_mean        <- data_expB$df_expB_repro_mean
df_expB_repro_single      <- data_expB$df_expB_repro_single
df_expB_repro_single_mean <- data_expB$df_expB_repro_single_mean

# Retriving EC50 
df_drc_param <- read.csv(here::here("data/DRC_parameters_cocoons_really_used.csv"))
EPX_EC50_drc <- df_drc_param$coef.drc.4.[3]
IMD_EC50_drc <- df_drc_param$coef.drc.4.[4]

```

## Initial state of the mixture experiment (experiment B)

We can first take a look at the initial weights of individuals from the mixture experiment (@fig-initMIXSpringcomp).

```{r D0, warning=F, message=F}
#| fig-cap: Initial weights of earthworms according to batches. 
#| label: fig-initMIXSpringcomp
#| fig-width: 10
#| fig-height: 4
pal_lot <- c(Nord_frost[3], Nord_polar[4])

# Weights at t=0
p <- ggplot(
  data = subset(df_expB_growth, t == 0),
  aes(
    x = Condition,
    y = w
  )
) +
  geom_boxplot(
    alpha = 0.2,
    color = Nord_polar[1]
  ) +
  geom_dotplot(
    aes(
      color = Lot,
      fill = Lot
    ),
    binaxis = "y",
    stackdir = "center",
    dotsize = 0.5,
    alpha = 0.7
  ) +
  scale_color_manual(values = pal_lot) +
  scale_fill_manual(values = pal_lot) +
  labs(x = "Condition", y = "Weight (mg)") +
  theme_classic(12) +
  theme(
    # legend.position = "none",
    legend.title = element_text(size = sizetitle - 2, face = "bold"),
    legend.text = element_text(size = sizetitle - 2, face = "plain"),
    title = element_text(size = sizetitle, face = "bold"),
    axis.title.x = element_blank(),
    axis.title.y = element_text(size = sizetitle, face = "plain"),

    # axis.text.x = element_blank(),
    axis.line.x = element_blank(),
    axis.ticks.x = element_blank(),
    strip.background = element_rect(
      color = "black",
      fill = "grey95",
      size = 0,
      linetype = "solid"
    )
  )
p
```

```{r saveinit, include=F}
ggsave(
  filename = "ExpB_initial_weights.png",
  plot = p,
  width = 8,
  height = 4,
  path = path_fig
)
ggsave(
  filename = "ExpB_initial_weights.jpg",
  plot = p,
  width = 8,
  height = 4,
  path = path_fig
)
ggsave(
  filename = "ExpB_initial_weights.svg",
  plot = p,
  width = 8,
  height = 4,
  path = path_fig
)
```

```{r}
summary(subset(df_expB_growth, t == 0))
```

## Comparison of the controls

```{r, message=F, warning=F}
#| fig-cap: Comparaison of the controls obtained in the mixture experiment (dark blues) with the results of the experiment UNI (blues). 
#| label: fig-drcIMDEPXcompctrl
#| fig-width: 4
#| fig-height: 5

df_expB_repro_ctrl <- subset(df_expB_repro, Ratio == "N") |>
  dplyr::select(Nb_cocoons) |>
  mutate(Experiment = "Experiment MIX")

df_expA_repro_ctrl <- subset(df_expA_repro, Dose == 0) |>
  dplyr::select(Nb_cocoons, Lot) |>
  mutate(Experiment = case_when(
    Lot == "A" ~ "Experiment UNI\nSpring 2024",
    Lot == "B" ~ "Experiment UNI\nSummer 2024"
  )) |>
  dplyr::select(Nb_cocoons, Experiment)

df_controls <- rbind(df_expA_repro_ctrl, df_expB_repro_ctrl)
df_controls$Experiment <- factor(df_controls$Experiment, levels = c("Experiment UNI\nSpring 2024", "Experiment UNI\nSummer 2024", "Experiment MIX"))

p <- ggplot(
  data = df_controls,
  aes(
    x = Experiment,
    y = Nb_cocoons
  )
) +
  geom_dotplot(
    binaxis = "y",
    stackdir = "center",
    dotsize = 0.8,
    alpha = 0.7,
    color = Nord_aurora[4],
    fill = Nord_aurora[4]
  ) +
  labs(
    x = "",
    y = "Number of cocoons produced per cosm (#)"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

p
```

```{r savecompctrl, include=F}
ggsave(
  filename = "Comp_expA_expB_ctrl.png",
  plot = p,
  width = 4, height = 5,
  path = path_fig
)
ggsave(
  filename = "Comp_expA_expB_ctrl.jpg",
  plot = p,
  width = 4, height = 5,
  path = path_fig
)
```

```{r testcompctrl, message=F, warning=F}
#| code-fold: show

pairwise.wilcox.test(df_controls$Nb_cocoons, df_controls$Experiment, p.adjust.method = "bonferroni", exact=F)

lm.controls <- lm(Nb_cocoons ~ Experiment, data = df_controls)
lsmeans(lm.controls,pairwise~Experiment,adjust='bonferroni')

```

The controls of the two different experiments are not significatively different.

## Dose-response curves

We then get the dose-response curves of the single substances from experiment UNI and experiment MIX.

### Experiment UNI - Dose-response curves

```{r drcexpA, warning=F, message=F}

drc.ExpA <- drm(
  Nb_cocoons ~ Dose, Molecule,
  data = df_expA_repro,
  type = "Poisson",
  fct = LL.4(
    names = c("slope", "Ymin", "Ymax", "EC50"),
    fixed = c(NA, 0, NA, NA)
  ),
  # Reproduction is expected to reach 0 for large concentrations
  pmodels = data.frame(Molecule, Molecule, Molecule)
)

data_CI_ExpA <- f_CI_drc(
  Dose_min = Val_Ctrl,
  Dose_max = 5000,
  Molecules = c("EPX", "IMD"),
  drc.model = drc.ExpA,
  signif_param = 3
)

df_CI_ExpA <- data_CI_ExpA$df_CI
df_param.ExpA <- data_CI_ExpA$df_param

EPX_EC50_ExpA <- coef(drc.ExpA)[5]
IMD_EC50_ExpA <- coef(drc.ExpA)[6]

summary(drc.ExpA)

```

### Experiment MIX - Dose-response curves

```{r drcexpB, warning=F, message=F}

# Common Ymax and slope
drc.ExpB <- drm(
  Nb_cocoons ~ Dose, Molecule,
  data = df_expB_repro_single,
  type = "Poisson",
  fct = LL.4(
    names = c("slope", "Ymin", "Ymax", "EC50"),
    fixed = c(NA, 0, NA, NA)
  ),
  # Reproduction is expected to reach 0 for large concentrations
  pmodels = data.frame(Molecule, Molecule, Molecule)
)

data_CI_ExpB <- f_CI_drc(
  Dose_min = Val_Ctrl,
  Dose_max = 5000,
  Molecules = c("EPX", "IMD"),
  drc.model = drc.ExpB,
  signif_param = 3
)

df_CI_ExpB <- data_CI_ExpB$df_CI
df_param.ExpB <- data_CI_ExpB$df_param

EPX_EC50_ExpB <- coef(drc.ExpB)[5]
IMD_EC50_ExpB <- coef(drc.ExpB)[6]

summary(drc.ExpB)

```

## Comparison of the two experiments for single substances

```{r, warning=F, message=F}
#| fig-cap: Comparaison of the results obtained in the experiment MIX (dark blues) with the results of Experiment UNI (blues). The line represents the dose-response curves obtained for the number of cocoons produced. Crosses correspond to the number of cocoons produced by one cosm and the bold points represents the mean per dose.
#| label: fig-drcIMDEPXcomp
#| fig-width: 8
#| fig-height: 4

df_expA_repro_IMD <- df_expA_repro |>
  filter(Molecule == "IMD")
df_expA_repro_EPX <- df_expA_repro |>
  filter(Molecule == "EPX")

df_expA_repro_IMD_mean <- df_expA_repro_mean |>
  filter(Molecule == "IMD")
df_expA_repro_EPX_mean <- df_expA_repro_mean |>
  filter(Molecule == "EPX")

df_expB_repro_single_IMD <- df_expB_repro_single |>
  filter(Molecule == "IMD")
df_expB_repro_single_EPX <- df_expB_repro_single |>
  filter(Molecule == "EPX")

df_expB_repro_single_IMD_mean <- df_expB_repro_single_mean |>
  filter(Molecule == "IMD")
df_expB_repro_single_EPX_mean <- df_expB_repro_single_mean |>
  filter(Molecule == "EPX")

x <- seq(0.0001, 5000, 0.01)
line_width <- 1.2

darkening <- 0.2
col_IMD_dark <- colorspace::darken(col_IMD, darkening)
col_EPX_dark <- colorspace::darken(col_EPX, darkening)

p_E <- ggplot() +
  geom_ribbon(
    data = subset(df_CI_ExpB, Molecule == "EPX"),
    aes(
      x = Dose,
      y = p,
      ymin = pmin,
      ymax = pmax
    ),
    alpha = 0.2,
    fill = col_EPX_dark,
  ) +
  geom_ribbon(
    data = subset(df_CI_ExpA, Molecule == "EPX"),
    aes(
      x = Dose,
      y = p,
      ymin = pmin,
      ymax = pmax
    ),
    alpha = 0.2,
    fill = col_EPX,
  ) +
  geom_line(
    data = subset(df_CI_ExpB, Molecule == "EPX"),
    aes(
      x = Dose,
      y = p
    ),
    color = col_EPX_dark,
    linewidth = line_width
  ) +
  geom_line(
    data = subset(df_CI_ExpA, Molecule == "EPX"),
    aes(
      x = Dose,
      y = p
    ),
    color = col_EPX,
    linewidth = line_width
  ) +
  geom_point(
    data = df_expB_repro_single_EPX,
    aes(
      x = Dose_plot,
      y = Nb_cocoons
    ),
    color = col_EPX_dark,
    alpha = 0.6,
    shape = 4
  ) +
  geom_point(
    data = df_expA_repro_EPX,
    aes(
      x = Dose_plot,
      y = Nb_cocoons
    ),
    color = col_EPX,
    alpha = 0.5,
    shape = 4
  ) +
  geom_point(
    data = df_expB_repro_single_EPX_mean,
    aes(
      x = Dose_plot,
      y = Nb_cocoons
    ),
    color = col_EPX_dark,
    size = 3
  ) +
  geom_point(
    data = subset(df_expA_repro_EPX_mean, Molecule == "EPX"),
    aes(
      x = Dose_plot,
      y = Nb_cocoons
    ),
    color = col_EPX,
    size = 3
  ) +
  annotate(
    geom = "text",
    x = 1500,
    y = 2,
    label = "E",
    fontface = "bold"
  ) +
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100), # inclure la valeur fictive
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100")
  ) +
  labs(
    x = "Concentration of EPX (mg/kg)",
    y = "Number of cocoons produced per cosm (#)"
  ) +
  theme_bw()

p_I <- ggplot() +
  geom_ribbon(
    data = subset(df_CI_ExpB, Molecule == "IMD"),
    aes(
      x = Dose,
      y = p,
      ymin = pmin,
      ymax = pmax
    ),
    alpha = 0.2,
    fill = col_IMD_dark,
    # color = col_IMD
  ) +
  geom_ribbon(
    data = subset(df_CI_ExpA, Molecule == "IMD"),
    aes(
      x = Dose,
      y = p,
      ymin = pmin,
      ymax = pmax
    ),
    alpha = 0.2,
    fill = col_IMD,
    # color = col_IMD
  ) +
  geom_line(
    data = subset(df_CI_ExpB, Molecule == "IMD"),
    aes(
      x = Dose,
      y = p
    ),
    color = col_IMD_dark,
    linewidth = line_width
  ) +
  geom_line(
    data = subset(df_CI_ExpA, Molecule == "IMD"),
    aes(
      x = Dose,
      y = p
    ),
    color = col_IMD,
    linewidth = line_width
  ) +
  geom_point(
    data = df_expB_repro_single_IMD,
    aes(
      x = Dose_plot,
      y = Nb_cocoons
    ),
    color = col_IMD_dark,
    alpha = 0.6,
    shape = 4
  ) +
  geom_point(
    data = df_expA_repro_IMD,
    aes(
      x = Dose_plot,
      y = Nb_cocoons
    ),
    color = col_IMD,
    alpha = 0.5,
    shape = 4
  ) +
  geom_point(
    data = df_expB_repro_single_IMD_mean,
    aes(
      x = Dose_plot,
      y = Nb_cocoons
    ),
    color = col_IMD_dark,
    size = 3
  ) +
  geom_point(
    data = subset(df_expA_repro_IMD_mean, Molecule == "IMD"),
    aes(
      x = Dose_plot,
      y = Nb_cocoons
    ),
    color = col_IMD,
    size = 3
  ) +
  annotate(
    geom = "text",
    x = 1500,
    y = 2,
    label = "I",
    fontface = "bold"
  ) +
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100), # inclure la valeur fictive
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100")
  ) +
  labs(
    x = "Concentration of IMD (mg/kg)",
    y = "Number of cocoons produced per cosm (#)"
  ) +
  theme_bw()

p <- p_E + p_I
p
```

```{r savecompdrc, include=F}
ggsave(
  filename = "Comp_expA_expB_drc.png",
  plot = p,
  width = 8, height = 4,
  path = path_fig
)
ggsave(
  filename = "Comp_expA_expB_drc.jpg",
  plot = p,
  width = 8, height = 4,
  path = path_fig
)
```

```{r synthparamdrc, results="hide", warning=F, message = F}
pEC50EPXExpA <- ED(drc.ExpA, 50, interval = "delta")[1,1]
pEC50EPXExpB <- ED(drc.ExpB, 50, interval = "delta")[1,1]
pEC50IMDExpA <- ED(drc.ExpA, 50, interval = "delta")[2,1]
pEC50IMDExpB <- ED(drc.ExpB, 50, interval = "delta")[2,1]

pminEC50EPXExpA <- ED(drc.ExpA, 50, interval = "delta")[1,3]
pminEC50EPXExpB <- ED(drc.ExpB, 50, interval = "delta")[1,3]
pminEC50IMDExpA <- ED(drc.ExpA, 50, interval = "delta")[2,3]
pminEC50IMDExpB <- ED(drc.ExpB, 50, interval = "delta")[2,3]

pmaxEC50EPXExpA <- ED(drc.ExpA, 50, interval = "delta")[1,4]
pmaxEC50EPXExpB <- ED(drc.ExpB, 50, interval = "delta")[1,4]
pmaxEC50IMDExpA <- ED(drc.ExpA, 50, interval = "delta")[2,4]
pmaxEC50IMDExpB <- ED(drc.ExpB, 50, interval = "delta")[2,4]

ec50_IMD_ExpA <- as.numeric(ED(drc.ExpA, 50, interval = "delta")[2,])
ec50_IMD_ExpB <- as.numeric(ED(drc.ExpB, 50, interval = "delta")[2,])

ec50_EPX_ExpA <- as.numeric(ED(drc.ExpA, 50, interval = "delta")[1,])
ec50_EPX_ExpB <- as.numeric(ED(drc.ExpB, 50, interval = "delta")[1,])
```

```{r, warning=F, message=F}
#| fig-cap: Comparison of the EC$_{50}$ obtained in the different experiments.
#| label: fig-EC50compmix
#| fig-width: 6
#| fig-height: 4

df_EC50_comp <- data.frame(
  Molecule = c("EPX", "EPX", "IMD", "IMD"),
  Experiment = c("UNI Exp", "MIX Exp", "UNI Exp", "MIX Exp"),
  p = c(pEC50EPXExpA, pEC50EPXExpB, pEC50IMDExpA, pEC50IMDExpB),
  pmin = c(pminEC50EPXExpA, pminEC50EPXExpB, pminEC50IMDExpA, pminEC50IMDExpB),
  pmax = c(pmaxEC50EPXExpA, pmaxEC50EPXExpB, pmaxEC50IMDExpA, pmaxEC50IMDExpB)
) |>
  mutate(color = as.factor(paste0(Molecule, Experiment)))

df_EC50_comp$Experiment <- factor(df_EC50_comp$Experiment, levels = c("UNI Exp", "MIX Exp"))

p <- ggplot(
  data = df_EC50_comp,
  aes(
    x = Experiment,
    y = p,
    ymin = pmin,
    ymax = pmax,
    color = color
  )
) +
  geom_pointrange() +
  facet_wrap(~Molecule, scales = "free") +
  scale_color_manual(values = c(col_EPX_dark, col_EPX, col_IMD_dark, col_IMD)) +
  labs(
    y = "EC50",
    x = ""
  ) +
  theme_minimal() +
  theme(legend.position = "none")
p
```

```{r savecompec, include=F}
ggsave(
  filename = "Comp_expA_expB_ec50.png",
  plot = p,
  width = 6, height = 4,
  path = path_fig
)
ggsave(
  filename = "Comp_expA_expB_ec50.jpg",
  plot = p,
  width = 6, height = 4,
  path = path_fig
)
```

```{r, warning=F, message=F}
#| tbl-cap: Inter-experiment comparison of dose-response curves for EPX & IMD.
#| label: tbl-MIXcompdrc

df_drc_comp <- data.frame(
  UNI_exp = c(
    coef(drc.ExpA)[1], coef(drc.ExpA)[2],
    coef(drc.ExpA)[3], coef(drc.ExpA)[4],
    coef(drc.ExpA)[5], coef(drc.ExpA)[6]
  ),
  MIX_exp = c(
    coef(drc.ExpB)[1], coef(drc.ExpB)[2],
    coef(drc.ExpB)[3], coef(drc.ExpB)[4],
    coef(drc.ExpB)[5], coef(drc.ExpB)[6]
  )
) |>
  mutate(
    Ratio = UNI_exp / MIX_exp,
    Per_difference = (MIX_exp - UNI_exp) / UNI_exp * 100
  ) |>
  mutate(across(where(is.numeric), signif, 2))

df_drc_comp |> datatable(options = list(dom = "t"), class = "hover")

```

```{r statcompdrc, warning=F, message=F}
df_expA_repro_simple_IMD <- df_expA_repro |>
  filter(Molecule == "IMD") |>
  dplyr::select(Molecule, Dose, Nb_cocoons) |>
  mutate(Experiment = "UNI")

df_expA_repro_simple_EPX <- df_expA_repro |>
  filter(Molecule == "EPX") |>
  dplyr::select(Molecule, Dose, Nb_cocoons) |>
  mutate(Experiment = "UNI")

df_expB_repro_simple_IMD <- df_expB_repro_single |>
  filter(Molecule == "IMD") |>
  dplyr::select(Molecule, Dose, Nb_cocoons) |>
  mutate(Experiment = "MIX")

df_expB_repro_simple_EPX <- df_expB_repro_single |>
  filter(Molecule == "EPX") |>
  dplyr::select(Molecule, Dose, Nb_cocoons) |>
  mutate(Experiment = "MIX")

df_comp_IMD <- rbind(df_expA_repro_simple_IMD, df_expB_repro_simple_IMD)
df_comp_EPX <- rbind(df_expA_repro_simple_EPX, df_expB_repro_simple_EPX)

drc.compIMD <- drm(
  Nb_cocoons ~ Dose, Experiment,
  data = df_comp_IMD,
  type = "Poisson",
  fct = LL.4(
    names = c("slope", "Ymin", "Ymax", "EC50"),
    fixed = c(NA, 0, NA, NA)
  ),
  # Reproduction is expected to reach 0 for large concentrations
  pmodels = data.frame(Experiment, Experiment, Experiment)
)

drc.compEPX <- drm(
  Nb_cocoons ~ Dose, Experiment,
  data = df_comp_EPX,
  type = "Poisson",
  fct = LL.4(
    names = c("slope", "Ymin", "Ymax", "EC50"),
    fixed = c(NA, 0, NA, NA)
  ),
  # Reproduction is expected to reach 0 for large concentrations
  pmodels = data.frame(Experiment, Experiment, Experiment)
)

drc.compIMD_same_ec <- drm(
  Nb_cocoons ~ Dose, Experiment,
  data = df_comp_IMD,
  type = "Poisson",
  fct = LL.4(
    names = c("slope", "Ymin", "Ymax", "EC50"),
    fixed = c(NA, 0, NA, NA)
  ),
  # Reproduction is expected to reach 0 for large concentrations
  pmodels = data.frame(Experiment, Experiment, 1)
)

drc.compEPX_same_ec <- drm(
  Nb_cocoons ~ Dose, Experiment,
  data = df_comp_EPX,
  type = "Poisson",
  fct = LL.4(
    names = c("slope", "Ymin", "Ymax", "EC50"),
    fixed = c(NA, 0, NA, NA)
  ),
  # Reproduction is expected to reach 0 for large concentrations
  pmodels = data.frame(Experiment, Experiment, 1)
)

cat("For IMD :")
anova(drc.compIMD_same_ec, drc.compIMD, test = "F")
cat("\nFor EPX :")
anova(drc.compEPX_same_ec, drc.compEPX, test = "F")

```

Estimated EC$_{50}$ are not significatively different.

However, for the Jonker model, it is preferable to calibrate the model using the dose–response curves obtained during the same experiment as the one used to estimate the interaction parameter. This ensures consistency in experimental conditions and accounts for potential inter-experiment variability.
