```{r lib, include=F}
library(here)
source(file = here::here("functions/fun.R"))
f_load_libraries_colors()

palette <- colorRampPalette(c("#5E81AC", "#88C0D0"))
col_mix <- Nord_polar[4]
pal_ratio <- c("#88C0D0", col_mix, col_mix, col_mix, "#5E81AC",col_mix)


```

# Comparison of the single substances experiment with the mixture experiment ? {#sec-MIXSpringComp}

Because the single substances were tested again during the mixture experiment, the goal here is to compare the observed effects in both experiments and therefore to judge the reproducibility between the experiments. We then need to compare the dose-response curves for EPX & IMD obtained with the experiment A and the experiment B (Autumn 2024 vs. Spring 2025).

## Data importation

```{r datamix, message = F, warning=F}

# Value given to controls for plot
Val_Ctrl <- 1e-4
Label_Ctrl <- "0 (Ctrl)"

# Data EC50

df_repro_tot <- read_excel(here::here("data/Data_EC50.xlsx"), sheet = "Repro") |>
  mutate(
    Dose = as.numeric(Dose),
    Dose_plot = case_when(
      Dose == 0 ~ Val_Ctrl,
      !(Dose == 0) ~ Dose
    ),
    Dose_f = as.factor(round(Dose, 4)),
    w = w_tot / Nb_ind,
    L = w^(1 / 3),
  )
# Data for EPX
df_repro_EPX <- subset(df_repro_tot, Molec %in% c("Ctrl_2", "EPX")) |>
  mutate(Molecule = "EPX")
# We only keep earthworms still alive at then end of the experiment
ID_alive_EPX <- subset(df_repro_EPX, t == 28 & (!Status == "D"))$ID_cosm
df_repro_EPX_alive <- subset(df_repro_EPX, ID_cosm %in% ID_alive_EPX)

# Data for IMD
df_repro_IMD <- subset(df_repro_tot, Molec %in% c("Ctrl_1", "Ctrl_2", "IMD")) |>
  mutate(Molecule = "IMD")
# We only keep earthworms still alive at then end of the experiment
ID_alive_IMD <- subset(df_repro_IMD, t == 28 & (!Status == "D"))$ID_cosm
df_repro_IMD_alive <- subset(df_repro_IMD, ID_cosm %in% ID_alive_IMD)
df_repro <- rbind(df_repro_EPX, df_repro_IMD)
df_repro_alive <- rbind(df_repro_EPX_alive, df_repro_IMD_alive)

Control_IMD <- mean(subset(df_repro_IMD_alive, Dose == 0)$Nb_cocoons, na.rm = T)
Control_EPX <- mean(subset(df_repro_EPX_alive, Dose == 0)$Nb_cocoons, na.rm = T)

df_repro_EPX_alive <- df_repro_EPX_alive |>
  mutate(
    r_Nb_cocoons = Nb_cocoons / Control_EPX * 100
  )

df_repro_IMD_alive <- df_repro_IMD_alive |>
  mutate(
    r_Nb_cocoons = Nb_cocoons / Control_EPX * 100
  )

df_repro_alive <- df_repro_alive |>
  mutate(
    r_Nb_cocoons = case_when(
      Molecule == "IMD" ~ Nb_cocoons / Control_IMD,
      Molecule == "EPX" ~ Nb_cocoons / Control_EPX
    ) * 100
  )

df_repro_alive_mean <- df_repro_alive |>
  dplyr::group_by(Dose, Dose_plot, Molecule) |>
  dplyr::summarise(
    Nb_cocoons = mean(Nb_cocoons, na.rm = TRUE),
    r_Nb_cocoons = mean(r_Nb_cocoons, na.rm = TRUE),
    .groups = "drop"
  )

# Retriving EC50 
df_drc_param <- read.csv(here::here("data/DRC_parameters_cocoons_really_used.csv"))
EPX_EC50_drc <- df_drc_param$coef.drc.4.[3]
IMD_EC50_drc <- df_drc_param$coef.drc.4.[4]


# Mixture data

df_mix_ind <- read_excel(here::here("data/Data_Mix.xlsx"), sheet = "ReproSpring2025weight") |>
  mutate(
    Condition = paste0(Ratio, Line),
    Nb_rep = as.factor(Nb_rep),
    w = as.numeric(w),
    L = w^(1 / 3),
    TU_drc = Dose_IMD / IMD_EC50_drc + Dose_EPX / EPX_EC50_drc,
    Dose_IMD_plot = case_when(
      Dose_IMD == 0 ~ Val_Ctrl,
      !(Dose_IMD == 0) ~ Dose_IMD
    ),
    Dose_EPX_plot = case_when(
      Dose_EPX == 0 ~ Val_Ctrl,
      !(Dose_EPX == 0) ~ Dose_EPX
    ),
    TU_drc_plot = case_when(
      TU_drc == 0 ~ Val_Ctrl,
      !(TU_drc == 0) ~ TU_drc
    )
  )

df_mix_coc <- read_excel(here::here("data/Data_Mix.xlsx"), sheet = "ReproSpring2025coc") |>
  mutate(
    Condition = paste0(Ratio, Line),
    w_coc = w_coc_tot / (Nb_cocoons - Nb_cocoons_crushed),
    TU_drc = Dose_IMD / IMD_EC50_drc + Dose_EPX / EPX_EC50_drc,
    Dose_IMD_plot = case_when(
      Dose_IMD == 0 ~ Val_Ctrl,
      !(Dose_IMD == 0) ~ Dose_IMD
    ),
    Dose_EPX_plot = case_when(
      Dose_EPX == 0 ~ Val_Ctrl,
      !(Dose_EPX == 0) ~ Dose_EPX
    ),
    TU_drc_plot = case_when(
      TU_drc == 0 ~ Val_Ctrl,
      !(TU_drc == 0) ~ TU_drc
    )
  )

df_coc_mean_controls <- subset(df_mix_coc, Dose_IMD == 0 & Dose_EPX == 0) |> 
  aggregate(Nb_cocoons ~ Lot, FUN = mean)

Mean_coc_controls <- mean(subset(df_mix_coc, Dose_IMD == 0 & Dose_EPX == 0)$Nb_cocoons)

#Shift <- 1e-6

df_mix_coc <- df_mix_coc |> 
  mutate(
    r_Nb_cocoons = Nb_cocoons/Mean_coc_controls
    )

df_mix_coc <- df_mix_coc |>
  mutate(
    Trans_r_Nb_cocoons = sqrt(r_Nb_cocoons)
    )

df_conc_mix <- df_mix_coc |> 
  dplyr::select(Condition, Dose_IMD, Dose_EPX)%>%
  distinct(Condition, .keep_all = TRUE)

df_mix_cocsize <- read_excel(here::here("data/Data_Mix.xlsx"), sheet="ReproSpring2025cocsize") |> 
  mutate(
    Condition = paste0(Ratio, Line),
    v_coc = 4/3*pi*Coc_height*Coc_width^2,
  ) |> 
  left_join(df_conc_mix, by = "Condition") |> 
  mutate(TU_drc = Dose_IMD / IMD_EC50_drc + Dose_EPX/EPX_EC50_drc)

df_mix_cocsize_cosm <- df_mix_cocsize |> 
  aggregate(v_coc ~ Ratio + Line + Nb_rep + TU_drc, FUN = mean) |> 
  mutate(Condition = paste0(Ratio, Line))

df_mix_coc <- df_mix_coc |> 
  full_join(df_mix_cocsize_cosm, by = c("Condition", "Nb_rep", "Ratio", "Line", "TU_drc")) |> 
  mutate(
    Id_Cond = w_coc/v_coc
    )

df_mix_coc_mean <- df_mix_coc |>
  dplyr::group_by(Condition, Dose_IMD, Dose_EPX, Dose_IMD_plot, Dose_EPX_plot, Ratio, Line, TU_drc) |>
  dplyr::summarise(
    Nb_cocoons = mean(Nb_cocoons, na.rm = TRUE),
    w_coc = mean(w_coc, na.rm = TRUE),
    v_coc = mean(v_coc, na.rm = TRUE),
    r_Nb_cocoons = mean(r_Nb_cocoons, na.rm = TRUE),
    Trans_r_Nb_cocoons = mean(Trans_r_Nb_cocoons, na.rm = TRUE),
    #Nb_cocoons_normalized = mean(Nb_cocoons_normalized, na.rm = TRUE),
    .groups = "drop"
  )

df_mix_coc_IMD_mean <- subset(df_mix_coc_mean, Dose_EPX ==0)
df_mix_coc_EPX_mean <- subset(df_mix_coc_mean, Dose_IMD ==0)



df_mix_coc_sd <- df_mix_coc |>
  dplyr::group_by(Condition, Dose_IMD, Dose_EPX, Dose_IMD_plot, Dose_EPX_plot, Ratio, Line, TU_drc) |>
  dplyr::summarise(
    Nb_cocoons = sd(Nb_cocoons, na.rm = TRUE),
    w_coc = sd(w_coc, na.rm = TRUE),
    v_coc = sd(v_coc, na.rm = TRUE),
    r_Nb_cocoons = sd(r_Nb_cocoons, na.rm = TRUE),
    Trans_r_Nb_cocoons = sd(Trans_r_Nb_cocoons, na.rm = TRUE),
    #Nb_cocoons_normalized = mean(Nb_cocoons_normalized, na.rm = TRUE),
    .groups = "drop"
  )

df_mix_coc_cv <- df_mix_coc_mean |>
  dplyr::rename_with(~ paste0(.x, "_mean"), -c(Condition, Dose_IMD, Dose_EPX, Dose_IMD_plot, Dose_EPX_plot, Ratio, Line, TU_drc)) |>
  dplyr::left_join(
    df_mix_coc_sd |> 
      dplyr::rename_with(~ paste0(.x, "_sd"), -c(Condition, Dose_IMD, Dose_EPX, Dose_IMD_plot, Dose_EPX_plot, Ratio, Line, TU_drc)),
    by = c("Condition", "Dose_IMD", "Dose_EPX", "Dose_IMD_plot", "Dose_EPX_plot", "Ratio", "Line", "TU_drc")
  ) |>
  dplyr::mutate(
    CV_Nb_cocoons = Nb_cocoons_sd / Nb_cocoons_mean,
    CV_w_coc = w_coc_sd / w_coc_mean,
    CV_v_coc = v_coc_sd / v_coc_mean,
    CV_r_Nb_cocoons = r_Nb_cocoons_sd / r_Nb_cocoons_mean,
    CV_Trans_r_Nb_cocoons = Trans_r_Nb_cocoons_sd / Trans_r_Nb_cocoons_mean
  )

# mean(df_mix_coc_cv$CV_Nb_cocoons, na.rm=TRUE)
# min(df_mix_coc_cv$CV_Nb_cocoons, na.rm=TRUE)
# max(df_mix_coc_cv$CV_Nb_cocoons, na.rm=TRUE)
# median(df_mix_coc_cv$CV_Nb_cocoons, na.rm=TRUE)

```

## Initial state of the mixture experiment (experiment B)

We can first take a look at the initial weights of individuals from the mixture experiment (@fig-init).

```{r D0, warning=F, message=F}
#| fig-cap: Initial weights of earthworms according to batches. 
#| label: fig-init
#| fig-width: 10
#| fig-height: 4

pal_lot <- c(Nord_frost[3], Nord_polar[4])

# Weights at t=0
p <- ggplot(
  data=subset(df_mix_ind,t==0), 
  aes(
    x=Condition, 
    y=w
    )
  )+

  geom_boxplot(
    alpha=0.2,
    color = Nord_polar[1]
    )+
  geom_dotplot(
    aes(
    color=Lot, 
    fill=Lot
    ),
    binaxis='y', 
    stackdir='center', 
    dotsize=0.5, 
    alpha=0.7
    )+
  
  scale_color_manual(values=pal_lot)+
  scale_fill_manual(values=pal_lot)+

  labs(x="Condition", y="Weight (mg)")+
  

  theme_classic(12)+
  theme(
    #legend.position = "none", 
    legend.title=element_text(size=sizetitle-2,face="bold"),
    legend.text = element_text(size=sizetitle-2,face="plain"),
    
    title=element_text(size=sizetitle, face="bold"), 
    
    axis.title.x = element_blank(),
    axis.title.y = element_text(size=sizetitle,face="plain"),
    
    #axis.text.x = element_blank(),
    axis.line.x=element_blank(),
    axis.ticks.x=element_blank(),
    
    strip.background = element_rect(
      color="black", 
      fill="grey95", 
      size=0, 
      linetype="solid"
      )
    )
p
```

```{r, include=F}
ggsave(
  filename="Mix_initial_weights_Spring.png",
  plot=p, 
  width=8, 
  height = 4, 
  path=here::here("fig/Mixture")
  )
ggsave(
  filename="Mix_initial_weights_Spring.jpg",
  plot=p, 
  width=8, 
  height = 4, 
  path=here::here("fig/Mixture")
  )
ggsave(
  filename="Mix_initial_weights_Spring.svg",
  plot=p, 
  width=8, 
  height = 4, 
  path=here::here("fig/Mixture")
  )
```

## Comparison of the controls

```{r, message=F, warning=F}
#| fig-cap: Comparaison of the controls obtained in the mixture experiment (dark blues) with the results of the experiment A (blues). 
#| label: fig-drcIMDEPXcompctrl
#| fig-width: 4
#| fig-height: 5

df_mix_coc_ctrl <- subset(df_mix_coc, Ratio == "N") |> 
  dplyr::select(Nb_cocoons) |> 
  mutate(Experiment = "Experiment B")

df_repro_alive_ctrl <- subset(df_repro_IMD_alive, Dose == 0) |> 
  dplyr::select(Nb_cocoons, Lot) |> 
  mutate(Experiment = case_when(
    Lot == "A" ~ "Experiment A\nSpring 2024",
    Lot == "B" ~ "Experiment A\nSummer 2024"
    )
    ) |> 
  dplyr::select(Nb_cocoons, Experiment)

df_controls <- rbind(df_repro_alive_ctrl,df_mix_coc_ctrl) 
df_controls$Experiment <- factor(df_controls$Experiment, levels = c("Experiment A\nSpring 2024", "Experiment A\nSummer 2024", "Experiment B"))

p <- ggplot(
  data = df_controls,
  aes(
    x = Experiment,
    y = Nb_cocoons
  )
)+
  geom_dotplot(
    binaxis='y', 
    stackdir='center', 
    dotsize=0.8, 
    alpha=0.7,
    color = Nord_aurora[4],
    fill = Nord_aurora[4]
    )+
  labs(
    x = "",
    y = "Number of cocoons produced per cosm (#)"
  )+
  theme_minimal()+
  theme(
    axis.text.x = element_text(angle=45, hjust=1)
  )

p
```

```{r, message=F, warning=F}
#| code-fold: show

pairwise.wilcox.test(df_controls$Nb_cocoons, df_controls$Experiment, p.adjust.method = "bonferroni", exact=F)

#wilcox.test(Nb_cocoons ~ Experiment, data = df_controls)

lm.controls <- lm(Nb_cocoons ~ Experiment, data = df_controls)
lsmeans(lm.controls,pairwise~Experiment,adjust='bonferroni')

#t.test(Nb_cocoons ~ Experiment, data = df_controls, var.equal = FALSE)
```

The controls of the two different experiments are not significatively different.

## Dose-response curves

### Experiment A - Dose-response curves

We then get the dose-response curves of the single substances from experiment A and experiment B.

```{r drcsingle, warning=F, message=F}

Dose_x <- expand.grid(
  exp(
    seq(
      log(0.0001),log(5000),
      by=(log(5000)-log(0.0001))/100
    )
  )
)

drc.ExpA<- drm(
  Nb_cocoons~Dose, Molecule, 
  data = df_repro_alive,
  type="Poisson",
  fct=LL.4(
    names = c("slope", "Ymin", "Ymax", "EC50"),
    fixed = c(NA, 0, NA, NA)
  ), 
  # Reproduction is expected to reach 0 for large concentrations
  pmodels=data.frame(Molecule, Molecule, Molecule)
)

CI.ExpA <- data.frame(
  Dose = c(Dose_x$Var1, Dose_x$Var1),
  Molecule = c(rep("EPX", length(Dose_x$Var1)), rep("IMD", length(Dose_x$Var1)))
)

pm.ExpA <- predict(drc.ExpA, newdata=CI.ExpA, interval="confidence")
CI.ExpA$p <- pm.ExpA[,1]
CI.ExpA$pmin <- pm.ExpA[,2]
CI.ExpA$pmax <- pm.ExpA[,3]

EPX_EC50_ExpA <- coef(drc.ExpA)[5]
IMD_EC50_ExpA <- coef(drc.ExpA)[6]

summary(drc.ExpA)

```

### Experiment B - Dose-response curves

```{r drcmix, warning=F, message=F}

df_mix_coc_IMD <- subset(df_mix_coc, Ratio %in% c("I", "N")) |>
  mutate(
    Dose = Dose_IMD,
    Dose_plot = Dose_IMD_plot,
    Molecule = "IMD"
  ) |>
  dplyr::select(Dose, Dose_plot, Nb_cocoons, Molecule, r_Nb_cocoons)

df_mix_coc_EPX <- subset(df_mix_coc, Ratio %in% c("E", "N")) |>
  mutate(
    Dose = Dose_EPX,
    Dose_plot = Dose_EPX_plot,
    Molecule = "EPX"
  ) |>
  dplyr::select(Dose, Dose_plot, Nb_cocoons, Molecule, r_Nb_cocoons)

df_mix_coc_single <- rbind(df_mix_coc_IMD, df_mix_coc_EPX)

df_mix_coc_single_mean <- df_mix_coc_single |>
  aggregate(Nb_cocoons ~ Dose + Dose_plot + Molecule, mean)

# Common Ymax and slope
drc.ExpB <- drm(
  Nb_cocoons ~ Dose, Molecule,
  data = df_mix_coc_single,
  type = "Poisson",
  fct = LL.4(
    names = c("slope", "Ymin", "Ymax", "EC50"),
    fixed = c(NA, 0, NA, NA)
  ),
  # Reproduction is expected to reach 0 for large concentrations
  pmodels = data.frame(Molecule, Molecule, Molecule)
)

CI.ExpB <- data.frame(
  Dose = c(Dose_x$Var1, Dose_x$Var1),
  Molecule = c(rep("EPX", length(Dose_x$Var1)), rep("IMD", length(Dose_x$Var1)))
)

pm.ExpB <- predict(drc.ExpB, newdata = CI.ExpB, interval = "confidence")
CI.ExpB$p <- pm.ExpB[, 1]
CI.ExpB$pmin <- pm.ExpB[, 2]
CI.ExpB$pmax <- pm.ExpB[, 3]

EPX_EC50_ExpB <- coef(drc.ExpB)[3]
IMD_EC50_ExpB <- coef(drc.ExpB)[4]

summary(drc.ExpB)

```

## Comparison of the two experiments for single substances

```{r, warning=F, message=F}
#| fig-cap: Comparaison of the results obtained in the experiment B (dark blues) with the results of Experiment A (blues). The line represents the dose-response curves obtained for the number of cocoons produced. Crosses correspond to the number of cocoons produced by one cosm and the bold points represents the mean per dose.
#| label: fig-drcIMDEPXcomp
#| fig-width: 8
#| fig-height: 4

x <- seq(0.0001, 5000, 0.01)
line_width <- 1.2

darkening <- 0.2
col_IMD_dark <- colorspace::darken(col_IMD, darkening)
col_EPX_dark <- colorspace::darken(col_EPX, darkening)

p_E <- ggplot() +
  geom_ribbon(
    data = subset(CI.ExpB, Molecule == "EPX"),
    aes(
      x = Dose,
      y = p,
      ymin = pmin,
      ymax = pmax
    ),
    alpha = 0.2,
    fill = col_EPX_dark,
    # color = col_IMD
  ) +
  geom_ribbon(
    data = subset(CI.ExpA, Molecule == "EPX"),
    aes(
      x = Dose,
      y = p,
      ymin = pmin,
      ymax = pmax
    ),
    alpha = 0.2,
    fill = col_EPX,
    # color = col_IMD
  ) +
  geom_line(
    data = subset(CI.ExpB, Molecule == "EPX"),
    aes(
      x = Dose,
      y = p
    ),
    color = col_EPX_dark,
    linewidth = line_width
  ) +
  geom_line(
    data = subset(CI.ExpA, Molecule == "EPX"),
    aes(
      x = Dose,
      y = p
    ),
    color = col_EPX,
    linewidth = line_width
  ) +
  geom_point(
    data = df_mix_coc_EPX,
    aes(
      x = Dose_plot,
      y = Nb_cocoons
    ),
    color = col_EPX_dark,
    alpha = 0.6,
    shape = 4
  ) +
  geom_point(
    data = df_repro_EPX_alive,
    aes(
      x = Dose_plot, 
      y = Nb_cocoons
      ),
    color = col_EPX,
    alpha = 0.5,
    shape = 4
  ) +
  geom_point(
    data = df_mix_coc_EPX_mean,
    aes(
      x = Dose_EPX_plot, 
      y = Nb_cocoons
      ),
    color = col_EPX_dark,
    size = 3
  ) +
  geom_point(
    data = subset(df_repro_alive_mean, Molecule == "EPX"),
    aes(
      x = Dose_plot, 
      y = Nb_cocoons
      ),
    color = col_EPX,
    size = 3
  ) +
  annotate(
    geom = "text",
    x = 1500,
    y = 2,
    label = "E",
    fontface = "bold"
  ) +
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100), # inclure la valeur fictive
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100")
  ) +
  labs(
    x = "Concentration of EPX (mg/kg)",
    y = "Number of cocoons produced per cosm (#)"
  ) +
  theme_bw()

p_I <- ggplot() +
  geom_ribbon(
    data = subset(CI.ExpB, Molecule == "IMD"),
    aes(
      x = Dose,
      y = p,
      ymin = pmin,
      ymax = pmax
    ),
    alpha = 0.2,
    fill = col_IMD_dark,
    # color = col_IMD
  ) +
  geom_ribbon(
    data = subset(CI.ExpA, Molecule == "IMD"),
    aes(
      x = Dose,
      y = p,
      ymin = pmin,
      ymax = pmax
    ),
    alpha = 0.2,
    fill = col_IMD,
    # color = col_IMD
  ) +
  geom_line(
    data = subset(CI.ExpB, Molecule == "IMD"),
    aes(
      x = Dose,
      y = p
    ),
    color = col_IMD_dark,
    linewidth = line_width
  ) +
  geom_line(
    data = subset(CI.ExpA, Molecule == "IMD"),
    aes(
      x = Dose,
      y = p
    ),
    color = col_IMD,
    linewidth = line_width
  ) +
  geom_point(
    data = df_mix_coc_IMD,
    aes(
      x = Dose_plot,
      y = Nb_cocoons
    ),
    color = col_IMD_dark,
    alpha = 0.6,
    shape = 4
  ) +
  geom_point(
    data = df_repro_IMD_alive,
    aes(
      x = Dose_plot,
      y = Nb_cocoons
    ),
    color = col_IMD,
    alpha = 0.5,
    shape = 4
  ) +
  geom_point(
    data = df_mix_coc_IMD_mean,
    aes(
      x = Dose_IMD_plot,
      y = Nb_cocoons
    ),
    color = col_IMD_dark,
    size = 3
  ) +
  geom_point(
    data = subset(df_repro_alive_mean, Molecule == "IMD"),
    aes(
      x = Dose_plot,
      y = Nb_cocoons
    ),
    color = col_IMD,
    size = 3
  ) +
  annotate(
    geom = "text",
    x = 1500,
    y = 2,
    label = "I",
    fontface = "bold"
  ) +
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100), # inclure la valeur fictive
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100")
  ) +
  labs(
    x = "Concentration of IMD (mg/kg)",
    y = "Number of cocoons produced per cosm (#)"
  ) +
  theme_bw()

p <- p_E + p_I
p
```

```{r, include=F}
ggsave(
  filename="Mix_spring_cocoons_compEC50.png", 
  plot=p, 
  width=8, height = 4, 
  path=here::here("fig/Mixture")
  )
ggsave(
  filename="Mix_spring_cocoons_compEC50.jpg", 
  plot=p, 
  width=8, height = 4, 
  path=here::here("fig/Mixture")
  )
# ggsave(
#   filename="Mix_spring_cocoons_compEC50.svg", 
#   plot=p, 
#   width=6, height = 6, 
#   path=here::here("fig/Mixture")
#   )
```

```{r, results="hide", warning=F, message = F}
pEC50EPXExpA <- ED(drc.ExpA, 50, interval = "delta")[1,1]
pEC50EPXExpB <- ED(drc.ExpB, 50, interval = "delta")[1,1]
pEC50IMDExpA <- ED(drc.ExpA, 50, interval = "delta")[2,1]
pEC50IMDExpB <- ED(drc.ExpB, 50, interval = "delta")[2,1]

pminEC50EPXExpA <- ED(drc.ExpA, 50, interval = "delta")[1,3]
pminEC50EPXExpB <- ED(drc.ExpB, 50, interval = "delta")[1,3]
pminEC50IMDExpA <- ED(drc.ExpA, 50, interval = "delta")[2,3]
pminEC50IMDExpB <- ED(drc.ExpB, 50, interval = "delta")[2,3]

pmaxEC50EPXExpA <- ED(drc.ExpA, 50, interval = "delta")[1,4]
pmaxEC50EPXExpB <- ED(drc.ExpB, 50, interval = "delta")[1,4]
pmaxEC50IMDExpA <- ED(drc.ExpA, 50, interval = "delta")[2,4]
pmaxEC50IMDExpB <- ED(drc.ExpB, 50, interval = "delta")[2,4]

ec50_IMD_ExpA <- as.numeric(ED(drc.ExpA, 50, interval = "delta")[2,])
ec50_IMD_ExpB <- as.numeric(ED(drc.ExpB, 50, interval = "delta")[2,])

ec50_EPX_ExpA <- as.numeric(ED(drc.ExpA, 50, interval = "delta")[1,])
ec50_EPX_ExpB <- as.numeric(ED(drc.ExpB, 50, interval = "delta")[1,])
```

```{r, warning=F, message=F}
#| fig-cap: Comparison of the EC$_{50}$ obtained in the different experiments.
#| label: fig-EC50compmix
#| fig-width: 6
#| fig-height: 4

df_EC50_comp <- data.frame(
  Molecule = c("EPX", "EPX", "IMD", "IMD"),
  Experiment = c("ExpA", "ExpB", "ExpA", "ExpB"),
  p = c(pEC50EPXExpA, pEC50EPXExpB, pEC50IMDExpA, pEC50IMDExpB),
  pmin = c(pminEC50EPXExpA, pminEC50EPXExpB, pminEC50IMDExpA, pminEC50IMDExpB),
  pmax = c(pmaxEC50EPXExpA, pmaxEC50EPXExpB, pmaxEC50IMDExpA, pmaxEC50IMDExpB)
) |>
  mutate(color = as.factor(paste0(Molecule, Experiment)))

df_EC50_comp$Experiment <- factor(df_EC50_comp$Experiment, levels = c("ExpA", "ExpB"))

p <- ggplot(
  data = df_EC50_comp,
  aes(
    x = Experiment,
    y = p,
    ymin = pmin,
    ymax = pmax,
    color = color
  )
) +
  geom_pointrange() +
  facet_wrap(~Molecule, scales = "free") +
  scale_color_manual(values = c(col_EPX_dark, col_EPX, col_IMD_dark, col_IMD)) +
  labs(
    y = "EC50",
    x = ""
  ) +
  theme_minimal() +
  theme(legend.position = "none")
p
```

```{r, warning=F, message=F}
#| tbl-cap: Inter-experiment comparison of dose-response curves for EPX & IMD.
#| label: tbl-MIXcompdrc

df_drc_comp <- data.frame(
  # Parameter = c("Ymax", "Slope", "EC50(EPX)", "EC50(IMD)"),
  ExpA = c(
    coef(drc.ExpA)[1], coef(drc.ExpA)[2],
    coef(drc.ExpA)[3], coef(drc.ExpA)[4],
    coef(drc.ExpA)[5], coef(drc.ExpA)[6]
    ),
  ExpB = c(
    coef(drc.ExpB)[1], coef(drc.ExpB)[2],
    coef(drc.ExpB)[3], coef(drc.ExpB)[4],
    coef(drc.ExpB)[5], coef(drc.ExpB)[6]
    )
  ) |>
  mutate(
    Ratio = ExpA / ExpB,
    Per_difference = (ExpB - ExpA) / ExpA * 100
  ) |>
  mutate(across(where(is.numeric), signif, 2))

df_drc_comp |> datatable(options = list(dom = "t"), class = "hover")

```

```{r, warning=F, message=F}

df_repro_alive_simple_IMD <- df_repro_alive |> 
  filter(Molecule == "IMD") |> 
  dplyr::select(Molecule, Dose, Nb_cocoons) |> 
  mutate(Experiment = "A")

df_repro_alive_simple_EPX<- df_repro_alive |> 
  filter(Molecule == "EPX") |> 
  dplyr::select(Molecule, Dose, Nb_cocoons) |> 
  mutate(Experiment = "A")

df_mix_coc_single_IMD <- df_mix_coc_single |> 
  filter(Molecule == "IMD") |> 
  dplyr::select(Molecule, Dose, Nb_cocoons) |> 
  mutate(Experiment = "B")

df_mix_coc_single_EPX <- df_mix_coc_single |> 
  filter(Molecule == "EPX") |> 
  dplyr::select(Molecule, Dose, Nb_cocoons) |> 
  mutate(Experiment = "B")

df_comp_IMD <- rbind(df_repro_alive_simple_IMD, df_mix_coc_single_IMD)
df_comp_EPX <- rbind(df_repro_alive_simple_EPX, df_mix_coc_single_EPX)

drc.compIMD<- drm(
  Nb_cocoons~Dose, Experiment, 
  data = df_comp_IMD,
  type="Poisson",
  fct=LL.4(
    names = c("slope", "Ymin", "Ymax", "EC50"),
    fixed = c(NA, 0, NA, NA)
  ), 
  # Reproduction is expected to reach 0 for large concentrations
  pmodels=data.frame(Experiment, Experiment, Experiment)
)

drc.compEPX<- drm(
  Nb_cocoons~Dose, Experiment, 
  data = df_comp_EPX,
  type="Poisson",
  fct=LL.4(
    names = c("slope", "Ymin", "Ymax", "EC50"),
    fixed = c(NA, 0, NA, NA)
  ), 
  # Reproduction is expected to reach 0 for large concentrations
  pmodels=data.frame(Experiment, Experiment, Experiment)
)

drc.compIMD_same_ec<- drm(
  Nb_cocoons~Dose, Experiment, 
  data = df_comp_IMD,
  type="Poisson",
  fct=LL.4(
    names = c("slope", "Ymin", "Ymax", "EC50"),
    fixed = c(NA, 0, NA, NA)
  ), 
  # Reproduction is expected to reach 0 for large concentrations
  pmodels=data.frame(Experiment, Experiment, 1)
)

drc.compEPX_same_ec<- drm(
  Nb_cocoons~Dose, Experiment, 
  data = df_comp_EPX,
  type="Poisson",
  fct=LL.4(
    names = c("slope", "Ymin", "Ymax", "EC50"),
    fixed = c(NA, 0, NA, NA)
  ), 
  # Reproduction is expected to reach 0 for large concentrations
  pmodels=data.frame(Experiment, Experiment, 1)
)

anova(drc.compIMD_same_ec, drc.compIMD, test = "F")
anova(drc.compEPX_same_ec, drc.compEPX, test = "F")

```

Estimated EC$_{50}$ are not significatively different.

However, for the Jonker model, it is preferable to calibrate the model using the dose–response curves obtained during the same experiment as the one used to estimate the interaction parameter. This ensures consistency in experimental conditions and accounts for potential inter-experiment variability.
