```{r lib, include=F}
library(here)
source(file = here::here("functions/fun.R"))
f_load_libraries_colors()

palette <- colorRampPalette(c("#5E81AC", "#88C0D0"))
col_mix <- Nord_polar[4]
pal_ratio <- c("#88C0D0", col_mix, col_mix, col_mix, "#5E81AC",col_mix)


```

# Results of the mixture experiments : Is there an interaction between the two active substances ? {#sec-MIXSpringJonker}

## Data importation

```{r datamix, message = F, warning=F}

# Value given to controls for plot
Val_Ctrl <- 1e-4
Label_Ctrl <- "0 (Ctrl)"

# Data EC50

df_repro_tot <- read_excel(here::here("data/Data_EC50.xlsx"), sheet = "Repro") |>
  mutate(
    Dose = as.numeric(Dose),
    Dose_plot = case_when(
      Dose == 0 ~ Val_Ctrl,
      !(Dose == 0) ~ Dose
    ),
    Dose_f = as.factor(round(Dose, 4)),
    w = w_tot / Nb_ind,
    L = w^(1 / 3),
  )
# Data for EPX
df_repro_EPX <- subset(df_repro_tot, Molec %in% c("Ctrl_2", "EPX")) |>
  mutate(Molecule = "EPX")
# We only keep earthworms still alive at then end of the experiment
ID_alive_EPX <- subset(df_repro_EPX, t == 28 & (!Status == "D"))$ID_cosm
df_repro_EPX_alive <- subset(df_repro_EPX, ID_cosm %in% ID_alive_EPX)

# Data for IMD
df_repro_IMD <- subset(df_repro_tot, Molec %in% c("Ctrl_1", "Ctrl_2", "IMD")) |>
  mutate(Molecule = "IMD")
# We only keep earthworms still alive at then end of the experiment
ID_alive_IMD <- subset(df_repro_IMD, t == 28 & (!Status == "D"))$ID_cosm
df_repro_IMD_alive <- subset(df_repro_IMD, ID_cosm %in% ID_alive_IMD)
df_repro <- rbind(df_repro_EPX, df_repro_IMD)
df_repro_alive <- rbind(df_repro_EPX_alive, df_repro_IMD_alive)

Control_IMD <- mean(subset(df_repro_IMD_alive, Dose == 0)$Nb_cocoons, na.rm = T)
Control_EPX <- mean(subset(df_repro_EPX_alive, Dose == 0)$Nb_cocoons, na.rm = T)

df_repro_EPX_alive <- df_repro_EPX_alive |>
  mutate(
    r_Nb_cocoons = Nb_cocoons / Control_EPX * 100
  )

df_repro_IMD_alive <- df_repro_IMD_alive |>
  mutate(
    r_Nb_cocoons = Nb_cocoons / Control_EPX * 100
  )

df_repro_alive <- df_repro_alive |>
  mutate(
    r_Nb_cocoons = case_when(
      Molecule == "IMD" ~ Nb_cocoons / Control_IMD,
      Molecule == "EPX" ~ Nb_cocoons / Control_EPX
    ) * 100
  )

df_repro_alive_mean <- df_repro_alive |>
  dplyr::group_by(Dose, Dose_plot, Molecule) |>
  dplyr::summarise(
    Nb_cocoons = mean(Nb_cocoons, na.rm = TRUE),
    r_Nb_cocoons = mean(r_Nb_cocoons, na.rm = TRUE),
    .groups = "drop"
  )

# Retriving EC50 
df_drc_param <- read.csv(here::here("data/DRC_parameters_cocoons_really_used.csv"))
EPX_EC50_drc <- df_drc_param$coef.drc.4.[3]
IMD_EC50_drc <- df_drc_param$coef.drc.4.[4]


# Mixture data

df_mix_ind <- read_excel(here::here("data/Data_Mix.xlsx"), sheet = "ReproSpring2025weight") |>
  mutate(
    Condition = paste0(Ratio, Line),
    Nb_rep = as.factor(Nb_rep),
    w = as.numeric(w),
    L = w^(1 / 3),
    TU_drc = Dose_IMD / IMD_EC50_drc + Dose_EPX / EPX_EC50_drc,
    Dose_IMD_plot = case_when(
      Dose_IMD == 0 ~ Val_Ctrl,
      !(Dose_IMD == 0) ~ Dose_IMD
    ),
    Dose_EPX_plot = case_when(
      Dose_EPX == 0 ~ Val_Ctrl,
      !(Dose_EPX == 0) ~ Dose_EPX
    ),
    TU_drc_plot = case_when(
      TU_drc == 0 ~ Val_Ctrl,
      !(TU_drc == 0) ~ TU_drc
    )
  )

df_mix_coc <- read_excel(here::here("data/Data_Mix.xlsx"), sheet = "ReproSpring2025coc") |>
  mutate(
    Condition = paste0(Ratio, Line),
    w_coc = w_coc_tot / (Nb_cocoons - Nb_cocoons_crushed),
    TU_drc = Dose_IMD / IMD_EC50_drc + Dose_EPX / EPX_EC50_drc,
    Dose_IMD_plot = case_when(
      Dose_IMD == 0 ~ Val_Ctrl,
      !(Dose_IMD == 0) ~ Dose_IMD
    ),
    Dose_EPX_plot = case_when(
      Dose_EPX == 0 ~ Val_Ctrl,
      !(Dose_EPX == 0) ~ Dose_EPX
    ),
    TU_drc_plot = case_when(
      TU_drc == 0 ~ Val_Ctrl,
      !(TU_drc == 0) ~ TU_drc
    )
  )

df_coc_mean_controls <- subset(df_mix_coc, Dose_IMD == 0 & Dose_EPX == 0) |> 
  aggregate(Nb_cocoons ~ Lot, FUN = mean)

Mean_coc_controls <- mean(subset(df_mix_coc, Dose_IMD == 0 & Dose_EPX == 0)$Nb_cocoons)

#Shift <- 1e-6

df_mix_coc <- df_mix_coc |> 
  mutate(
    r_Nb_cocoons = Nb_cocoons/Mean_coc_controls
    )

df_mix_coc <- df_mix_coc |>
  mutate(
    Trans_r_Nb_cocoons = sqrt(r_Nb_cocoons)
    )

df_conc_mix <- df_mix_coc |> 
  dplyr::select(Condition, Dose_IMD, Dose_EPX)%>%
  distinct(Condition, .keep_all = TRUE)

df_mix_cocsize <- read_excel(here::here("data/Data_Mix.xlsx"), sheet="ReproSpring2025cocsize") |> 
  mutate(
    Condition = paste0(Ratio, Line),
    v_coc = 4/3*pi*Coc_height*Coc_width^2,
  ) |> 
  left_join(df_conc_mix, by = "Condition") |> 
  mutate(TU_drc = Dose_IMD / IMD_EC50_drc + Dose_EPX/EPX_EC50_drc)

df_mix_cocsize_cosm <- df_mix_cocsize |> 
  aggregate(v_coc ~ Ratio + Line + Nb_rep + TU_drc, FUN = mean) |> 
  mutate(Condition = paste0(Ratio, Line))

df_mix_coc <- df_mix_coc |> 
  full_join(df_mix_cocsize_cosm, by = c("Condition", "Nb_rep", "Ratio", "Line", "TU_drc")) |> 
  mutate(
    Id_Cond = w_coc/v_coc
    )

df_mix_coc_mean <- df_mix_coc |>
  dplyr::group_by(Condition, Dose_IMD, Dose_EPX, Dose_IMD_plot, Dose_EPX_plot, Ratio, Line, TU_drc) |>
  dplyr::summarise(
    Nb_cocoons = mean(Nb_cocoons, na.rm = TRUE),
    w_coc = mean(w_coc, na.rm = TRUE),
    v_coc = mean(v_coc, na.rm = TRUE),
    r_Nb_cocoons = mean(r_Nb_cocoons, na.rm = TRUE),
    Trans_r_Nb_cocoons = mean(Trans_r_Nb_cocoons, na.rm = TRUE),
    #Nb_cocoons_normalized = mean(Nb_cocoons_normalized, na.rm = TRUE),
    .groups = "drop"
  )

df_mix_coc_IMD_mean <- subset(df_mix_coc_mean, Dose_EPX ==0)
df_mix_coc_EPX_mean <- subset(df_mix_coc_mean, Dose_IMD ==0)



df_mix_coc_sd <- df_mix_coc |>
  dplyr::group_by(Condition, Dose_IMD, Dose_EPX, Dose_IMD_plot, Dose_EPX_plot, Ratio, Line, TU_drc) |>
  dplyr::summarise(
    Nb_cocoons = sd(Nb_cocoons, na.rm = TRUE),
    w_coc = sd(w_coc, na.rm = TRUE),
    v_coc = sd(v_coc, na.rm = TRUE),
    r_Nb_cocoons = sd(r_Nb_cocoons, na.rm = TRUE),
    Trans_r_Nb_cocoons = sd(Trans_r_Nb_cocoons, na.rm = TRUE),
    #Nb_cocoons_normalized = mean(Nb_cocoons_normalized, na.rm = TRUE),
    .groups = "drop"
  )

df_mix_coc_cv <- df_mix_coc_mean |>
  dplyr::rename_with(~ paste0(.x, "_mean"), -c(Condition, Dose_IMD, Dose_EPX, Dose_IMD_plot, Dose_EPX_plot, Ratio, Line, TU_drc)) |>
  dplyr::left_join(
    df_mix_coc_sd |> 
      dplyr::rename_with(~ paste0(.x, "_sd"), -c(Condition, Dose_IMD, Dose_EPX, Dose_IMD_plot, Dose_EPX_plot, Ratio, Line, TU_drc)),
    by = c("Condition", "Dose_IMD", "Dose_EPX", "Dose_IMD_plot", "Dose_EPX_plot", "Ratio", "Line", "TU_drc")
  ) |>
  dplyr::mutate(
    CV_Nb_cocoons = Nb_cocoons_sd / Nb_cocoons_mean,
    CV_w_coc = w_coc_sd / w_coc_mean,
    CV_v_coc = v_coc_sd / v_coc_mean,
    CV_r_Nb_cocoons = r_Nb_cocoons_sd / r_Nb_cocoons_mean,
    CV_Trans_r_Nb_cocoons = Trans_r_Nb_cocoons_sd / Trans_r_Nb_cocoons_mean
  )

# mean(df_mix_coc_cv$CV_Nb_cocoons, na.rm=TRUE)
# min(df_mix_coc_cv$CV_Nb_cocoons, na.rm=TRUE)
# max(df_mix_coc_cv$CV_Nb_cocoons, na.rm=TRUE)
# median(df_mix_coc_cv$CV_Nb_cocoons, na.rm=TRUE)

```

## Initial state

We can first take a look at the initial weights of individuals (@fig-init).

```{r D0, warning=F, message=F}
#| fig-cap: Initial weights of earthworms according to batches. 
#| label: fig-init
#| fig-width: 10
#| fig-height: 4

pal_lot <- c(Nord_frost[3], Nord_polar[4])

# Weights at t=0
p <- ggplot(
  data=subset(df_mix_ind,t==0), 
  aes(
    x=Condition, 
    y=w
    )
  )+

  geom_boxplot(
    alpha=0.2,
    color = Nord_polar[1]
    )+
  geom_dotplot(
    aes(
    color=Lot, 
    fill=Lot
    ),
    binaxis='y', 
    stackdir='center', 
    dotsize=0.5, 
    alpha=0.7
    )+
  
  scale_color_manual(values=pal_lot)+
  scale_fill_manual(values=pal_lot)+

  labs(x="Condition", y="Weight (mg)")+
  

  theme_classic(12)+
  theme(
    #legend.position = "none", 
    legend.title=element_text(size=sizetitle-2,face="bold"),
    legend.text = element_text(size=sizetitle-2,face="plain"),
    
    title=element_text(size=sizetitle, face="bold"), 
    
    axis.title.x = element_blank(),
    axis.title.y = element_text(size=sizetitle,face="plain"),
    
    #axis.text.x = element_blank(),
    axis.line.x=element_blank(),
    axis.ticks.x=element_blank(),
    
    strip.background = element_rect(
      color="black", 
      fill="grey95", 
      size=0, 
      linetype="solid"
      )
    )
p
```

```{r, include=F}
ggsave(
  filename="Mix_initial_weights_Spring.png",
  plot=p, 
  width=8, 
  height = 4, 
  path=here::here("fig/Mixture")
  )
ggsave(
  filename="Mix_initial_weights_Spring.jpg",
  plot=p, 
  width=8, 
  height = 4, 
  path=here::here("fig/Mixture")
  )
ggsave(
  filename="Mix_initial_weights_Spring.svg",
  plot=p, 
  width=8, 
  height = 4, 
  path=here::here("fig/Mixture")
  )
```

## Is the effect of single molecules the same in experiment A as in experiment B ?

To judge the reproducibility between the experiments, we need to compare the dose-response curves for EPX & IMD obtained with the experiment A and the experiment B (Autumn 2024 vs. Spring 2025).

Considering the inter-batch variability observed in control treatments, we standardized all responses by expressing them relative to the corresponding batch control. It gives us `r_Nb_cocoons`.

### Comparison of the controls

```{r, message=F, warning=F}
#| fig-cap: Comparaison of the controls obtained in the mixture experiment (dark blues) with the results of the experiment A (blues). 
#| label: fig-drcIMDEPXcompctrl
#| fig-width: 4
#| fig-height: 5

df_mix_coc_ctrl <- subset(df_mix_coc, Ratio == "N") |> 
  dplyr::select(Nb_cocoons) |> 
  mutate(Experiment = "Experiment B")

df_repro_alive_ctrl <- subset(df_repro_IMD_alive, Dose == 0) |> 
  dplyr::select(Nb_cocoons, Lot) |> 
  mutate(Experiment = case_when(
    Lot == "A" ~ "Experiment A\nSpring 2024",
    Lot == "B" ~ "Experiment A\nSummer 2024"
    )
    ) |> 
  dplyr::select(Nb_cocoons, Experiment)

df_controls <- rbind(df_repro_alive_ctrl,df_mix_coc_ctrl) 
df_controls$Experiment <- factor(df_controls$Experiment, levels = c("Experiment A\nSpring 2024", "Experiment A\nSummer 2024", "Experiment B"))

p <- ggplot(
  data = df_controls,
  aes(
    x = Experiment,
    y = Nb_cocoons
  )
)+
  geom_dotplot(
    binaxis='y', 
    stackdir='center', 
    dotsize=0.8, 
    alpha=0.7,
    color = Nord_aurora[4],
    fill = Nord_aurora[4]
    )+
  labs(
    x = "",
    y = "Number of cocoons produced per cosm (#)"
  )+
  theme_minimal()+
  theme(
    axis.text.x = element_text(angle=45, hjust=1)
  )

p
```

```{r, message=F, warning=F}
#| code-fold: show

pairwise.wilcox.test(df_controls$Nb_cocoons, df_controls$Experiment, p.adjust.method = "bonferroni", exact=F)

#wilcox.test(Nb_cocoons ~ Experiment, data = df_controls)

lm.controls <- lm(Nb_cocoons ~ Experiment, data = df_controls)
lsmeans(lm.controls,pairwise~Experiment,adjust='bonferroni')

#t.test(Nb_cocoons ~ Experiment, data = df_controls, var.equal = FALSE)
```

The controls of the two different experiments are not significatively different.

### Experiment A - Dose-response curves

We then get the dose-response curves of the single substances from experiment A and experiment B.

```{r drcsingle, warning=F, message=F}

Dose_x <- expand.grid(
  exp(
    seq(
      log(0.0001),log(5000),
      by=(log(5000)-log(0.0001))/100
    )
  )
)

drc.ExpA<- drm(
  Nb_cocoons~Dose, Molecule, 
  data = df_repro_alive,
  type="Poisson",
  fct=LL.4(
    names = c("slope", "Ymin", "Ymax", "EC50"),
    fixed = c(NA, 0, NA, NA)
  ), 
  # Reproduction is expected to reach 0 for large concentrations
  pmodels=data.frame(Molecule, Molecule, Molecule)
)

CI.ExpA <- data.frame(
  Dose = c(Dose_x$Var1, Dose_x$Var1),
  Molecule = c(rep("EPX", length(Dose_x$Var1)), rep("IMD", length(Dose_x$Var1)))
)

pm.ExpA <- predict(drc.ExpA, newdata=CI.ExpA, interval="confidence")
CI.ExpA$p <- pm.ExpA[,1]
CI.ExpA$pmin <- pm.ExpA[,2]
CI.ExpA$pmax <- pm.ExpA[,3]

EPX_EC50_ExpA <- coef(drc.ExpA)[5]
IMD_EC50_ExpA <- coef(drc.ExpA)[6]

summary(drc.ExpA)

```

### Experiment B - Dose-response curves

```{r drcmix, warning=F, message=F}

df_mix_coc_IMD <- subset(df_mix_coc, Ratio %in% c("I", "N")) |>
  mutate(
    Dose = Dose_IMD,
    Dose_plot = Dose_IMD_plot,
    Molecule = "IMD"
  ) |>
  dplyr::select(Dose, Dose_plot, Nb_cocoons, Molecule, r_Nb_cocoons)

df_mix_coc_EPX <- subset(df_mix_coc, Ratio %in% c("E", "N")) |>
  mutate(
    Dose = Dose_EPX,
    Dose_plot = Dose_EPX_plot,
    Molecule = "EPX"
  ) |>
  dplyr::select(Dose, Dose_plot, Nb_cocoons, Molecule, r_Nb_cocoons)

df_mix_coc_single <- rbind(df_mix_coc_IMD, df_mix_coc_EPX)

df_mix_coc_single_mean <- df_mix_coc_single |>
  aggregate(Nb_cocoons ~ Dose + Dose_plot + Molecule, mean)

# Common Ymax and slope
drc.ExpB <- drm(
  Nb_cocoons ~ Dose, Molecule,
  data = df_mix_coc_single,
  type = "Poisson",
  fct = LL.4(
    names = c("slope", "Ymin", "Ymax", "EC50"),
    fixed = c(NA, 0, NA, NA)
  ),
  # Reproduction is expected to reach 0 for large concentrations
  pmodels = data.frame(Molecule, Molecule, Molecule)
)

CI.ExpB <- data.frame(
  Dose = c(Dose_x$Var1, Dose_x$Var1),
  Molecule = c(rep("EPX", length(Dose_x$Var1)), rep("IMD", length(Dose_x$Var1)))
)

pm.ExpB <- predict(drc.ExpB, newdata = CI.ExpB, interval = "confidence")
CI.ExpB$p <- pm.ExpB[, 1]
CI.ExpB$pmin <- pm.ExpB[, 2]
CI.ExpB$pmax <- pm.ExpB[, 3]

EPX_EC50_ExpB <- coef(drc.ExpB)[3]
IMD_EC50_ExpB <- coef(drc.ExpB)[4]

summary(drc.ExpB)

```

### Comparison of the two experiments for single substances

```{r, warning=F, message=F}
#| fig-cap: Comparaison of the results obtained in the experiment B (dark blues) with the results of Experiment A (blues). The line represents the dose-response curves obtained for the number of cocoons produced. Crosses correspond to the number of cocoons produced by one cosm and the bold points represents the mean per dose.
#| label: fig-drcIMDEPXcomp
#| fig-width: 8
#| fig-height: 4

x <- seq(0.0001, 5000, 0.01)
line_width <- 1.2

darkening <- 0.2
col_IMD_dark <- colorspace::darken(col_IMD, darkening)
col_EPX_dark <- colorspace::darken(col_EPX, darkening)

p_E <- ggplot() +
  geom_ribbon(
    data = subset(CI.ExpB, Molecule == "EPX"),
    aes(
      x = Dose,
      y = p,
      ymin = pmin,
      ymax = pmax
    ),
    alpha = 0.2,
    fill = col_EPX_dark,
    # color = col_IMD
  ) +
  geom_ribbon(
    data = subset(CI.ExpA, Molecule == "EPX"),
    aes(
      x = Dose,
      y = p,
      ymin = pmin,
      ymax = pmax
    ),
    alpha = 0.2,
    fill = col_EPX,
    # color = col_IMD
  ) +
  geom_line(
    data = subset(CI.ExpB, Molecule == "EPX"),
    aes(
      x = Dose,
      y = p
    ),
    color = col_EPX_dark,
    linewidth = line_width
  ) +
  geom_line(
    data = subset(CI.ExpA, Molecule == "EPX"),
    aes(
      x = Dose,
      y = p
    ),
    color = col_EPX,
    linewidth = line_width
  ) +
  geom_point(
    data = df_mix_coc_EPX,
    aes(
      x = Dose_plot,
      y = Nb_cocoons
    ),
    color = col_EPX_dark,
    alpha = 0.6,
    shape = 4
  ) +
  geom_point(
    data = df_repro_EPX_alive,
    aes(
      x = Dose_plot, 
      y = Nb_cocoons
      ),
    color = col_EPX,
    alpha = 0.5,
    shape = 4
  ) +
  geom_point(
    data = df_mix_coc_EPX_mean,
    aes(
      x = Dose_EPX_plot, 
      y = Nb_cocoons
      ),
    color = col_EPX_dark,
    size = 3
  ) +
  geom_point(
    data = subset(df_repro_alive_mean, Molecule == "EPX"),
    aes(
      x = Dose_plot, 
      y = Nb_cocoons
      ),
    color = col_EPX,
    size = 3
  ) +
  annotate(
    geom = "text",
    x = 1500,
    y = 2,
    label = "E",
    fontface = "bold"
  ) +
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100), # inclure la valeur fictive
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100")
  ) +
  labs(
    x = "Concentration of EPX (mg/kg)",
    y = "Number of cocoons produced per cosm (#)"
  ) +
  theme_bw()

p_I <- ggplot() +
  geom_ribbon(
    data = subset(CI.ExpB, Molecule == "IMD"),
    aes(
      x = Dose,
      y = p,
      ymin = pmin,
      ymax = pmax
    ),
    alpha = 0.2,
    fill = col_IMD_dark,
    # color = col_IMD
  ) +
  geom_ribbon(
    data = subset(CI.ExpA, Molecule == "IMD"),
    aes(
      x = Dose,
      y = p,
      ymin = pmin,
      ymax = pmax
    ),
    alpha = 0.2,
    fill = col_IMD,
    # color = col_IMD
  ) +
  geom_line(
    data = subset(CI.ExpB, Molecule == "IMD"),
    aes(
      x = Dose,
      y = p
    ),
    color = col_IMD_dark,
    linewidth = line_width
  ) +
  geom_line(
    data = subset(CI.ExpA, Molecule == "IMD"),
    aes(
      x = Dose,
      y = p
    ),
    color = col_IMD,
    linewidth = line_width
  ) +
  geom_point(
    data = df_mix_coc_IMD,
    aes(
      x = Dose_plot,
      y = Nb_cocoons
    ),
    color = col_IMD_dark,
    alpha = 0.6,
    shape = 4
  ) +
  geom_point(
    data = df_repro_IMD_alive,
    aes(
      x = Dose_plot,
      y = Nb_cocoons
    ),
    color = col_IMD,
    alpha = 0.5,
    shape = 4
  ) +
  geom_point(
    data = df_mix_coc_IMD_mean,
    aes(
      x = Dose_IMD_plot,
      y = Nb_cocoons
    ),
    color = col_IMD_dark,
    size = 3
  ) +
  geom_point(
    data = subset(df_repro_alive_mean, Molecule == "IMD"),
    aes(
      x = Dose_plot,
      y = Nb_cocoons
    ),
    color = col_IMD,
    size = 3
  ) +
  annotate(
    geom = "text",
    x = 1500,
    y = 2,
    label = "I",
    fontface = "bold"
  ) +
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100), # inclure la valeur fictive
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100")
  ) +
  labs(
    x = "Concentration of IMD (mg/kg)",
    y = "Number of cocoons produced per cosm (#)"
  ) +
  theme_bw()

p <- p_E + p_I
p
```

```{r, include=F}
ggsave(
  filename="Mix_spring_cocoons_compEC50.png", 
  plot=p, 
  width=8, height = 4, 
  path=here::here("fig/Mixture")
  )
ggsave(
  filename="Mix_spring_cocoons_compEC50.jpg", 
  plot=p, 
  width=8, height = 4, 
  path=here::here("fig/Mixture")
  )
# ggsave(
#   filename="Mix_spring_cocoons_compEC50.svg", 
#   plot=p, 
#   width=6, height = 6, 
#   path=here::here("fig/Mixture")
#   )
```

```{r, results="hide", warning=F, message = F}
pEC50EPXExpA <- ED(drc.ExpA, 50, interval = "delta")[1,1]
pEC50EPXExpB <- ED(drc.ExpB, 50, interval = "delta")[1,1]
pEC50IMDExpA <- ED(drc.ExpA, 50, interval = "delta")[2,1]
pEC50IMDExpB <- ED(drc.ExpB, 50, interval = "delta")[2,1]

pminEC50EPXExpA <- ED(drc.ExpA, 50, interval = "delta")[1,3]
pminEC50EPXExpB <- ED(drc.ExpB, 50, interval = "delta")[1,3]
pminEC50IMDExpA <- ED(drc.ExpA, 50, interval = "delta")[2,3]
pminEC50IMDExpB <- ED(drc.ExpB, 50, interval = "delta")[2,3]

pmaxEC50EPXExpA <- ED(drc.ExpA, 50, interval = "delta")[1,4]
pmaxEC50EPXExpB <- ED(drc.ExpB, 50, interval = "delta")[1,4]
pmaxEC50IMDExpA <- ED(drc.ExpA, 50, interval = "delta")[2,4]
pmaxEC50IMDExpB <- ED(drc.ExpB, 50, interval = "delta")[2,4]

ec50_IMD_ExpA <- as.numeric(ED(drc.ExpA, 50, interval = "delta")[2,])
ec50_IMD_ExpB <- as.numeric(ED(drc.ExpB, 50, interval = "delta")[2,])

ec50_EPX_ExpA <- as.numeric(ED(drc.ExpA, 50, interval = "delta")[1,])
ec50_EPX_ExpB <- as.numeric(ED(drc.ExpB, 50, interval = "delta")[1,])
```

```{r, warning=F, message=F}
#| fig-cap: Comparison of the EC$_{50}$ obtained in the different experiments.
#| label: fig-EC50compmix
#| fig-width: 6
#| fig-height: 4

df_EC50_comp <- data.frame(
  Molecule = c("EPX", "EPX", "IMD", "IMD"),
  Experiment = c("ExpA", "ExpB", "ExpA", "ExpB"),
  p = c(pEC50EPXExpA, pEC50EPXExpB, pEC50IMDExpA, pEC50IMDExpB),
  pmin = c(pminEC50EPXExpA, pminEC50EPXExpB, pminEC50IMDExpA, pminEC50IMDExpB),
  pmax = c(pmaxEC50EPXExpA, pmaxEC50EPXExpB, pmaxEC50IMDExpA, pmaxEC50IMDExpB)
) |>
  mutate(color = as.factor(paste0(Molecule, Experiment)))

df_EC50_comp$Experiment <- factor(df_EC50_comp$Experiment, levels = c("ExpA", "ExpB"))

p <- ggplot(
  data = df_EC50_comp,
  aes(
    x = Experiment,
    y = p,
    ymin = pmin,
    ymax = pmax,
    color = color
  )
) +
  geom_pointrange() +
  facet_wrap(~Molecule, scales = "free") +
  scale_color_manual(values = c(col_EPX_dark, col_EPX, col_IMD_dark, col_IMD)) +
  labs(
    y = "EC50",
    x = ""
  ) +
  theme_minimal() +
  theme(legend.position = "none")
p
```

```{r, warning=F, message=F}
#| tbl-cap: Inter-experiment comparison of dose-response curves for EPX & IMD.
#| label: tbl-MIXcompdrc

df_drc_comp <- data.frame(
  # Parameter = c("Ymax", "Slope", "EC50(EPX)", "EC50(IMD)"),
  ExpA = c(
    coef(drc.ExpA)[1], coef(drc.ExpA)[2],
    coef(drc.ExpA)[3], coef(drc.ExpA)[4],
    coef(drc.ExpA)[5], coef(drc.ExpA)[6]
    ),
  ExpB = c(
    coef(drc.ExpB)[1], coef(drc.ExpB)[2],
    coef(drc.ExpB)[3], coef(drc.ExpB)[4],
    coef(drc.ExpB)[5], coef(drc.ExpB)[6]
    )
  ) |>
  mutate(
    Ratio = ExpA / ExpB,
    Per_difference = (ExpB - ExpA) / ExpA * 100
  ) |>
  mutate(across(where(is.numeric), signif, 2))

df_drc_comp |> datatable(options = list(dom = "t"), class = "hover")

```

!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

```{r, warning=F, message=F}

df_repro_alive_simple_IMD <- df_repro_alive |> 
  filter(Molecule == "IMD") |> 
  dplyr::select(Molecule, Dose, Nb_cocoons) |> 
  mutate(Experiment = "A")

df_repro_alive_simple_EPX<- df_repro_alive |> 
  filter(Molecule == "EPX") |> 
  dplyr::select(Molecule, Dose, Nb_cocoons) |> 
  mutate(Experiment = "A")

df_mix_coc_single_IMD <- df_mix_coc_single |> 
  filter(Molecule == "IMD") |> 
  dplyr::select(Molecule, Dose, Nb_cocoons) |> 
  mutate(Experiment = "B")

df_mix_coc_single_EPX <- df_mix_coc_single |> 
  filter(Molecule == "EPX") |> 
  dplyr::select(Molecule, Dose, Nb_cocoons) |> 
  mutate(Experiment = "B")

df_comp_IMD <- rbind(df_repro_alive_simple_IMD, df_mix_coc_single_IMD)
df_comp_EPX <- rbind(df_repro_alive_simple_EPX, df_mix_coc_single_EPX)

drc.compIMD<- drm(
  Nb_cocoons~Dose, Experiment, 
  data = df_comp_IMD,
  type="Poisson",
  fct=LL.4(
    names = c("slope", "Ymin", "Ymax", "EC50"),
    fixed = c(NA, 0, NA, NA)
  ), 
  # Reproduction is expected to reach 0 for large concentrations
  pmodels=data.frame(Experiment, Experiment, Experiment)
)

drc.compEPX<- drm(
  Nb_cocoons~Dose, Experiment, 
  data = df_comp_EPX,
  type="Poisson",
  fct=LL.4(
    names = c("slope", "Ymin", "Ymax", "EC50"),
    fixed = c(NA, 0, NA, NA)
  ), 
  # Reproduction is expected to reach 0 for large concentrations
  pmodels=data.frame(Experiment, Experiment, Experiment)
)

drc.compIMD_same_ec<- drm(
  Nb_cocoons~Dose, Experiment, 
  data = df_comp_IMD,
  type="Poisson",
  fct=LL.4(
    names = c("slope", "Ymin", "Ymax", "EC50"),
    fixed = c(NA, 0, NA, NA)
  ), 
  # Reproduction is expected to reach 0 for large concentrations
  pmodels=data.frame(Experiment, Experiment, 1)
)

drc.compEPX_same_ec<- drm(
  Nb_cocoons~Dose, Experiment, 
  data = df_comp_EPX,
  type="Poisson",
  fct=LL.4(
    names = c("slope", "Ymin", "Ymax", "EC50"),
    fixed = c(NA, 0, NA, NA)
  ), 
  # Reproduction is expected to reach 0 for large concentrations
  pmodels=data.frame(Experiment, Experiment, 1)
)

anova(drc.compIMD_same_ec, drc.compIMD, test = "F")
anova(drc.compEPX_same_ec, drc.compEPX, test = "F")

```

Estimated EC$_{50}$ are not significatively different.

However, for the Jonker model, it is preferable to calibrate the model using the dose–response curves obtained during the same experiment as the one used to estimate the interaction parameter. This ensures consistency in experimental conditions and accounts for potential inter-experiment variability.

## Interaction ?

### Step 1 - Dose-response curves from the mixture data

We need to note that the number of produced cocoons `Nb_cocoons` is a count variable that follows a Poisson distribution. Models will have to be made accordingly.

```{r drcmixratios, warning=F, message=F}

df_mix_coc_IMD <- subset(df_mix_coc, Ratio %in% c("I", "N")) |> 
  mutate(
    Dose = Dose_IMD,
    Dose_plot = Dose_IMD_plot,
    Molecule = "IMD"
    ) |> 
  dplyr::select(Dose, Dose_plot, Nb_cocoons, Molecule)

# We do not take the controls into account twice
df_mix_coc_EPX <- subset(df_mix_coc, Ratio  %in% c("E")) |> 
  mutate(
    Dose = Dose_EPX,
    Dose_plot = Dose_EPX_plot,
    Molecule = "EPX"
    ) |>  
  dplyr::select(Dose, Dose_plot, Nb_cocoons, Molecule)

df_mix_coc_EPX_plot <- subset(df_mix_coc, Ratio  %in% c("E", "N")) |> 
  mutate(
    Dose = Dose_EPX,
    Dose_plot = Dose_EPX_plot,
    Molecule = "EPX"
    ) |>  
  dplyr::select(Dose, Dose_plot, Nb_cocoons, Molecule)

df_mix_coc_single <- rbind(df_mix_coc_IMD, df_mix_coc_EPX)

df_mix_coc_single_mean <- df_mix_coc_single |> 
  aggregate(Nb_cocoons ~ Dose+Molecule, mean)

Dose_x <- expand.grid(
  exp(
    seq(
      log(Val_Ctrl),log(5000),
      by=(log(5000)-log(Val_Ctrl))/100
    )
  )
)

# Common Ymax and slope
drc.mix.IE<- drm(
  Nb_cocoons~Dose, Molecule, 
  data = df_mix_coc_single,
  type="Poisson",
  fct=LL.4(
    names = c("slope", "Ymin", "Ymax", "EC50"),
    fixed = c(NA, 0, NA, NA)
  ), 
  # Reproduction is expected to reach 0 for large concentrations
  pmodels=data.frame(1, 1, Molecule)
)

CI.mix.IE <- data.frame(
  Dose = c(Dose_x$Var1, Dose_x$Var1),
  Molecule = c(rep("EPX", length(Dose_x$Var1)), rep("IMD", length(Dose_x$Var1)))
)

pm.mix.IE <- predict(drc.mix.IE, newdata=CI.mix.IE, interval="confidence")
CI.mix.IE$p <- pm.mix.IE[,1]
CI.mix.IE$pmin <- pm.mix.IE[,2]
CI.mix.IE$pmax <- pm.mix.IE[,3]

Hill.mix.IE <- function(Dose, Molecule){
  
  i <- 0
  if(Molecule == "IMD"){i <- 1}
  
  Y_min <- 0
  slope <- coef(drc.mix.IE)[1]
  Y_max <- coef(drc.mix.IE)[2]
  EC50 <- coef(drc.mix.IE)[3+i]
  
  return(Y_min+(Y_max-Y_min)/(1+exp(slope*(log(Dose)-log(EC50)))))
}
EPX_EC50_mix.IE <- coef(drc.mix.IE)[3]
IMD_EC50_mix.IE <- coef(drc.mix.IE)[4]

df_mix_coc <- df_mix_coc |> 
  mutate(
    TU_mix = Dose_IMD/IMD_EC50_mix.IE + Dose_EPX/EPX_EC50_mix.IE,
    TU_mix_plot = case_when(
      TU_mix == 0 ~ Val_Ctrl,
      !(TU_mix == 0) ~ TU_mix
    )
    )

df_mix_coc_mean <- df_mix_coc_mean |> 
  mutate(
    TU_mix = Dose_IMD/IMD_EC50_mix.IE + Dose_EPX/EPX_EC50_mix.IE,
    TU_mix_plot = case_when(
      TU_mix == 0 ~ Val_Ctrl,
      !(TU_mix == 0) ~ TU_mix
    )
    )

summary(drc.mix.IE)

est <- coef(drc.mix.IE)
ci <- confint(drc.mix.IE)
params_tab <- data.frame(
  estimate  = unname(est),
  CI_lower  = ci[,1],
  CI_upper  = ci[,2]
)

params_tab

```

We can consider that the slope is the same if there is not difference between this model and a model without common slope.

```{r verifcommonslopes, warning=F, message=F}
drc.mix.IE_notcommonslope<- drm(
  Nb_cocoons~Dose, Molecule, 
  data = df_mix_coc_single,
  type="Poisson",
  fct=LL.4(
    names = c("slope", "Ymin", "Ymax", "EC50"),
    fixed = c(NA, 0, NA, NA)
  ), 
  # Reproduction is expected to reach 0 for large concentrations
  pmodels=data.frame(1, Molecule, Molecule)
)

anova(drc.mix.IE_notcommonslope, drc.mix.IE, test="F")

```

Which is the case here.

```{r, warning=F, message=F}
#| fig-cap: Dose response curves obtained with cocoon production. The line represents the modelled dose-response curve (with common $Y_{max}$ and slope for the 2 active substances). Crosses correspond to the number of cocoons produced by one cosm and the bold points represents the mean per dose.
#| label: fig-drcIMDEPXmixr
#| fig-width: 8
#| fig-height: 4

x <- seq(Val_Ctrl, 5000, 0.01)
line_width <- 1.2
ymax <- 22.5

p_I <- ggplot()+
  geom_ribbon(
    data = subset(CI.mix.IE, Molecule == "IMD"), 
    aes(
      x = Dose, 
      y = p, 
      ymin = pmin, 
      ymax = pmax
      ), 
    alpha=0.2,
    fill = col_IMD
    )+
  geom_line(
    data = subset(CI.mix.IE, Molecule == "IMD"), 
    aes(
      x=Dose, 
      y=p
    ), 
    color=col_IMD, 
    linewidth=line_width
  )+
  geom_point(
    data = df_mix_coc_IMD, 
    aes(x = Dose_plot, y = Nb_cocoons),
    color = col_IMD,
    alpha = 0.6,
    shape = 4
  )+
  geom_point(
    data = df_mix_coc_IMD_mean, 
    aes(x = Dose_IMD_plot, y = Nb_cocoons),
    color = col_IMD,
    size = 3
  )+
  
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100),  # inclure la valeur fictive
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100")
  )+
  ylim(NA, ymax)+
  labs(
    x = "Concentration of IMD (mg/kg)",
    y = "Cocoon production (#)"
  )+
  theme_bw()

p_E <- ggplot()+
  geom_ribbon(
    data = subset(CI.mix.IE, Molecule == "EPX"), 
    aes(
      x = Dose, 
      y = p, 
      ymin = pmin, 
      ymax = pmax
    ), 
    alpha=0.2,
    fill = col_EPX,
    #color = col_IMD
  )+
  geom_line(
    data = subset(CI.mix.IE, Molecule == "EPX"), 
    aes(
      x=Dose, 
      y=p
    ), 
    color=col_EPX, 
    linewidth=line_width
  )+
  geom_point(
    data = df_mix_coc_EPX_plot, 
    aes(x = Dose_plot, y = Nb_cocoons),
    color = col_EPX,
    alpha = 0.6,
    shape = 4
  )+
  geom_point(
    data = df_mix_coc_EPX_mean, 
    aes(x = Dose_EPX_plot, y = Nb_cocoons),
    color = col_EPX,
    size = 3
  )+
  
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100),  # inclure la valeur fictive
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100")
  )+
  ylim(NA, ymax)+
  labs(
     x = "Concentration of EPX (mg/kg)",
    y = "Cocoon production (#)"
  )+
  theme_bw()

p <- p_I + p_E
p
```

```{r, include=F}
ggsave(
  filename="Mix_spring_cocoons_drcmix.png", 
  plot=p, 
  width=8, height = 4, 
  path=here::here("fig/Mixture")
  )
ggsave(
  filename="Mix_spring_cocoons_drcmix.jpg", 
  plot=p, 
  width=8, height = 4, 
  path=here::here("fig/Mixture")
  )
```

These dose-response curves will be used for the simple interaction model of Jonker.

We can visualise the results of the experiment by looking at the resulting dose-response curves for each mixture ratio.

```{r, warning=F, message=F}
Dose_x <- expand.grid(
  exp(
    seq(
      log(0.0001),log(5000),
      by=(log(5000)-log(0.0001))/1000
    )
  )
)

# Common Ymax
drc.ratios<- drm(
  Nb_cocoons~TU_mix, Ratio, 
  data = df_mix_coc,
  type="Poisson",
  fct=LL.4(
    names = c("slope", "Ymin", "Ymax", "EC50"),
    fixed = c(NA, 0, NA, NA)
  ), 
  # Reproduction is expected to reach 0 for large concentrations
  pmodels=data.frame(Ratio, 1, Ratio)
)

CI.ratios <- data.frame(
  TU_mix = c(rep(Dose_x$Var1,1)),
  Ratio = c(rep("E", length(Dose_x$Var1)), 
             rep("F", length(Dose_x$Var1)),
             rep("G", length(Dose_x$Var1)), 
             rep("H", length(Dose_x$Var1)), 
             rep("I", length(Dose_x$Var1))
             )
)

pm.ratios <- predict(drc.ratios, newdata=CI.ratios, interval="confidence")
CI.ratios$p <- pm.ratios[,1]
CI.ratios$pmin <- pm.ratios[,2]
CI.ratios$pmax <- pm.ratios[,3]

summary(drc.ratios)
```

```{r, warning=F, message=F}
#| fig-cap: Dose-response curves obtained for each mixture ratio. The lines represent the dose-response curves obtained (with common Ymax and Ymin set to 0). Crosses correspond to the number of cocoons produced by one cosm and the bold points represent the mean per condition.
#| label: fig-drcIMDEPXratios
#| fig-width: 8
#| fig-height: 6

line_width <- 1.2

Ratio_E <- "1:0 (EPX only)"
Ratio_I <- "0:1 (IMD only)"
Ratio_F <- "3:1"
Ratio_G <- "1:1"
Ratio_H <- "1:3"

df_mix_coc_mean_I <- subset(df_mix_coc_mean, Ratio %in% c("I", "N")) |> 
  mutate(Ratio_plot = Ratio_I)
df_mix_coc_mean_H <- subset(df_mix_coc_mean, Ratio %in% c("H", "N")) |> 
  mutate(Ratio_plot = Ratio_H)
df_mix_coc_mean_G <- subset(df_mix_coc_mean, Ratio %in% c("G", "N")) |> 
  mutate(Ratio_plot = Ratio_G)
df_mix_coc_mean_F <- subset(df_mix_coc_mean, Ratio %in% c("F", "N")) |> 
  mutate(Ratio_plot = Ratio_F)
df_mix_coc_mean_E <- subset(df_mix_coc_mean, Ratio %in% c("E", "N")) |> 
  mutate(Ratio_plot = Ratio_E)

df_mix_coc_mean_plotdrc <- rbind(
  df_mix_coc_mean_I,
  df_mix_coc_mean_H,
  df_mix_coc_mean_G,
  df_mix_coc_mean_F,
  df_mix_coc_mean_E
) |> 
  mutate(
    Ratio_plot = fct_relevel(Ratio_plot, c(Ratio_E, Ratio_F, Ratio_G, Ratio_H, Ratio_I))
  )

df_mix_coc_I <- subset(df_mix_coc, Ratio %in% c("I", "N")) |> 
  mutate(Ratio_plot = Ratio_I)
df_mix_coc_H <- subset(df_mix_coc, Ratio %in% c("H", "N")) |> 
  mutate(Ratio_plot = Ratio_H)
df_mix_coc_G <- subset(df_mix_coc, Ratio %in% c("G", "N")) |> 
  mutate(Ratio_plot = Ratio_G)
df_mix_coc_F <- subset(df_mix_coc, Ratio %in% c("F", "N")) |> 
  mutate(Ratio_plot = Ratio_F)
df_mix_coc_E <- subset(df_mix_coc, Ratio %in% c("E", "N")) |> 
  mutate(Ratio_plot = Ratio_E)

df_mix_coc_plotdrc <- rbind(
  df_mix_coc_I,
  df_mix_coc_H,
  df_mix_coc_G,
  df_mix_coc_F,
  df_mix_coc_E
)|> 
  mutate(
    Ratio_plot = fct_relevel(Ratio_plot, c(Ratio_E, Ratio_F, Ratio_G, Ratio_H, Ratio_I))
  )

CI.ratios <- CI.ratios |> 
  mutate(
    Ratio_plot = case_when(
      Ratio == "E" ~ Ratio_E,
      Ratio == "F" ~ Ratio_F,
      Ratio == "G" ~ Ratio_G,
      Ratio == "H" ~ Ratio_H,
      Ratio == "I" ~ Ratio_I,
      )
    )|> 
  mutate(
    Ratio_plot = fct_relevel(Ratio_plot, c(Ratio_E, Ratio_F, Ratio_G, Ratio_H, Ratio_I))
  )

size_axistitle <- 11

library(ggh4x)

p_full <- ggplot() +
  geom_ribbon(
    data = CI.ratios, 
    aes(
      x = TU_mix, 
      y = p, 
      ymin = pmin, 
      ymax = pmax, 
      fill = Ratio_plot
      ), 
    alpha = 0.2
  ) +
  geom_line(
    data = CI.ratios, 
    aes(
      x = TU_mix, 
      y = p, 
      color = Ratio_plot, 
      fill = Ratio_plot
      ), 
    linewidth = line_width
  ) +
  geom_point(
    data = df_mix_coc_plotdrc,
    aes(
      x = TU_mix_plot, 
      y = Nb_cocoons, 
      color = Ratio_plot, 
      fill = Ratio_plot
      ),
    alpha = 0.6, shape = 4
  ) +
  geom_point(
    data = df_mix_coc_mean_plotdrc,
    aes(
      x = TU_mix_plot, 
      y = Nb_cocoons, 
      color = Ratio_plot, 
      fill = Ratio_plot
      ),
    size = 3
  ) +
  scale_color_manual(values = pal_ratio) +
  scale_fill_manual(values = pal_ratio) +
  facet_wrap2(~ Ratio_plot, axes = "x") +
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100),
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100")
  ) +
  labs(
    x = "Toxic Unit (TU)",
    y = "Number of cocoons produced per cosm (#)"
  ) +
  theme_bw() +
  theme(
    axis.title.x = element_text(size = size_axistitle),
    axis.title.y = element_text(size = size_axistitle),
    axis.text.x = element_text(),  
    axis.ticks.x = element_line(),    
    legend.position = "none",
    strip.text = element_text(face = "bold"),
    strip.placement = "outside",
    strip.background = element_rect(color = "black", fill = "grey95", size = 0, linetype = "solid"),
    panel.spacing = unit(0.6, "lines") 
  )
p_comp <- ggplot()+

  geom_line(
    data = CI.ratios, 
    aes(
      x=TU_mix, 
      y=p,
      color=Ratio_plot,
      fill = Ratio_plot
    ), 
    linewidth=line_width
  )+

  scale_color_manual(values = pal_ratio)+
  scale_fill_manual(values = pal_ratio)+
  
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100),  # inclure la valeur fictive
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100")
  )+
  labs(
    x = "Toxic Unit (TU)",
    y = "Number of cocoons produced per cosm (#)"
  )+
  
  theme_bw()+
  theme(
    legend.position = "none",
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    strip.background = element_rect(
      color="black", 
      fill="grey95", 
      size=0, 
      linetype="solid"
      )
  )

p <- p_full + 
  inset_element(
    p_comp,
    left = 0.67, bottom = -0.05, right = 1, top = 0.45
    )
p
```

```{r, include=F}
ggsave(
  filename="Mix_spring_cocoons_drcRatios.png", 
  plot=p, 
  width=8, height = 6, 
  path=here::here("fig/Mixture")
  )
ggsave(
  filename="Mix_spring_cocoons_drcRatios.jpg", 
  plot=p, 
  width=8, height = 6, 
  path=here::here("fig/Mixture")
  )
# ggsave(
#   filename="Mix_spring_cocoons_drcRatios.svg", 
#   plot=p, 
#   width=6, height = 6, 
#   path=here::here("fig/Mixture")
#   )
```

The dose-response curves per ratio do not differ widely visually. An important interaction is not to be expected.

### Step 2 - Fit of the model to our data

The different Jonker models can be fit to our data.

```{r modelsentry, warning=F, message=F}

# Preparation of model entry

df_design <- read.csv(here::here("data/Design_mixture.csv"))

slope <- coef(drc.mix.IE)[1]
Y_max <- coef(drc.mix.IE)[2]
EPX_EC50 <- coef(drc.mix.IE)[3]
IMD_EC50 <- coef(drc.mix.IE)[4]
Y_min <- 0

C_mat = cbind(df_design$EPX,df_design$IMD)
Max = Y_max
Slopes = c(slope, slope)
Ec50s = c(EPX_EC50, IMD_EC50)

param <- data.frame(Slopes=Slopes, Max=Max, Ec50s=Ec50s)

min_dose_EPX <- min(subset(df_design, !EPX==0)$EPX)
max_dose_EPX <- max(subset(df_design, !EPX==0)$EPX)

min_dose_IMD <- min(subset(df_design, !IMD==0)$IMD)
max_dose_IMD <- max(subset(df_design, !IMD==0)$IMD)

by_EPX <- (log(max_dose_EPX)-log(min_dose_EPX))/100
by_IMD <- (log(max_dose_IMD)-log(min_dose_IMD))/100

# Créer une grille pour x et y en utilisant expand.grid
grid_C1 <- exp(seq(log(min_dose_EPX), log(max_dose_EPX), by = by_EPX))
grid_C2 <- exp(seq(log(min_dose_IMD), log(max_dose_IMD), by = by_IMD))
grid <- expand.grid(
  x = grid_C1, 
  y = grid_C2
  )

df_mix_coc_int <- df_mix_coc |> 
  mutate(Response = Nb_cocoons) |> 
  dplyr::select(Dose_EPX, Dose_IMD, Response, Line, Ratio, TU_mix, TU_drc) |> 
  as.data.frame() |> 
  filter(!(Dose_IMD == 0 & Dose_EPX == 0))
```

```{r ModelsFit, warning=F, message=F}

signif_LL <- 5 # Significative digits for LL printing

######## CA ##################################################################

CA_fit <- data.frame(Error = NA)
CA_fit$Error <- CA_complete2_Poisson(
  C_mat=cbind(                                                    # <1>
    df_mix_coc_int$Dose_EPX,                                      # <1>
    df_mix_coc_int$Dose_IMD                                       # <1>
    ),                                                            # <1>
  Response=df_mix_coc_int$Response,                               # <1>
  Max = Max, 
  Slopes = Slopes,
  Ec50s = Ec50s,
  interact="none",                                                # <1>
  multicore = TRUE, 
  mc.cores = 4
)

LogLikelihood_CA <- CA_fit$Error 

CA_fit$a <- NA
CA_fit$b <- NA
CA_fit$Type <- "CA"
CA_fit$Ref <- "CA"

CA_fit <- CA_fit |> 
  as.data.frame()

######## IA ##################################################################

IA_fit <- data.frame(Error = NA)
IA_fit$Error <- IA_complete2_Poisson(
  C_mat=cbind(                                                  
    df_mix_coc_int$Dose_EPX,                                    
    df_mix_coc_int$Dose_IMD                                      
    ),                                                          
  Response=df_mix_coc_int$Response,                              
  Max = Max, 
  Slopes = Slopes,
  Ec50s = Ec50s,
  interact="none"
)

LogLikelihood_IA <- IA_fit$Error 

IA_fit$a <- NA
IA_fit$b <- NA
IA_fit$Type <- "IA"
IA_fit$Ref <- "IA"

IA_fit <- IA_fit |> 
  as.data.frame()

######## CASA ##################################################################

CASA_fit<-CA_complete_fit_speed(                                    # <1>
  C_mat=cbind(                                                    # <1>
    df_mix_coc_int$Dose_EPX,                                      # <1>
    df_mix_coc_int$Dose_IMD                                       # <1>
    ),                                                            # <1>
  Response=df_mix_coc_int$Response,                               # <1>
  interact="SA",                                                  # <1>
  param=param,                                                    # <1>
  error_type = "Poisson",
  multicore = TRUE,                                               # <1>
  mc.cores = 4                                                    # <1>
  ) |>                                                                # <1>
  as.data.frame()
CASA_fit$Type <- "SA"
CASA_fit$Ref <- "CA"

LogLikelihood_CASA <- CASA_fit$Error                              
a_CASA <- CASA_fit$a
CASA_fit$b <- NA
# Printing results
a_CASA_print <- signif(a_CASA, 3)
LogLikelihood_CASA_print <- signif(LogLikelihood_CASA, signif_LL)

######## IASA ##################################################################

IASA_fit<-IA_complete_fit_speed(                                    # <1>
  C_mat=cbind(                                                    # <1>
    df_mix_coc_int$Dose_EPX,                                      # <1>
    df_mix_coc_int$Dose_IMD                                       # <1>
    ),                                                            # <1>
  Response=df_mix_coc_int$Response,                               # <1>
  interact="SA",                                                  # <1>
  param=param,                                                    # <1>
  error_type = "Poisson",
  multicore = TRUE,                                               # <1>
  mc.cores = 4                                                    # <1>
  ) |>                                                                # <1>
  as.data.frame()
IASA_fit$Type <- "SA"
IASA_fit$Ref <- "IA"

LogLikelihood_IASA <- IASA_fit$Error                              
a_IASA <- IASA_fit$a
IASA_fit$b <- NA
# Printing results
a_IASA_print <- signif(a_IASA, 3)
LogLikelihood_IASA_print <- signif(LogLikelihood_IASA, signif_LL)

######## CADL ##################################################################

CADL_fit<-CA_complete_fit_speed(                                    # <1>
  C_mat=cbind(                                                    # <1>
    df_mix_coc_int$Dose_EPX,                                      # <1>
    df_mix_coc_int$Dose_IMD                                       # <1>
    ),                                                            # <1>
  Response=df_mix_coc_int$Response,                               # <1>
  interact="DL",                                                  # <1>
  param=param,                                                    # <1>
  error_type = "Poisson",
  multicore = TRUE,                                               # <1>
  mc.cores = 4                                                    # <1>
  ) |>                                                                # <1>
  as.data.frame()
CADL_fit$Type <- "DL"
CADL_fit$Ref <- "CA"

LogLikelihood_CADL <- CADL_fit$Error
a_CADL <- CADL_fit$a
b_CADL <- CADL_fit$b
# Printing results
a_CADL_print <- signif(a_CADL, 3)
b_CADL_print <- signif(b_CADL, 3)
LogLikelihood_CADL_print <- signif(LogLikelihood_CADL, signif_LL)

######## IADL ##################################################################

IADL_fit<-IA_complete_fit_speed(                                    # <1>
  C_mat=cbind(                                                    # <1>
    df_mix_coc_int$Dose_EPX,                                      # <1>
    df_mix_coc_int$Dose_IMD                                       # <1>
    ),                                                            # <1>
  Response=df_mix_coc_int$Response,                               # <1>
  interact="DL",                                                  # <1>
  param=param,                                                    # <1>
  error_type = "Poisson",
  multicore = TRUE,                                               # <1>
  mc.cores = 4                                                    # <1>
  ) |>                                                                # <1>
  as.data.frame()
IADL_fit$Type <- "DL"
IADL_fit$Ref <- "IA"

LogLikelihood_IADL <- IADL_fit$Error
a_IADL <- IADL_fit$a
b_IADL <- IADL_fit$b
# Printing results
a_IADL_print <- signif(a_IADL, 3)
b_IADL_print <- signif(b_IADL, 3)
LogLikelihood_IADL_print <- signif(LogLikelihood_IADL, signif_LL)

######## CADR ##################################################################

CADR_fit<-CA_complete_fit_speed(                                    # <1>
  C_mat=cbind(                                                    # <1>
    df_mix_coc_int$Dose_EPX,                                      # <1>
    df_mix_coc_int$Dose_IMD                                       # <1>
    ),                                                            # <1>
  Response=df_mix_coc_int$Response,                               # <1>
  interact="DR",                                                  # <1>
  param=param,                                                    # <1>
  error_type = "Poisson",
  multicore = TRUE,                                               # <1>
  mc.cores = 4                                                    # <1>
  ) |>                                                                # <1>
  as.data.frame()
CADR_fit$Type <- "DR"
CADR_fit$Ref <- "CA"

LogLikelihood_CADR <- CADR_fit$Error
a_CADR <- CADR_fit$a
b_CADR <- CADR_fit$b
# Printing results
a_CADR_print <- signif(a_CADR, 3)
b_CADR_print <- signif(b_CADR, 3)
LogLikelihood_CADR_print <- signif(LogLikelihood_CADR, signif_LL)

######## IADR ##################################################################

IADR_fit<-IA_complete_fit_speed(                                    # <1>
  C_mat=cbind(                                                    # <1>
    df_mix_coc_int$Dose_EPX,                                      # <1>
    df_mix_coc_int$Dose_IMD                                       # <1>
    ),                                                            # <1>
  Response=df_mix_coc_int$Response,                               # <1>
  interact="DR",                                                  # <1>
  param=param,                                                    # <1>
  error_type = "Poisson",
  multicore = TRUE,                                               # <1>
  mc.cores = 4                                                    # <1>
  ) |>                                                                # <1>
  as.data.frame()
IADR_fit$Type <- "DR"
IADR_fit$Ref <- "IA"

LogLikelihood_IADR <- IADR_fit$Error
a_IADR <- IADR_fit$a
b_IADR <- IADR_fit$b
# Printing results
a_IADR_print <- signif(a_IADR, 3)
b_IADR_print <- signif(b_IADR, 3)
LogLikelihood_IADR_print <- signif(LogLikelihood_IADR, signif_LL)
```

```{r CI, message=F, warning=F}

N_draws <- 2000
# CI_CASA <- f_Jonker_CI_calculations_condition(
#   df_data = df_mix_coc_int,
#   N_draws = N_draws,
#   interact = "SA",
#   reference = "CA",
#   error_type = "Poisson"
#     )

#save(CI_CASA, file = here::here("mod/CI_cond_CASA.RData"))

load(here::here("mod/CI_cond_CASA.RData"))

# CI_CADL <- f_Jonker_CI_calculations_condition(
#   df_data = df_mix_coc_int,
#   N_draws = N_draws,
#   interact = "DL",
#   reference = "CA",
#   error_type = "Poisson"
#     )
# 
# save(CI_CADL, file = here::here("mod/CI_cond_CADL.RData"))
# 
load(here::here("mod/CI_cond_CADL.RData"))

# CI_CADR <- f_Jonker_CI_calculations_condition(
#   df_data = df_mix_coc_int,
#   N_draws = N_draws,
#   interact = "DR",
#   reference = "CA",
#   error_type = "Poisson"
#     )
# 
# save(CI_CADR, file = here::here("mod/CI_cond_CADR.RData"))
# 
load(here::here("mod/CI_cond_CADR.RData"))


# CI_IASA <- f_Jonker_CI_calculations_condition(
#   df_data = df_mix_coc_int,
#   N_draws = N_draws,
#   interact = "SA",
#   reference = "IA",
#   error_type = "Poisson"
#     )

#save(CI_IASA, file = here::here("mod/CI_cond_IASA.RData"))

load(here::here("mod/CI_cond_IASA.RData"))

# CI_IADL <- f_Jonker_CI_calculations_condition(
#   df_data = df_mix_coc_int,
#   N_draws = N_draws,
#   interact = "DL",
#   reference = "IA",
#   error_type = "Poisson"
#     )
# 
# save(CI_IADL, file = here::here("mod/CI_cond_IADL.RData"))
# 
load(here::here("mod/CI_cond_IADL.RData"))

# CI_IADR <- f_Jonker_CI_calculations_condition(
#   df_data = df_mix_coc_int,
#   N_draws = N_draws,
#   interact = "DR",
#   reference = "IA",
#   error_type = "Poisson"
#     )
# 
# save(CI_IADR, file = here::here("mod/CI_cond_IADR.RData"))
# 
load(here::here("mod/CI_cond_IADR.RData"))

```

```{r resJonker, warning=F, message=F}
df_Jonker <- rbind(CA_fit, CASA_fit, CADL_fit, CADR_fit, IA_fit, IASA_fit, IADL_fit, IADR_fit) |> 
  as.data.frame() |> 
  mutate(Likelihood = Error)

df_Jonker$a_2.5 <- c(NA, CI_CASA$a_2.5, CI_CADL$a_2.5, CI_CADR$a_2.5, 
                     NA, CI_IASA$a_2.5, CI_IADL$a_2.5, CI_IADR$a_2.5)
df_Jonker$a_97.5 <- c(NA, CI_CASA$a_97.5, CI_CADL$a_97.5, CI_CADR$a_97.5, 
                      NA, CI_IASA$a_97.5, CI_IADL$a_97.5, CI_IADR$a_97.5)
df_Jonker$b_2.5 <- c(NA, CI_CASA$b_2.5, CI_CADL$b_2.5, CI_CADR$b_2.5, 
                     NA, CI_IASA$b_2.5, CI_IADL$b_2.5, CI_IADR$b_2.5)
df_Jonker$b_97.5 <- c(NA, CI_CASA$b_97.5, CI_CADL$b_97.5, CI_CADR$b_97.5, 
                      NA, CI_IASA$b_97.5, CI_IADL$b_97.5, CI_IADR$b_97.5)

df_Jonker <- df_Jonker[, c("Type", "a", "a_2.5", "a_97.5",
                           "b", "b_2.5", "b_97.5", "Likelihood", "Ref")]

df_Jonker |> datatable(options = list(dom = 't'), class="hover") |> 
  formatSignif(columns = c("a", "a_2.5", "a_97.5", "b", "b_2.5", "b_97.5", "Likelihood"), c(4, 4, 4, 4, 4, 4,7))
```

### Step 3 - Test of models

We need first to test the acceptability of the CA and IA model against an anova model.

Creation of the anova model :

```{r}
# The anova model 
glm_anova <- glm(Response ~ Dose_EPX + Dose_IMD, family = poisson(link = "log"), data = df_mix_coc_int)
LogLikelihood_anova <- as.numeric(logLik(glm_anova))
k_anova <- attr(logLik(glm_anova), "df")   # nombre de paramètres (inclut intercept)

```

```{r FtestCAanova, warning=F, message=F}
LL0 <- LogLikelihood_anova    # log-vraisemblance du modèle CA
LL1 <- LogLikelihood_CA    # log-vraisemblance du modèle SA (CA reference)

p0 <- k_anova         
p1 <- 4     

D <- 2 * (LL1 - LL0)
p_val <- pchisq(D, df = p1 - p0, lower.tail = FALSE)

cat("Comparison Anova/CA - D =", D, "p =", p_val, "\n")

```

```{r FtestIAanova, warning=F, message=F}
LL0 <- LogLikelihood_anova    # log-vraisemblance du modèle CA
LL1 <- LogLikelihood_IA    # log-vraisemblance du modèle SA (CA reference)

p0 <- k_anova         
p1 <- 4     

D <- 2 * (LL1 - LL0)
p_val <- pchisq(D, df = p1 - p0, lower.tail = FALSE)

cat("Comparison Anova/IA - D =", D, "p =", p_val, "\n")

```

#### CA reference

We are now able to conduct an Log-Likelihood Ratio test to compare the models with the CA reference :

```{r FtestCASA, warning=F, message=F}
LL0 <- LogLikelihood_CA    # log-vraisemblance du modèle CA
LL1 <- LogLikelihood_CASA    # log-vraisemblance du modèle SA (CA reference)

p0 <- 0         # nombre de paramètres additionnels dans le modèle CA (par rapport à ta base)
p1 <- 1         # un paramètre d'interaction dans le modèle SA (CA reference)

D <- 2 * (LL1 - LL0)
p_val <- pchisq(D, df = p1 - p0, lower.tail = FALSE)

cat("Comparison CA/SA - D =", D, "p =", p_val, "\n")

```

The SA model is not significatively different than the CA model. There is no significant interaction between EPX & IMD for cocoon production. Therefore, the best model to represent the data is the CA model.

```{r FtestCADL, warning=F, message=F}
LL0 <- LogLikelihood_CA    # log-vraisemblance du modèle CA 
LL1 <- LogLikelihood_CADL    # log-vraisemblance du modèle DL (CA reference)

p0 <- 0         # nombre de paramètres additionnels dans le modèle CA (par rapport à ta base)
p1 <- 2         # un paramètre d'interaction dans le modèle DL (CA reference)

D <- 2 * (LL1 - LL0)
p_val <- pchisq(D, df = p1 - p0, lower.tail = FALSE)

cat("Comparison CA/DL - D =", D, "p =", p_val, "\n")

```

```{r FtestCADR, warning=F, message=F}
LL0 <- LogLikelihood_CA    # log-vraisemblance du modèle CA
LL1 <- LogLikelihood_CADR    # log-vraisemblance du modèle DR

p0 <- 0         # nombre de paramètres additionnels dans le modèle CA (par rapport à ta base)
p1 <- 1         # un paramètre d'interaction dans le modèle DR (CA reference)

D <- 2 * (LL1 - LL0)
p_val <- pchisq(D, df = p1 - p0, lower.tail = FALSE)

cat("Comparison CA/DR - D =", D, "p =", p_val, "\n")

```

#### IA reference

We are now able to conduct an Log-Likelihood Ratio test to compare the models with the IA reference :

```{r FtestIASA, warning=F, message=F}
LL0 <- LogLikelihood_IA    # log-vraisemblance du modèle IA
LL1 <- LogLikelihood_IASA    # log-vraisemblance du modèle (IA reference)

p0 <- 0         # nombre de paramètres additionnels dans le modèle IA (par rapport à ta base)
p1 <- 1         # un paramètre d'interaction dans le modèle SA (IA reference)

D <- 2 * (LL1 - LL0)
p_val <- pchisq(D, df = p1 - p0, lower.tail = FALSE)

cat("Comparison IA/SA - D =", D, "p =", p_val, "\n")

```

The SA model is not significatively different than the CA model. There is no significant interaction between EPX & IMD for cocoon production. Therefore, the best model to represent the data is the CA model.

```{r FtestIADL, warning=F, message=F}
LL0 <- LogLikelihood_IA    # log-vraisemblance du modèle IA
LL1 <- LogLikelihood_IADL    # log-vraisemblance du modèle DL (IA reference)

p0 <- 0         # nombre de paramètres additionnels dans le modèle IA (par rapport à ta base)
p1 <- 2         # un paramètre d'interaction dans le modèle DL (IA reference)

D <- 2 * (LL1 - LL0)
p_val <- pchisq(D, df = p1 - p0, lower.tail = FALSE)

cat("Comparison IA/DL - D =", D, "p =", p_val, "\n")

```

```{r FtestIADR, warning=F, message=F}
LL0 <- LogLikelihood_IA    # log-vraisemblance du modèle IA
LL1 <- LogLikelihood_IADR    # log-vraisemblance du modèle SA (IA reference)

p0 <- 0         # nombre de paramètres additionnels dans le modèle IA (par rapport à ta base)
p1 <- 1         # un paramètre d'interaction dans le modèle SA (IA reference)

D <- 2 * (LL1 - LL0)
p_val <- pchisq(D, df = p1 - p0, lower.tail = FALSE)

cat("Comparison IA/DR - D =", D, "p =", p_val, "\n")

```

### Step 4 - Graphical representation

```{r calcSurface, message=F, warning=F, execute = F}
########### CA ################################

df_data_solved_surf_CA <- CA_complete2(
  C_mat=grid,
  Max=Max,
  Slopes=Slopes,
  Ec50s=Ec50s,
  interact="none",
  multicore = TRUE
  )

save(df_data_solved_surf_CA, file = here::here("mod/MIX/Surface_CA.RData"))

########### CASA ################################

df_data_solved_surf_CASA <- CA_complete2(
  C_mat=grid,
  Max=Max,
  Slopes=Slopes,
  Ec50s=Ec50s,
  interact="SA",
  a = a_CASA,
  multicore = TRUE
  )

save(df_data_solved_surf_CASA, file = here::here("mod/MIX/Surface_CASA.RData"))

########### CADL ################################

df_data_solved_surf_CADL <- CA_complete2(
  C_mat=grid,
  Max=Max,
  Slopes=Slopes,
  Ec50s=Ec50s,
  interact="DL",
  a = a_CADL,
  b = b_CADL,
  multicore = TRUE
  )

save(df_data_solved_surf_CADL, file = here::here("mod/MIX/Surface_CADL.RData"))

########### CADR ################################

df_data_solved_surf_CADR <- CA_complete2(
  C_mat=grid,
  Max=Max,
  Slopes=Slopes,
  Ec50s=Ec50s,
  interact="DR",
  a = a_CADR,
  b = b_CADR,
  multicore = TRUE
  )

save(df_data_solved_surf_CADR, file = here::here("mod/MIX/Surface_CADR.RData"))

########### IA ################################

df_data_solved_surf_IA <- IA_complete2(
  C_mat=grid,
  Max=Max,
  Slopes=Slopes,
  Ec50s=Ec50s,
  interact="none"
  )

save(df_data_solved_surf_IA, file = here::here("mod/MIX/Surface_IA.RData"))

########### IASA ################################

df_data_solved_surf_IASA <- IA_complete2(
  C_mat=grid,
  Max=Max,
  Slopes=Slopes,
  Ec50s=Ec50s,
  interact="SA",
  a = a_IASA
  )

save(df_data_solved_surf_IASA, file = here::here("mod/MIX/Surface_IASA.RData"))

########### IADL ################################

df_data_solved_surf_IADL <- IA_complete2(
  C_mat=grid,
  Max=Max,
  Slopes=Slopes,
  Ec50s=Ec50s,
  interact="DL",
  a = a_IADL,
  b = b_IADL
  )

save(df_data_solved_surf_IADL, file = here::here("mod/MIX/Surface_IADL.RData"))

########### IADR ################################

df_data_solved_surf_IADR <- IA_complete2(
  C_mat=grid,
  Max=Max,
  Slopes=Slopes,
  Ec50s=Ec50s,
  interact="DR",
  a = a_IADR,
  b = b_IADR
  )

save(df_data_solved_surf_IADR, file = here::here("mod/MIX/Surface_IADR.RData"))
```

```{r simdataCAfit}

########### CA ################################

load(here::here("mod/MIX/Surface_CA.RData"))

df_data_solved_surf_ordered_CA <- df_data_solved_surf_CA[order(grid[,2])]

z_CA <- matrix(
  df_data_solved_surf_ordered_CA,
  nrow=length(grid_C1),
  ncol=length(grid_C2),
  byrow=FALSE
  )

########### CASA ################################

load(here::here("mod/MIX/Surface_CASA.RData"))

df_data_solved_surf_ordered_CASA <- df_data_solved_surf_CASA[order(grid[,2])]

z_CASA <- matrix(
  df_data_solved_surf_ordered_CASA,
  nrow=length(grid_C1),
  ncol=length(grid_C2),
  byrow=FALSE
  )

########### CADL ################################

load(here::here("mod/MIX/Surface_CADL.RData"))

df_data_solved_surf_ordered_CADL <- df_data_solved_surf_CADL[order(grid[,2])]

z_CADL <- matrix(
  df_data_solved_surf_ordered_CADL,
  nrow=length(grid_C1),
  ncol=length(grid_C2),
  byrow=FALSE
  )

########### CADR ################################

load(here::here("mod/MIX/Surface_CADR.RData"))

df_data_solved_surf_ordered_CADR <- df_data_solved_surf_CADR[order(grid[,2])]

z_CADR <- matrix(
  df_data_solved_surf_ordered_CADR,
  nrow=length(grid_C1),
  ncol=length(grid_C2),
  byrow=FALSE
  )

########### IA ################################

load(here::here("mod/MIX/Surface_IA.RData"))

df_data_solved_surf_ordered_IA <- df_data_solved_surf_IA[order(grid[,2])]

z_IA <- matrix(
  df_data_solved_surf_ordered_IA,
  nrow=length(grid_C1),
  ncol=length(grid_C2),
  byrow=FALSE
  )

########### IASA ################################

load(here::here("mod/MIX/Surface_IASA.RData"))

df_data_solved_surf_ordered_IASA <- df_data_solved_surf_IASA[order(grid[,2])]

z_IASA <- matrix(
  df_data_solved_surf_ordered_IASA,
  nrow=length(grid_C1),
  ncol=length(grid_C2),
  byrow=FALSE
  )

########### IADL ################################

load(here::here("mod/MIX/Surface_IADL.RData"))

df_data_solved_surf_ordered_IADL <- df_data_solved_surf_IADL[order(grid[,2])]

z_IADL <- matrix(
  df_data_solved_surf_ordered_IADL,
  nrow=length(grid_C1),
  ncol=length(grid_C2),
  byrow=FALSE
  )

########### IADR ################################

load(here::here("mod/MIX/Surface_IADR.RData"))

df_data_solved_surf_ordered_IADR <- df_data_solved_surf_IADR[order(grid[,2])]

z_IADR <- matrix(
  df_data_solved_surf_ordered_IADR,
  nrow=length(grid_C1),
  ncol=length(grid_C2),
  byrow=FALSE
  )

```

#### 2D representations

```{r, warning = F, message = F, results=F}

# Calculation of the equivalent doses of the mono-substances that would give the said effect

f_dose_eq <- function(model, resp) {
  out <- tryCatch(
    ED(model, as.numeric(resp), type = "absolute", interval = "delta"),
    error = function(e) matrix(NA, nrow = 4, ncol = 2) # si erreur
  )

  m <- as.matrix(out)

  # Si moins de 4 lignes → compléter avec NA
  if (nrow(m) < 4) {
    m <- rbind(m, matrix(NA, nrow = 4 - nrow(m), ncol = ncol(m)))
  }

  tibble(
    Dose_eq_IMD       = m[1, 2],
    Dose_eq_EPX       = m[1, 1],
    Dose_eq_IMD_lower = m[3, 2],
    Dose_eq_EPX_lower = m[3, 1],
    Dose_eq_IMD_upper = m[4, 2],
    Dose_eq_EPX_upper = m[4, 1]
  )
}

df_mix_coc_plot <- df_mix_coc_mean %>%
  rowwise() %>%
  mutate(f_dose_eq(drc.mix.IE, Nb_cocoons)) %>%
  ungroup()

# Graphique
ggplot(
  df_mix_coc_plot, 
  aes(
    x = Dose_eq_IMD, 
    y = Dose_eq_EPX
    )
  ) +
  geom_point(size = 3) +
  geom_errorbarh(
    aes(
      xmin = Dose_eq_IMD_lower, 
      xmax = Dose_eq_IMD_upper
      ), 
    height = 0
    ) +
  geom_errorbar(
    aes(
      ymin = Dose_eq_EPX_lower, 
      ymax = Dose_eq_EPX_upper
      ), 
    width = 0
    ) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    x = "Imidacloprid equivalent (mg/kg)",
    y = "Epoxiconazole equivalent (mg/kg)"
  ) +
  theme_minimal()


```

::: panel-tabset
## SA model (CA ref.)

```{r, warning=F, message=F}
#| fig-cap: Estimated surface isobols for cocoon production. The CA model is represented by the grey dotted lines and the SA model by the blue curves.
#| label: fig-SurfCASA2Ddata
#| fig-width: 5
#| fig-height: 4

target_effect <- 50

grid <- expand.grid(x = grid_C1, y = grid_C2)
grid$z_CA <- as.vector(z_CA)
grid$z_CASA <- as.vector(z_CASA)

bin_contour <- 1

p <- ggplot(
  grid, 
  aes(x = x, y = y)
) +
  geom_contour(
    aes(z = z_CA),
    color = Nord_polar[4],
    linewidth = 0.8,
    linetype = "dotted",
    binwidth = bin_contour
  ) +
  geom_contour(
    aes(z = z_CASA),
    color = Nord_frost[4], 
    linewidth = 1,
    binwidth = bin_contour
  ) +
  metR::geom_text_contour(
    aes(z = z_CASA), 
    stroke = 0.2,
    size = 4,
    color = Nord_frost[4],
    skip = 1,
    label.placer = label_placer_flattest(),
    binwidth = bin_contour
  ) +
  labs(
    x = expression("[EPX] (mg·kg"^-1*")"),
    y = expression("[IMD] (mg·kg"^-1*")")
  ) +
  theme_minimal(base_size = 13) +
  theme(
    axis.title = element_text(face = "bold"),
    axis.text = element_text(color = "black"),
    plot.margin = margin(10, 10, 10, 10)
  )

p

```

```{r, include=F}
ggsave(
  filename="Mix_spring_mix_contour_data_CASA.png", 
  plot=p, 
  width=6, height = 5, 
  path=here::here("fig/Mixture")
  )
ggsave(
  filename="Mix_spring_mix_contour_data_CASA.svg", 
  plot=p, 
  width=6, height = 5, 
  path=here::here("fig/Mixture")
  )
```

## DL model (CA ref.)

```{r, warning=F, message=F}
#| fig-cap: Estimated surface isobols for cocoon production. The CA model is represented by the grey dotted lines and the DL model by the blue curves.
#| label: fig-SurfCADL2D
#| fig-width: 5
#| fig-height: 4

grid <- expand.grid(x = grid_C1, y = grid_C2)
grid$z_CA <- as.vector(z_CA)
grid$z_CADL <- as.vector(z_CADL)

bin_contour <- 1

p <- ggplot(
  grid, 
  aes(x = x, y = y)
) +
  geom_contour(
    aes(z = z_CA),
    color = Nord_polar[4],
    linewidth = 0.8,
    linetype = "dotted",
    binwidth = bin_contour
  ) +
  geom_contour(
    aes(z = z_CADL),
    color = Nord_frost[4], 
    linewidth = 1,
    binwidth = bin_contour
  ) +
  metR::geom_text_contour(
    aes(z = z_CADL), 
    stroke = 0.2,
    size = 4,
    color = Nord_frost[4],
    skip = 1,
    label.placer = label_placer_flattest(),
    binwidth = bin_contour
  ) +
  labs(
    x = expression("[EPX] (mg·kg"^-1*")"),
    y = expression("[IMD] (mg·kg"^-1*")")
  ) +
  theme_minimal(base_size = 13) +
  theme(
    axis.title = element_text(face = "bold"),
    axis.text = element_text(color = "black"),
    plot.margin = margin(10, 10, 10, 10)
  )

p

```

```{r, include=F}
ggsave(
  filename="Mix_spring_mix_contour_data_CADL.png", 
  plot=p, 
  width=6, height = 5, 
  path=here::here("fig/Mixture")
  )
ggsave(
  filename="Mix_spring_mix_contour_data_CADL.svg", 
  plot=p, 
  width=6, height = 5, 
  path=here::here("fig/Mixture")
  )
```

## SA model (IA ref.)

```{r, warning=F, message=F}
#| fig-cap: Estimated surface isobols for cocoon production. The IA model is represented by the grey dotted lines and the SA model by the blue curves.
#| label: fig-SurfIASA2Ddata
#| fig-width: 5
#| fig-height: 4

target_effect <- 50

grid <- expand.grid(x = grid_C1, y = grid_C2)
grid$z_IA <- as.vector(z_IA)
grid$z_IASA <- as.vector(z_IASA)

bin_contour <- 1

p <- ggplot(
  grid, 
  aes(x = x, y = y)
) +
  geom_contour(
    aes(z = z_IA),
    color = Nord_polar[4],
    linewidth = 0.8,
    linetype = "dotted",
    binwidth = bin_contour
  ) +
  geom_contour(
    aes(z = z_IASA),
    color = Nord_frost[4], 
    linewidth = 1,
    binwidth = bin_contour
  ) +
  metR::geom_text_contour(
    aes(z = z_IASA), 
    stroke = 0.2,
    size = 4,
    color = Nord_frost[4],
    skip = 1,
    label.placer = label_placer_flattest(),
    binwidth = bin_contour
  ) +
  labs(
    x = expression("[EPX] (mg·kg"^-1*")"),
    y = expression("[IMD] (mg·kg"^-1*")")
  ) +
  theme_minimal(base_size = 13) +
  theme(
    axis.title = element_text(face = "bold"),
    axis.text = element_text(color = "black"),
    plot.margin = margin(10, 10, 10, 10)
  )

p

```

```{r, include=F}
ggsave(
  filename="Mix_spring_mix_contour_data_IASA.png", 
  plot=p, 
  width=6, height = 5, 
  path=here::here("fig/Mixture")
  )
ggsave(
  filename="Mix_spring_mix_contour_data_IASA.svg", 
  plot=p, 
  width=6, height = 5, 
  path=here::here("fig/Mixture")
  )
```

## DL model (IA ref.)

```{r, warning=F, message=F}
#| fig-cap: Estimated surface isobols for cocoon production. The IA model is represented by the grey dotted lines and the DL model by the blue curves.
#| label: fig-SurfIADL2Ddata
#| fig-width: 5
#| fig-height: 4

target_effect <- 50

grid <- expand.grid(x = grid_C1, y = grid_C2)
grid$z_IA <- as.vector(z_IA)
grid$z_IADL <- as.vector(z_IADL)

bin_contour <- 1

p <- ggplot(
  grid, 
  aes(x = x, y = y)
) +
  geom_contour(
    aes(z = z_IA),
    color = Nord_polar[4],
    linewidth = 0.8,
    linetype = "dotted",
    binwidth = bin_contour
  ) +
  geom_contour(
    aes(z = z_IADL),
    color = Nord_frost[4], 
    linewidth = 1,
    binwidth = bin_contour
  ) +
  metR::geom_text_contour(
    aes(z = z_IADL), 
    stroke = 0.2,
    size = 4,
    color = Nord_frost[4],
    skip = 1,
    label.placer = label_placer_flattest(),
    binwidth = bin_contour
  ) +
  labs(
    x = expression("[EPX] (mg·kg"^-1*")"),
    y = expression("[IMD] (mg·kg"^-1*")")
  ) +
  theme_minimal(base_size = 13) +
  theme(
    axis.title = element_text(face = "bold"),
    axis.text = element_text(color = "black"),
    plot.margin = margin(10, 10, 10, 10)
  )

p

```

```{r, include=F}
ggsave(
  filename="Mix_spring_mix_contour_data_IADL.png", 
  plot=p, 
  width=6, height = 5, 
  path=here::here("fig/Mixture")
  )
ggsave(
  filename="Mix_spring_mix_contour_data_IADL.svg", 
  plot=p, 
  width=6, height = 5, 
  path=here::here("fig/Mixture")
  )
```
:::

##### Dose-response curves per ratio

```{r drcratiopred, message=F, warning=F}

xIMD_I <- expand.grid(
  exp(
    seq(
      log(0.00001),log(5000),
      by=(log(5000)-log(0.00001))/100
    )
  )
)

xEPX_E <- expand.grid(
  exp(
    seq(
      log(0.00001),log(5000),
      by=(log(5000)-log(0.00001))/100
    )
  )
)

df_x_E <- data.frame(
  Dose_EPX = xEPX_E$Var1
) |> 
  mutate(
    Dose_IMD = 0,
    Ratio = "I"
    )

df_x_I <- data.frame(
  Dose_IMD = xIMD_I$Var1
) |> 
  mutate(
    Dose_EPX = 0,
    Ratio = "E"
    )

df_x_F <- data.frame(
  Dose_EPX = 3/4*Ec50s[1]/Ec50s[2]*xEPX_E$Var1/100,
  Dose_IMD = 1/4*Ec50s[1]/Ec50s[2]*xIMD_I$Var1/100
) |> 
  mutate(Ratio = "F")
df_x_G <- data.frame(
  Dose_EPX = 1/2*Ec50s[1]/Ec50s[2]*xEPX_E$Var1/200,
  Dose_IMD = 1/2*Ec50s[1]/Ec50s[2]*xIMD_I$Var1/200
) |> 
  mutate(Ratio = "G")
df_x_H <- data.frame(
  Dose_EPX = 1/4*Ec50s[1]/Ec50s[2]*xEPX_E$Var1/200,
  Dose_IMD = 3/4*Ec50s[1]/Ec50s[2]*xIMD_I$Var1/200
) |> 
  mutate(Ratio = "H")

df_pred_drc_ratio <- rbind(df_x_E, df_x_F, df_x_G, df_x_H, df_x_I)

# Vérification of the lines

# width_iso <- 1.1
# size_points <- 3

# plot_design <- ggplot()+
#   # Design points
#   geom_point(
#     data=df_pred_drc_ratio, 
#     aes(
#       x=Dose_EPX, 
#       y=Dose_IMD,
#       color = Ratio
#       ), 
#     size=size_points
#     )+
#   
#   labs(
#     x="Epoxiconazole (mg/kg)",
#     y="Imidacloprid (mg/kg)"
#     )+
#   
#   lims(x = c(0, 10000), y = c(0, 10000))+
#   
#   theme_minimal(12)

C_mat_E <- cbind(df_x_E$Dose_EPX,df_x_E$Dose_IMD)
C_mat_F <- cbind(df_x_F$Dose_EPX,df_x_F$Dose_IMD)
C_mat_G <- cbind(df_x_G$Dose_EPX,df_x_G$Dose_IMD)
C_mat_H <- cbind(df_x_H$Dose_EPX,df_x_H$Dose_IMD)
C_mat_I <- cbind(df_x_I$Dose_EPX,df_x_I$Dose_IMD)

# We should set the a SA interaction parameter to around 1000 to see a difference between the dose-response curves for the different ratios

response_CA_E <- CA_complete2(
  C_mat_E, 
  Max, Slopes, Ec50s, 
  interact="none"
  )
response_CASA_E <- CA_complete2(
  C_mat_E, 
  Max, Slopes, Ec50s, 
  interact="SA", 
  a=a_CASA
  )
response_CADL_E <- CA_complete2(
  C_mat_E, 
  Max, Slopes, Ec50s, 
  interact="DL", 
  a=a_CADL,
  b=b_CADL
  )

response_CA_F <- CA_complete2(
  C_mat_F, 
  Max, Slopes, Ec50s, 
  interact="none"
  )
response_CASA_F <- CA_complete2(
  C_mat_F, 
  Max, Slopes, Ec50s, 
  interact="SA", 
  a=a_CASA
  )
response_CADL_F <- CA_complete2(
  C_mat_F, 
  Max, Slopes, Ec50s, 
  interact="DL", 
  a=a_CADL,
  b=b_CADL
  )

response_CA_G <- CA_complete2(
  C_mat_G, 
  Max, Slopes, Ec50s, 
  interact="none"
  )
response_CASA_G <- CA_complete2(
  C_mat_G, 
  Max, Slopes, Ec50s, 
  interact="SA", 
  a=a_CASA
  )
response_CADL_G <- CA_complete2(
  C_mat_G, 
  Max, Slopes, Ec50s, 
  interact="DL", 
  a=a_CADL,
  b=b_CADL
  )

response_CA_H <- CA_complete2(
  C_mat_H, 
  Max, Slopes, Ec50s, 
  interact="none"
  )
response_CASA_H <- CA_complete2(
  C_mat_H, 
  Max, Slopes, Ec50s, 
  interact="SA", 
  a=a_CASA
  )
response_CADL_H <- CA_complete2(
  C_mat_H, 
  Max, Slopes, Ec50s, 
  interact="DL", 
  a=a_CADL,
  b=b_CADL
  )

response_CA_I <- CA_complete2(
  C_mat_I, 
  Max, Slopes, Ec50s, 
  interact="none"
  )
response_CASA_I <- CA_complete2(
  C_mat_I, 
  Max, Slopes, Ec50s, 
  interact="SA", 
  a=a_CASA
  )
response_CADL_I <- CA_complete2(
  C_mat_I, 
  Max, Slopes, Ec50s, 
  interact="DL", 
  a=a_CADL,
  b = b_CADL
  )


response_IA_E <- IA_complete2(
  C_mat_E, 
  Max, Slopes, Ec50s, 
  interact="none"
  )
response_IASA_E <- IA_complete2(
  C_mat_E, 
  Max, Slopes, Ec50s, 
  interact="SA", 
  a=a_IASA
  )
response_IADL_E <- IA_complete2(
  C_mat_E, 
  Max, Slopes, Ec50s, 
  interact="DL", 
  a=a_IADL,
  b = b_IADL
  )

response_IA_F <- IA_complete2(
  C_mat_F, 
  Max, Slopes, Ec50s, 
  interact="none"
  )
response_IASA_F <- IA_complete2(
  C_mat_F, 
  Max, Slopes, Ec50s, 
  interact="SA", 
  a=a_IASA
  )
response_IADL_F <- IA_complete2(
  C_mat_F, 
  Max, Slopes, Ec50s, 
  interact="DL", 
  a=a_IADL,
  b=b_IADL
  )

response_IA_G <- IA_complete2(
  C_mat_G, 
  Max, Slopes, Ec50s, 
  interact="none"
  )
response_IASA_G <- IA_complete2(
  C_mat_G, 
  Max, Slopes, Ec50s, 
  interact="SA", 
  a=a_IASA
  )
response_IADL_G <- IA_complete2(
  C_mat_G, 
  Max, Slopes, Ec50s, 
  interact="DL", 
  a=a_IADL,
  b=b_IADL
  )

response_IA_H <- IA_complete2(
  C_mat_H, 
  Max, Slopes, Ec50s, 
  interact="none"
  )
response_IASA_H <- IA_complete2(
  C_mat_H, 
  Max, Slopes, Ec50s, 
  interact="SA", 
  a=a_IASA
  )
response_IADL_H <- IA_complete2(
  C_mat_H, 
  Max, Slopes, Ec50s, 
  interact="DL", 
  a=a_IADL,
  b=b_IADL
  )

response_IA_I <- IA_complete2(
  C_mat_I, 
  Max, Slopes, Ec50s, 
  interact="none"
  )
response_IASA_I <- IA_complete2(
  C_mat_I, 
  Max, Slopes, Ec50s, 
  interact="SA", 
  a=a_IASA
  )
response_IADL_I <- IA_complete2(
  C_mat_I, 
  Max, Slopes, Ec50s, 
  interact="DL", 
  a=a_IADL,
  b = b_IADL
  )


responses_CA <- c(
  response_CA_E,
  response_CA_F,
  response_CA_G,
  response_CA_H,
  response_CA_I
  )

responses_CASA <- c(
  response_CASA_E, 
  response_CASA_F,
  response_CASA_G, 
  response_CASA_H,
  response_CASA_I
  )

responses_CADL <- c(
  response_CADL_E, 
  response_CADL_F,
  response_CADL_G, 
  response_CADL_H,
  response_CADL_I
  )


responses_IA <- c(
  response_IA_E,
  response_IA_F,
  response_IA_G,
  response_IA_H,
  response_IA_I
  )

responses_IASA <- c(
  response_IASA_E, 
  response_IASA_F,
  response_IASA_G, 
  response_IASA_H,
  response_IASA_I
  )

responses_IADL <- c(
  response_IADL_E, 
  response_IADL_F,
  response_IADL_G, 
  response_IADL_H,
  response_IADL_I
  )



Ratio_E <- "1:0 (EPX only)"
Ratio_I <- "0:1 (IMD only)"
Ratio_F <- "3:1"
Ratio_G <- "1:1"
Ratio_H <- "1:3"

df_pred_drc_ratio_CA <- cbind(df_pred_drc_ratio, Response = responses_CA) |> 
  mutate(
    TU = Dose_IMD/Ec50s[2] + Dose_EPX/Ec50s[1],
    Ratio_plot = case_when(
      Ratio == "E" ~ Ratio_E,
      Ratio == "F" ~ Ratio_F,
      Ratio == "G" ~ Ratio_G,
      Ratio == "H" ~ Ratio_H,
      Ratio == "I" ~ Ratio_I
    ),
    Ratio_plot = fct_relevel(Ratio_plot, c(Ratio_E, Ratio_F, Ratio_G, Ratio_H, Ratio_I))
    )
df_pred_drc_ratio_CASA <- cbind(df_pred_drc_ratio, Response = responses_CASA) |> 
  mutate(
    TU = Dose_IMD/Ec50s[2] + Dose_EPX/Ec50s[1],
    Ratio_plot = case_when(
      Ratio == "E" ~ Ratio_E,
      Ratio == "F" ~ Ratio_F,
      Ratio == "G" ~ Ratio_G,
      Ratio == "H" ~ Ratio_H,
      Ratio == "I" ~ Ratio_I
    ),
    Ratio_plot = fct_relevel(Ratio_plot, c(Ratio_E, Ratio_F, Ratio_G, Ratio_H, Ratio_I))
    )
df_pred_drc_ratio_CADL <- cbind(df_pred_drc_ratio, Response = responses_CADL) |> 
  mutate(
    TU = Dose_IMD/Ec50s[2] + Dose_EPX/Ec50s[1],
    Ratio_plot = case_when(
      Ratio == "E" ~ Ratio_E,
      Ratio == "F" ~ Ratio_F,
      Ratio == "G" ~ Ratio_G,
      Ratio == "H" ~ Ratio_H,
      Ratio == "I" ~ Ratio_I
    ),
    Ratio_plot = fct_relevel(Ratio_plot, c(Ratio_E, Ratio_F, Ratio_G, Ratio_H, Ratio_I))
    )

df_pred_drc_ratio_IA <- cbind(df_pred_drc_ratio, Response = responses_IA) |> 
  mutate(
    TU = Dose_IMD/Ec50s[2] + Dose_EPX/Ec50s[1],
    Ratio_plot = case_when(
      Ratio == "E" ~ Ratio_E,
      Ratio == "F" ~ Ratio_F,
      Ratio == "G" ~ Ratio_G,
      Ratio == "H" ~ Ratio_H,
      Ratio == "I" ~ Ratio_I
    ),
    Ratio_plot = fct_relevel(Ratio_plot, c(Ratio_E, Ratio_F, Ratio_G, Ratio_H, Ratio_I))
    )
df_pred_drc_ratio_IASA <- cbind(df_pred_drc_ratio, Response = responses_IASA) |> 
  mutate(
    TU = Dose_IMD/Ec50s[2] + Dose_EPX/Ec50s[1],
    Ratio_plot = case_when(
      Ratio == "E" ~ Ratio_E,
      Ratio == "F" ~ Ratio_F,
      Ratio == "G" ~ Ratio_G,
      Ratio == "H" ~ Ratio_H,
      Ratio == "I" ~ Ratio_I
    ),
    Ratio_plot = fct_relevel(Ratio_plot, c(Ratio_E, Ratio_F, Ratio_G, Ratio_H, Ratio_I))
    )
df_pred_drc_ratio_IADL <- cbind(df_pred_drc_ratio, Response = responses_IADL) |> 
  mutate(
    TU = Dose_IMD/Ec50s[2] + Dose_EPX/Ec50s[1],
    Ratio_plot = case_when(
      Ratio == "E" ~ Ratio_E,
      Ratio == "F" ~ Ratio_F,
      Ratio == "G" ~ Ratio_G,
      Ratio == "H" ~ Ratio_H,
      Ratio == "I" ~ Ratio_I
    ),
    Ratio_plot = fct_relevel(Ratio_plot, c(Ratio_E, Ratio_F, Ratio_G, Ratio_H, Ratio_I))
    )

```

::: panel-tabset
## CA model

```{r, warning=F, message=F}
#| fig-cap: Dose-response curves predicted by the CA model for each mixture ratio. Crosses correspond to the number of cocoons produced by one cosm and the bold points represent the mean per condition.
#| label: fig-drcIMDEPXratiosPredCA
#| fig-width: 8
#| fig-height: 6

line_width <- 1.2
size_axistitle <- 11

p_facetCA <- ggplot()+
  geom_line(
    data = df_pred_drc_ratio_CA,
    aes(
      x = TU, 
      y = Response,
      color=Ratio_plot
    )
  )+
  geom_point(
    data = df_mix_coc_plotdrc,
    aes(
      x = TU_mix_plot,
      y = Nb_cocoons,
      color=Ratio_plot,
      fill = Ratio_plot
      ),
    alpha = 0.6,
    shape = 4
  )+
  geom_point(
    data = df_mix_coc_mean_plotdrc,
    aes(
      x = TU_mix_plot,
      y = Nb_cocoons,
      color=Ratio_plot,
      fill = Ratio_plot
      ),
    size = 3
  )+
  scale_color_manual(values = pal_ratio)+
  scale_fill_manual(values = pal_ratio)+
  facet_wrap2(~ Ratio_plot, axes = "x") +
  #ylim(0, 3)+
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100),  # inclure la valeur fictive
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100")
  )+
  labs(
    x = "Toxic Unit (TU)",
    y = "Number of cocoons produced per cosm (#)"
  )+
  theme_bw()+
  theme(
    axis.title.x = element_text(size = size_axistitle),
    axis.title.y = element_text(size = size_axistitle),
    axis.text.x = element_text(),  
    axis.ticks.x = element_line(),    
    legend.position = "none",
    strip.text = element_text(face = "bold"),
    strip.placement = "outside",
    strip.background = element_rect(color = "black", fill = "grey95", size = 0, linetype = "solid"),
    panel.spacing = unit(0.6, "lines") 
  )

p_comp_CA <- ggplot()+

  geom_line(
    data = df_pred_drc_ratio_CA,
    aes(
      x = TU, 
      y = Response,
      color=Ratio_plot
    )
  )+

  scale_color_manual(values = pal_ratio)+
  scale_fill_manual(values = pal_ratio)+
  
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100),  # inclure la valeur fictive
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100")
  )+
  labs(
    x = "Toxic Unit (TU)",
    y = "Number of cocoons produced per cosm (#)"
  )+
  
  theme_bw()+
  theme(
    legend.position = "none",
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    strip.background = element_rect(
      color="black", 
      fill="grey95", 
      size=0, 
      linetype="solid"
      )
  )


p_CA <- p_facetCA + 
  inset_element(
    p_comp_CA,
    left = 0.67, bottom = -0.05, right = 1, top = 0.45
    )
p_CA
```

## SA model (CA ref.)

```{r, warning=F, message=F}
#| fig-cap: Dose-response curves predicted by the SA model with CA as reference for each mixture ratio. Crosses correspond to the number of cocoons produced by one cosm and the bold points represent the mean per condition.
#| label: fig-drcIMDEPXratiosPredCASA
#| fig-width: 8
#| fig-height: 6

line_width <- 1.2
size_axistitle <- 11

p_facetCASA <- ggplot()+
  geom_line(
    data = df_pred_drc_ratio_CASA,
    aes(
      x = TU, 
      y = Response,
      color=Ratio_plot
    )
  )+
  geom_point(
    data = df_mix_coc_plotdrc,
    aes(
      x = TU_mix_plot,
      y = Nb_cocoons,
      color=Ratio_plot,
      fill = Ratio_plot
      ),
    alpha = 0.6,
    shape = 4
  )+
  geom_point(
    data = df_mix_coc_mean_plotdrc,
    aes(
      x = TU_mix_plot,
      y = Nb_cocoons,
      color=Ratio_plot,
      fill = Ratio_plot
      ),
    size = 3
  )+
  scale_color_manual(values = pal_ratio)+
  scale_fill_manual(values = pal_ratio)+
  facet_wrap2(~ Ratio_plot, axes = "x") +
  #ylim(0, 3)+
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100),  # inclure la valeur fictive
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100"),
    limits=c(0.0001, 101)
  )+
  labs(
    x = "Toxic Unit (TU)",
    y = "Number of cocoons produced per cosm (#)"
  )+
  theme_bw()+
  theme(
    axis.title.x = element_text(size = size_axistitle),
    axis.title.y = element_text(size = size_axistitle),
    axis.text.x = element_text(),  
    axis.ticks.x = element_line(),    
    legend.position = "none",
    strip.text = element_text(face = "bold"),
    strip.placement = "outside",
    strip.background = element_rect(color = "black", fill = "grey95", size = 0, linetype = "solid"),
    panel.spacing = unit(0.6, "lines") 
  )

p_comp_CASA <- ggplot()+

  geom_line(
    data = df_pred_drc_ratio_CASA,
    aes(
      x = TU, 
      y = Response,
      color=Ratio_plot
    )
  )+

  scale_color_manual(values = pal_ratio)+
  scale_fill_manual(values = pal_ratio)+
  
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100),  # inclure la valeur fictive
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100"),
    limits=c(0.0001, 101)
  )+
  labs(
    x = "Toxic Unit (TU)",
    y = "Number of cocoons produced per cosm (#)"
  )+
  
  theme_bw()+
  theme(
    legend.position = "none",
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    strip.background = element_rect(
      color="black", 
      fill="grey95", 
      size=0, 
      linetype="solid"
      )
  )


p_CASA <- p_facetCASA + 
  inset_element(
    p_comp_CASA,
    left = 0.67, bottom = -0.05, right = 1, top = 0.45
    )
p_CASA
```

## DL model (CA ref.)

```{r, warning=F, message=F}
#| fig-cap: Dose-response curves predicted by the DL model with CA as reference for each mixture ratio. Crosses correspond to the number of cocoons produced by one cosm and the bold points represent the mean per condition.
#| label: fig-drcIMDEPXratiosPredCADL
#| fig-width: 8
#| fig-height: 6

line_width <- 1.2
size_axistitle <- 11

p_facetCADL <- ggplot()+
  geom_line(
    data = df_pred_drc_ratio_CADL,
    aes(
      x = TU, 
      y = Response,
      color=Ratio_plot
    )
  )+
  geom_point(
    data = df_mix_coc_plotdrc,
    aes(
      x = TU_mix_plot,
      y = Nb_cocoons,
      color=Ratio_plot,
      fill = Ratio_plot
      ),
    alpha = 0.6,
    shape = 4
  )+
  geom_point(
    data = df_mix_coc_mean_plotdrc,
    aes(
      x = TU_mix_plot,
      y = Nb_cocoons,
      color=Ratio_plot,
      fill = Ratio_plot
      ),
    size = 3
  )+
  scale_color_manual(values = pal_ratio)+
  scale_fill_manual(values = pal_ratio)+
  facet_wrap2(~ Ratio_plot, axes = "x") +
  #ylim(0, 3)+
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100),  # inclure la valeur fictive
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100"),
    limits=c(0.009, 101)
  )+
  labs(
    x = "Toxic Unit (TU)",
    y = "Number of cocoons produced per cosm (#)"
  )+
  theme_bw()+
  theme(
    axis.title.x = element_text(size = size_axistitle),
    axis.title.y = element_text(size = size_axistitle),
    axis.text.x = element_text(),  
    axis.ticks.x = element_line(),    
    legend.position = "none",
    strip.text = element_text(face = "bold"),
    strip.placement = "outside",
    strip.background = element_rect(color = "black", fill = "grey95", size = 0, linetype = "solid"),
    panel.spacing = unit(0.6, "lines") 
  )

p_comp_CADL <- ggplot()+

  geom_line(
    data = df_pred_drc_ratio_CADL,
    aes(
      x = TU, 
      y = Response,
      color=Ratio_plot
    )
  )+
  scale_color_manual(values = pal_ratio)+
  scale_fill_manual(values = pal_ratio)+
  
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100),  # inclure la valeur fictive
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100"),
    limits=c(0.009, 101)
  )+
  labs(
    x = "Toxic Unit (TU)",
    y = "Number of cocoons produced per cosm (#)"
  )+
  
  theme_bw()+
  theme(
    legend.position = "none",
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    strip.background = element_rect(
      color="black", 
      fill="grey95", 
      size=0, 
      linetype="solid"
      )
  )


p_CADL <- p_facetCADL + 
  inset_element(
    p_comp_CADL,
    left = 0.67, bottom = -0.05, right = 1, top = 0.45
    )
p_CADL
```

## IA model

```{r, warning=F, message=F}
#| fig-cap: Dose-response curves predicted by the IA model for each mixture ratio. Crosses correspond to the number of cocoons produced by one cosm and the bold points represent the mean per condition.
#| label: fig-drcIMDEPXratiosPredIA
#| fig-width: 8
#| fig-height: 6

line_width <- 1.2
size_axistitle <- 11

p_facetIA <- ggplot()+
  geom_line(
    data = df_pred_drc_ratio_IA,
    aes(
      x = TU, 
      y = Response,
      color=Ratio_plot
    )
  )+
  geom_point(
    data = df_mix_coc_plotdrc,
    aes(
      x = TU_mix_plot,
      y = Nb_cocoons,
      color=Ratio_plot,
      fill = Ratio_plot
      ),
    alpha = 0.6,
    shape = 4
  )+
  geom_point(
    data = df_mix_coc_mean_plotdrc,
    aes(
      x = TU_mix_plot,
      y = Nb_cocoons,
      color=Ratio_plot,
      fill = Ratio_plot
      ),
    size = 3
  )+
  scale_color_manual(values = pal_ratio)+
  scale_fill_manual(values = pal_ratio)+
  facet_wrap2(~ Ratio_plot, axes = "x") +
  #ylim(0, 3)+
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100),  # inclure la valeur fictive
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100")
  )+
  labs(
    x = "Toxic Unit (TU)",
    y = "Number of cocoons produced per cosm (#)"
  )+
  theme_bw()+
  theme(
    axis.title.x = element_text(size = size_axistitle),
    axis.title.y = element_text(size = size_axistitle),
    axis.text.x = element_text(),  
    axis.ticks.x = element_line(),    
    legend.position = "none",
    strip.text = element_text(face = "bold"),
    strip.placement = "outside",
    strip.background = element_rect(color = "black", fill = "grey95", size = 0, linetype = "solid"),
    panel.spacing = unit(0.6, "lines") 
  )

p_comp_IA <- ggplot()+

  geom_line(
    data = df_pred_drc_ratio_IA,
    aes(
      x = TU, 
      y = Response,
      color=Ratio_plot
    )
  )+

  scale_color_manual(values = pal_ratio)+
  scale_fill_manual(values = pal_ratio)+
  
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100),  # inclure la valeur fictive
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100")
  )+
  labs(
    x = "Toxic Unit (TU)",
    y = "Number of cocoons produced per cosm (#)"
  )+
  
  theme_bw()+
  theme(
    legend.position = "none",
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    strip.background = element_rect(
      color="black", 
      fill="grey95", 
      size=0, 
      linetype="solid"
      )
  )


p_IA <- p_facetIA + 
  inset_element(
    p_comp_CA,
    left = 0.67, bottom = -0.05, right = 1, top = 0.45
    )
p_IA
```

## SA model (IA ref.)

```{r, warning=F, message=F}
#| fig-cap: Dose-response curves predicted by the SA model with IA as reference for each mixture ratio. Crosses correspond to the number of cocoons produced by one cosm and the bold points represent the mean per condition.
#| label: fig-drcIMDEPXratiosPredIASA
#| fig-width: 8
#| fig-height: 6

line_width <- 1.2
size_axistitle <- 11

p_facetIASA <- ggplot()+
  geom_line(
    data = df_pred_drc_ratio_IASA,
    aes(
      x = TU, 
      y = Response,
      color=Ratio_plot
    )
  )+
  geom_point(
    data = df_mix_coc_plotdrc,
    aes(
      x = TU_mix_plot,
      y = Nb_cocoons,
      color=Ratio_plot,
      fill = Ratio_plot
      ),
    alpha = 0.6,
    shape = 4
  )+
  geom_point(
    data = df_mix_coc_mean_plotdrc,
    aes(
      x = TU_mix_plot,
      y = Nb_cocoons,
      color=Ratio_plot,
      fill = Ratio_plot
      ),
    size = 3
  )+
  scale_color_manual(values = pal_ratio)+
  scale_fill_manual(values = pal_ratio)+
  facet_wrap2(~ Ratio_plot, axes = "x") +
  #ylim(0, 3)+
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100),  # inclure la valeur fictive
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100"),
    limits=c(0.0001, 101)
  )+
  labs(
    x = "Toxic Unit (TU)",
    y = "Number of cocoons produced per cosm (#)"
  )+
  theme_bw()+
  theme(
    axis.title.x = element_text(size = size_axistitle),
    axis.title.y = element_text(size = size_axistitle),
    legend.position = "none",
    strip.text = element_text(face = "bold"),
    strip.background = element_rect(
      color="black", 
      fill="grey95", 
      size=0, 
      linetype="solid"
      )
  )

p_comp_IASA <- ggplot()+

  geom_line(
    data = df_pred_drc_ratio_IASA,
    aes(
      x = TU, 
      y = Response,
      color=Ratio_plot
    )
  )+

  scale_color_manual(values = pal_ratio)+
  scale_fill_manual(values = pal_ratio)+
  
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100),  # inclure la valeur fictive
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100"),
    limits=c(0.0001, 101)
  )+
  labs(
    x = "Toxic Unit (TU)",
    y = "Number of cocoons produced per cosm (#)"
  )+
  
  theme_bw()+
  theme(
    axis.title.x = element_text(size = size_axistitle),
    axis.title.y = element_text(size = size_axistitle),
    axis.text.x = element_text(),  
    axis.ticks.x = element_line(),    
    legend.position = "none",
    strip.text = element_text(face = "bold"),
    strip.placement = "outside",
    strip.background = element_rect(color = "black", fill = "grey95", size = 0, linetype = "solid"),
    panel.spacing = unit(0.6, "lines") 
  )


p_IASA <- p_facetIASA + 
  inset_element(
    p_comp_IASA,
    left = 0.67, bottom = -0.05, right = 1, top = 0.45
    )
p_IASA
```

## DL model (IA ref.)

```{r, warning=F, message=F}
#| fig-cap: Dose-response curves predicted by the DL model with IA as reference for each mixture ratio. Crosses correspond to the number of cocoons produced by one cosm and the bold points represent the mean per condition.
#| label: fig-drcIMDEPXratiosPredIADL
#| fig-width: 8
#| fig-height: 6

line_width <- 1.2
size_axistitle <- 11

p_facetIADL <- ggplot()+
  geom_line(
    data = df_pred_drc_ratio_IADL,
    aes(
      x = TU, 
      y = Response,
      color=Ratio_plot
    )
  )+
  geom_point(
    data = df_mix_coc_plotdrc,
    aes(
      x = TU_mix_plot,
      y = Nb_cocoons,
      color=Ratio_plot,
      fill = Ratio_plot
      ),
    alpha = 0.6,
    shape = 4
  )+
  geom_point(
    data = df_mix_coc_mean_plotdrc,
    aes(
      x = TU_mix_plot,
      y = Nb_cocoons,
      color=Ratio_plot,
      fill = Ratio_plot
      ),
    size = 3
  )+
  scale_color_manual(values = pal_ratio)+
  scale_fill_manual(values = pal_ratio)+
  facet_wrap2(~ Ratio_plot, axes = "x") +
  #ylim(0, 3)+
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100),  # inclure la valeur fictive
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100"),
    limits=c(0.009, 101)
  )+
  labs(
    x = "Toxic Unit (TU)",
    y = "Number of cocoons produced per cosm (#)"
  )+
  theme_bw()+
  theme(
    axis.title.x = element_text(size = size_axistitle),
    axis.title.y = element_text(size = size_axistitle),
    axis.text.x = element_text(),  
    axis.ticks.x = element_line(),    
    legend.position = "none",
    strip.text = element_text(face = "bold"),
    strip.placement = "outside",
    strip.background = element_rect(color = "black", fill = "grey95", size = 0, linetype = "solid"),
    panel.spacing = unit(0.6, "lines") 
  )

p_comp_IADL <- ggplot()+

  geom_line(
    data = df_pred_drc_ratio_IADL,
    aes(
      x = TU, 
      y = Response,
      color=Ratio_plot
    )
  )+
  scale_color_manual(values = pal_ratio)+
  scale_fill_manual(values = pal_ratio)+
  
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100),  # inclure la valeur fictive
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100"),
    limits=c(0.009, 101)
  )+
  labs(
    x = "Toxic Unit (TU)",
    y = "Number of cocoons produced per cosm (#)"
  )+
  
  theme_bw()+
  theme(
    legend.position = "none",
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    strip.background = element_rect(
      color="black", 
      fill="grey95", 
      size=0, 
      linetype="solid"
      )
  )


p_IADL <- p_facetIADL + 
  inset_element(
    p_comp_IADL,
    left = 0.67, bottom = -0.05, right = 1, top = 0.45
    )
p_IADL
```
:::

```{r, include=F}
ggsave(
  filename="Mix_spring_mix_pred_drc_ratios_CA.png", 
  plot=p_CA, 
  width=8, height = 6, 
  path=here::here("fig/Mixture")
  )
ggsave(
  filename="Mix_spring_mix_pred_drc_ratios_CASA.png", 
  plot=p_CASA, 
  width=8, height = 6, 
  path=here::here("fig/Mixture")
  )
ggsave(
  filename="Mix_spring_mix_pred_drc_ratios_CADL.png", 
  plot=p_CADL, 
  width=8, height = 6, 
  path=here::here("fig/Mixture")
  )

ggsave(
  filename="Mix_spring_mix_pred_drc_ratios_IA.png", 
  plot=p_IA, 
  width=8, height = 6, 
  path=here::here("fig/Mixture")
  )
ggsave(
  filename="Mix_spring_mix_pred_drc_ratios_IASA.png", 
  plot=p_IASA, 
  width=8, height = 6, 
  path=here::here("fig/Mixture")
  )
ggsave(
  filename="Mix_spring_mix_pred_drc_ratios_IADL.png", 
  plot=p_IADL, 
  width=8, height = 6, 
  path=here::here("fig/Mixture")
  )
```

#### 3D representation

::: panel-tabset
## CA model

```{r, message=F, warning=F}
#| fig-cap: Estimated surface (CA model). Small grey dots represents the measurements at the replicate level while the bigger black dots represent the mean per condition. 
#| label: fig-SurfCAdyn
#| fig-width: 5
#| fig-height: 4

p_CA <- plotly::plot_ly(
  x=grid_C2, 
  y=grid_C1, 
  z=~z_CA, 
  colors=Nord_frost
  )%>%
  add_surface(showlegend = FALSE, showscale=FALSE)%>%
  layout(scene = list(
    xaxis = list(title = '[IMD] (mg/kg)'),
    yaxis = list(title = '[EPX] (mg/kg)'),
    zaxis = list(title = 'Cocoon production'),
    camera = list(eye = list(x = 2.5, y = -1.2, z = 1))
    ),
    paper_bgcolor = 'rgba(0, 0, 0, 0)',
    plot_bgcolor = 'rgba(0, 0, 0, 0)'
    )%>%
  add_markers(
    y=df_mix_coc$Dose_EPX,
    x=df_mix_coc$Dose_IMD,
    z=df_mix_coc$Nb_cocoons,
    type = "scatter3d",
    mode="markers",
    showlegend = FALSE,
    marker = list(
      size = 3, 
      color = Nord_polar[4], 
      symbol = 104
      )
    )%>%
  add_markers(
    y=df_mix_coc_mean$Dose_EPX,
    x=df_mix_coc_mean$Dose_IMD,
    z=df_mix_coc_mean$Nb_cocoons,
    type = "scatter3d",
    mode="markers",
    marker = list(
      size = 7, 
      color = Nord_polar[1], 
      symbol = 104
      ),
    showlegend = FALSE
    )

p_CA
```

## SA model (CA ref.)

```{r, message=F, warning=F}
#| fig-cap: Estimated surface (SA model with CA as reference). Small grey dots represents the measurements at the replicate level while the bigger black dots represent the mean per condition.
#| label: fig-SurfCASAdyn
#| fig-width: 5
#| fig-height: 4

p_CASA <- plotly::plot_ly(
  x=grid_C2, 
  y=grid_C1, 
  z=~z_CASA, 
  colors=Nord_frost
  )%>%
  add_surface(showlegend = FALSE, showscale=FALSE)%>%
  layout(scene = list(
    xaxis = list(title = '[IMD] (mg/kg)'),
    yaxis = list(title = '[EPX] (mg/kg)'),
    zaxis = list(title = 'Cocoon production'),
    camera = list(eye = list(x = 2.5, y = -1.2, z = 1))
    ),
    # paper_bgcolor = "#F9FAFC",
    # plot_bgcolor = "#F9FAFC"
    paper_bgcolor = 'rgba(0, 0, 0, 0)',
    plot_bgcolor = 'rgba(0, 0, 0, 0)'
    )%>%
  colorbar(title=list(text="Production of cocoons per cosm"))%>%
  add_markers(
    y=df_mix_coc$Dose_EPX,
    x=df_mix_coc$Dose_IMD,
    z=df_mix_coc$Nb_cocoons,
    type = "scatter3d",
    mode="markers",
    marker = list(
      size = 3, 
      color = Nord_polar[4], 
      symbol = 104
      ),
    showlegend = FALSE
    )%>%
  add_markers(
    y=df_mix_coc_mean$Dose_EPX,
    x=df_mix_coc_mean$Dose_IMD,
    z=df_mix_coc_mean$Nb_cocoons,
    type = "scatter3d",
    mode="markers",
    marker = list(
      size = 7, 
      color = Nord_polar[1], 
      symbol = 104
      ),
    showlegend = FALSE
    )

p_CASA
```

## DL model (CA ref.)

```{r, message=F, warning=F}
#| fig-cap: Estimated surface (DL model with CA as reference). Small grey dots represents the measurements at the replicate level while the bigger black dots represent the mean per condition.
#| label: fig-SurfCADLdyn
#| fig-width: 5
#| fig-height: 4

p_CADL <- plotly::plot_ly(
  x=grid_C2, 
  y=grid_C1, 
  z=~z_CADL, 
  colors=Nord_frost
  )%>%
  add_surface(showlegend = FALSE, showscale=FALSE)%>%
  layout(scene = list(
    xaxis = list(title = '[IMD] (mg/kg)'),
    yaxis = list(title = '[EPX] (mg/kg)'),
    zaxis = list(title = 'Cocoon production'),
    camera = list(eye = list(x = 2.5, y = -1.2, z = 1))
    ),
    # paper_bgcolor = "#F9FAFC",
    # plot_bgcolor = "#F9FAFC"
    paper_bgcolor = 'rgba(0, 0, 0, 0)',
    plot_bgcolor = 'rgba(0, 0, 0, 0)'
    )%>%
  colorbar(title=list(text="Production of cocoons per cosm"))%>%
  add_markers(
    y=df_mix_coc$Dose_EPX,
    x=df_mix_coc$Dose_IMD,
    z=df_mix_coc$Nb_cocoons,
    type = "scatter3d",
    mode="markers",
    marker = list(
      size = 3, 
      color = Nord_polar[4], 
      symbol = 104
      ),
    showlegend = FALSE
    )%>%
  add_markers(
    y=df_mix_coc_mean$Dose_EPX,
    x=df_mix_coc_mean$Dose_IMD,
    z=df_mix_coc_mean$Nb_cocoons,
    type = "scatter3d",
    mode="markers",
    marker = list(
      size = 7, 
      color = Nord_polar[1], 
      symbol = 104
      ),
    showlegend = FALSE
    )

p_CADL
```

## IA model

```{r, message=F, warning=F}
#| fig-cap: Estimated surface (IA model). Small grey dots represents the measurements at the replicate level while the bigger black dots represent the mean per condition. 
#| label: fig-SurfIAdyn
#| fig-width: 5
#| fig-height: 4

p_IA <- plotly::plot_ly(
  x=grid_C2, 
  y=grid_C1, 
  z=~z_IA, 
  colors=Nord_frost
  )%>%
  add_surface(showlegend = FALSE, showscale=FALSE)%>%
  layout(scene = list(
    xaxis = list(title = '[IMD] (mg/kg)'),
    yaxis = list(title = '[EPX] (mg/kg)'),
    zaxis = list(title = 'Cocoon production'),
    camera = list(eye = list(x = 2.5, y = -1.2, z = 1))
    ),
    paper_bgcolor = 'rgba(0, 0, 0, 0)',
    plot_bgcolor = 'rgba(0, 0, 0, 0)'
    )%>%
  add_markers(
    y=df_mix_coc$Dose_EPX,
    x=df_mix_coc$Dose_IMD,
    z=df_mix_coc$Nb_cocoons,
    type = "scatter3d",
    mode="markers",
    showlegend = FALSE,
    marker = list(
      size = 3, 
      color = Nord_polar[4], 
      symbol = 104
      )
    )%>%
  add_markers(
    y=df_mix_coc_mean$Dose_EPX,
    x=df_mix_coc_mean$Dose_IMD,
    z=df_mix_coc_mean$Nb_cocoons,
    type = "scatter3d",
    mode="markers",
    marker = list(
      size = 7, 
      color = Nord_polar[1], 
      symbol = 104
      ),
    showlegend = FALSE
    )

p_IA
```

## SA model (IA ref.)

```{r, message=F, warning=F}
#| fig-cap: Estimated surface (SA model with IA as reference). Small grey dots represents the measurements at the replicate level while the bigger black dots represent the mean per condition.
#| label: fig-SurfIASAdyn
#| fig-width: 5
#| fig-height: 4

p_IASA <- plotly::plot_ly(
  x=grid_C2, 
  y=grid_C1, 
  z=~z_IASA, 
  colors=Nord_frost
  )%>%
  add_surface(showlegend = FALSE, showscale=FALSE)%>%
  layout(scene = list(
    xaxis = list(title = '[IMD] (mg/kg)'),
    yaxis = list(title = '[EPX] (mg/kg)'),
    zaxis = list(title = 'Cocoon production'),
    camera = list(eye = list(x = 2.5, y = -1.2, z = 1))
    ),
    # paper_bgcolor = "#F9FAFC",
    # plot_bgcolor = "#F9FAFC"
    paper_bgcolor = 'rgba(0, 0, 0, 0)',
    plot_bgcolor = 'rgba(0, 0, 0, 0)'
    )%>%
  colorbar(title=list(text="Production of cocoons per cosm"))%>%
  add_markers(
    y=df_mix_coc$Dose_EPX,
    x=df_mix_coc$Dose_IMD,
    z=df_mix_coc$Nb_cocoons,
    type = "scatter3d",
    mode="markers",
    marker = list(
      size = 3, 
      color = Nord_polar[4], 
      symbol = 104
      ),
    showlegend = FALSE
    )%>%
  add_markers(
    y=df_mix_coc_mean$Dose_EPX,
    x=df_mix_coc_mean$Dose_IMD,
    z=df_mix_coc_mean$Nb_cocoons,
    type = "scatter3d",
    mode="markers",
    marker = list(
      size = 7, 
      color = Nord_polar[1], 
      symbol = 104
      ),
    showlegend = FALSE
    )

p_IASA
```

## DL model (IA ref.)

```{r, message=F, warning=F}
#| fig-cap: Estimated surface (DL model with IA as reference). Small grey dots represents the measurements at the replicate level while the bigger black dots represent the mean per condition.
#| label: fig-SurfIADLdyn
#| fig-width: 5
#| fig-height: 4

p_IADL <- plotly::plot_ly(
  x=grid_C2, 
  y=grid_C1, 
  z=~z_IADL, 
  colors=Nord_frost
  )%>%
  add_surface(showlegend = FALSE, showscale=FALSE)%>%
  layout(scene = list(
    xaxis = list(title = '[IMD] (mg/kg)'),
    yaxis = list(title = '[EPX] (mg/kg)'),
    zaxis = list(title = 'Cocoon production'),
    camera = list(eye = list(x = 2.5, y = -1.2, z = 1))
    ),
    # paper_bgcolor = "#F9FAFC",
    # plot_bgcolor = "#F9FAFC"
    paper_bgcolor = 'rgba(0, 0, 0, 0)',
    plot_bgcolor = 'rgba(0, 0, 0, 0)'
    )%>%
  colorbar(title=list(text="Production of cocoons per cosm"))%>%
  add_markers(
    y=df_mix_coc$Dose_EPX,
    x=df_mix_coc$Dose_IMD,
    z=df_mix_coc$Nb_cocoons,
    type = "scatter3d",
    mode="markers",
    marker = list(
      size = 3, 
      color = Nord_polar[4], 
      symbol = 104
      ),
    showlegend = FALSE
    )%>%
  add_markers(
    y=df_mix_coc_mean$Dose_EPX,
    x=df_mix_coc_mean$Dose_IMD,
    z=df_mix_coc_mean$Nb_cocoons,
    type = "scatter3d",
    mode="markers",
    marker = list(
      size = 7, 
      color = Nord_polar[1], 
      symbol = 104
      ),
    showlegend = FALSE
    )

p_IADL
```
:::

```{r, include = F}

orca(p_CA, 
     file = "../../fig/Mixture/Mix_spring_mixsurfaceJonkerCA.png",
     width = 800,
     height = 600,
     scale = 2,
     format = "png",
     # → clé ici :
     #image = "png",
     mathjax = "local"
)

orca(p_CASA, 
     file = "../../fig/Mixture/Mix_spring_mixsurfaceJonkerCASA.png",
     width = 800,
     height = 600,
     scale = 2,
     format = "png",
     # → clé ici :
     #image = "png",
     mathjax = "local"
)

orca(p_CADL, 
     file = "../../fig/Mixture/Mix_spring_mixsurfaceJonkerCADL.png",
     width = 800,
     height = 600,
     scale = 2,
     format = "png",
     # → clé ici :
     #image = "png",
     mathjax = "local"
)

orca(p_IA, 
     file = "../../fig/Mixture/Mix_spring_mixsurfaceJonkerIA.png",
     width = 800,
     height = 600,
     scale = 2,
     format = "png",
     # → clé ici :
     #image = "png",
     mathjax = "local"
)

orca(p_IASA, 
     file = "../../fig/Mixture/Mix_spring_mixsurfaceJonkerIASA.png",
     width = 800,
     height = 600,
     scale = 2,
     format = "png",
     # → clé ici :
     #image = "png",
     mathjax = "local"
)

orca(p_IADL, 
     file = "../../fig/Mixture/Mix_spring_mixsurfaceJonkerIADL.png",
     width = 800,
     height = 600,
     scale = 2,
     format = "png",
     # → clé ici :
     #image = "png",
     mathjax = "local"
)
```

### Step 5 - Evaluation of model fit

```{r dfpredobs, message=F, warning=F}

C_mat=cbind(                                            
    df_mix_coc_int$Dose_EPX,                             
    df_mix_coc_int$Dose_IMD                             
    )

# Calculation of effects for the design concentrations 
res_CA <- CA_complete2(
  C_mat, 
  Max, Slopes, Ec50s, 
  interact="none"
  )
res_CASA <- CA_complete2(
  C_mat, 
  Max, Slopes, Ec50s, 
  interact="SA",
  a = CASA_fit$a
  )
res_CADL <- CA_complete2(
  C_mat, 
  Max, Slopes, Ec50s, 
  interact="DL",
  a = CADL_fit$a,
  b = CADL_fit$b
  )
res_CADR <- CA_complete2(
  C_mat, 
  Max, Slopes, Ec50s, 
  interact="DR",
  a = CADR_fit$a,
  b = CADR_fit$b
  )

res_IA <- IA_complete2(
  C_mat, 
  Max, Slopes, Ec50s, 
  interact="none"
  )
res_IASA <- IA_complete2(
  C_mat, 
  Max, Slopes, Ec50s, 
  interact="SA",
  a = IASA_fit$a
  )
res_IADL <- IA_complete2(
  C_mat, 
  Max, Slopes, Ec50s, 
  interact="DL",
  a = IADL_fit$a,
  b = IADL_fit$b
  )
res_IADR <- IA_complete2(
  C_mat, 
  Max, Slopes, Ec50s, 
  interact="DR",
  a = IADR_fit$a,
  b = IADR_fit$b
  )


# We add the corresponding response to our design
df_predobs_CA <- df_mix_coc_int%>%
  mutate(Predicted=res_CA)
df_predobs_CASA <- df_mix_coc_int%>%
  mutate(Predicted=res_CASA)
df_predobs_CADL <- df_mix_coc_int%>%
  mutate(Predicted=res_CADL)
df_predobs_CADR <- df_mix_coc_int%>%
  mutate(Predicted=res_CADR)

df_predobs_IA <- df_mix_coc_int%>%
  mutate(Predicted=res_IA)
df_predobs_IASA <- df_mix_coc_int%>%
  mutate(Predicted=res_IASA)
df_predobs_IADL <- df_mix_coc_int%>%
  mutate(Predicted=res_IADL)
df_predobs_IADR <- df_mix_coc_int%>%
  mutate(Predicted=res_IADR)
```

#### Predicted vs. observed

::: panel-tabset
## CA model

```{r, warning = F, message = F}
#| fig-cap: Predicted vs observed (CA model). 
#| label: fig-CApredobs
#| fig-width: 5
#| fig-height: 4

fact_1 <- 2
fact_2 <- 5

col_line0 <- Nord_polar[1]
col_line1 <- Nord_polar[4]
col_line2 <- Nord_snow[1]
xmin <- 0.1
xmax <- 15
step <- 0.5
seq_line <- seq(xmin, xmax, step)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_CA <- ggplot()+
  geom_point(
    data = df_predobs_CA,
    mapping = aes(
        x = Response,
        y = Predicted,
        color = as.factor(Line)
        ),
    alpha=0.5,
    size=1.5
  )+
  geom_line(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  scale_color_manual(
    name = "Isobole",
    values = c(Nord_aurora,Nord_frost)
    )+
  scale_x_log10(
    #limits = c(0.15, 1.5)
    )+
  scale_y_log10(
    #limits = c(0.15, 1.5)
    )+
  #ylim(NA,1.5)+
  labs(
    x = "Observed response",
    y = "Predicted response"
  )+
  theme_minimal()
p_CA

```

## SA model (CA ref.)

```{r, warning = F, message = F}
#| fig-cap: Predicted vs observed (SA model with CA as reference). 
#| label: fig-CASApredobs
#| fig-width: 5
#| fig-height: 4

fact_1 <- 2
fact_2 <- 5

col_line0 <- Nord_polar[1]
col_line1 <- Nord_polar[4]
col_line2 <- Nord_snow[1]
seq_line <- seq(xmin, xmax, step)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_CASA <- ggplot()+
  geom_point(
    data = df_predobs_CASA,
    mapping = aes(
        x = Response,
        y = Predicted,
        color = as.factor(Line)
        ),
    alpha=0.5,
    size=1.5
  )+
  geom_line(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  scale_color_manual(
    name = "Isobole",
    values = c(Nord_aurora,Nord_frost)
    )+
  scale_x_log10(
    #limits = c(0.15, 1.5)
    )+
  scale_y_log10(
    #limits = c(0.15, 1.5)
    )+
  #ylim(NA,1.5)+
  labs(
    x = "Observed response",
    y = "Predicted response"
  )+
  theme_minimal()
p_CASA

```

## DL model (CA ref.)

```{r, warning = F, message = F}
#| fig-cap: Predicted vs observed (DL model with CA as reference). 
#| label: fig-CADLpredobs
#| fig-width: 5
#| fig-height: 4

fact_1 <- 2
fact_2 <- 5

col_line0 <- Nord_polar[1]
col_line1 <- Nord_polar[4]
col_line2 <- Nord_snow[1]
seq_line <- seq(xmin, xmax, step)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_CADL <- ggplot()+
  geom_point(
    data = df_predobs_CADL,
    mapping = aes(
        x = Response,
        y = Predicted,
        color = as.factor(Line)
        ),
    alpha=0.5,
    size=1.5
  )+
  geom_line(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  scale_color_manual(
    name = "Isobole",
    values = c(Nord_aurora,Nord_frost)
    )+
  scale_x_log10(
    #limits = c(0.15, 1.5)
    )+
  scale_y_log10(
    #limits = c(0.15, 1.5)
    )+
  #ylim(NA,1.5)+
  labs(
    x = "Observed response",
    y = "Predicted response"
  )+
  theme_minimal()
p_CADL

```

## IA model

```{r, warning = F, message = F}
#| fig-cap: Predicted vs observed (IA model). 
#| label: fig-IApredobs
#| fig-width: 5
#| fig-height: 4

fact_1 <- 2
fact_2 <- 5

col_line0 <- Nord_polar[1]
col_line1 <- Nord_polar[4]
col_line2 <- Nord_snow[1]
xmin <- 0.1
xmax <- 15
step <- 0.5
seq_line <- seq(xmin, xmax, step)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_IA <- ggplot()+
  geom_point(
    data = df_predobs_IA,
    mapping = aes(
        x = Response,
        y = Predicted,
        color = as.factor(Line)
        ),
    alpha=0.5,
    size=1.5
  )+
  geom_line(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  scale_color_manual(
    name = "Isobole",
    values = c(Nord_aurora,Nord_frost)
    )+
  scale_x_log10(
    #limits = c(0.15, 1.5)
    )+
  scale_y_log10(
    #limits = c(0.15, 1.5)
    )+
  #ylim(NA,1.5)+
  labs(
    x = "Observed response",
    y = "Predicted response"
  )+
  theme_minimal()
p_IA

```

## SA model (IA ref.)

```{r, warning = F, message = F}
#| fig-cap: Predicted vs observed (SA model with IA as reference). 
#| label: fig-IASApredobs
#| fig-width: 5
#| fig-height: 4

fact_1 <- 2
fact_2 <- 5

col_line0 <- Nord_polar[1]
col_line1 <- Nord_polar[4]
col_line2 <- Nord_snow[1]
seq_line <- seq(xmin, xmax, step)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_IASA <- ggplot()+
  geom_point(
    data = df_predobs_IASA,
    mapping = aes(
        x = Response,
        y = Predicted,
        color = as.factor(Line)
        ),
    alpha=0.5,
    size=1.5
  )+
  geom_line(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  scale_color_manual(
    name = "Isobole",
    values = c(Nord_aurora,Nord_frost)
    )+
  scale_x_log10(
    #limits = c(0.15, 1.5)
    )+
  scale_y_log10(
    #limits = c(0.15, 1.5)
    )+
  #ylim(NA,1.5)+
  labs(
    x = "Observed response",
    y = "Predicted response"
  )+
  theme_minimal()
p_IASA

```

## DL model (IA ref.)

```{r, warning = F, message = F}
#| fig-cap: Predicted vs observed (DL model with IA as reference). 
#| label: fig-IADLpredobs
#| fig-width: 5
#| fig-height: 4

fact_1 <- 2
fact_2 <- 5

col_line0 <- Nord_polar[1]
col_line1 <- Nord_polar[4]
col_line2 <- Nord_snow[1]
seq_line <- seq(xmin, xmax, step)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line*fact_1,
  x_1 = seq_line,
  y_1 = seq_line/fact_1,
  x2  = seq_line,
  y2  = seq_line*fact_2,
  x_2 = seq_line,
  y_2 = seq_line/fact_2
  )

p_IADL <- ggplot()+
  geom_point(
    data = df_predobs_IADL,
    mapping = aes(
        x = Response,
        y = Predicted,
        color = as.factor(Line)
        ),
    alpha=0.5,
    size=1.5
  )+
  geom_line(
    data=df_line,
    mapping=aes(x=x1, y=y1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_1, y=y_1),
    color = col_line1
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x2, y=y2),
    color = col_line2
    )+
  geom_line(
    data=df_line,
    mapping=aes(x=x_2, y=y_2),
    color = col_line2
    )+
  
  geom_abline(
    slope=1, 
    intercept = 0, 
    color = col_line0,
    linewidth = 1
    )+
  scale_color_manual(
    name = "Isobole",
    values = c(Nord_aurora,Nord_frost)
    )+
  scale_x_log10(
    #limits = c(0.15, 1.5)
    )+
  scale_y_log10(
    #limits = c(0.15, 1.5)
    )+
  #ylim(NA,1.5)+
  labs(
    x = "Observed response",
    y = "Predicted response"
  )+
  theme_minimal()
p_IADL

```
:::

```{r, include=F}
ggsave(
  filename="Mix_spring_mix_predobs_CA.png", 
  plot=p_CA, 
  width=4, height = 3, 
  path=here::here("fig/Mixture")
  )
ggsave(
  filename="Mix_spring_mix_predobs_CA.svg", 
  plot=p_CA, 
  width=4, height = 3, 
  path=here::here("fig/Mixture")
  )

ggsave(
  filename="Mix_spring_mix_predobs_CASA.png", 
  plot=p_CASA, 
  width=4, height = 3, 
  path=here::here("fig/Mixture")
  )
ggsave(
  filename="Mix_spring_mix_predobs_CASA.svg", 
  plot=p_CASA, 
  width=4, height = 3, 
  path=here::here("fig/Mixture")
  )

ggsave(
  filename="Mix_spring_mix_predobs_CADL.png", 
  plot=p_CADL, 
  width=4, height = 3, 
  path=here::here("fig/Mixture")
  )
ggsave(
  filename="Mix_spring_mix_predobs_CADL.svg", 
  plot=p_CADL, 
  width=4, height = 3, 
  path=here::here("fig/Mixture")
  )

ggsave(
  filename="Mix_spring_mix_predobs_IA.png", 
  plot=p_IA, 
  width=4, height = 3, 
  path=here::here("fig/Mixture")
  )
ggsave(
  filename="Mix_spring_mix_predobs_IA.svg", 
  plot=p_IA, 
  width=4, height = 3, 
  path=here::here("fig/Mixture")
  )

ggsave(
  filename="Mix_spring_mix_predobs_IASA.png", 
  plot=p_IASA, 
  width=4, height = 3, 
  path=here::here("fig/Mixture")
  )
ggsave(
  filename="Mix_spring_mix_predobs_IASA.svg", 
  plot=p_IASA, 
  width=4, height = 3, 
  path=here::here("fig/Mixture")
  )

ggsave(
  filename="Mix_spring_mix_predobs_IADL.png", 
  plot=p_IADL, 
  width=4, height = 3, 
  path=here::here("fig/Mixture")
  )
ggsave(
  filename="Mix_spring_mix_predobs_IADL.svg", 
  plot=p_IADL, 
  width=4, height = 3, 
  path=here::here("fig/Mixture")
  )
```

```{r perpredobs, warning = F, message = F}
#| tbl-cap: Percentage of predictions falling inside fold 2 and fold 5 for each model.
#| label: tbl-MIXpredobsfold

calculate_predobs_stats <- function(df) {
  df <- df |> 
    mutate(
      Ratio_predobs = Predicted / Response,
      Residuals = Predicted - Response
    )
  
  per_fold2 <- mean(df$Ratio_predobs >= 0.5 & df$Ratio_predobs <= 2) * 100
  per_fold5 <- mean(df$Ratio_predobs >= 0.2 & df$Ratio_predobs <= 5) * 100
  
  list(df = df, per_fold2 = per_fold2, per_fold5 = per_fold5)
}


dfs <- list(
  CA = df_predobs_CA, SA = df_predobs_CASA, DL = df_predobs_CADL, DR = df_predobs_CADR,
  IA = df_predobs_IA, "IA-SA" = df_predobs_IASA, "IA-DL" = df_predobs_IADL, "IA-DR" = df_predobs_IADR
)

results <- lapply(dfs, calculate_predobs_stats)

df_predobs_summary <- data.frame(
  Reference_model = c(rep("CA", 4), rep("IA", 4)),
  Model = names(dfs),
  Per_fold2 = sapply(results, `[[`, "per_fold2"),
  Per_fold5 = sapply(results, `[[`, "per_fold5")
)

df_predobs_summary |> datatable(options = list(dom="t"), class="hover")

```

#### Residuals

::: panel-tabset
## CA model

```{r, warning = F, message = F}
#| fig-cap: Residuals (CA model). 
#| label: fig-CAresiduals
#| fig-width: 5
#| fig-height: 4

p <- ggplot()+
  geom_dotplot(
    data = df_predobs_CA,
    aes(
      x = Line,
      y = Residuals,
      color = as.factor(Line),
      fill = as.factor(Line)
    ),
    binaxis='y', 
    stackdir='center', 
    alpha = 0.5,
    dotsize=0.8
  )+
  geom_abline(
    slope=0,
    intercept = 0
  )+
  scale_color_manual(name = "Line", values = c(Nord_aurora, rev(Nord_frost)))+
  scale_fill_manual(name = "Line", values = c(Nord_aurora, rev(Nord_frost)))+
  #scale_x_log10()+
  theme_minimal()
p
```

## SA model (CA ref.)

```{r, warning = F, message = F}
#| fig-cap: Residuals (SA model with CA as reference). 
#| label: fig-CASAresiduals
#| fig-width: 5
#| fig-height: 4

p <- ggplot()+
  geom_dotplot(
    data = df_predobs_CASA,
    aes(
      x = Line,
      y = Residuals,
      color = as.factor(Line),
      fill = as.factor(Line)
    ),
    binaxis='y', 
    stackdir='center', 
    alpha = 0.5,
    dotsize=0.8
  )+
  geom_abline(
    slope=0,
    intercept = 0
  )+
  scale_color_manual(name = "Line", values = c(Nord_aurora, rev(Nord_frost)))+
  scale_fill_manual(name = "Line", values = c(Nord_aurora, rev(Nord_frost)))+
  #scale_x_log10()+
  theme_minimal()
p
```

## DL model (CA ref.)

```{r, warning = F, message = F}
#| fig-cap: Residuals (DL model with CA as reference). 
#| label: fig-CADLresiduals
#| fig-width: 5
#| fig-height: 4

p <- ggplot()+
  geom_dotplot(
    data = df_predobs_CADL,
    aes(
      x = Line,
      y = Residuals,
      color = as.factor(Line),
      fill = as.factor(Line)
    ),
    binaxis='y', 
    stackdir='center', 
    alpha = 0.5,
    dotsize=0.8
  )+
  geom_abline(
    slope=0,
    intercept = 0
  )+
  scale_color_manual(name = "Line", values = c(Nord_aurora, rev(Nord_frost)))+
  scale_fill_manual(name = "Line", values = c(Nord_aurora, rev(Nord_frost)))+
  #scale_x_log10()+
  theme_minimal()
p
```

## IA model

```{r, warning = F, message = F}
#| fig-cap: Residuals (IA model). 
#| label: fig-IAresiduals
#| fig-width: 5
#| fig-height: 4

p <- ggplot()+
  geom_dotplot(
    data = df_predobs_IA,
    aes(
      x = Line,
      y = Residuals,
      color = as.factor(Line),
      fill = as.factor(Line)
    ),
    binaxis='y', 
    stackdir='center', 
    alpha = 0.5,
    dotsize=0.8
  )+
  geom_abline(
    slope=0,
    intercept = 0
  )+
  scale_color_manual(name = "Line", values = c(Nord_aurora, rev(Nord_frost)))+
  scale_fill_manual(name = "Line", values = c(Nord_aurora, rev(Nord_frost)))+
  #scale_x_log10()+
  theme_minimal()
p
```

## SA model (IA ref.)

```{r, warning = F, message = F}
#| fig-cap: Residuals (SA model with IA as reference). 
#| label: fig-IASAresiduals
#| fig-width: 5
#| fig-height: 4

p <- ggplot()+
  geom_dotplot(
    data = df_predobs_IASA,
    aes(
      x = Line,
      y = Residuals,
      color = as.factor(Line),
      fill = as.factor(Line)
    ),
    binaxis='y', 
    stackdir='center', 
    alpha = 0.5,
    dotsize=0.8
  )+
  geom_abline(
    slope=0,
    intercept = 0
  )+
  scale_color_manual(name = "Line", values = c(Nord_aurora, rev(Nord_frost)))+
  scale_fill_manual(name = "Line", values = c(Nord_aurora, rev(Nord_frost)))+
  #scale_x_log10()+
  theme_minimal()
p
```

## DL model (IA ref.)

```{r, warning = F, message = F}
#| fig-cap: Residuals (DL model with IA as reference). 
#| label: fig-IADLresiduals
#| fig-width: 5
#| fig-height: 4

p <- ggplot()+
  geom_dotplot(
    data = df_predobs_IADL,
    aes(
      x = Line,
      y = Residuals,
      color = as.factor(Line),
      fill = as.factor(Line)
    ),
    binaxis='y', 
    stackdir='center', 
    alpha = 0.5,
    dotsize=0.8
  )+
  geom_abline(
    slope=0,
    intercept = 0
  )+
  scale_color_manual(name = "Line", values = c(Nord_aurora, rev(Nord_frost)))+
  scale_fill_manual(name = "Line", values = c(Nord_aurora, rev(Nord_frost)))+
  #scale_x_log10()+
  theme_minimal()
p
```
:::

## Summary

```{r, message=F, warning=F}
#| fig-cap: Estimated surface (CA model). Small grey dots represents the measurements at the replicate level while the bigger black dots represent the mean per condition. 
#| label: fig-SurfCAres
#| fig-width: 6
#| fig-height: 6


df_mix_coc_plot_f <- df_mix_coc %>%
  group_by(Condition) %>%
  summarise(
    mean = mean(Nb_cocoons),
    sd = sd(Nb_cocoons),
    q2.5 = quantile(Nb_cocoons, 0.025),
    q97.5 = quantile(Nb_cocoons, 0.975),
    Dose_IMD = Dose_IMD,
    Dose_EPX = Dose_EPX,
    .groups = "drop"
  ) |> 
  mutate(
    zmin = mean - sd,
    zmax = mean + sd
  )

p_CA <- plot_ly(
  x = grid_C2, 
  y = grid_C1, 
  z = ~z_CA, 
  colors = Nord_frost
) %>%
  add_surface(showlegend = FALSE, showscale=FALSE, opacity = .7) %>%
  layout(
    scene = list(
      xaxis = list(title = '[IMD] (mg/kg)'),
      yaxis = list(title = '[EPX] (mg/kg)'),
      zaxis = list(title = 'Cocoon production'),
      camera = list(eye = list(x = 2.5, y = -1.2, z = 1))
    ),
    paper_bgcolor = 'rgba(0, 0, 0, 0)',
    plot_bgcolor = 'rgba(0, 0, 0, 0)'
  ) %>%
  colorbar(title = list(text = "Production of cocoons per cosm")) %>%
  # add_markers(
  #   y = df_mix_coc$Dose_EPX,
  #   x = df_mix_coc$Dose_IMD,
  #   z = df_mix_coc$Nb_cocoons,
  #   type = "scatter3d",
  #   mode = "markers",
  #   marker = list(size = 3, color = Nord_polar[4], symbol = 104)
  # ) %>%
  add_markers(
    y = df_mix_coc_mean$Dose_EPX,
    x = df_mix_coc_mean$Dose_IMD,
    z = df_mix_coc_mean$Nb_cocoons,
    type = "scatter3d",
    mode = "markers",
    marker = list(size = 7, color = Nord_polar[1], symbol = 104),
    showlegend = FALSE, opacity = 1
  )

# Ajout des barres d'erreur comme segments
for (i in seq_len(nrow(df_mix_coc_plot_f))) {
  
  p_CA <- p_CA %>%
    add_trace(
      x = df_mix_coc_plot_f$Dose_IMD[i],
      y = df_mix_coc_plot_f$Dose_EPX[i],
        z = c(df_mix_coc_plot_f$zmin[i], df_mix_coc_plot_f$zmax[i]),
      type = "scatter3d",
      mode = "lines",
      line = list(color = Nord_polar[1], width = 2), # bien visible
      showlegend = FALSE
    )
}

p_CA

```

```{r, warning=F}
orca(p_CA, 
     file = "../../fig/Mixture/Mix_spring_mixsurfaceJonkerCA_errorbar.png",
     width = 800,
     height = 600,
     scale = 2,
     format = "png",
     # → clé ici :
     #image = "png",
     mathjax = "local"
)
```
