```{r lib, include=F}
library(here)
source(file = here::here("functions/fun.R"))
f_load_libraries_colors()

palette <- colorRampPalette(c("#5E81AC", "#88C0D0"))
pal_ratio <- c("#88C0D0", "#81A1C1", "#81A1C1", "#81A1C1", "#5E81AC", Nord_polar[4])
```

# Results of the mixture experiments - Effects on other endpoints

## Data importation

```{r datamix, message = F, warning=F}

# Value given to controls for plot
Val_Ctrl <- 1e-4
Label_Ctrl <- "0 (Ctrl)"

# Data EC50

df_repro_tot <- read_excel(here::here("data/Data_EC50.xlsx"), sheet="Repro") |> 
  mutate(
    Dose = as.numeric(Dose),
    Dose_plot = case_when(
      Dose == 0 ~ Val_Ctrl,
      !(Dose == 0) ~ Dose
    ),
    Dose_f = as.factor(round(Dose, 4)),
    w=w_tot/Nb_ind,
    L=w^(1/3),
    )

# Data for EPX
df_repro_EPX <- subset(df_repro_tot, Molec %in% c("Ctrl_2", "EPX")) |> 
  mutate(Molecule = "EPX")
# We only keep earthworms still alive at then end of the experiment
ID_alive_EPX <- subset(df_repro_EPX, t==28 & (!Status=="D"))$ID_cosm
df_repro_EPX_alive <- subset(df_repro_EPX, ID_cosm %in% ID_alive_EPX)

# Data for IMD
df_repro_IMD <- subset(df_repro_tot, Molec %in% c("Ctrl_1", "Ctrl_2", "IMD")) |> 
  mutate(Molecule = "IMD")
# We only keep earthworms still alive at then end of the experiment
ID_alive_IMD <- subset(df_repro_IMD, t==28 & (!Status=="D"))$ID_cosm
df_repro_IMD_alive <- subset(df_repro_IMD, ID_cosm %in% ID_alive_IMD)

df_repro <- rbind(df_repro_EPX, df_repro_IMD)
df_repro_alive <- rbind(df_repro_EPX_alive, df_repro_IMD_alive)

Control_IMD <- mean(subset(df_repro_IMD_alive, Dose == 0)$Nb_cocoons, na.rm=T)
Control_EPX <- mean(subset(df_repro_EPX_alive, Dose == 0)$Nb_cocoons, na.rm=T)

df_repro_EPX_alive <- df_repro_EPX_alive |> 
  mutate(
    r_Nb_cocoons = Nb_cocoons / Control_EPX *100
    ) 
df_repro_IMD_alive <- df_repro_IMD_alive |> 
  mutate(
    r_Nb_cocoons = Nb_cocoons / Control_EPX * 100
    ) 


df_repro_alive <- df_repro_alive |> 
  mutate(
    r_Nb_cocoons = case_when(
      Molecule == "IMD" ~ Nb_cocoons / Control_IMD,
      Molecule == "EPX" ~ Nb_cocoons / Control_EPX
    ) * 100
    ) 

df_repro_alive_mean <- df_repro_alive |>
  dplyr::group_by(Dose, Dose_plot, Molecule) |>
  dplyr::summarise(
    Nb_cocoons = mean(Nb_cocoons, na.rm = TRUE),
    r_Nb_cocoons = mean(r_Nb_cocoons, na.rm = TRUE),
    .groups = "drop"
  )

# Retriving EC50 
df_drc_param <- read.csv(here::here("data/DRC_parameters_cocoons_really_used.csv"))
EPX_EC50_drc <- df_drc_param$coef.drc.4.[3]
IMD_EC50_drc <- df_drc_param$coef.drc.4.[4]


# Mixture data

df_mix_ind <- read_excel(here::here("data/Data_Mix.xlsx"), sheet="ReproSpring2025weight") |> 
  mutate(
    Condition = paste0(Ratio, Line),
    Nb_rep = as.factor(Nb_rep),
    w = as.numeric(w),
    L = w^(1/3),
    TU_drc = Dose_IMD/IMD_EC50_drc + Dose_EPX/EPX_EC50_drc,
    
    Dose_IMD_plot = case_when(
      Dose_IMD == 0 ~ Val_Ctrl,
      !(Dose_IMD == 0) ~ Dose_IMD
    ),
    Dose_EPX_plot = case_when(
      Dose_EPX == 0 ~ Val_Ctrl,
      !(Dose_EPX == 0) ~ Dose_EPX
    ),
    TU_drc_plot = case_when(
      TU_drc == 0 ~ Val_Ctrl,
      !(TU_drc == 0) ~ TU_drc
    )
  )

df_mix_growth_mean <- df_mix_ind |> 
  aggregate(w~Ratio+Line+Nb_rep, FUN = mean)

df_mix_coc <- read_excel(here::here("data/Data_Mix.xlsx"), sheet="ReproSpring2025coc") |> 
  mutate(
    Condition = paste0(Ratio, Line),
    w_coc = w_coc_tot/(Nb_cocoons-Nb_cocoons_crushed),
    TU_drc = Dose_IMD/IMD_EC50_drc + Dose_EPX/EPX_EC50_drc,
    Nb_rep = as.factor(Nb_rep),
    
    Dose_IMD_plot = case_when(
      Dose_IMD == 0 ~ Val_Ctrl,
      !(Dose_IMD == 0) ~ Dose_IMD
    ),
    Dose_EPX_plot = case_when(
      Dose_EPX == 0 ~ Val_Ctrl,
      !(Dose_EPX == 0) ~ Dose_EPX
    ),
    TU_drc_plot = case_when(
      TU_drc == 0 ~ Val_Ctrl,
      !(TU_drc == 0) ~ TU_drc
    )
  )|> 
  left_join(df_mix_growth_mean, by = c("Nb_rep", "Ratio", "Line"))

coc_mean_controls <- subset(df_mix_coc, Dose_IMD == 0 & Dose_EPX == 0) |> 
  aggregate(Nb_cocoons ~ Lot, FUN = mean)

df_mix_coc <- df_mix_coc |> 
  mutate(
    r_Nb_cocoons = 
      sqrt(case_when(
        Lot == "D" ~ Nb_cocoons/coc_mean_controls$Nb_cocoons[1],
        Lot == "E" ~ Nb_cocoons/coc_mean_controls$Nb_cocoons[2]
        )),
    Trans_r_Nb_cocoons = sqrt(r_Nb_cocoons)
    )

df_conc_mix <- df_mix_coc |> 
  dplyr::select(Condition, Dose_IMD, Dose_EPX)%>%
  distinct(Condition, .keep_all = TRUE)

df_mix_cocsize <- read_excel(here::here("data/Data_Mix.xlsx"), sheet="ReproSpring2025cocsize") |> 
  mutate(
    Condition = paste0(Ratio, Line),
    v_coc = 4/3*pi*Coc_height*Coc_width^2,
    Nb_rep = as.factor(Nb_rep)
  ) |> 
  left_join(df_conc_mix, by = "Condition") |> 
  mutate(
    TU_drc = Dose_IMD / IMD_EC50_drc + Dose_EPX/EPX_EC50_drc,
    Dose_IMD_plot = case_when(
      Dose_IMD == 0 ~ Val_Ctrl,
      !(Dose_IMD == 0) ~ Dose_IMD
    ),
    Dose_EPX_plot = case_when(
      Dose_EPX == 0 ~ Val_Ctrl,
      !(Dose_EPX == 0) ~ Dose_EPX
    )
    )

df_mix_cocsize_cosm <- df_mix_cocsize |> 
  aggregate(v_coc ~ Ratio + Line + Nb_rep + TU_drc, FUN = mean) |> 
  mutate(Condition = paste0(Ratio, Line))

df_mix_coc <- df_mix_coc |> 
  full_join(df_mix_cocsize_cosm, by = c("Condition", "Nb_rep", "Ratio", "Line", "TU_drc")) |> 
  mutate(
    Id_Cond = w_coc/v_coc
    )

df_mix_coc_mean <- df_mix_coc |>
  dplyr::group_by(Condition, Dose_IMD, Dose_EPX, Dose_IMD_plot, Dose_EPX_plot, Ratio, Line, TU_drc) |>
  dplyr::summarise(
    Nb_cocoons = mean(Nb_cocoons, na.rm = TRUE),
    w_coc = mean(w_coc, na.rm = TRUE),
    v_coc = mean(v_coc, na.rm = TRUE),
    r_Nb_cocoons = mean(r_Nb_cocoons, na.rm = TRUE),
    Trans_r_Nb_cocoons = mean(Trans_r_Nb_cocoons, na.rm = TRUE),
    .groups = "drop"
  )

df_mix_coc_IMD_mean <- subset(df_mix_coc_mean, Dose_EPX ==0)
df_mix_coc_EPX_mean <- subset(df_mix_coc_mean, Dose_IMD ==0)

Date_D28_LotD <- dmy("23/04/2025")
Date_D28_LotE <- dmy("29/04/2025")

df_mix_hatch_wide_D <- read_excel(here::here("data/Data_Mix.xlsx"), sheet="ReproSpring2025hatchlingsLotD") |> 
  dplyr::select(-Reste) |> 
  mutate(across(`23/04/2025`:`20/06/2025`, ~replace_na(.x, 0))) |> 
  mutate(
    ID_rep = paste0(Ratio, Line, Nb_rep),
    Condition = paste0(Ratio,Line)
  )

df_mix_hatch_wide_E <- read_excel(here::here("data/Data_Mix.xlsx"), sheet="ReproSpring2025hatchlingsLotE") |> 
  dplyr::select(-Reste)|> 
  mutate(across(`29/04/2025`:`20/06/2025`, ~replace_na(.x, 0))) |> 
  mutate(
    ID_rep = paste0(Ratio, Line, Nb_rep),
    Condition = paste0(Ratio,Line)
  )

df_mix_hatch_long_D <- df_mix_hatch_wide_D %>%
  pivot_longer(
    cols = matches("\\d{2}/\\d{2}/\\d{4}"), 
    names_to = "Date",
    values_to = "Nb_hatch"
  ) %>%
  mutate(Date = dmy(Date)) 

df_mix_hatch_long_E <- df_mix_hatch_wide_E %>%
  pivot_longer(
    cols = matches("\\d{2}/\\d{2}/\\d{4}"), 
    names_to = "Date",
    values_to = "Nb_hatch"
  ) %>%
  mutate(Date = dmy(Date)) 

df_mix_hatch_long <- rbind(df_mix_hatch_long_D, df_mix_hatch_long_E)

df_mix_hatch_long_D_rep <- df_mix_hatch_long_D %>%
  arrange(ID_rep, Date) %>%
  group_by(ID_rep) %>%
  mutate(Cumul_hatch = cumsum(Nb_hatch)) %>%
  ungroup()

df_mix_hatch_long_E_rep <- df_mix_hatch_long_E %>%
  arrange(ID_rep, Date) %>%
  group_by(ID_rep) %>%
  mutate(Cumul_hatch = cumsum(Nb_hatch)) %>%
  ungroup()

df_mix_hatch <- rbind(df_mix_hatch_long_D_rep, df_mix_hatch_long_E_rep) |> 
  mutate(
    t = case_when(
      Lot == "D" ~ as.numeric(Date - Date_D28_LotD),
      Lot == "E" ~ as.numeric(Date - Date_D28_LotE)
    ),
    Cumul_per_hatch = Cumul_hatch/Tot_coc
  )

tot_coc_per_condition <- df_mix_coc %>%
  group_by(Condition) %>%
  summarise(Tot_coc_cond = sum(Nb_cocoons, na.rm = TRUE), .groups = "drop")

df_mix_hatch_mean <- df_mix_hatch_long |> 
  mutate(
    t = case_when(
      Lot == "D" ~ as.numeric(Date - Date_D28_LotD),
      Lot == "E" ~ as.numeric(Date - Date_D28_LotE)
    )
  ) |> 
  arrange(Condition, t, Ratio, Line) |> 
  group_by(Condition, Date, t, Ratio, Line) |> 
  summarise(
    Nb_hatch = sum(Nb_hatch, na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(Condition, t, Ratio, Line) |> 
  group_by(Condition) |> 
  mutate(Cumul_hatch = cumsum(Nb_hatch)) |> 
  ungroup() |> 
  left_join(tot_coc_per_condition, by = "Condition") |> 
  mutate(Cumul_perc_hatch = Cumul_hatch / Tot_coc_cond * 100)

```

## Initial state

We can first take a look at the initial weights of individuals (@fig-init).

```{r D0, warning=F, message=F}
#| fig-cap: Initial weights of earthworms according to batches. 
#| label: fig-init
#| fig-width: 8
#| fig-height: 4

pal_lot <- c(Nord_frost[3], Nord_polar[4])

# Weights at t=0
p <- ggplot(
  data=subset(df_mix_ind,t==0), 
  aes(
    x=Condition, 
    y=w
    )
  )+

  geom_boxplot(
    alpha=0.2,
    color = Nord_polar[1]
    )+
  geom_dotplot(
    aes(
    color=Lot, 
    fill=Lot
    ),
    binaxis='y', 
    stackdir='center', 
    dotsize=0.5, 
    alpha=0.7
    )+
  
  scale_color_manual(values=pal_lot)+
  scale_fill_manual(values=pal_lot)+

  labs(x="Condition", y="Weight (mg)")+
  

  theme_classic(12)+
  theme(
    legend.position = "none", 
    legend.title=element_text(size=sizetitle-2,face="bold"),
    legend.text = element_text(size=sizetitle-2,face="plain"),
    
    title=element_text(size=sizetitle, face="bold"), 
    
    axis.title.x = element_blank(),
    axis.title.y = element_text(size=sizetitle,face="plain"),
    
    #axis.text.x = element_blank(),
    axis.line.x=element_blank(),
    axis.ticks.x=element_blank(),
    
    
    strip.background = element_rect(
      color="black", 
      fill="grey95", 
      size=0, 
      linetype="solid"
      )
    )
p
```

```{r, include=F}
ggsave(
  filename="Mix_spring_initial_weights.png",
  plot=p, 
  width=8, 
  height = 4, 
  path=here::here("fig/Mixture")
  )
ggsave(
  filename="Mix_spring_initial_weights.svg",
  plot=p, 
  width=8, 
  height = 4, 
  path=here::here("fig/Mixture")
  )
```

!!!!! Test effet condition sur la masse init des vers !!!!!!

## Effects on growth of individuals

```{r growthcurves, warning=F, message=F}
#| fig-cap: Growth curves of each individual. 
#| label: fig-growthcurves
#| fig-width: 8
#| fig-height: 8

p <- ggplot(
  data = df_mix_ind, 
  aes(
    x = t, 
    y = w, 
    group = ID, 
    color = Ratio
    )
  )+
  geom_point()+
  geom_line(alpha=0.7)+
  facet_wrap(~Condition, ncol = 7)+
  #facet_grid(rows = vars(Ratio), cols = vars(Line))+
  scale_color_manual(values = pal_ratio)+
  labs(
    x = "Time (days)",
    y = "Weight of the earthworm (mg)"
  )+
  theme_bw()+
  theme(
    legend.position = "none"
  )
p

```

```{r, include=F}
ggsave(
  filename="Mix_spring_growth_curves.png", 
  plot=p, 
  width=8, height = 8, 
  path=here::here("fig/Mixture")
  )
ggsave(
  filename="Mix_spring_growth_curves.svg", 
  plot=p, 
  width=8, height = 8, 
  path=here::here("fig/Mixture")
  )
```

Calculation of growth rates :

```{r calcgrowthrates, message = F, warning=F}
f_growth_rate <- function(data){
  a_init <- 0.1
  a_i <- c()
  
  # Calculation of the growth rate for each individual
  for(i in subset(data, t==0)$ID){
    data_i <- data.frame(L = subset(data, ID==i)$L,
                         t = subset(data, ID==i)$t)
    L0_i <- subset(data, ID==i & t==0)$L
    if(length(na.omit(data_i$L))==2){ # If only 2 data points
      a.Est <- (subset(data_i, !t==0)$L-subset(data_i, t==0)$L)/
        subset(data_i, !t==0)$t
    }else{
      a.Est <- NA
    }
    a_i <- rbind(a_i, a.Est)
  }
  return(a_i)
}

a_i <- f_growth_rate(df_mix_ind)

df_mix_ind_grate <- cbind(subset(df_mix_ind, t == 0), a_i)
df_mix_ind_grate_mean <- df_mix_ind_grate |> 
  aggregate(a_i ~ Condition + Dose_EPX + Dose_IMD + Ratio + TU_drc, FUN = "mean")

```

```{r growthrates, warning=F, message=F}
#| fig-cap: Mean growth rates of each cosm and per condition. 
#| label: fig-growthrates
#| fig-width: 8
#| fig-height: 8

p <- ggplot(
  data = df_mix_ind_grate, 
  aes(
    x = "", 
    y = a_i, 
    #group = Nb_rep, 
  )
)+
  geom_boxplot(
    color = Nord_polar[4]
  )+
  geom_dotplot(
    binaxis='y', 
    stackdir='center', 
    dotsize=2, 
    alpha=0.7,
    aes(
      color = Ratio,
      fill = Ratio
      )
  )+
  facet_wrap(
    ~Condition,
    ncol = 7,
    #scales = "free"
    )+
  #facet_grid(rows = vars(Ratio), cols = vars(Line))+
  #scale_y_log10()+
  scale_color_manual(values = pal_ratio)+
  scale_fill_manual(values = pal_ratio)+
  labs(
    x = "Condition",
    y = expression("Growth rate (mg"^(1/3)*"/d)")
  )+
  theme_bw()+
  theme(
    legend.position = "none"
  )
p
```

```{r, include=F}
ggsave(
  filename="Mix_spring_growth_rates.png", 
  plot=p, 
  width=8, height = 8, 
  path=here::here("fig/Mixture")
  )
ggsave(
  filename="Mix_spring_growth_rates.svg", 
  plot=p, 
  width=8, height = 8, 
  path=here::here("fig/Mixture")
  )
```

```{r lmcocgrate}
df_grate_lm <- subset(df_mix_ind_grate, !Ratio == "N")

lm.grate <- lm(a_i ~ Ratio:TU_drc, data = df_grate_lm)
summary(lm.grate)

```

## Effects on reproduction

### Number of cocoons produced

See @sec-MIXSpringJonker for a more detailed analysis.

::: panel-tabset
## Number of cocoons

```{r cocprodbox, warning=F, message=F}
#| fig-cap: Cocoons produced by each cosme and per condition. 
#| label: fig-cocbox1
#| fig-width: 8
#| fig-height: 8

p <- ggplot(
  data = df_mix_coc, 
  aes(
    x = "Condition", 
    y = Nb_cocoons, 
    )
  )+
  #geom_boxplot()+
  geom_dotplot(
    binaxis='y', 
    stackdir='center', 
    dotsize=2, 
    alpha=0.5,
    aes(color = Ratio, fill = Ratio)
  )+
  geom_dotplot(
    binaxis='y',
    stackdir='center',
    dotsize=3,
    alpha=1,
    data = df_mix_coc_mean,
    aes(
      color = Ratio,
      fill = Ratio
      )
  )+
  facet_wrap(~Condition, ncol = 7)+
  #facet_grid(rows = vars(Ratio), cols = vars(Line))+
  scale_color_manual(values = pal_ratio)+
  scale_fill_manual(values = pal_ratio)+
  labs(
    x = "Condition",
    y = "Number of cocoons produced in one cosm"
  )+
  theme_bw()+
  theme(
    legend.position = "none"
  )
p

```

## Number of cocoons per g of earthworm

```{r cocprodbox, warning=F, message=F}
#| fig-cap: Cocoons produced by each cosme per g of earthworm and per condition. 
#| label: fig-cocbox2
#| fig-width: 8
#| fig-height: 8

df_mix_coc <- df_mix_coc |> 
  mutate(
    RatioRW = Nb_cocoons/(2*w)
  )

p <- ggplot(
  data = df_mix_coc, 
  aes(
    x = "Condition", 
    y = RatioRW, 
    )
  )+
  #geom_boxplot()+
  geom_dotplot(
    binaxis='y', 
    stackdir='center', 
    dotsize=2, 
    alpha=0.5,
    aes(color = Ratio, fill = Ratio)
  )+

  facet_wrap(~Condition, ncol = 7)+
  #facet_grid(rows = vars(Ratio), cols = vars(Line))+
  scale_color_manual(values = pal_ratio)+
  scale_fill_manual(values = pal_ratio)+
  labs(
    x = "Condition",
    y = "Number of cocoons produced in one cosm per g of earthworm"
  )+
  theme_bw()+
  theme(
    legend.position = "none"
  )
p

```

```{r, include=F}
ggsave(
  filename="Mix_spring_cocoons_boxplot.png", 
  plot=p, 
  width=8, height = 8, 
  path=here::here("fig/Mixture")
  )
ggsave(
  filename="Mix_spring_cocoons_boxplot.svg", 
  plot=p, 
  width=8, height = 8, 
  path=here::here("fig/Mixture")
  )
```
:::

### Cocoons weight

!!!! Fitter des NEC + slope ? !!!!!

```{r cocweight, warning=F, message=F}
#| fig-cap: Mean weight of cocoons produced by each cosme and per condition. 
#| label: fig-cocbox
#| fig-width: 8
#| fig-height: 8

p <- ggplot(
  
  )+
  geom_boxplot()+
  geom_dotplot(
    data = df_mix_coc,
    aes(
      x = "",
      y = w_coc, 
      color = Ratio,
      fill = Ratio
      ),
    binaxis='y',
    stackdir='center',
    dotsize=2,
    alpha=0.5
  )+
  geom_dotplot(
    data = df_mix_coc_mean, 
    aes(
      x = "", 
      y = w_coc, 
      color = Ratio,
      fill = Ratio
      ),
    binaxis='y', 
    stackdir='center', 
    dotsize=3, 
    alpha=1
  )+
  facet_wrap(~Condition, ncol = 7)+
  #facet_grid(rows = vars(Ratio), cols = vars(Line))+
  scale_color_manual(values = pal_ratio)+
  scale_fill_manual(values = pal_ratio)+
  labs(
    x = "Condition",
    y = "Mean weight of cocoons produced in one cosm"
  )+
  theme_bw()+
  theme(
    legend.position = "none"
  )
p

```

```{r, include=F}
ggsave(
  filename="Mix_spring_cocoons_weight_boxplot.png", 
  plot=p, 
  width=8, height = 8, 
  path=here::here("fig/Mixture")
  )
ggsave(
  filename="Mix_spring_cocoons_weight_boxplot.svg", 
  plot=p, 
  width=8, height = 8, 
  path=here::here("fig/Mixture")
  )
```

```{r lmcocw, warning=F, message=F}
df_coc_weight_lm <- subset(df_mix_coc, !Ratio == "N")

lm.cocw <- lm(w_coc ~ Ratio:TU_drc, data = df_coc_weight_lm)
summary(lm.cocw)

```

```{r drcweigthcoc, warning=F, message=F}
#| fig-cap: Mean weight of cocoons in cosms exposed to IMD or EPX only. 
#| label: fig-drcweightcoc
#| fig-width: 6
#| fig-height: 6

p_IMD <- ggplot(
  data = subset(df_mix_coc, Dose_EPX == 0),
  aes(
    x = Dose_IMD_plot,
    y = w_coc
  )
)+
  geom_point(
    alpha=0.5,
    color = col_IMD
  )+
  geom_point(
    data = subset(df_mix_coc_mean, Dose_EPX == 0),
      aes(
        x = Dose_IMD_plot,
        y = w_coc
      ),
    size = 3,
    color = col_IMD
  )+
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100), 
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100")
  )+
  labs(
    x = "Imidacloprid concentration (mg/kg)",
    y = "Mean weight of cocoons\nproduced in one cosm (mg)"
  )+
  theme_minimal()

p_EPX <- ggplot(
  data = subset(df_mix_coc, Dose_IMD ==0),
  aes(
    x = Dose_EPX_plot,
    y = w_coc
  )
)+
  geom_point(
    alpha=0.5,
    color = col_EPX
  )+
  geom_point(
    data = subset(df_mix_coc_mean, Dose_IMD == 0),
      aes(
        x = Dose_EPX_plot,
        y = w_coc
      ),
    size = 3,
    color = col_EPX
  )+
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100), 
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100")
  )+
  labs(
    x = "Epoxiconazole concentration (mg/kg)",
    y = "Mean weight of cocoons\nproduced in one cosm (mg)"
  )+
  theme_minimal()

p <- p_IMD/p_EPX
p

```

```{r, include=F}
ggsave(
  filename="Mix_spring_cocoons_weight_drc.png", 
  plot=p, 
  width=6, height = 6, 
  path=here::here("fig/Mixture")
  )
ggsave(
  filename="Mix_spring_cocoons_weigth_drc.svg", 
  plot=p, 
  width=6, height = 6, 
  path=here::here("fig/Mixture")
  )
```

### Cocoons volume

```{r, warning=F, message=F}
#| fig-cap: Correlation between length and width of cocoons produced per conditions.
#| label: fig-cocsizecorr
#| fig-width: 8
#| fig-height: 8

p <- ggplot(
  data = df_mix_cocsize,
  aes(
    x = Coc_height,
    y = Coc_width,
    color = Lot
  )
)+
  geom_point(
    alpha = 0.5
  )+
  facet_wrap(~Condition, ncol = 7)+
  scale_color_manual(values = pal_lot)+
  scale_fill_manual(values = pal_lot)+
  labs(
    x = "Length of cocoons produced (mm)",
    y = "Width of cocoons produced (mm)"
  )+
  theme_bw()
p
```

```{r, include=F}
ggsave(
  filename="Mix_spring_cocoons_size_corr_boxplot.png", 
  plot=p, 
  width=8, height = 8, 
  path=here::here("fig/Mixture")
  )
ggsave(
  filename="Mix_spring_cocoons_size_corr_boxplot.svg", 
  plot=p, 
  width=8, height = 8, 
  path=here::here("fig/Mixture")
  )
```

```{r, warning=F, message=F}
#| fig-cap: Estimated volume of cocoons produced per conditions.
#| label: fig-cocvol
#| fig-width: 8
#| fig-height: 8

p_V <- ggplot(
  data = df_mix_cocsize, 
  aes(
    x = "Condition", 
      y = v_coc
    )
  )+
  geom_boxplot()+
  geom_dotplot(
    binaxis='y', 
    stackdir='center', 
    dotsize=2, 
    alpha=0.7,
    aes(
      color = Ratio,
      fill = Ratio
      ),
  )+
  facet_wrap(~Condition, ncol = 7)+
  scale_color_manual(values = pal_ratio)+
  scale_fill_manual(values = pal_ratio)+
  labs(
    x = "Condition",
    y = expression("Estimated volume of cocoons produced (mm"^3*")")
  )+
  theme_bw()+
  theme(
    legend.position = "none"
  )
p_V
```

```{r, include=F}
ggsave(
  filename="Mix_spring_cocoons_vol_boxplot.png", 
  plot=p_V, 
  width=8, height = 8, 
  path=here::here("fig/Mixture")
  )
ggsave(
  filename="Mix_spring_cocoons_vol_boxplot.svg", 
  plot=p_V, 
  width=8, height = 8, 
  path=here::here("fig/Mixture")
  )
```

```{r lmcocv, warning=F, message=F}
df_coc_vol_lm <- subset(df_mix_cocsize, !Ratio == "N")

lm.cocv <- lm(v_coc ~ Ratio:TU_drc, data = df_coc_vol_lm)
summary(lm.cocv)

```

```{r drcvolcoc, warning=F, message=F}
#| fig-cap: Mean Volume of cocoons in cosms exposed to IMD or EPX only. 
#| label: fig-drcvolcoc
#| fig-width: 6
#| fig-height: 6

Max_x <- 500

p_IMD <- ggplot(
  data = subset(df_mix_cocsize, Dose_EPX == 0),
  aes(
    x = Dose_IMD_plot,
    y = v_coc
  )
)+
  geom_point(
    alpha=0.5,
    color = col_IMD
  )+
  geom_point(
    data = subset(df_mix_coc_mean, Dose_EPX == 0),
      aes(
        x = Dose_IMD_plot,
        y = v_coc
      ),
    size = 3,
    color = col_IMD
  )+
  scale_x_log10(
    limits= c(Val_Ctrl, Max_x),
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100), 
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100")
  )+
  labs(
    x = "Imidacloprid concentration (mg/kg)",
    y = expression("Estimated volume of\ncocoons produced (mm"^3*")")
  )+
  theme_minimal()

p_EPX <- ggplot(
  data = subset(df_mix_cocsize, Dose_IMD ==0),
  aes(
    x = Dose_EPX_plot,
    y = v_coc
  )
)+
  geom_point(
    alpha=0.5,
    color = col_EPX
  )+
  geom_point(
    data = subset(df_mix_coc_mean, Dose_IMD == 0),
      aes(
        x = Dose_EPX_plot,
        y = v_coc
      ),
    size = 3,
    color = col_EPX
  )+
  scale_x_log10(
    limits= c(Val_Ctrl, Max_x),
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100), 
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100")
  )+
  labs(
    x = "Epoxiconazole concentration (mg/kg)",
    y = expression("Estimated volume of\ncocoons produced (mm"^3*")")
  )+
  theme_minimal()

p <- p_IMD/p_EPX
p

```

```{r, include=F}
ggsave(
  filename="Mix_spring_cocoons_vol_drc.png", 
  plot=p, 
  width=6, height = 6, 
  path=here::here("fig/Mixture")
  )
ggsave(
  filename="Mix_spring_cocoons_vol_drc.svg", 
  plot=p, 
  width=6, height = 6, 
  path=here::here("fig/Mixture")
  )
```

### Hatchling time and success

Per replicate :

```{r, warning = F, message = F}
#| fig-cap: Cumulative percentage of hatchlings over time since cocoon retrieval per replicate
#| label: fig-hatchcumt
#| fig-width: 6
#| fig-height: 6

p <- ggplot(
  data = df_mix_hatch,
  aes(
    x =t,
    y = Cumul_per_hatch,
    color = Ratio,
    group = ID_rep
  )
)+
  geom_line()+
  geom_abline(
    intercept = 1,
    slope = 0,
    linetype = "dotted",
    color = Nord_polar[4]
  )+
  facet_wrap(~Condition, ncol=7)+
  scale_color_manual(values = pal_ratio)+
  scale_fill_manual(values = pal_ratio)+
  labs(
    x = "Time (days)",
    y = "Cumulative number of hatchlings"
  )+
  theme_bw()+
  theme(
    legend.position = "none"
  )
p

```

Per condition :

```{r, warning = F, message = F}
#| fig-cap: Mean cumulative percentage of hatchlings over time since cocoon retrieval per condition
#| label: fig-hatchcumtmean
#| fig-width: 8
#| fig-height: 6

p <- ggplot(
  data = df_mix_hatch_mean,
  aes(
    x = t,
    y = Cumul_perc_hatch,
    color = as.factor(Line), 
    group = Condition
  )
)+
  geom_line()+
  geom_abline(
    intercept = 100,
    slope = 0,
    linetype = "dotted",
    color = Nord_polar[4]
  )+
  facet_wrap(~Ratio, ncol=7)+
  # scale_color_manual(values = pal_ratio)+
  # scale_fill_manual(values = pal_ratio)+
  scale_color_manual(
    values = rev(nord(palette = "aurora", n=8)),
    name="Line"
    )+
  scale_fill_manual(
    values = rev(nord(palette = "aurora", n=8)),
    name="Line"
    )+
  labs(
    x = "Time (days)",
    y = "Mean cumulative percentage of hatchlings"
  )+
  theme_bw()+
  theme(
    legend.position = "right"
  )
p

```

```{r, warning = F, message = F}
#| fig-cap: Mean cumulative percentage of hatchlings over time since cocoon retrieval per condition
#| label: fig-hatchcumtmeansingle
#| fig-width: 8
#| fig-height: 6

p <- ggplot(
  data = subset(df_mix_hatch_mean, Ratio %in% c("E", "I", "N")),
  aes(
    x = t,
    y = Cumul_perc_hatch,
    color = as.factor(Line), 
    group = Condition
  )
)+
  geom_line()+
  geom_abline(
    intercept = 100,
    slope = 0,
    linetype = "dotted",
    color = Nord_polar[4]
  )+
  facet_wrap(~Ratio, ncol=7)+
  # scale_color_manual(values = pal_ratio)+
  # scale_fill_manual(values = pal_ratio)+
  scale_color_manual(
    values = rev(nord(palette = "aurora", n=8)),
    name="Line"
    )+
  scale_fill_manual(
    values = rev(nord(palette = "aurora", n=8)),
    name="Line"
    )+
  labs(
    x = "Time (days)",
    y = "Mean cumulative percentage of hatchlings"
  )+
  theme_bw()+
  theme(
    legend.position = "right"
  )
p

```

### Observations on hatchlings

A few observations could be made while monitoring hatchlings :

-   Usually, *Aporrectodea caliginosa* gives only one hatchling per cocoon. Here, it happened a few times that there were two. Each time it was seen, one very small earthworm was with a more normal weight earthworm. All occurence could not be witnessed as we could not observe all cocoons hatch.
-   Some hatchlings were really small (@fig-smallhatch), probably because of the previous point but it could also have happened in cocoons resulting in only one individual.
-   A small number of hatchlings were with malformations like two bodies (happenned, twice, @fig-twobodieshatch), or anormal masses (happened twice, @fig-cancerhatch).
