```{r lib, include=F}
library(here)
source(file = here::here("functions/fun.R"))

f_load_libraries_colors()

palette <- colorRampPalette(c("#5E81AC", "#88C0D0"))
col_mix <- Nord_polar[4]
pal_ratio <- c("#88C0D0", col_mix, col_mix, col_mix, "#5E81AC", col_mix)

path_fig <- here::here("fig/Mixture/Spring")
```

# Results of the mixture experiments : Is there an interaction between the two active substances ? {#sec-MIXSpringJonker}

## Data importation

```{r datamix, message = F, warning=F}
# Value given to controls for plot
Val_Ctrl <- 1e-4
Label_Ctrl <- "0 (Ctrl)"


# Data from experiment A (Single substances experiement)
data_expA_repro <- f_read_data_expA_repro()
df_expA_repro_tot <- data_expA_repro$df_expA_repro
df_expA_repro <- data_expA_repro$df_expA_repro_alive
df_expA_repro_mean <- data_expA_repro$df_expA_repro_alive_mean

# Retriving EC50
df_drc_param <- read.csv(here::here("data/DRC_parameters_cocoons_really_used.csv"))
EPX_EC50_drc <- df_drc_param$coef.drc.4.[3]
IMD_EC50_drc <- df_drc_param$coef.drc.4.[4]

# Data from experiment B (Mixture experiment)
data_expB <- f_read_data_expB()
df_expB_growth <- data_expB$df_expB_growth
df_expB_repro <- data_expB$df_expB_repro
df_expB_repro_mean <- data_expB$df_expB_repro_mean
df_expB_repro_single <- data_expB$df_expB_repro_single
df_expB_repro_single_mean <- data_expB$df_expB_repro_single_mean
```

## Initial state

We can first take a look at the initial weights of individuals (@fig-initExpB).

```{r, warning=F, message=F}
#| fig-cap: Initial weights of earthworms according to batches.
#| label: fig-initExpB
#| fig-width: 10
#| fig-height: 4

pal_lot <- c(Nord_frost[3], Nord_polar[4])

p <- ggplot(
  data = subset(df_expB_growth, t == 0),
  aes(
    x = Condition,
    y = w
  )
) +
  geom_boxplot(
    alpha = 0.2,
    color = Nord_polar[1]
  ) +
  geom_dotplot(
    aes(
      color = Lot,
      fill = Lot
    ),
    binaxis = "y",
    stackdir = "center",
    dotsize = 0.5,
    alpha = 0.7
  ) +
  scale_color_manual(values = pal_lot) +
  scale_fill_manual(values = pal_lot) +
  labs(x = "Condition", y = "Weight (mg)") +
  theme_classic(12) +
  theme(
    legend.title = element_text(size = sizetitle - 2, face = "bold"),
    legend.text = element_text(size = sizetitle - 2, face = "plain"),
    title = element_text(size = sizetitle, face = "bold"),
    axis.title.x = element_blank(),
    axis.title.y = element_text(size = sizetitle, face = "plain"),
    axis.line.x = element_blank(),
    axis.ticks.x = element_blank(),
    strip.background = element_rect(
      color = "black",
      fill = "grey95",
      size = 0,
      linetype = "solid"
    )
  )
p
```

```{r saveD0, include=F}
ggsave(
  filename = "ExpB_initial_weights.png",
  plot = p,
  width = 8,
  height = 4,
  path = path_fig
)
ggsave(
  filename = "ExpB_initial_weights.jpg",
  plot = p,
  width = 8,
  height = 4,
  path = path_fig
)
ggsave(
  filename = "ExpB_initial_weights.svg",
  plot = p,
  width = 8,
  height = 4,
  path = path_fig
)
```

## Mean-Variance relationship

```{r overdispersion, message=FALSE, warning=FALSE}
df_expB_repro <- df_expB_repro |>
  mutate(
    Condition = paste0(Ratio, Line),
    Condition_f = as.factor(Condition)
  )

# Models with different distributions
m.Poisson <- glm(Nb_cocoons ~ Condition_f, family = poisson, data = df_expB_repro)
m.NB <- glm.nb(Nb_cocoons ~ Condition_f, data = df_expB_repro)
theta_nb <- summary(m.NB)$theta

# Dispersion test
dispersion <- sum(residuals(m.Poisson, type = "pearson")^2) / m.Poisson$df.residual
cat("Dispersion : ", dispersion)

library(AER)
dispersiontest(m.Poisson)

variance_mean <- df_expB_repro %>%
  group_by(Condition_f) %>%
  summarise(
    mean = mean(Nb_cocoons),
    variance = var(Nb_cocoons),
    n = n()
  )

mean_range <- seq(0, max(variance_mean$mean) * 1.1, length.out = 100)

theoretical <- data.frame(
  mean = rep(mean_range, 3),
  variance = c(
    mean_range, # Poisson
    dispersion * mean_range, # Quasi-Poisson
    mean_range + mean_range^2 / theta_nb # Negative Binomial
  ),
  model = rep(c("Poisson", "Quasi-Poisson", "Binomiale Negative"),
    each = length(mean_range)
  )
)
```

```{r}
#| fig-cap: Dose response curves obtained with cocoon production. The line represents the modelled dose-response curve (with $Y_{min} set to zero, and $common $Y_{max}$ and slope for the 2 active substances). Crosses correspond to the number of cocoons produced by one cosm and the bold points represents the mean per dose.
#| label: fig-Overdispersionplot
#| fig-width: 6
#| fig-height: 6

p <- ggplot() +
  # Theoretical lines
  geom_line(
    data = theoretical,
    aes(x = mean, y = variance, color = model, linetype = model),
    linewidth = 1.2
  ) +
  # Experimental data
  geom_point(
    data = variance_mean,
    aes(x = mean, y = variance),
    size = 4, color = "black", alpha = 0.5
  ) +
  # Labels of conditions
  geom_text(
    data = variance_mean,
    aes(x = mean, y = variance, label = Condition_f),
    vjust = -1.2, hjust = 0.5, size = 3.5, fontface = "bold"
  ) +
  labs(
    x = "Mean (μ)",
    y = "Variance (σ²)",
    title = "Variance-Mean Relationship - Choice of distribution model",
    subtitle = "Black points represent observed values per condition",
    color = "Theoretical distribution",
    linetype = "Theoretical distribution"
  ) +
  theme_minimal(base_size = 12) +
  lims(y = c(NA, 85)) +
  theme(
    legend.position = "bottom",
    legend.title = element_text(face = "bold"),
    plot.title = element_text(face = "bold", size = 14),
    plot.subtitle = element_text(size = 10, color = "gray30")
  ) +
  scale_color_manual(values = c(
    "Poisson" = Nord_polar[1],
    "Quasi-Poisson" = Nord_aurora[1],
    "Binomiale Negative" = Nord_frost[2]
  )) +
  scale_linetype_manual(values = c(
    "Poisson" = "dashed",
    "Quasi-Poisson" = "solid",
    "Binomiale Negative" = "solid"
  )) +
  guides(
    color = guide_legend(nrow = 3),
    linetype = guide_legend(nrow = 3)
  )

p

variance_mean |> datatable(options = list(dom = "t"), class = "hover")
```

```{r savemeanvariance, include=F}
ggsave(
  filename = "ExpB_Mean_Variance.png",
  plot = p,
  width = 8, height = 6,
  path = path_fig
)

ggsave(
  filename = "ExpB_Mean_Variance.jpg",
  plot = p,
  width = 8, height = 6,
  path = path_fig
)
```

For count data, the default distribution is Poisson. Our data are overdispersed for intermediate values of produced cocoons. This overdispersion cannot be reproduced using neither the Quasi-Poisson nor the Negative Binomial distributions. We therefore made the choice to keep a Poisson distribution.

## Step 1 - Dose-response curves from experiment B

Dose-response curves were fitted to single exposure data from the MIX experiment in order to check the underlying assumptions of an identical slope and identical minimum responses ($Y_{min}$) and responses in control conditions ($Y_{max}$) for both substances. This assumption was tested with a likelihood-ratio test. Dose-response modeling of mixture data was only performed when these assumptions were satisfied and model fit was evaluated using lack-of-fit tests.

### Dose-response curves for single-substances (Ratio E & I)

```{r drcmixratios, warning=F, message=F}
# Common Ymax and slope
drc.mix.IE <- drm(
  Nb_cocoons ~ Dose, Molecule,
  data = df_expB_repro_single,
  type = "Poisson",
  fct = LL.4(
    names = c("slope", "Ymin", "Ymax", "EC50"),
    fixed = c(NA, 0, NA, NA)
  ),
  # Reproduction is expected to reach 0 for large concentrations
  pmodels = data.frame(1, 1, Molecule)
)

data_CI_mix.IE <- f_CI_drc(
  Dose_min = Val_Ctrl,
  Dose_max = 5000,
  Molecules = c("EPX", "IMD"),
  drc.model = drc.mix.IE,
  signif_param = 3
)

df_CI_mix.IE <- data_CI_mix.IE$df_CI
df_param.mix.IE <- data_CI_mix.IE$df_param

EPX_EC50_mix.IE <- coef(drc.mix.IE)[3]
IMD_EC50_mix.IE <- coef(drc.mix.IE)[4]

df_expB_repro <- df_expB_repro |>
  mutate(
    TU_mix = Dose_IMD / IMD_EC50_mix.IE + Dose_EPX / EPX_EC50_mix.IE,
    TU_mix_plot = case_when(
      TU_mix == 0 ~ Val_Ctrl,
      !(TU_mix == 0) ~ TU_mix
    )
  )

df_expB_repro_mean <- df_expB_repro_mean |>
  mutate(
    TU_mix = Dose_IMD / IMD_EC50_mix.IE + Dose_EPX / EPX_EC50_mix.IE,
    TU_mix_plot = case_when(
      TU_mix == 0 ~ Val_Ctrl,
      !(TU_mix == 0) ~ TU_mix
    )
  )

summary(drc.mix.IE)

df_param.mix.IE
```

```{r, warning=F, message=F}
#| fig-cap: Dose response curves obtained with cocoon production. The line represents the modelled dose-response curve (with $Y_{min} set to zero, and $common $Y_{max}$ and slope for the 2 active substances). Crosses correspond to the number of cocoons produced by one cosm and the bold points represents the mean per dose.
#| label: fig-drcIMDEPXmixr
#| fig-width: 8
#| fig-height: 4

x <- seq(Val_Ctrl, 5000, 0.01)
line_width <- 1.2
ymax <- 22.5

df_expB_repro_single_IMD <- df_expB_repro_single |>
  filter(Molecule == "IMD")

df_expB_repro_single_EPX <- df_expB_repro_single |>
  filter(Molecule == "EPX")

df_expB_repro_single_EPX_plot <- rbind(
  df_expB_repro_single_EPX,
  subset(df_expB_repro_single_IMD, Dose == 0)
) |>
  mutate(
    Molecule = "EPX"
  )

df_expB_repro_single_IMD_mean <- df_expB_repro_single_mean |>
  filter(Molecule == "IMD")

df_expB_repro_single_EPX_mean <- df_expB_repro_single_mean |>
  filter(Molecule == "EPX")

df_expB_repro_single_EPX_mean_plot <- rbind(
  df_expB_repro_single_EPX_mean,
  subset(df_expB_repro_single_IMD_mean, Dose == 0)
)

p_I <- ggplot() +
  geom_ribbon(
    data = subset(df_CI_mix.IE, Molecule == "IMD"),
    aes(
      x = Dose,
      y = p,
      ymin = pmin,
      ymax = pmax
    ),
    alpha = 0.2,
    fill = col_IMD
  ) +
  geom_line(
    data = subset(df_CI_mix.IE, Molecule == "IMD"),
    aes(
      x = Dose,
      y = p
    ),
    color = col_IMD,
    linewidth = line_width
  ) +
  geom_point(
    data = df_expB_repro_single_IMD,
    aes(x = Dose_plot, y = Nb_cocoons),
    color = col_IMD,
    alpha = 0.6,
    shape = 4
  ) +
  geom_point(
    data = df_expB_repro_single_IMD_mean,
    aes(x = Dose_plot, y = Nb_cocoons),
    color = col_IMD,
    size = 3
  ) +
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100), # inclure la valeur fictive
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100")
  ) +
  ylim(NA, ymax) +
  labs(
    x = "Concentration of IMD (mg/kg)",
    y = "Cocoon production (#)"
  ) +
  theme_bw()

p_E <- ggplot() +
  geom_ribbon(
    data = subset(df_CI_mix.IE, Molecule == "EPX"),
    aes(
      x = Dose,
      y = p,
      ymin = pmin,
      ymax = pmax
    ),
    alpha = 0.2,
    fill = col_EPX,
    # color = col_IMD
  ) +
  geom_line(
    data = subset(df_CI_mix.IE, Molecule == "EPX"),
    aes(
      x = Dose,
      y = p
    ),
    color = col_EPX,
    linewidth = line_width
  ) +
  geom_point(
    data = df_expB_repro_single_EPX_plot,
    aes(x = Dose_plot, y = Nb_cocoons),
    color = col_EPX,
    alpha = 0.6,
    shape = 4
  ) +
  geom_point(
    data = df_expB_repro_single_EPX_mean_plot,
    aes(x = Dose_plot, y = Nb_cocoons),
    color = col_EPX,
    size = 3
  ) +
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100), # inclure la valeur fictive
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100")
  ) +
  ylim(NA, ymax) +
  labs(
    x = "Concentration of EPX (mg/kg)",
    y = "Cocoon production (#)"
  ) +
  theme_bw()

p <- p_I + p_E
p
```

```{r savedrcmixsingle, include=F}
ggsave(
  filename = "ExpB_drc_single_commonslope.png",
  plot = p,
  width = 8, height = 4,
  path = path_fig
)

ggsave(
  filename = "ExpB_drc_single_commonslope.jpg",
  plot = p,
  width = 8, height = 4,
  path = path_fig
)
```

#### Acceptability of common slope

We can consider that the slope is the same if there is not difference between this model and a model without common slope.

```{r verifcommonslopes, warning=F, message=F}
drc.mix.IE_notcommonslope <- drm(
  Nb_cocoons ~ Dose, Molecule,
  data = df_expB_repro_single,
  type = "Poisson",
  fct = LL.4(
    names = c("slope", "Ymin", "Ymax", "EC50"),
    fixed = c(NA, 0, NA, NA)
  ),
  # Reproduction is expected to reach 0 for large concentrations
  pmodels = data.frame(Molecule, 1, Molecule)
)

data_CI_mix.IE_notcommonslope <- f_CI_drc(
  Dose_min = Val_Ctrl,
  Dose_max = 5000,
  Molecules = c("EPX", "IMD"),
  drc.model = drc.mix.IE_notcommonslope,
  signif_param = 3
)

df_CI_mix.IE_notcommonslope <- data_CI_mix.IE_notcommonslope$df_CI |>
  mutate(Ratio = Molecule)
df_param.mix.IE_notcommonslope <- data_CI_mix.IE_notcommonslope$df_param

summary(drc.mix.IE_notcommonslope)
df_param.mix.IE_notcommonslope

anova(drc.mix.IE_notcommonslope, drc.mix.IE, test = "Chisq")
```

Which is the case here.

#### lacke-of-fit test

We need to perform a lacke of fit test for these dose-response curves.

```{r anovamodeldrcmix}
# Anova model
df_expB_repro_single <- df_expB_repro_single |>
  mutate(
    Condition_f = as.factor(paste0(Molecule, Dose_plot)),
    Molecule = as.factor(Molecule)
  )

anova.IE <- glm(
  Nb_cocoons ~ Condition_f,
  family = poisson(link = "log"),
  data = df_expB_repro_single
)
# check_model(glm_anova)
# predict(glm_anova)
```

```{r lofdrcsingle}
# Likelihoods
LL_model <- as.numeric(logLik(drc.mix.IE))
LL_anova <- as.numeric(logLik(anova.IE))

# Number of parameters
k_model <- 4
k_anova <- attr(logLik(anova.IE), "df")

f_LLRatio_test(LL_model, LL_anova, k_model, k_anova, 3)
```

These dose-response curves will be used for the simple interaction model of Jonker.

### Dose-response curves for each ratio

We can visualise the results of the experiment by looking at the resulting dose-response curves for each mixture ratio.

```{r drcratios, warning=F, message=F}
# Common Ymax
drc.ratios <- drm(
  Nb_cocoons ~ TU_mix, Ratio,
  data = df_expB_repro,
  type = "Poisson",
  fct = LL.4(
    names = c("slope", "Ymin", "Ymax", "EC50"),
    fixed = c(NA, 0, NA, NA)
  ),
  # Reproduction is expected to reach 0 for large concentrations
  pmodels = data.frame(Ratio, 1, Ratio)
)

data_CI_ratios <- f_CI_drc(
  Dose_min = 0.0001,
  Dose_max = 5000,
  Molecules = c("E", "F", "G", "H", "I"),
  drc.model = drc.ratios,
  signif_param = 3
)

df_CI_ratios <- data_CI_ratios$df_CI |>
  mutate(Ratio = Molecule)
df_param.ratios <- data_CI_ratios$df_param

summary(drc.ratios)
df_param.ratios

line_width <- 1.2

Ratio_E <- "1:0 (EPX only)"
Ratio_I <- "0:1 (IMD only)"
Ratio_F <- "3:1"
Ratio_G <- "1:1"
Ratio_H <- "1:3"

df_expB_repro_mean_I <- subset(df_expB_repro_mean, Ratio %in% c("I", "N")) |>
  mutate(Ratio_plot = Ratio_I)
df_expB_repro_mean_H <- subset(df_expB_repro_mean, Ratio %in% c("H", "N")) |>
  mutate(Ratio_plot = Ratio_H)
df_expB_repro_mean_G <- subset(df_expB_repro_mean, Ratio %in% c("G", "N")) |>
  mutate(Ratio_plot = Ratio_G)
df_expB_repro_mean_F <- subset(df_expB_repro_mean, Ratio %in% c("F", "N")) |>
  mutate(Ratio_plot = Ratio_F)
df_expB_repro_mean_E <- subset(df_expB_repro_mean, Ratio %in% c("E", "N")) |>
  mutate(Ratio_plot = Ratio_E)

df_expB_repro_mean_plotdrc <- rbind(
  df_expB_repro_mean_I,
  df_expB_repro_mean_H,
  df_expB_repro_mean_G,
  df_expB_repro_mean_F,
  df_expB_repro_mean_E
) |>
  mutate(
    Ratio_plot = fct_relevel(Ratio_plot, c(Ratio_E, Ratio_F, Ratio_G, Ratio_H, Ratio_I))
  )

df_expB_repro_I <- subset(df_expB_repro, Ratio %in% c("I", "N")) |>
  mutate(Ratio_plot = Ratio_I)
df_expB_repro_H <- subset(df_expB_repro, Ratio %in% c("H", "N")) |>
  mutate(Ratio_plot = Ratio_H)
df_expB_repro_G <- subset(df_expB_repro, Ratio %in% c("G", "N")) |>
  mutate(Ratio_plot = Ratio_G)
df_expB_repro_F <- subset(df_expB_repro, Ratio %in% c("F", "N")) |>
  mutate(Ratio_plot = Ratio_F)
df_expB_repro_E <- subset(df_expB_repro, Ratio %in% c("E", "N")) |>
  mutate(Ratio_plot = Ratio_E)

df_expB_repro_plotdrc <- rbind(
  df_expB_repro_I,
  df_expB_repro_H,
  df_expB_repro_G,
  df_expB_repro_F,
  df_expB_repro_E
) |>
  mutate(
    Ratio_plot = fct_relevel(Ratio_plot, c(Ratio_E, Ratio_F, Ratio_G, Ratio_H, Ratio_I))
  )

df_CI_ratios <- df_CI_ratios |>
  mutate(
    Ratio_plot = case_when(
      Ratio == "E" ~ Ratio_E,
      Ratio == "F" ~ Ratio_F,
      Ratio == "G" ~ Ratio_G,
      Ratio == "H" ~ Ratio_H,
      Ratio == "I" ~ Ratio_I,
    )
  ) |>
  mutate(
    Ratio_plot = fct_relevel(Ratio_plot, c(Ratio_E, Ratio_F, Ratio_G, Ratio_H, Ratio_I))
  )
```

```{r, warning=FALSE}
#| fig-cap: Dose-response curves obtained for each mixture ratio. The lines represent the dose-response curves obtained (with common Ymax and Ymin set to 0). Crosses correspond to the number of cocoons produced by one cosm and the bold points represent the mean per condition.
#| label: fig-drcIMDEPXratios
#| fig-width: 8
#| fig-height: 6

size_axistitle <- 11

p_full <- ggplot() +
  geom_ribbon(
    data = df_CI_ratios,
    aes(
      x = Dose,
      y = p,
      ymin = pmin,
      ymax = pmax,
      fill = Ratio_plot
    ),
    alpha = 0.2
  ) +
  geom_line(
    data = df_CI_ratios,
    aes(
      x = Dose,
      y = p,
      color = Ratio_plot,
      fill = Ratio_plot
    ),
    linewidth = line_width
  ) +
  geom_point(
    data = df_expB_repro_plotdrc,
    aes(
      x = TU_mix_plot,
      y = Nb_cocoons,
      color = Ratio_plot,
      fill = Ratio_plot
    ),
    alpha = 0.6, shape = 4
  ) +
  geom_point(
    data = df_expB_repro_mean_plotdrc,
    aes(
      x = TU_mix_plot,
      y = Nb_cocoons,
      color = Ratio_plot,
      fill = Ratio_plot
    ),
    size = 3
  ) +
  scale_color_manual(values = pal_ratio) +
  scale_fill_manual(values = pal_ratio) +
  facet_wrap2(~Ratio_plot, axes = "x") +
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100),
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100")
  ) +
  labs(
    x = "Toxic Unit (TU)",
    y = "Number of cocoons produced per cosm (#)"
  ) +
  theme_bw() +
  theme(
    axis.title.x = element_text(size = size_axistitle),
    axis.title.y = element_text(size = size_axistitle),
    axis.text.x = element_text(),
    axis.ticks.x = element_line(),
    legend.position = "none",
    strip.text = element_text(face = "bold"),
    strip.placement = "outside",
    strip.background = element_rect(color = "black", fill = "grey95", size = 0, linetype = "solid"),
    panel.spacing = unit(0.6, "lines")
  )
p_comp <- ggplot() +
  geom_line(
    data = df_CI_ratios,
    aes(
      x = Dose,
      y = p,
      color = Ratio_plot,
      fill = Ratio_plot
    ),
    linewidth = 0.8
  ) +
  scale_color_manual(values = pal_ratio) +
  scale_fill_manual(values = pal_ratio) +
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100), # inclure la valeur fictive
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100")
  ) +
  labs(
    x = "Toxic Unit (TU)",
    y = "Number of cocoons produced per cosm (#)"
  ) +
  theme_bw() +
  theme(
    legend.position = "none",
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    strip.background = element_rect(
      color = "black",
      fill = "grey95",
      size = 0,
      linetype = "solid"
    )
  )

p <- p_full +
  inset_element(
    p_comp,
    left = 0.67, bottom = -0.05, right = 1, top = 0.45
  )

p
```

```{r savedrcratios, include=F}

ggsave(
  filename = "ExpB_drcRatios.png",
  plot = p,
  width = 8, height = 6,
  path = path_fig
)
ggsave(
  filename = "ExpB_drcRatios.jpg",
  plot = p,
  width = 8, height = 6,
  path = path_fig
)
ggsave(
  filename = "ExpB_drcRatios.svg",
  plot = p,
  width = 6, height = 6,
  path = path_fig
)
```

The dose-response curves per ratio do not differ widely visually. An important interaction is not to be expected.

#### Lacke-of-fit test

```{r anovamodeldrcratios}
# Anova model
df_expB_repro <- df_expB_repro |>
  mutate(
    Condition_f = as.factor(paste0(Ratio, Line))
  )

anova.ratios <- glm(
  Nb_cocoons ~ Condition_f,
  family = poisson(link = "log"),
  data = df_expB_repro
)
# check_model(glm_anova)
# predict(glm_anova)
```

```{r lofdrcratios}
# Likelihoods
LL_model <- as.numeric(logLik(drc.ratios))
LL_anova <- as.numeric(logLik(anova.ratios))

# Number of parameters
k_model <- 11
k_anova <- attr(logLik(anova.ratios), "df")

f_LLRatio_test(LL_model, LL_anova, k_model, k_anova, 3)
```

## Step 2 - Fit of the model to our data

Next, the procedure proposed by Jonker et al. (2005) to analyse mixture data consist first in fitting the CA and the IA model under the assumption of common slope, $Y_{min}$ and $Y_{max}$ across dose-response curves. As the endpoint is cocoon production, a Poisson error model is used which implies reformulation of the loss function used during parameter optimisation. The CA and the IA model is then extended stepwise with interaction terms (a and optionally b), leading to the SA, DL, or DR formulations.

```{r modelsentry, warning=F, message=F}
# Preparation of model entry

df_design <- read.csv(here::here("data/Design_mixture.csv"))

slope <- coef(drc.mix.IE)[1]
Y_max <- coef(drc.mix.IE)[2]
EPX_EC50 <- coef(drc.mix.IE)[3]
IMD_EC50 <- coef(drc.mix.IE)[4]
Y_min <- 0

C_mat <- cbind(df_design$EPX, df_design$IMD)
Max <- Y_max
Slopes <- c(slope, slope)
Ec50s <- c(EPX_EC50, IMD_EC50)

param <- data.frame(Slopes = Slopes, Max = Max, Ec50s = Ec50s)

min_dose_EPX <- min(subset(df_design, !EPX == 0)$EPX)
max_dose_EPX <- max(subset(df_design, !EPX == 0)$EPX)

min_dose_IMD <- min(subset(df_design, !IMD == 0)$IMD)
max_dose_IMD <- max(subset(df_design, !IMD == 0)$IMD)

by_EPX <- (log(max_dose_EPX) - log(min_dose_EPX)) / 100
by_IMD <- (log(max_dose_IMD) - log(min_dose_IMD)) / 100

grid_C1 <- exp(seq(log(min_dose_EPX), log(max_dose_EPX), by = by_EPX))
grid_C2 <- exp(seq(log(min_dose_IMD), log(max_dose_IMD), by = by_IMD))
grid <- expand.grid(
  x = grid_C1,
  y = grid_C2
)

df_expB_repro_Jonker <- df_expB_repro |>
  mutate(Response = Nb_cocoons) |>
  dplyr::select(Dose_EPX, Dose_IMD, Response, Line, Ratio, TU_mix, TU_drc, Nb_rep) |>
  as.data.frame() |>
  # Because there are log calculations :
  mutate(
    Dose_EPX = case_when(
      Ratio == "N" ~ 1e-10,
      Ratio != "N" ~ Dose_EPX
    ),
    Dose_IMD = case_when(
      Ratio == "N" ~ 1e-10,
      Ratio != "N" ~ Dose_IMD
    )
  ) # |>
# filter(!(Dose_IMD == 0 & Dose_EPX == 0))

# save(
#   df_expB_repro_Jonker,
#   file = here::here("mod/Docs_for_CI_calc/Data_mix_CI.RData")
# )
```

```{r ModelsFit, warning=F, message=F, results='hide'}
signif_LL <- 5 # Significative digits for LL printing

######## CA ##################################################################

CA_fit <- data.frame(Error = NA)
CA_fit$Error <- CA_complete2_Poisson(
  C_mat = cbind(
    df_expB_repro_Jonker$Dose_EPX,
    df_expB_repro_Jonker$Dose_IMD
  ),
  Response = df_expB_repro_Jonker$Response,
  Max = Max,
  Slopes = Slopes,
  Ec50s = Ec50s,
  interact = "none",
  multicore = TRUE,
  mc.cores = 4
)

LogLikelihood_CA <- -CA_fit$Error

CA_fit$a <- NA
CA_fit$b <- NA
CA_fit$Type <- "CA"
CA_fit$Ref <- "CA"

CA_fit <- CA_fit |>
  as.data.frame()

######## IA ##################################################################

IA_fit <- data.frame(Error = NA)
IA_fit$Error <- IA_complete2_Poisson(
  C_mat = cbind(
    df_expB_repro_Jonker$Dose_EPX,
    df_expB_repro_Jonker$Dose_IMD
  ),
  Response = df_expB_repro_Jonker$Response,
  Max = Max,
  Slopes = Slopes,
  Ec50s = Ec50s,
  interact = "none"
)

LogLikelihood_IA <- -IA_fit$Error

IA_fit$a <- NA
IA_fit$b <- NA
IA_fit$Type <- "IA"
IA_fit$Ref <- "IA"

IA_fit <- IA_fit |>
  as.data.frame()

######## CASA ##################################################################

CASA_fit <- CA_complete_fit_speed(
  C_mat = cbind(
    df_expB_repro_Jonker$Dose_EPX,
    df_expB_repro_Jonker$Dose_IMD
  ),
  Response = df_expB_repro_Jonker$Response,
  interact = "SA",
  param = param,
  error_type = "Poisson",
  multicore = TRUE,
  mc.cores = 4
) |>
  as.data.frame()
CASA_fit$Type <- "SA"
CASA_fit$Ref <- "CA"

LogLikelihood_CASA <- -CASA_fit$Error
a_CASA <- CASA_fit$a
CASA_fit$b <- NA
# Printing results
a_CASA_print <- signif(a_CASA, 3)
LogLikelihood_CASA_print <- signif(LogLikelihood_CASA, signif_LL)

######## IASA ##################################################################

IASA_fit <- IA_complete_fit_speed(
  C_mat = cbind(
    df_expB_repro_Jonker$Dose_EPX,
    df_expB_repro_Jonker$Dose_IMD
  ),
  Response = df_expB_repro_Jonker$Response,
  interact = "SA",
  param = param,
  error_type = "Poisson",
  multicore = TRUE,
  mc.cores = 4
) |>
  as.data.frame()
IASA_fit$Type <- "SA"
IASA_fit$Ref <- "IA"

LogLikelihood_IASA <- -IASA_fit$Error
a_IASA <- IASA_fit$a
IASA_fit$b <- NA
# Printing results
a_IASA_print <- signif(a_IASA, 3)
LogLikelihood_IASA_print <- signif(LogLikelihood_IASA, signif_LL)

######## CADL ##################################################################

CADL_fit <- CA_complete_fit_speed(
  C_mat = cbind(
    df_expB_repro_Jonker$Dose_EPX,
    df_expB_repro_Jonker$Dose_IMD
  ),
  Response = df_expB_repro_Jonker$Response,
  interact = "DL",
  param = param,
  error_type = "Poisson",
  multicore = TRUE,
  mc.cores = 4
) |>
  as.data.frame()
CADL_fit$Type <- "DL"
CADL_fit$Ref <- "CA"

LogLikelihood_CADL <- -CADL_fit$Error
a_CADL <- CADL_fit$a
b_CADL <- CADL_fit$b
# Printing results
a_CADL_print <- signif(a_CADL, 3)
b_CADL_print <- signif(b_CADL, 3)
LogLikelihood_CADL_print <- signif(LogLikelihood_CADL, signif_LL)

######## IADL ##################################################################

IADL_fit <- IA_complete_fit_speed(
  C_mat = cbind(
    df_expB_repro_Jonker$Dose_EPX,
    df_expB_repro_Jonker$Dose_IMD
  ),
  Response = df_expB_repro_Jonker$Response,
  interact = "DL",
  param = param,
  error_type = "Poisson",
  multicore = TRUE,
  mc.cores = 4
) |>
  as.data.frame()
IADL_fit$Type <- "DL"
IADL_fit$Ref <- "IA"

LogLikelihood_IADL <- -IADL_fit$Error
a_IADL <- IADL_fit$a
b_IADL <- IADL_fit$b
# Printing results
a_IADL_print <- signif(a_IADL, 3)
b_IADL_print <- signif(b_IADL, 3)
LogLikelihood_IADL_print <- signif(LogLikelihood_IADL, signif_LL)

######## CADR ##################################################################

CADR_fit <- CA_complete_fit_speed(
  C_mat = cbind(
    df_expB_repro_Jonker$Dose_EPX,
    df_expB_repro_Jonker$Dose_IMD
  ),
  Response = df_expB_repro_Jonker$Response,
  interact = "DR",
  param = param,
  error_type = "Poisson",
  multicore = TRUE,
  mc.cores = 4
) |>
  as.data.frame()
CADR_fit$Type <- "DR"
CADR_fit$Ref <- "CA"

LogLikelihood_CADR <- -CADR_fit$Error
a_CADR <- CADR_fit$a
b_CADR <- CADR_fit$b
# Printing results
a_CADR_print <- signif(a_CADR, 3)
b_CADR_print <- signif(b_CADR, 3)
LogLikelihood_CADR_print <- signif(LogLikelihood_CADR, signif_LL)

######## IADR ##################################################################

IADR_fit <- IA_complete_fit_speed(
  C_mat = cbind(
    df_expB_repro_Jonker$Dose_EPX,
    df_expB_repro_Jonker$Dose_IMD
  ),
  Response = df_expB_repro_Jonker$Response,
  interact = "DR",
  param = param,
  error_type = "Poisson",
  multicore = TRUE,
  mc.cores = 4
) |>
  as.data.frame()
IADR_fit$Type <- "DR"
IADR_fit$Ref <- "IA"

LogLikelihood_IADR <- -IADR_fit$Error
a_IADR <- IADR_fit$a
b_IADR <- IADR_fit$b
# Printing results
a_IADR_print <- signif(a_IADR, 3)
b_IADR_print <- signif(b_IADR, 3)
LogLikelihood_IADR_print <- signif(LogLikelihood_IADR, signif_LL)
```

```{r CIcalculations, message=F, warning=F}
N_draws <- 2000

# CI_CASA <- f_Jonker_CI_calculations_condition(
#   df_data = df_expB_repro_Jonker,
#   N_draws = N_draws,
#   interact = "SA",
#   reference = "CA",
#   error_type = "Poisson"
#     )

# save(CI_CASA, file = here::here("mod/CI_cond_CASA.RData"))

load(here::here("mod/CI_cond_CASA.RData"))

# CI_CADL <- f_Jonker_CI_calculations_condition(
#   df_data = df_expB_repro_Jonker,
#   N_draws = N_draws,
#   interact = "DL",
#   reference = "CA",
#   error_type = "Poisson"
#     )
#
# save(CI_CADL, file = here::here("mod/CI_cond_CADL.RData"))
#
load(here::here("mod/CI_cond_CADL.RData"))

# CI_CADR <- f_Jonker_CI_calculations_condition(
#   df_data = df_expB_repro_Jonker,
#   N_draws = N_draws,
#   interact = "DR",
#   reference = "CA",
#   error_type = "Poisson"
#     )
#
# save(CI_CADR, file = here::here("mod/CI_cond_CADR.RData"))
#
load(here::here("mod/CI_cond_CADR.RData"))


# CI_IASA <- f_Jonker_CI_calculations_condition(
#   df_data = df_expB_repro_Jonker,
#   N_draws = N_draws,
#   interact = "SA",
#   reference = "IA",
#   error_type = "Poisson"
#     )

# save(CI_IASA, file = here::here("mod/CI_cond_IASA.RData"))

load(here::here("mod/CI_cond_IASA.RData"))

# CI_IADL <- f_Jonker_CI_calculations_condition(
#   df_data = df_expB_repro_Jonker,
#   N_draws = N_draws,
#   interact = "DL",
#   reference = "IA",
#   error_type = "Poisson"
#     )
#
# save(CI_IADL, file = here::here("mod/CI_cond_IADL.RData"))
#
load(here::here("mod/CI_cond_IADL.RData"))

# CI_IADR <- f_Jonker_CI_calculations_condition(
#   df_data = df_expB_repro_Jonker,
#   N_draws = N_draws,
#   interact = "DR",
#   reference = "IA",
#   error_type = "Poisson"
#     )
#
# save(CI_IADR, file = here::here("mod/CI_cond_IADR.RData"))
#
load(here::here("mod/CI_cond_IADR.RData"))
```

```{r resJonker, warning=F, message=F}
df_Jonker <- rbind(CA_fit, CASA_fit, CADL_fit, CADR_fit, IA_fit, IASA_fit, IADL_fit, IADR_fit) |>
  as.data.frame() |>
  mutate(Likelihood = Error)

df_Jonker$a_2.5 <- c(
  NA, CI_CASA$a_2.5, CI_CADL$a_2.5, CI_CADR$a_2.5,
  NA, CI_IASA$a_2.5, CI_IADL$a_2.5, CI_IADR$a_2.5
)
df_Jonker$a_97.5 <- c(
  NA, CI_CASA$a_97.5, CI_CADL$a_97.5, CI_CADR$a_97.5,
  NA, CI_IASA$a_97.5, CI_IADL$a_97.5, CI_IADR$a_97.5
)
df_Jonker$b_2.5 <- c(
  NA, CI_CASA$b_2.5, CI_CADL$b_2.5, CI_CADR$b_2.5,
  NA, CI_IASA$b_2.5, CI_IADL$b_2.5, CI_IADR$b_2.5
)
df_Jonker$b_97.5 <- c(
  NA, CI_CASA$b_97.5, CI_CADL$b_97.5, CI_CADR$b_97.5,
  NA, CI_IASA$b_97.5, CI_IADL$b_97.5, CI_IADR$b_97.5
)

df_Jonker <- df_Jonker[, c(
  "Type", "a", "a_2.5", "a_97.5",
  "b", "b_2.5", "b_97.5", "Likelihood", "Ref"
)]

df_Jonker |>
  datatable(options = list(dom = "t"), class = "hover") |>
  formatSignif(columns = c("a", "a_2.5", "a_97.5", "b", "b_2.5", "b_97.5", "Likelihood"), c(4, 4, 4, 4, 4, 4, 7))
```

## Step 3 - Test of models

Due to the structure of the error model, model comparison using F-tests is not possible. Instead, likelihood-ratio tests were employed to compare models. The adequacy of the CA and IA model is evaluated by comparing them to an Generalized Linear model with Poisson error - this ANOVA modelled the response as a function of the tested conditions using a Likelihood ratio test (lack-of-fit test).

The performance of these models was then compared against the CA or IA baseline using Likelihood ratio tests, in order to determine whether including interaction terms significantly improved model fit. Uncertainty around the interaction parameters ($a$, $b$) was quantified by bootstrap resampling ($n$ = 5000 with the same number of draws per condition), which provided confidence intervals and allowed us to classify interactions as synergistic, antagonistic, or additive.

### lacke-of-fit tests

We need first to test the acceptability of the CA and IA model against an anova model.

Creation of the anova model :

```{r anovamodeljonker}
# Anova model
df_expB_repro_Jonker_anova <- df_expB_repro_Jonker |>
  mutate(
    Dose_EPX_f = as.factor(Dose_EPX),
    Dose_IMD_f = as.factor(Dose_IMD),
    Dose_IMD_EPX_f = paste0(Dose_EPX_f, Dose_IMD_f)
  )

# The anova model
anova.mix <- glm(
  Response ~ Dose_IMD_EPX_f,
  family = poisson(link = "log"),
  data = df_expB_repro_Jonker_anova
)
# check_model(glm_anova)
# predict(glm_anova)
```

```{r loftestjonker}
##### CA #####

print("lacke-of-Fit test - CA")
# Likelihoods
LL_model <- LogLikelihood_CA
LL_anova <- as.numeric(logLik(anova.mix))
# Number of parameters
k_model <- 4
k_anova <- attr(logLik(anova.mix), "df")

f_LLRatio_test(LL_model, LL_anova, k_model, k_anova, 3)


##### IA #####

print("lacke-of-Fit test - IA")
# Likelihoods
LL_model <- LogLikelihood_IA
LL_anova <- as.numeric(logLik(anova.mix))
# Number of parameters
k_model <- 4
k_anova <- attr(logLik(anova.mix), "df")

f_LLRatio_test(LL_model, LL_anova, k_model, k_anova, 3)

##### CASA #####

print("lacke-of-Fit test - CASA")
# Likelihoods
LL_model <- LogLikelihood_CASA
LL_anova <- as.numeric(logLik(anova.mix))
# Number of parameters
k_model <- 5
k_anova <- attr(logLik(anova.mix), "df")

f_LLRatio_test(LL_model, LL_anova, k_model, k_anova, 3)

##### IASA #####

print("lacke-of-Fit test - IASA")
# Likelihoods
LL_model <- LogLikelihood_IASA
LL_anova <- as.numeric(logLik(anova.mix))
# Number of parameters
k_model <- 5
k_anova <- attr(logLik(anova.mix), "df")

f_LLRatio_test(LL_model, LL_anova, k_model, k_anova, 3)

##### CADL #####

print("lacke-of-Fit test - CADL")
# Likelihoods
LL_model <- LogLikelihood_CADL
LL_anova <- as.numeric(logLik(anova.mix))
# Number of parameters
k_model <- 6
k_anova <- attr(logLik(anova.mix), "df")

f_LLRatio_test(LL_model, LL_anova, k_model, k_anova, 3)

##### IADL #####

print("lacke-of-Fit test - IADL")
# Likelihoods
LL_model <- LogLikelihood_IADL
LL_anova <- as.numeric(logLik(anova.mix))
# Number of parameters
k_model <- 6
k_anova <- attr(logLik(anova.mix), "df")

f_LLRatio_test(LL_model, LL_anova, k_model, k_anova, 3)

##### CADR #####

print("lacke-of-Fit test - CADR")
# Likelihoods
LL_model <- LogLikelihood_CADR
LL_anova <- as.numeric(logLik(anova.mix))
# Number of parameters
k_model <- 6
k_anova <- attr(logLik(anova.mix), "df")

f_LLRatio_test(LL_model, LL_anova, k_model, k_anova, 3)

##### IADR #####

print("lacke-of-Fit test - IADR")
# Likelihoods
LL_model <- LogLikelihood_IADR
LL_anova <- as.numeric(logLik(anova.mix))
# Number of parameters
k_model <- 6
k_anova <- attr(logLik(anova.mix), "df")

f_LLRatio_test(LL_model, LL_anova, k_model, k_anova, 3)
```

### Model comparison

```{r modelcompjonker}
print("Comparison CA & CASA")
# Likelihoods
LL_model <- LogLikelihood_CA
LL_anova <- LogLikelihood_CASA
# Number of parameters
k_model <- 0
k_anova <- 1

f_LLRatio_test(LL_model, LL_anova, k_model, k_anova, 3)

print("Comparison CA & CADL")
# Likelihoods
LL_model <- LogLikelihood_CA
LL_anova <- LogLikelihood_CADL
# Number of parameters
k_model <- 0
k_anova <- 2

f_LLRatio_test(LL_model, LL_anova, k_model, k_anova, 3)

print("Comparison CA & CADR")
# Likelihoods
LL_model <- LogLikelihood_CA
LL_anova <- LogLikelihood_CADR
# Number of parameters
k_model <- 0
k_anova <- 2

f_LLRatio_test(LL_model, LL_anova, k_model, k_anova, 3)

print("Comparison CASA & CADL")
# Likelihoods
LL_model <- LogLikelihood_CASA
LL_anova <- LogLikelihood_CADL
# Number of parameters
k_model <- 1
k_anova <- 2

f_LLRatio_test(LL_model, LL_anova, k_model, k_anova, 3)

print("Comparison CASA & CADR")
# Likelihoods
LL_model <- LogLikelihood_CASA
LL_anova <- LogLikelihood_CADR
# Number of parameters
k_model <- 1
k_anova <- 2

f_LLRatio_test(LL_model, LL_anova, k_model, k_anova, 3)


print("Comparison IA & IASA")
# Likelihoods
LL_model <- LogLikelihood_IA
LL_anova <- LogLikelihood_IASA
# Number of parameters
k_model <- 0
k_anova <- 1

f_LLRatio_test(LL_model, LL_anova, k_model, k_anova, 3)

print("Comparison IA & IADL")
# Likelihoods
LL_model <- LogLikelihood_IA
LL_anova <- LogLikelihood_IADL
# Number of parameters
k_model <- 0
k_anova <- 2

f_LLRatio_test(LL_model, LL_anova, k_model, k_anova, 3)

print("Comparison IA & IADR")
# Likelihoods
LL_model <- LogLikelihood_IA
LL_anova <- LogLikelihood_IADR
# Number of parameters
k_model <- 0
k_anova <- 2

f_LLRatio_test(LL_model, LL_anova, k_model, k_anova, 3)

print("Comparison IASA & IADL")
# Likelihoods
LL_model <- LogLikelihood_IASA
LL_anova <- LogLikelihood_IADL
# Number of parameters
k_model <- 1
k_anova <- 2

f_LLRatio_test(LL_model, LL_anova, k_model, k_anova, 3)

print("Comparison IASA & IADR")
# Likelihoods
LL_model <- LogLikelihood_IASA
LL_anova <- LogLikelihood_IADR
# Number of parameters
k_model <- 1
k_anova <- 2

f_LLRatio_test(LL_model, LL_anova, k_model, k_anova, 3)
```

A significant synergistic interaction in the epoxiconazole–imidacloprid mixture was detected relatively to the IA reference model (IA-SA model, a = -1.5), whereas the CA-SA model did not identify a departure from additivity, which is consistent with the more conservative nature of the CA reference. Power analysis confirmed that interactions of this magnitude (-1.5 or lower) were reliably detectable with the IA-SA model (@sec-power).

The synergy suggested by the IA-SA model aligns with theoretical expectations based on toxicokinetic mechanisms described in the literature. Although the dose-response curves from experiment A were not statistically different, their estimated EC50 values differed substantially. Retesting the single substances thus proved essential to avoid bias in the estimation of mixture effects. Without retesting, this discrepancy could have generated an artificially strong synergistic signal (false positive), driven solely by the higher sensitivity of earthworms to imidacloprid in the second experiment rather than by a true mixture interaction.

However, an important statistical limitation must be acknowledged: all lack-of-fit tests for the CA and IA reference models, as well as for their associated interaction models, were significant. Strictly speaking, this indicates that none of the fitted dose–response surfaces fully captured the variability in the data. While part of this lack-of-fit may be influenced by heterogeneous variance in the response, particularly localized overdispersion observed for intermediate cocoon counts, it cannot be fully attributed to the choice of error distribution, as alternative formulations (e.g., negative-binomial or quasi-Poisson) did not resolve the lack-of-fit. Significant deviations may therefore also reflect limitations in the mean structure of the fitted surfaces or biological processes not explicitly represented in the Jonker framework, such as nonlinear or context-dependent interactions. Consequently, interaction estimates derived from these models should be interpreted with caution. Additional replication or refined experimental designs would be required to more robustly characterize the magnitude and consistency of the observed synergistic pattern.

## Step 4 - Graphical representation

```{r calcSurface, message=F, warning=F, execute = F}
########### CA ################################

# df_data_solved_surf_CA <- CA_complete2(
#   C_mat = grid,
#   Max = Max,
#   Slopes = Slopes,
#   Ec50s = Ec50s,
#   interact = "none",
#   multicore = TRUE
# )

# save(df_data_solved_surf_CA, file = here::here("mod/MIX/Surface_CA.RData"))

########### CASA ################################

# df_data_solved_surf_CASA <- CA_complete2(
#   C_mat = grid,
#   Max = Max,
#   Slopes = Slopes,
#   Ec50s = Ec50s,
#   interact = "SA",
#   a = a_CASA,
#   multicore = TRUE
# )

# save(df_data_solved_surf_CASA, file = here::here("mod/MIX/Surface_CASA.RData"))

########### CADL ################################

# df_data_solved_surf_CADL <- CA_complete2(
#   C_mat = grid,
#   Max = Max,
#   Slopes = Slopes,
#   Ec50s = Ec50s,
#   interact = "DL",
#   a = a_CADL,
#   b = b_CADL,
#   multicore = TRUE
# )

# save(df_data_solved_surf_CADL, file = here::here("mod/MIX/Surface_CADL.RData"))

########### CADR ################################

# df_data_solved_surf_CADR <- CA_complete2(
#   C_mat = grid,
#   Max = Max,
#   Slopes = Slopes,
#   Ec50s = Ec50s,
#   interact = "DR",
#   a = a_CADR,
#   b = b_CADR,
#   multicore = TRUE
# )

# save(df_data_solved_surf_CADR, file = here::here("mod/MIX/Surface_CADR.RData"))

########### IA ################################

# df_data_solved_surf_IA <- IA_complete2(
#   C_mat = grid,
#   Max = Max,
#   Slopes = Slopes,
#   Ec50s = Ec50s,
#   interact = "none"
# )

# save(df_data_solved_surf_IA, file = here::here("mod/MIX/Surface_IA.RData"))

########### IASA ################################

# df_data_solved_surf_IASA <- IA_complete2(
#   C_mat = grid,
#   Max = Max,
#   Slopes = Slopes,
#   Ec50s = Ec50s,
#   interact = "SA",
#   a = a_IASA
# )

# save(df_data_solved_surf_IASA, file = here::here("mod/MIX/Surface_IASA.RData"))

########### IADL ################################

# df_data_solved_surf_IADL <- IA_complete2(
#   C_mat = grid,
#   Max = Max,
#   Slopes = Slopes,
#   Ec50s = Ec50s,
#   interact = "DL",
#   a = a_IADL,
#   b = b_IADL
# )

# save(df_data_solved_surf_IADL, file = here::here("mod/MIX/Surface_IADL.RData"))

########### IADR ################################

# df_data_solved_surf_IADR <- IA_complete2(
#   C_mat = grid,
#   Max = Max,
#   Slopes = Slopes,
#   Ec50s = Ec50s,
#   interact = "DR",
#   a = a_IADR,
#   b = b_IADR
# )

# save(df_data_solved_surf_IADR, file = here::here("mod/MIX/Surface_IADR.RData"))
```

```{r simdataCAfit}
########### CA ################################

load(here::here("mod/MIX/Surface_CA.RData"))

df_data_solved_surf_ordered_CA <- df_data_solved_surf_CA[order(grid[, 2])]

z_CA <- matrix(
  df_data_solved_surf_ordered_CA,
  nrow = length(grid_C1),
  ncol = length(grid_C2),
  byrow = FALSE
)

########### CASA ################################

load(here::here("mod/MIX/Surface_CASA.RData"))

df_data_solved_surf_ordered_CASA <- df_data_solved_surf_CASA[order(grid[, 2])]

z_CASA <- matrix(
  df_data_solved_surf_ordered_CASA,
  nrow = length(grid_C1),
  ncol = length(grid_C2),
  byrow = FALSE
)

########### CADL ################################

load(here::here("mod/MIX/Surface_CADL.RData"))

df_data_solved_surf_ordered_CADL <- df_data_solved_surf_CADL[order(grid[, 2])]

z_CADL <- matrix(
  df_data_solved_surf_ordered_CADL,
  nrow = length(grid_C1),
  ncol = length(grid_C2),
  byrow = FALSE
)

########### CADR ################################

load(here::here("mod/MIX/Surface_CADR.RData"))

df_data_solved_surf_ordered_CADR <- df_data_solved_surf_CADR[order(grid[, 2])]

z_CADR <- matrix(
  df_data_solved_surf_ordered_CADR,
  nrow = length(grid_C1),
  ncol = length(grid_C2),
  byrow = FALSE
)

########### IA ################################

load(here::here("mod/MIX/Surface_IA.RData"))

df_data_solved_surf_ordered_IA <- df_data_solved_surf_IA[order(grid[, 2])]

z_IA <- matrix(
  df_data_solved_surf_ordered_IA,
  nrow = length(grid_C1),
  ncol = length(grid_C2),
  byrow = FALSE
)

########### IASA ################################

load(here::here("mod/MIX/Surface_IASA.RData"))

df_data_solved_surf_ordered_IASA <- df_data_solved_surf_IASA[order(grid[, 2])]

z_IASA <- matrix(
  df_data_solved_surf_ordered_IASA,
  nrow = length(grid_C1),
  ncol = length(grid_C2),
  byrow = FALSE
)

########### IADL ################################

load(here::here("mod/MIX/Surface_IADL.RData"))

df_data_solved_surf_ordered_IADL <- df_data_solved_surf_IADL[order(grid[, 2])]

z_IADL <- matrix(
  df_data_solved_surf_ordered_IADL,
  nrow = length(grid_C1),
  ncol = length(grid_C2),
  byrow = FALSE
)

########### IADR ################################

load(here::here("mod/MIX/Surface_IADR.RData"))

df_data_solved_surf_ordered_IADR <- df_data_solved_surf_IADR[order(grid[, 2])]

z_IADR <- matrix(
  df_data_solved_surf_ordered_IADR,
  nrow = length(grid_C1),
  ncol = length(grid_C2),
  byrow = FALSE
)
```

### 2D representations

::: panel-tabset
## CA vs. IA

```{r, warning=F, message=F}
#| fig-cap: Estimated surfaces isobols for cocoon production with the CA and the IA models.
#| label: fig-SurfCAIA2Ddata
#| fig-width: 5
#| fig-height: 4

target_effect <- 50

grid <- expand.grid(x = grid_C1, y = grid_C2)
grid$z_CA <- as.vector(z_CA)
grid$z_IA <- as.vector(z_IA)

bin_contour <- 2

p <- ggplot(
  grid,
  aes(x = x, y = y)
) +
  geom_contour(
    aes(z = z_CA),
    color = Nord_polar[4],
    linewidth = 0.8,
    binwidth = bin_contour
  ) +
  geom_contour(
    aes(z = z_IA),
    color = Nord_aurora[4],
    linewidth = 0.8,
    binwidth = bin_contour
  ) +
  metR::geom_text_contour(
    aes(z = z_IA),
    stroke = 0.2,
    size = 4,
    color = Nord_frost[4],
    # skip = 1,
    label.placer = label_placer_flattest(),
    binwidth = bin_contour
  ) +
  labs(
    x = expression("[EPX] (mg·kg"^-1 * ")"),
    y = expression("[IMD] (mg·kg"^-1 * ")")
  ) +
  theme_minimal(base_size = 13) +
  theme(
    axis.title = element_text(face = "bold"),
    axis.text = element_text(color = "black"),
    plot.margin = margin(10, 10, 10, 10)
  )

p
```

```{r save2DCAIA, include=F}
ggsave(
  filename = "ExpB_2D_data_CAIA.png",
  plot = p,
  width = 6, height = 5,
  path = path_fig
)
ggsave(
  filename = "ExpB_2D_data_CAIA.svg",
  plot = p,
  width = 6, height = 5,
  path = path_fig
)
```

## SA model (CA ref.)

```{r, warning=F, message=F}
#| fig-cap: Estimated surface isobols for cocoon production. The CA model is represented by the grey dotted lines and the SA model by the blue curves.
#| label: fig-SurfCASA2Ddata
#| fig-width: 5
#| fig-height: 4

target_effect <- 50

grid <- expand.grid(x = grid_C1, y = grid_C2)
grid$z_CA <- as.vector(z_CA)
grid$z_CASA <- as.vector(z_CASA)

bin_contour <- 1

p <- ggplot(
  grid,
  aes(x = x, y = y)
) +
  geom_contour(
    aes(z = z_CA),
    color = Nord_polar[4],
    linewidth = 0.8,
    linetype = "dotted",
    binwidth = bin_contour
  ) +
  geom_contour(
    aes(z = z_CASA),
    color = Nord_frost[4],
    linewidth = 1,
    binwidth = bin_contour
  ) +
  metR::geom_text_contour(
    aes(z = z_CASA),
    stroke = 0.2,
    size = 4,
    color = Nord_frost[4],
    skip = 1,
    label.placer = label_placer_flattest(),
    binwidth = bin_contour
  ) +
  labs(
    x = expression("[EPX] (mg·kg"^-1 * ")"),
    y = expression("[IMD] (mg·kg"^-1 * ")")
  ) +
  theme_minimal(base_size = 13) +
  theme(
    axis.title = element_text(face = "bold"),
    axis.text = element_text(color = "black"),
    plot.margin = margin(10, 10, 10, 10)
  )

p
```

```{r save2DCASA, include=F}
ggsave(
  filename = "ExpB_2D_data_CASA.png",
  plot = p,
  width = 6, height = 5,
  path = path_fig
)
ggsave(
  filename = "ExpB_2D_data_CASA.svg",
  plot = p,
  width = 6, height = 5,
  path = path_fig
)
```

## DL model (CA ref.)

```{r, warning=F, message=F}
#| fig-cap: Estimated surface isobols for cocoon production. The CA model is represented by the grey dotted lines and the DL model by the blue curves.
#| label: fig-SurfCADL2D
#| fig-width: 5
#| fig-height: 4

grid <- expand.grid(x = grid_C1, y = grid_C2)
grid$z_CA <- as.vector(z_CA)
grid$z_CADL <- as.vector(z_CADL)

bin_contour <- 1

p <- ggplot(
  grid,
  aes(x = x, y = y)
) +
  geom_contour(
    aes(z = z_CA),
    color = Nord_polar[4],
    linewidth = 0.8,
    linetype = "dotted",
    binwidth = bin_contour
  ) +
  geom_contour(
    aes(z = z_CADL),
    color = Nord_frost[4],
    linewidth = 1,
    binwidth = bin_contour
  ) +
  metR::geom_text_contour(
    aes(z = z_CADL),
    stroke = 0.2,
    size = 4,
    color = Nord_frost[4],
    skip = 1,
    label.placer = label_placer_flattest(),
    binwidth = bin_contour
  ) +
  labs(
    x = expression("[EPX] (mg·kg"^-1 * ")"),
    y = expression("[IMD] (mg·kg"^-1 * ")")
  ) +
  theme_minimal(base_size = 13) +
  theme(
    axis.title = element_text(face = "bold"),
    axis.text = element_text(color = "black"),
    plot.margin = margin(10, 10, 10, 10)
  )

p
```

```{r save2DCADL, include=F}
ggsave(
  filename = "ExpB_2D_data_CADL.png",
  plot = p,
  width = 6, height = 5,
  path = path_fig
)
ggsave(
  filename = "ExpB_2D_data_CADL.svg",
  plot = p,
  width = 6, height = 5,
  path = path_fig
)
```

## DR model (CA ref.)

```{r, warning=F, message=F}
#| fig-cap: Estimated surface isobols for cocoon production. The CA model is represented by the grey dotted lines and the DR model by the blue curves.
#| label: fig-SurfCADR2D
#| fig-width: 5
#| fig-height: 4

# grid <- expand.grid(x = grid_C1, y = grid_C2)
# grid$z_CA <- as.vector(z_CA)
# grid$z_CADR <- as.vector(z_CADR)
#
# bin_contour <- 1
#
# p <- ggplot(
#   grid,
#   aes(x = x, y = y)
# ) +
#   geom_contour(
#     aes(z = z_CA),
#     color = Nord_polar[4],
#     linewidth = 0.8,
#     linetype = "dotted",
#     binwidth = bin_contour
#   ) +
#   geom_contour(
#     aes(z = z_CADR),
#     color = Nord_frost[4],
#     linewidth = 1,
#     binwidth = bin_contour
#   ) +
#   metR::geom_text_contour(
#     aes(z = z_CADR),
#     stroke = 0.2,
#     size = 4,
#     color = Nord_frost[4],
#     skip = 1,
#     label.placer = label_placer_flattest(),
#     binwidth = bin_contour
#   ) +
#   labs(
#     x = expression("[EPX] (mg·kg"^-1*")"),
#     y = expression("[IMD] (mg·kg"^-1*")")
#   ) +
#   theme_minimal(base_size = 13) +
#   theme(
#     axis.title = element_text(face = "bold"),
#     axis.text = element_text(color = "black"),
#     plot.margin = margin(10, 10, 10, 10)
#   )
#
# p
```

```{r save2DCADR, include=F}
# ggsave(
#   filename="ExpB_2D_data_CADR.png",
#   plot=p,
#   width=6, height = 5,
#   path=path_fig
#   )
# ggsave(
#   filename="ExpB_2D_data_CADR.svg",
#   plot=p,
#   width=6, height = 5,
#   path=path_fig
#   )
```

## SA model (IA ref.)

```{r, warning=F, message=F}
#| fig-cap: Estimated surface isobols for cocoon production. The IA model is represented by the grey dotted lines and the SA model by the blue curves.
#| label: fig-SurfIASA2Ddata
#| fig-width: 5
#| fig-height: 4

target_effect <- 50

grid <- expand.grid(x = grid_C1, y = grid_C2)
grid$z_IA <- as.vector(z_IA)
grid$z_IASA <- as.vector(z_IASA)

bin_contour <- 1

p <- ggplot(
  grid,
  aes(x = x, y = y)
) +
  geom_contour(
    aes(z = z_IA),
    color = Nord_polar[4],
    linewidth = 0.8,
    linetype = "dotted",
    binwidth = bin_contour
  ) +
  geom_contour(
    aes(z = z_IASA),
    color = Nord_frost[4],
    linewidth = 1,
    binwidth = bin_contour
  ) +
  metR::geom_text_contour(
    aes(z = z_IASA),
    stroke = 0.2,
    size = 4,
    color = Nord_frost[4],
    skip = 1,
    label.placer = label_placer_flattest(),
    binwidth = bin_contour
  ) +
  labs(
    x = expression("[EPX] (mg·kg"^-1 * ")"),
    y = expression("[IMD] (mg·kg"^-1 * ")")
  ) +
  theme_minimal(base_size = 13) +
  theme(
    axis.title = element_text(face = "bold"),
    axis.text = element_text(color = "black"),
    plot.margin = margin(10, 10, 10, 10)
  )

p
```

```{r save2DIASA, include=F}
ggsave(
  filename = "ExpB_2D_data_IASA.png",
  plot = p,
  width = 6, height = 5,
  path = path_fig
)
ggsave(
  filename = "ExpB_2D_data_IASA.svg",
  plot = p,
  width = 6, height = 5,
  path = path_fig
)

# Poster 

p_poster <- p +
  theme(
    panel.background = element_rect(fill = "transparent", color = NA),
    plot.background  = element_rect(fill = "transparent", color = NA),
    legend.background = element_rect(fill = "transparent", color = NA),
    legend.box.background = element_rect(fill = "transparent", color = NA)
  )

ggsave(
  filename = "ExpB_2D_data_IASA_poster.png",
  plot = p_poster,
  width = 6,
  height = 5,
  bg = "transparent",
  path = path_fig
)
```

## DL model (IA ref.)

```{r, warning=F, message=F}
#| fig-cap: Estimated surface isobols for cocoon production. The IA model is represented by the grey dotted lines and the DL model by the blue curves.
#| label: fig-SurfIADL2Ddata
#| fig-width: 5
#| fig-height: 4

target_effect <- 50

grid <- expand.grid(x = grid_C1, y = grid_C2)
grid$z_IA <- as.vector(z_IA)
grid$z_IADL <- as.vector(z_IADL)

bin_contour <- 1

p <- ggplot(
  grid,
  aes(x = x, y = y)
) +
  geom_contour(
    aes(z = z_IA),
    color = Nord_polar[4],
    linewidth = 0.8,
    linetype = "dotted",
    binwidth = bin_contour
  ) +
  geom_contour(
    aes(z = z_IADL),
    color = Nord_frost[4],
    linewidth = 1,
    binwidth = bin_contour
  ) +
  metR::geom_text_contour(
    aes(z = z_IADL),
    stroke = 0.2,
    size = 4,
    color = Nord_frost[4],
    skip = 1,
    label.placer = label_placer_flattest(),
    binwidth = bin_contour
  ) +
  labs(
    x = expression("[EPX] (mg·kg"^-1 * ")"),
    y = expression("[IMD] (mg·kg"^-1 * ")")
  ) +
  theme_minimal(base_size = 13) +
  theme(
    axis.title = element_text(face = "bold"),
    axis.text = element_text(color = "black"),
    plot.margin = margin(10, 10, 10, 10)
  )

p
```

```{r save2DIADL, include=F}
ggsave(
  filename = "ExpB_2D_data_IADL.png",
  plot = p,
  width = 6, height = 5,
  path = path_fig
)
ggsave(
  filename = "ExpB_2D_data_IADL.svg",
  plot = p,
  width = 6, height = 5,
  path = path_fig
)
```

## DR model (IA ref.)

```{r, warning=F, message=F}
#| fig-cap: Estimated surface isobols for cocoon production. The IA model is represented by the grey dotted lines and the DL model by the blue curves.
#| label: fig-SurfIADR2Ddata
#| fig-width: 5
#| fig-height: 4

# target_effect <- 50
#
# grid <- expand.grid(x = grid_C1, y = grid_C2)
# grid$z_IA <- as.vector(z_IA)
# grid$z_IADL <- as.vector(z_IADR)
#
# bin_contour <- 1
#
# p <- ggplot(
#   grid,
#   aes(x = x, y = y)
# ) +
#   geom_contour(
#     aes(z = z_IA),
#     color = Nord_polar[4],
#     linewidth = 0.8,
#     linetype = "dotted",
#     binwidth = bin_contour
#   ) +
#   geom_contour(
#     aes(z = z_IADR),
#     color = Nord_frost[4],
#     linewidth = 1,
#     binwidth = bin_contour
#   ) +
#   metR::geom_text_contour(
#     aes(z = z_IADR),
#     stroke = 0.2,
#     size = 4,
#     color = Nord_frost[4],
#     skip = 1,
#     label.placer = label_placer_flattest(),
#     binwidth = bin_contour
#   ) +
#   labs(
#     x = expression("[EPX] (mg·kg"^-1*")"),
#     y = expression("[IMD] (mg·kg"^-1*")")
#   ) +
#   theme_minimal(base_size = 13) +
#   theme(
#     axis.title = element_text(face = "bold"),
#     axis.text = element_text(color = "black"),
#     plot.margin = margin(10, 10, 10, 10)
#   )
#
# p
```

```{r save2DIADR, include=F}
# ggsave(
#   filename="ExpB_2D_data_IADR.png",
#   plot=p,
#   width=6, height = 5,
#   path=path_fig
#   )
# ggsave(
#   filename="ExpB_2D_data_IARL.svg",
#   plot=p,
#   width=6, height = 5,
#   path=path_fig
#   )
```
:::

##### Dose-response curves per ratio

```{r drcratiopred, message=F, warning=F}
xIMD_I <- expand.grid(
  exp(
    seq(
      log(0.00001), log(5000),
      by = (log(5000) - log(0.00001)) / 100
    )
  )
)

xEPX_E <- expand.grid(
  exp(
    seq(
      log(0.00001), log(5000),
      by = (log(5000) - log(0.00001)) / 100
    )
  )
)

df_x_E <- data.frame(
  Dose_EPX = xEPX_E$Var1
) |>
  mutate(
    Dose_IMD = 0,
    Ratio = "I"
  )

df_x_I <- data.frame(
  Dose_IMD = xIMD_I$Var1
) |>
  mutate(
    Dose_EPX = 0,
    Ratio = "E"
  )

df_x_F <- data.frame(
  Dose_EPX = 3 / 4 * Ec50s[1] / Ec50s[2] * xEPX_E$Var1 / 100,
  Dose_IMD = 1 / 4 * Ec50s[1] / Ec50s[2] * xIMD_I$Var1 / 100
) |>
  mutate(Ratio = "F")
df_x_G <- data.frame(
  Dose_EPX = 1 / 2 * Ec50s[1] / Ec50s[2] * xEPX_E$Var1 / 200,
  Dose_IMD = 1 / 2 * Ec50s[1] / Ec50s[2] * xIMD_I$Var1 / 200
) |>
  mutate(Ratio = "G")
df_x_H <- data.frame(
  Dose_EPX = 1 / 4 * Ec50s[1] / Ec50s[2] * xEPX_E$Var1 / 200,
  Dose_IMD = 3 / 4 * Ec50s[1] / Ec50s[2] * xIMD_I$Var1 / 200
) |>
  mutate(Ratio = "H")

df_pred_drc_ratio <- rbind(df_x_E, df_x_F, df_x_G, df_x_H, df_x_I)

C_mat_E <- cbind(df_x_E$Dose_EPX, df_x_E$Dose_IMD)
C_mat_F <- cbind(df_x_F$Dose_EPX, df_x_F$Dose_IMD)
C_mat_G <- cbind(df_x_G$Dose_EPX, df_x_G$Dose_IMD)
C_mat_H <- cbind(df_x_H$Dose_EPX, df_x_H$Dose_IMD)
C_mat_I <- cbind(df_x_I$Dose_EPX, df_x_I$Dose_IMD)

# We should set the a SA interaction parameter to around 1000 to see a difference between the dose-response curves for the different ratios

response_CA_E <- CA_complete2(
  C_mat_E,
  Max, Slopes, Ec50s,
  interact = "none"
)
response_CASA_E <- CA_complete2(
  C_mat_E,
  Max, Slopes, Ec50s,
  interact = "SA",
  a = a_CASA
)
response_CADL_E <- CA_complete2(
  C_mat_E,
  Max, Slopes, Ec50s,
  interact = "DL",
  a = a_CADL,
  b = b_CADL
)

response_CA_F <- CA_complete2(
  C_mat_F,
  Max, Slopes, Ec50s,
  interact = "none"
)
response_CASA_F <- CA_complete2(
  C_mat_F,
  Max, Slopes, Ec50s,
  interact = "SA",
  a = a_CASA
)
response_CADL_F <- CA_complete2(
  C_mat_F,
  Max, Slopes, Ec50s,
  interact = "DL",
  a = a_CADL,
  b = b_CADL
)

response_CA_G <- CA_complete2(
  C_mat_G,
  Max, Slopes, Ec50s,
  interact = "none"
)
response_CASA_G <- CA_complete2(
  C_mat_G,
  Max, Slopes, Ec50s,
  interact = "SA",
  a = a_CASA
)
response_CADL_G <- CA_complete2(
  C_mat_G,
  Max, Slopes, Ec50s,
  interact = "DL",
  a = a_CADL,
  b = b_CADL
)

response_CA_H <- CA_complete2(
  C_mat_H,
  Max, Slopes, Ec50s,
  interact = "none"
)
response_CASA_H <- CA_complete2(
  C_mat_H,
  Max, Slopes, Ec50s,
  interact = "SA",
  a = a_CASA
)
response_CADL_H <- CA_complete2(
  C_mat_H,
  Max, Slopes, Ec50s,
  interact = "DL",
  a = a_CADL,
  b = b_CADL
)

response_CA_I <- CA_complete2(
  C_mat_I,
  Max, Slopes, Ec50s,
  interact = "none"
)
response_CASA_I <- CA_complete2(
  C_mat_I,
  Max, Slopes, Ec50s,
  interact = "SA",
  a = a_CASA
)
response_CADL_I <- CA_complete2(
  C_mat_I,
  Max, Slopes, Ec50s,
  interact = "DL",
  a = a_CADL,
  b = b_CADL
)


response_IA_E <- IA_complete2(
  C_mat_E,
  Max, Slopes, Ec50s,
  interact = "none"
)
response_IASA_E <- IA_complete2(
  C_mat_E,
  Max, Slopes, Ec50s,
  interact = "SA",
  a = a_IASA
)
response_IADL_E <- IA_complete2(
  C_mat_E,
  Max, Slopes, Ec50s,
  interact = "DL",
  a = a_IADL,
  b = b_IADL
)

response_IA_F <- IA_complete2(
  C_mat_F,
  Max, Slopes, Ec50s,
  interact = "none"
)
response_IASA_F <- IA_complete2(
  C_mat_F,
  Max, Slopes, Ec50s,
  interact = "SA",
  a = a_IASA
)
response_IADL_F <- IA_complete2(
  C_mat_F,
  Max, Slopes, Ec50s,
  interact = "DL",
  a = a_IADL,
  b = b_IADL
)

response_IA_G <- IA_complete2(
  C_mat_G,
  Max, Slopes, Ec50s,
  interact = "none"
)
response_IASA_G <- IA_complete2(
  C_mat_G,
  Max, Slopes, Ec50s,
  interact = "SA",
  a = a_IASA
)
response_IADL_G <- IA_complete2(
  C_mat_G,
  Max, Slopes, Ec50s,
  interact = "DL",
  a = a_IADL,
  b = b_IADL
)

response_IA_H <- IA_complete2(
  C_mat_H,
  Max, Slopes, Ec50s,
  interact = "none"
)
response_IASA_H <- IA_complete2(
  C_mat_H,
  Max, Slopes, Ec50s,
  interact = "SA",
  a = a_IASA
)
response_IADL_H <- IA_complete2(
  C_mat_H,
  Max, Slopes, Ec50s,
  interact = "DL",
  a = a_IADL,
  b = b_IADL
)

response_IA_I <- IA_complete2(
  C_mat_I,
  Max, Slopes, Ec50s,
  interact = "none"
)
response_IASA_I <- IA_complete2(
  C_mat_I,
  Max, Slopes, Ec50s,
  interact = "SA",
  a = a_IASA
)
response_IADL_I <- IA_complete2(
  C_mat_I,
  Max, Slopes, Ec50s,
  interact = "DL",
  a = a_IADL,
  b = b_IADL
)


responses_CA <- c(
  response_CA_E,
  response_CA_F,
  response_CA_G,
  response_CA_H,
  response_CA_I
)

responses_CASA <- c(
  response_CASA_E,
  response_CASA_F,
  response_CASA_G,
  response_CASA_H,
  response_CASA_I
)

responses_CADL <- c(
  response_CADL_E,
  response_CADL_F,
  response_CADL_G,
  response_CADL_H,
  response_CADL_I
)


responses_IA <- c(
  response_IA_E,
  response_IA_F,
  response_IA_G,
  response_IA_H,
  response_IA_I
)

responses_IASA <- c(
  response_IASA_E,
  response_IASA_F,
  response_IASA_G,
  response_IASA_H,
  response_IASA_I
)

responses_IADL <- c(
  response_IADL_E,
  response_IADL_F,
  response_IADL_G,
  response_IADL_H,
  response_IADL_I
)

Ratio_E <- "1:0 (EPX only)"
Ratio_I <- "0:1 (IMD only)"
Ratio_F <- "3:1"
Ratio_G <- "1:1"
Ratio_H <- "1:3"

df_pred_drc_ratio_CA <- cbind(df_pred_drc_ratio, Response = responses_CA) |>
  mutate(
    TU = Dose_IMD / Ec50s[2] + Dose_EPX / Ec50s[1],
    Ratio_plot = case_when(
      Ratio == "E" ~ Ratio_E,
      Ratio == "F" ~ Ratio_F,
      Ratio == "G" ~ Ratio_G,
      Ratio == "H" ~ Ratio_H,
      Ratio == "I" ~ Ratio_I
    ),
    Ratio_plot = fct_relevel(Ratio_plot, c(Ratio_E, Ratio_F, Ratio_G, Ratio_H, Ratio_I))
  )
df_pred_drc_ratio_CASA <- cbind(df_pred_drc_ratio, Response = responses_CASA) |>
  mutate(
    TU = Dose_IMD / Ec50s[2] + Dose_EPX / Ec50s[1],
    Ratio_plot = case_when(
      Ratio == "E" ~ Ratio_E,
      Ratio == "F" ~ Ratio_F,
      Ratio == "G" ~ Ratio_G,
      Ratio == "H" ~ Ratio_H,
      Ratio == "I" ~ Ratio_I
    ),
    Ratio_plot = fct_relevel(Ratio_plot, c(Ratio_E, Ratio_F, Ratio_G, Ratio_H, Ratio_I))
  )
df_pred_drc_ratio_CADL <- cbind(df_pred_drc_ratio, Response = responses_CADL) |>
  mutate(
    TU = Dose_IMD / Ec50s[2] + Dose_EPX / Ec50s[1],
    Ratio_plot = case_when(
      Ratio == "E" ~ Ratio_E,
      Ratio == "F" ~ Ratio_F,
      Ratio == "G" ~ Ratio_G,
      Ratio == "H" ~ Ratio_H,
      Ratio == "I" ~ Ratio_I
    ),
    Ratio_plot = fct_relevel(Ratio_plot, c(Ratio_E, Ratio_F, Ratio_G, Ratio_H, Ratio_I))
  )

df_pred_drc_ratio_IA <- cbind(df_pred_drc_ratio, Response = responses_IA) |>
  mutate(
    TU = Dose_IMD / Ec50s[2] + Dose_EPX / Ec50s[1],
    Ratio_plot = case_when(
      Ratio == "E" ~ Ratio_E,
      Ratio == "F" ~ Ratio_F,
      Ratio == "G" ~ Ratio_G,
      Ratio == "H" ~ Ratio_H,
      Ratio == "I" ~ Ratio_I
    ),
    Ratio_plot = fct_relevel(Ratio_plot, c(Ratio_E, Ratio_F, Ratio_G, Ratio_H, Ratio_I))
  )
df_pred_drc_ratio_IASA <- cbind(df_pred_drc_ratio, Response = responses_IASA) |>
  mutate(
    TU = Dose_IMD / Ec50s[2] + Dose_EPX / Ec50s[1],
    Ratio_plot = case_when(
      Ratio == "E" ~ Ratio_E,
      Ratio == "F" ~ Ratio_F,
      Ratio == "G" ~ Ratio_G,
      Ratio == "H" ~ Ratio_H,
      Ratio == "I" ~ Ratio_I
    ),
    Ratio_plot = fct_relevel(Ratio_plot, c(Ratio_E, Ratio_F, Ratio_G, Ratio_H, Ratio_I))
  )
df_pred_drc_ratio_IADL <- cbind(df_pred_drc_ratio, Response = responses_IADL) |>
  mutate(
    TU = Dose_IMD / Ec50s[2] + Dose_EPX / Ec50s[1],
    Ratio_plot = case_when(
      Ratio == "E" ~ Ratio_E,
      Ratio == "F" ~ Ratio_F,
      Ratio == "G" ~ Ratio_G,
      Ratio == "H" ~ Ratio_H,
      Ratio == "I" ~ Ratio_I
    ),
    Ratio_plot = fct_relevel(Ratio_plot, c(Ratio_E, Ratio_F, Ratio_G, Ratio_H, Ratio_I))
  )
```

::: panel-tabset
## CA model

```{r, warning=F, message=F}
#| fig-cap: Dose-response curves predicted by the CA model for each mixture ratio. Crosses correspond to the number of cocoons produced by one cosm and the bold points represent the mean per condition.
#| label: fig-drcIMDEPXratiosPredCA
#| fig-width: 8
#| fig-height: 6

line_width <- 1.2
size_axistitle <- 11

p_facetCA <- ggplot() +
  geom_line(
    data = df_pred_drc_ratio_CA,
    aes(
      x = TU,
      y = Response,
      color = Ratio_plot
    )
  ) +
  geom_point(
    data = df_expB_repro_plotdrc,
    aes(
      x = TU_mix_plot,
      y = Nb_cocoons,
      color = Ratio_plot,
      fill = Ratio_plot
    ),
    alpha = 0.6,
    shape = 4
  ) +
  geom_point(
    data = df_expB_repro_mean_plotdrc,
    aes(
      x = TU_mix_plot,
      y = Nb_cocoons,
      color = Ratio_plot,
      fill = Ratio_plot
    ),
    size = 3
  ) +
  scale_color_manual(values = pal_ratio) +
  scale_fill_manual(values = pal_ratio) +
  facet_wrap2(~Ratio_plot, axes = "x") +
  # ylim(0, 3)+
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100), # inclure la valeur fictive
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100")
  ) +
  labs(
    x = "Toxic Unit (TU)",
    y = "Number of cocoons produced per cosm (#)"
  ) +
  theme_bw() +
  theme(
    axis.title.x = element_text(size = size_axistitle),
    axis.title.y = element_text(size = size_axistitle),
    axis.text.x = element_text(),
    axis.ticks.x = element_line(),
    legend.position = "none",
    strip.text = element_text(face = "bold"),
    strip.placement = "outside",
    strip.background = element_rect(color = "black", fill = "grey95", size = 0, linetype = "solid"),
    panel.spacing = unit(0.6, "lines")
  )

p_comp_CA <- ggplot() +
  geom_line(
    data = df_pred_drc_ratio_CA,
    aes(
      x = TU,
      y = Response,
      color = Ratio_plot
    )
  ) +
  scale_color_manual(values = pal_ratio) +
  scale_fill_manual(values = pal_ratio) +
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100), # inclure la valeur fictive
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100")
  ) +
  labs(
    x = "Toxic Unit (TU)",
    y = "Number of cocoons produced per cosm (#)"
  ) +
  theme_bw() +
  theme(
    legend.position = "none",
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    strip.background = element_rect(
      color = "black",
      fill = "grey95",
      size = 0,
      linetype = "solid"
    )
  )


p_CA <- p_facetCA +
  inset_element(
    p_comp_CA,
    left = 0.67, bottom = -0.05, right = 1, top = 0.45
  )
p_CA
```

## SA model (CA ref.)

```{r, warning=F, message=F}
#| fig-cap: Dose-response curves predicted by the SA model with CA as reference for each mixture ratio. Crosses correspond to the number of cocoons produced by one cosm and the bold points represent the mean per condition.
#| label: fig-drcIMDEPXratiosPredCASA
#| fig-width: 8
#| fig-height: 6

line_width <- 1.2
size_axistitle <- 11

p_facetCASA <- ggplot() +
  geom_line(
    data = df_pred_drc_ratio_CASA,
    aes(
      x = TU,
      y = Response,
      color = Ratio_plot
    )
  ) +
  geom_point(
    data = df_expB_repro_plotdrc,
    aes(
      x = TU_mix_plot,
      y = Nb_cocoons,
      color = Ratio_plot,
      fill = Ratio_plot
    ),
    alpha = 0.6,
    shape = 4
  ) +
  geom_point(
    data = df_expB_repro_mean_plotdrc,
    aes(
      x = TU_mix_plot,
      y = Nb_cocoons,
      color = Ratio_plot,
      fill = Ratio_plot
    ),
    size = 3
  ) +
  scale_color_manual(values = pal_ratio) +
  scale_fill_manual(values = pal_ratio) +
  facet_wrap2(~Ratio_plot, axes = "x") +
  # ylim(0, 3)+
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100), # inclure la valeur fictive
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100"),
    limits = c(0.0001, 101)
  ) +
  labs(
    x = "Toxic Unit (TU)",
    y = "Number of cocoons produced per cosm (#)"
  ) +
  theme_bw() +
  theme(
    axis.title.x = element_text(size = size_axistitle),
    axis.title.y = element_text(size = size_axistitle),
    axis.text.x = element_text(),
    axis.ticks.x = element_line(),
    legend.position = "none",
    strip.text = element_text(face = "bold"),
    strip.placement = "outside",
    strip.background = element_rect(color = "black", fill = "grey95", size = 0, linetype = "solid"),
    panel.spacing = unit(0.6, "lines")
  )

p_comp_CASA <- ggplot() +
  geom_line(
    data = df_pred_drc_ratio_CASA,
    aes(
      x = TU,
      y = Response,
      color = Ratio_plot
    )
  ) +
  scale_color_manual(values = pal_ratio) +
  scale_fill_manual(values = pal_ratio) +
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100), # inclure la valeur fictive
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100"),
    limits = c(0.0001, 101)
  ) +
  labs(
    x = "Toxic Unit (TU)",
    y = "Number of cocoons produced per cosm (#)"
  ) +
  theme_bw() +
  theme(
    legend.position = "none",
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    strip.background = element_rect(
      color = "black",
      fill = "grey95",
      size = 0,
      linetype = "solid"
    )
  )


p_CASA <- p_facetCASA +
  inset_element(
    p_comp_CASA,
    left = 0.67, bottom = -0.05, right = 1, top = 0.45
  )
p_CASA
```

## DL model (CA ref.)

```{r, warning=F, message=F}
#| fig-cap: Dose-response curves predicted by the DL model with CA as reference for each mixture ratio. Crosses correspond to the number of cocoons produced by one cosm and the bold points represent the mean per condition.
#| label: fig-drcIMDEPXratiosPredCADL
#| fig-width: 8
#| fig-height: 6

line_width <- 1.2
size_axistitle <- 11

p_facetCADL <- ggplot() +
  geom_line(
    data = df_pred_drc_ratio_CADL,
    aes(
      x = TU,
      y = Response,
      color = Ratio_plot
    )
  ) +
  geom_point(
    data = df_expB_repro_plotdrc,
    aes(
      x = TU_mix_plot,
      y = Nb_cocoons,
      color = Ratio_plot,
      fill = Ratio_plot
    ),
    alpha = 0.6,
    shape = 4
  ) +
  geom_point(
    data = df_expB_repro_mean_plotdrc,
    aes(
      x = TU_mix_plot,
      y = Nb_cocoons,
      color = Ratio_plot,
      fill = Ratio_plot
    ),
    size = 3
  ) +
  scale_color_manual(values = pal_ratio) +
  scale_fill_manual(values = pal_ratio) +
  facet_wrap2(~Ratio_plot, axes = "x") +
  # ylim(0, 3)+
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100), # inclure la valeur fictive
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100"),
    limits = c(0.009, 101)
  ) +
  labs(
    x = "Toxic Unit (TU)",
    y = "Number of cocoons produced per cosm (#)"
  ) +
  theme_bw() +
  theme(
    axis.title.x = element_text(size = size_axistitle),
    axis.title.y = element_text(size = size_axistitle),
    axis.text.x = element_text(),
    axis.ticks.x = element_line(),
    legend.position = "none",
    strip.text = element_text(face = "bold"),
    strip.placement = "outside",
    strip.background = element_rect(color = "black", fill = "grey95", size = 0, linetype = "solid"),
    panel.spacing = unit(0.6, "lines")
  )

p_comp_CADL <- ggplot() +
  geom_line(
    data = df_pred_drc_ratio_CADL,
    aes(
      x = TU,
      y = Response,
      color = Ratio_plot
    )
  ) +
  scale_color_manual(values = pal_ratio) +
  scale_fill_manual(values = pal_ratio) +
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100), # inclure la valeur fictive
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100"),
    limits = c(0.009, 101)
  ) +
  labs(
    x = "Toxic Unit (TU)",
    y = "Number of cocoons produced per cosm (#)"
  ) +
  theme_bw() +
  theme(
    legend.position = "none",
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    strip.background = element_rect(
      color = "black",
      fill = "grey95",
      size = 0,
      linetype = "solid"
    )
  )


p_CADL <- p_facetCADL +
  inset_element(
    p_comp_CADL,
    left = 0.67, bottom = -0.05, right = 1, top = 0.45
  )
p_CADL
```

## IA model

```{r, warning=F, message=F}
#| fig-cap: Dose-response curves predicted by the IA model for each mixture ratio. Crosses correspond to the number of cocoons produced by one cosm and the bold points represent the mean per condition.
#| label: fig-drcIMDEPXratiosPredIA
#| fig-width: 8
#| fig-height: 6

line_width <- 1.2
size_axistitle <- 11

p_facetIA <- ggplot() +
  geom_line(
    data = df_pred_drc_ratio_IA,
    aes(
      x = TU,
      y = Response,
      color = Ratio_plot
    )
  ) +
  geom_point(
    data = df_expB_repro_plotdrc,
    aes(
      x = TU_mix_plot,
      y = Nb_cocoons,
      color = Ratio_plot,
      fill = Ratio_plot
    ),
    alpha = 0.6,
    shape = 4
  ) +
  geom_point(
    data = df_expB_repro_mean_plotdrc,
    aes(
      x = TU_mix_plot,
      y = Nb_cocoons,
      color = Ratio_plot,
      fill = Ratio_plot
    ),
    size = 3
  ) +
  scale_color_manual(values = pal_ratio) +
  scale_fill_manual(values = pal_ratio) +
  facet_wrap2(~Ratio_plot, axes = "x") +
  # ylim(0, 3)+
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100), # inclure la valeur fictive
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100")
  ) +
  labs(
    x = "Toxic Unit (TU)",
    y = "Number of cocoons produced per cosm (#)"
  ) +
  theme_bw() +
  theme(
    axis.title.x = element_text(size = size_axistitle),
    axis.title.y = element_text(size = size_axistitle),
    axis.text.x = element_text(),
    axis.ticks.x = element_line(),
    legend.position = "none",
    strip.text = element_text(face = "bold"),
    strip.placement = "outside",
    strip.background = element_rect(color = "black", fill = "grey95", size = 0, linetype = "solid"),
    panel.spacing = unit(0.6, "lines")
  )

p_comp_IA <- ggplot() +
  geom_line(
    data = df_pred_drc_ratio_IA,
    aes(
      x = TU,
      y = Response,
      color = Ratio_plot
    )
  ) +
  scale_color_manual(values = pal_ratio) +
  scale_fill_manual(values = pal_ratio) +
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100), # inclure la valeur fictive
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100")
  ) +
  labs(
    x = "Toxic Unit (TU)",
    y = "Number of cocoons produced per cosm (#)"
  ) +
  theme_bw() +
  theme(
    legend.position = "none",
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    strip.background = element_rect(
      color = "black",
      fill = "grey95",
      size = 0,
      linetype = "solid"
    )
  )


p_IA <- p_facetIA +
  inset_element(
    p_comp_CA,
    left = 0.67, bottom = -0.05, right = 1, top = 0.45
  )
p_IA
```

## SA model (IA ref.)

```{r, warning=F, message=F}
#| fig-cap: Dose-response curves predicted by the SA model with IA as reference for each mixture ratio. Crosses correspond to the number of cocoons produced by one cosm and the bold points represent the mean per condition.
#| label: fig-drcIMDEPXratiosPredIASA
#| fig-width: 8
#| fig-height: 6

line_width <- 1.2
size_axistitle <- 11

p_facetIASA <- ggplot() +
  geom_line(
    data = df_pred_drc_ratio_IASA,
    aes(
      x = TU,
      y = Response,
      color = Ratio_plot
    )
  ) +
  geom_point(
    data = df_expB_repro_plotdrc,
    aes(
      x = TU_mix_plot,
      y = Nb_cocoons,
      color = Ratio_plot,
      fill = Ratio_plot
    ),
    alpha = 0.6,
    shape = 4
  ) +
  geom_point(
    data = df_expB_repro_mean_plotdrc,
    aes(
      x = TU_mix_plot,
      y = Nb_cocoons,
      color = Ratio_plot,
      fill = Ratio_plot
    ),
    size = 3
  ) +
  scale_color_manual(values = pal_ratio) +
  scale_fill_manual(values = pal_ratio) +
  facet_wrap2(~Ratio_plot, axes = "x") +
  # ylim(0, 3)+
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100), # inclure la valeur fictive
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100"),
    limits = c(0.0001, 101)
  ) +
  labs(
    x = "Toxic Unit (TU)",
    y = "Number of cocoons produced per cosm (#)"
  ) +
  theme_bw() +
  theme(
    axis.title.x = element_text(size = size_axistitle),
    axis.title.y = element_text(size = size_axistitle),
    legend.position = "none",
    strip.text = element_text(face = "bold"),
    strip.background = element_rect(
      color = "black",
      fill = "grey95",
      size = 0,
      linetype = "solid"
    )
  )

p_comp_IASA <- ggplot() +
  geom_line(
    data = df_pred_drc_ratio_IASA,
    aes(
      x = TU,
      y = Response,
      color = Ratio_plot
    )
  ) +
  scale_color_manual(values = pal_ratio) +
  scale_fill_manual(values = pal_ratio) +
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100), # inclure la valeur fictive
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100"),
    limits = c(0.0001, 101)
  ) +
  labs(
    x = "Toxic Unit (TU)",
    y = "Number of cocoons produced per cosm (#)"
  ) +
  theme_bw() +
  theme(
    axis.title.x = element_text(size = size_axistitle),
    axis.title.y = element_text(size = size_axistitle),
    axis.text.x = element_text(),
    axis.ticks.x = element_line(),
    legend.position = "none",
    strip.text = element_text(face = "bold"),
    strip.placement = "outside",
    strip.background = element_rect(color = "black", fill = "grey95", size = 0, linetype = "solid"),
    panel.spacing = unit(0.6, "lines")
  )


p_IASA <- p_facetIASA +
  inset_element(
    p_comp_IASA,
    left = 0.67, bottom = -0.05, right = 1, top = 0.45
  )
p_IASA
```

## DL model (IA ref.)

```{r, warning=F, message=F}
#| fig-cap: Dose-response curves predicted by the DL model with IA as reference for each mixture ratio. Crosses correspond to the number of cocoons produced by one cosm and the bold points represent the mean per condition.
#| label: fig-drcIMDEPXratiosPredIADL
#| fig-width: 8
#| fig-height: 6

line_width <- 1.2
size_axistitle <- 11

p_facetIADL <- ggplot() +
  geom_line(
    data = df_pred_drc_ratio_IADL,
    aes(
      x = TU,
      y = Response,
      color = Ratio_plot
    )
  ) +
  geom_point(
    data = df_expB_repro_plotdrc,
    aes(
      x = TU_mix_plot,
      y = Nb_cocoons,
      color = Ratio_plot,
      fill = Ratio_plot
    ),
    alpha = 0.6,
    shape = 4
  ) +
  geom_point(
    data = df_expB_repro_mean_plotdrc,
    aes(
      x = TU_mix_plot,
      y = Nb_cocoons,
      color = Ratio_plot,
      fill = Ratio_plot
    ),
    size = 3
  ) +
  scale_color_manual(values = pal_ratio) +
  scale_fill_manual(values = pal_ratio) +
  facet_wrap2(~Ratio_plot, axes = "x") +
  # ylim(0, 3)+
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100), # inclure la valeur fictive
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100"),
    limits = c(0.009, 101)
  ) +
  labs(
    x = "Toxic Unit (TU)",
    y = "Number of cocoons produced per cosm (#)"
  ) +
  theme_bw() +
  theme(
    axis.title.x = element_text(size = size_axistitle),
    axis.title.y = element_text(size = size_axistitle),
    axis.text.x = element_text(),
    axis.ticks.x = element_line(),
    legend.position = "none",
    strip.text = element_text(face = "bold"),
    strip.placement = "outside",
    strip.background = element_rect(color = "black", fill = "grey95", size = 0, linetype = "solid"),
    panel.spacing = unit(0.6, "lines")
  )

p_comp_IADL <- ggplot() +
  geom_line(
    data = df_pred_drc_ratio_IADL,
    aes(
      x = TU,
      y = Response,
      color = Ratio_plot
    )
  ) +
  scale_color_manual(values = pal_ratio) +
  scale_fill_manual(values = pal_ratio) +
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100), # inclure la valeur fictive
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100"),
    limits = c(0.009, 101)
  ) +
  labs(
    x = "Toxic Unit (TU)",
    y = "Number of cocoons produced per cosm (#)"
  ) +
  theme_bw() +
  theme(
    legend.position = "none",
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    strip.background = element_rect(
      color = "black",
      fill = "grey95",
      size = 0,
      linetype = "solid"
    )
  )


p_IADL <- p_facetIADL +
  inset_element(
    p_comp_IADL,
    left = 0.67, bottom = -0.05, right = 1, top = 0.45
  )
p_IADL
```
:::

```{r savepreddrc, include=F}
ggsave(
  filename = "ExpB_pred_drc_ratios_CA.png",
  plot = p_CA,
  width = 8, height = 6,
  path = path_fig
)
ggsave(
  filename = "ExpB_pred_drc_ratios_CASA.png",
  plot = p_CASA,
  width = 8, height = 6,
  path = path_fig
)
ggsave(
  filename = "ExpB_pred_drc_ratios_CADL.png",
  plot = p_CADL,
  width = 8, height = 6,
  path = path_fig
)

ggsave(
  filename = "ExpB_pred_drc_ratios_IA.png",
  plot = p_IA,
  width = 8, height = 6,
  path = path_fig
)
ggsave(
  filename = "ExpB_pred_drc_ratios_IASA.png",
  plot = p_IASA,
  width = 8, height = 6,
  path = path_fig
)
ggsave(
  filename = "ExpB_pred_drc_ratios_IADL.png",
  plot = p_IADL,
  width = 8, height = 6,
  path = path_fig
)
```

#### 3D representation

::: panel-tabset
## CA model

```{r, message=F, warning=F}
#| fig-cap: Estimated surface (CA model). Small grey dots represents the measurements at the replicate level while the bigger black dots represent the mean per condition.
#| label: fig-SurfCAdyn
#| fig-width: 5
#| fig-height: 4

p_CA <- plotly::plot_ly(
  x = grid_C2,
  y = grid_C1,
  z = ~z_CA,
  colors = Nord_frost
) %>%
  add_surface(showlegend = FALSE, showscale = FALSE) %>%
  layout(
    scene = list(
      xaxis = list(title = "[IMD] (mg/kg)"),
      yaxis = list(title = "[EPX] (mg/kg)"),
      zaxis = list(title = "Cocoon production"),
      camera = list(eye = list(x = 2.5, y = -1.2, z = 1))
    ),
    paper_bgcolor = "rgba(0, 0, 0, 0)",
    plot_bgcolor = "rgba(0, 0, 0, 0)"
  ) %>%
  add_markers(
    y = df_expB_repro$Dose_EPX,
    x = df_expB_repro$Dose_IMD,
    z = df_expB_repro$Nb_cocoons,
    type = "scatter3d",
    mode = "markers",
    showlegend = FALSE,
    marker = list(
      size = 3,
      color = Nord_polar[4],
      symbol = 104
    )
  ) %>%
  add_markers(
    y = df_expB_repro_mean$Dose_EPX,
    x = df_expB_repro_mean$Dose_IMD,
    z = df_expB_repro_mean$Nb_cocoons,
    type = "scatter3d",
    mode = "markers",
    marker = list(
      size = 7,
      color = Nord_polar[1],
      symbol = 104
    ),
    showlegend = FALSE
  )

p_CA
```

## SA model (CA ref.)

```{r, message=F, warning=F}
#| fig-cap: Estimated surface (SA model with CA as reference). Small grey dots represents the measurements at the replicate level while the bigger black dots represent the mean per condition.
#| label: fig-SurfCASAdyn
#| fig-width: 5
#| fig-height: 4

p_CASA <- plotly::plot_ly(
  x = grid_C2,
  y = grid_C1,
  z = ~z_CASA,
  colors = Nord_frost
) %>%
  add_surface(showlegend = FALSE, showscale = FALSE) %>%
  layout(
    scene = list(
      xaxis = list(title = "[IMD] (mg/kg)"),
      yaxis = list(title = "[EPX] (mg/kg)"),
      zaxis = list(title = "Cocoon production"),
      camera = list(eye = list(x = 2.5, y = -1.2, z = 1))
    ),
    # paper_bgcolor = "#F9FAFC",
    # plot_bgcolor = "#F9FAFC"
    paper_bgcolor = "rgba(0, 0, 0, 0)",
    plot_bgcolor = "rgba(0, 0, 0, 0)"
  ) %>%
  colorbar(title = list(text = "Production of cocoons per cosm")) %>%
  add_markers(
    y = df_expB_repro$Dose_EPX,
    x = df_expB_repro$Dose_IMD,
    z = df_expB_repro$Nb_cocoons,
    type = "scatter3d",
    mode = "markers",
    marker = list(
      size = 3,
      color = Nord_polar[4],
      symbol = 104
    ),
    showlegend = FALSE
  ) %>%
  add_markers(
    y = df_expB_repro_mean$Dose_EPX,
    x = df_expB_repro_mean$Dose_IMD,
    z = df_expB_repro_mean$Nb_cocoons,
    type = "scatter3d",
    mode = "markers",
    marker = list(
      size = 7,
      color = Nord_polar[1],
      symbol = 104
    ),
    showlegend = FALSE
  )

p_CASA
```

## DL model (CA ref.)

```{r, message=F, warning=F}
#| fig-cap: Estimated surface (DL model with CA as reference). Small grey dots represents the measurements at the replicate level while the bigger black dots represent the mean per condition.
#| label: fig-SurfCADLdyn
#| fig-width: 5
#| fig-height: 4

p_CADL <- plotly::plot_ly(
  x = grid_C2,
  y = grid_C1,
  z = ~z_CADL,
  colors = Nord_frost
) %>%
  add_surface(showlegend = FALSE, showscale = FALSE) %>%
  layout(
    scene = list(
      xaxis = list(title = "[IMD] (mg/kg)"),
      yaxis = list(title = "[EPX] (mg/kg)"),
      zaxis = list(title = "Cocoon production"),
      camera = list(eye = list(x = 2.5, y = -1.2, z = 1))
    ),
    # paper_bgcolor = "#F9FAFC",
    # plot_bgcolor = "#F9FAFC"
    paper_bgcolor = "rgba(0, 0, 0, 0)",
    plot_bgcolor = "rgba(0, 0, 0, 0)"
  ) %>%
  colorbar(title = list(text = "Production of cocoons per cosm")) %>%
  add_markers(
    y = df_expB_repro$Dose_EPX,
    x = df_expB_repro$Dose_IMD,
    z = df_expB_repro$Nb_cocoons,
    type = "scatter3d",
    mode = "markers",
    marker = list(
      size = 3,
      color = Nord_polar[4],
      symbol = 104
    ),
    showlegend = FALSE
  ) %>%
  add_markers(
    y = df_expB_repro_mean$Dose_EPX,
    x = df_expB_repro_mean$Dose_IMD,
    z = df_expB_repro_mean$Nb_cocoons,
    type = "scatter3d",
    mode = "markers",
    marker = list(
      size = 7,
      color = Nord_polar[1],
      symbol = 104
    ),
    showlegend = FALSE
  )

p_CADL
```

## IA model

```{r, message=F, warning=F}
#| fig-cap: Estimated surface (IA model). Small grey dots represents the measurements at the replicate level while the bigger black dots represent the mean per condition.
#| label: fig-SurfIAdyn
#| fig-width: 5
#| fig-height: 4

p_IA <- plotly::plot_ly(
  x = grid_C2,
  y = grid_C1,
  z = ~z_IA,
  colors = Nord_frost
) %>%
  add_surface(showlegend = FALSE, showscale = FALSE) %>%
  layout(
    scene = list(
      xaxis = list(title = "[IMD] (mg/kg)"),
      yaxis = list(title = "[EPX] (mg/kg)"),
      zaxis = list(title = "Cocoon production"),
      camera = list(eye = list(x = 2.5, y = -1.2, z = 1))
    ),
    paper_bgcolor = "rgba(0, 0, 0, 0)",
    plot_bgcolor = "rgba(0, 0, 0, 0)"
  ) %>%
  add_markers(
    y = df_expB_repro$Dose_EPX,
    x = df_expB_repro$Dose_IMD,
    z = df_expB_repro$Nb_cocoons,
    type = "scatter3d",
    mode = "markers",
    showlegend = FALSE,
    marker = list(
      size = 3,
      color = Nord_polar[4],
      symbol = 104
    )
  ) %>%
  add_markers(
    y = df_expB_repro_mean$Dose_EPX,
    x = df_expB_repro_mean$Dose_IMD,
    z = df_expB_repro_mean$Nb_cocoons,
    type = "scatter3d",
    mode = "markers",
    marker = list(
      size = 7,
      color = Nord_polar[1],
      symbol = 104
    ),
    showlegend = FALSE
  )

p_IA
```

## SA model (IA ref.)

```{r, message=F, warning=F}
#| fig-cap: Estimated surface (SA model with IA as reference). Small grey dots represents the measurements at the replicate level while the bigger black dots represent the mean per condition.
#| label: fig-SurfIASAdyn
#| fig-width: 5
#| fig-height: 4

p_IASA <- plotly::plot_ly(
  x = grid_C2,
  y = grid_C1,
  z = ~z_IASA,
  colors = Nord_frost
) %>%
  add_surface(showlegend = FALSE, showscale = FALSE) %>%
  layout(
    scene = list(
      xaxis = list(title = "[IMD] (mg/kg)"),
      yaxis = list(title = "[EPX] (mg/kg)"),
      zaxis = list(title = "Cocoon production"),
      camera = list(eye = list(x = 2.5, y = -1.2, z = 1))
    ),
    # paper_bgcolor = "#F9FAFC",
    # plot_bgcolor = "#F9FAFC"
    paper_bgcolor = "rgba(0, 0, 0, 0)",
    plot_bgcolor = "rgba(0, 0, 0, 0)"
  ) %>%
  colorbar(title = list(text = "Production of cocoons per cosm")) %>%
  add_markers(
    y = df_expB_repro$Dose_EPX,
    x = df_expB_repro$Dose_IMD,
    z = df_expB_repro$Nb_cocoons,
    type = "scatter3d",
    mode = "markers",
    marker = list(
      size = 3,
      color = Nord_polar[4],
      symbol = 104
    ),
    showlegend = FALSE
  ) %>%
  add_markers(
    y = df_expB_repro_mean$Dose_EPX,
    x = df_expB_repro_mean$Dose_IMD,
    z = df_expB_repro_mean$Nb_cocoons,
    type = "scatter3d",
    mode = "markers",
    marker = list(
      size = 7,
      color = Nord_polar[1],
      symbol = 104
    ),
    showlegend = FALSE
  )

p_IASA
```

## DL model (IA ref.)

```{r, message=F, warning=F}
#| fig-cap: Estimated surface (DL model with IA as reference). Small grey dots represents the measurements at the replicate level while the bigger black dots represent the mean per condition.
#| label: fig-SurfIADLdyn
#| fig-width: 5
#| fig-height: 4

p_IADL <- plotly::plot_ly(
  x = grid_C2,
  y = grid_C1,
  z = ~z_IADL,
  colors = Nord_frost
) %>%
  add_surface(showlegend = FALSE, showscale = FALSE) %>%
  layout(
    scene = list(
      xaxis = list(title = "[IMD] (mg/kg)"),
      yaxis = list(title = "[EPX] (mg/kg)"),
      zaxis = list(title = "Cocoon production"),
      camera = list(eye = list(x = 2.5, y = -1.2, z = 1))
    ),
    # paper_bgcolor = "#F9FAFC",
    # plot_bgcolor = "#F9FAFC"
    paper_bgcolor = "rgba(0, 0, 0, 0)",
    plot_bgcolor = "rgba(0, 0, 0, 0)"
  ) %>%
  colorbar(title = list(text = "Production of cocoons per cosm")) %>%
  add_markers(
    y = df_expB_repro$Dose_EPX,
    x = df_expB_repro$Dose_IMD,
    z = df_expB_repro$Nb_cocoons,
    type = "scatter3d",
    mode = "markers",
    marker = list(
      size = 3,
      color = Nord_polar[4],
      symbol = 104
    ),
    showlegend = FALSE
  ) %>%
  add_markers(
    y = df_expB_repro_mean$Dose_EPX,
    x = df_expB_repro_mean$Dose_IMD,
    z = df_expB_repro_mean$Nb_cocoons,
    type = "scatter3d",
    mode = "markers",
    marker = list(
      size = 7,
      color = Nord_polar[1],
      symbol = 104
    ),
    showlegend = FALSE
  )

p_IADL
```
:::

```{r save3Ds, include = F}
orca(p_CA,
  # file = paste0("../../",path_fig, "/ExpB_3D_surface_CA.png"),
  file = "../../fig/Mixture/Spring/ExpB_3D_surface_CA.png",
  width = 800,
  height = 600,
  scale = 2,
  format = "png",
  mathjax = "local"
)

orca(p_CASA,
  file = "../../fig/Mixture/Spring/ExpB_3D_surface_CASA.png",
  width = 800,
  height = 600,
  scale = 2,
  format = "png",
  mathjax = "local"
)

orca(p_CADL,
  file = "../../fig/Mixture/Spring/ExpB_3D_surface_CADL.png",
  width = 800,
  height = 600,
  scale = 2,
  format = "png",
  mathjax = "local"
)

orca(p_IA,
  file = "../../fig/Mixture/Spring/ExpB_3D_surface_IA.png",
  width = 800,
  height = 600,
  scale = 2,
  format = "png",
  mathjax = "local"
)

orca(p_IASA,
  file = "../../fig/Mixture/Spring/ExpB_3D_surface_IASA.png",
  width = 800,
  height = 600,
  scale = 2,
  format = "png",
  mathjax = "local"
)

orca(p_IADL,
  file = "../../fig/Mixture/Spring/ExpB_3D_surface_IADL.png",
  width = 800,
  height = 600,
  scale = 2,
  format = "png",
  mathjax = "local"
)
```

## Step 5 - Evaluation of model fit

```{r dfpredobs, message=F, warning=F}
C_mat <- cbind(
  df_expB_repro_Jonker$Dose_EPX,
  df_expB_repro_Jonker$Dose_IMD
)

# Calculation of effects for the design concentrations
res_CA <- CA_complete2(
  C_mat,
  Max, Slopes, Ec50s,
  interact = "none"
)
res_CASA <- CA_complete2(
  C_mat,
  Max, Slopes, Ec50s,
  interact = "SA",
  a = CASA_fit$a
)
res_CADL <- CA_complete2(
  C_mat,
  Max, Slopes, Ec50s,
  interact = "DL",
  a = CADL_fit$a,
  b = CADL_fit$b
)
res_CADR <- CA_complete2(
  C_mat,
  Max, Slopes, Ec50s,
  interact = "DR",
  a = CADR_fit$a,
  b = CADR_fit$b
)

res_IA <- IA_complete2(
  C_mat,
  Max, Slopes, Ec50s,
  interact = "none"
)
res_IASA <- IA_complete2(
  C_mat,
  Max, Slopes, Ec50s,
  interact = "SA",
  a = IASA_fit$a
)
res_IADL <- IA_complete2(
  C_mat,
  Max, Slopes, Ec50s,
  interact = "DL",
  a = IADL_fit$a,
  b = IADL_fit$b
)
res_IADR <- IA_complete2(
  C_mat,
  Max, Slopes, Ec50s,
  interact = "DR",
  a = IADR_fit$a,
  b = IADR_fit$b
)


# We add the corresponding response to our design
df_predobs_CA <- df_expB_repro_Jonker %>%
  mutate(Predicted = res_CA)
df_predobs_CASA <- df_expB_repro_Jonker %>%
  mutate(Predicted = res_CASA)
df_predobs_CADL <- df_expB_repro_Jonker %>%
  mutate(Predicted = res_CADL)
df_predobs_CADR <- df_expB_repro_Jonker %>%
  mutate(Predicted = res_CADR)

df_predobs_IA <- df_expB_repro_Jonker %>%
  mutate(Predicted = res_IA)
df_predobs_IASA <- df_expB_repro_Jonker %>%
  mutate(Predicted = res_IASA)
df_predobs_IADL <- df_expB_repro_Jonker %>%
  mutate(Predicted = res_IADL)
df_predobs_IADR <- df_expB_repro_Jonker %>%
  mutate(Predicted = res_IADR)
```

#### Predicted vs. observed

::: panel-tabset
## CA model

```{r, warning = F, message = F}
#| fig-cap: Predicted vs observed (CA model).
#| label: fig-CApredobs
#| fig-width: 5
#| fig-height: 4

fact_1 <- 2
fact_2 <- 5

col_line0 <- Nord_polar[1]
col_line1 <- Nord_polar[4]
col_line2 <- Nord_snow[1]
xmin <- 0.1
xmax <- 15
step <- 0.5
seq_line <- seq(xmin, xmax, step)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line * fact_1,
  x_1 = seq_line,
  y_1 = seq_line / fact_1,
  x2  = seq_line,
  y2  = seq_line * fact_2,
  x_2 = seq_line,
  y_2 = seq_line / fact_2
)

p_CA <- ggplot() +
  geom_point(
    data = df_predobs_CA,
    mapping = aes(
      x = Response,
      y = Predicted,
      color = as.factor(Line),
      shape = as.factor(Ratio)
    ),
    alpha = 0.5,
    size = 1.5
  ) +
  geom_line(
    data = df_line,
    mapping = aes(x = x1, y = y1),
    color = col_line1
  ) +
  geom_line(
    data = df_line,
    mapping = aes(x = x_1, y = y_1),
    color = col_line1
  ) +
  geom_line(
    data = df_line,
    mapping = aes(x = x2, y = y2),
    color = col_line2
  ) +
  geom_line(
    data = df_line,
    mapping = aes(x = x_2, y = y_2),
    color = col_line2
  ) +
  geom_abline(
    slope = 1,
    intercept = 0,
    color = col_line0,
    linewidth = 1
  ) +
  scale_color_manual(
    name = "Isobole",
    values = c(Nord_aurora, Nord_frost)
  ) +
  scale_x_log10(
    limits = c(0.001, 100)
  ) +
  scale_y_log10(
    limits = c(0.001, 100)
  ) +
  # ylim(NA,1.5)+
  labs(
    x = "Observed response",
    y = "Predicted response"
  ) +
  theme_minimal()
p_CA
```

## SA model (CA ref.)

```{r, warning = F, message = F}
#| fig-cap: Predicted vs observed (SA model with CA as reference).
#| label: fig-CASApredobs
#| fig-width: 5
#| fig-height: 4

fact_1 <- 2
fact_2 <- 5

col_line0 <- Nord_polar[1]
col_line1 <- Nord_polar[4]
col_line2 <- Nord_snow[1]
seq_line <- seq(xmin, xmax, step)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line * fact_1,
  x_1 = seq_line,
  y_1 = seq_line / fact_1,
  x2  = seq_line,
  y2  = seq_line * fact_2,
  x_2 = seq_line,
  y_2 = seq_line / fact_2
)

p_CASA <- ggplot() +
  geom_point(
    data = df_predobs_CASA,
    mapping = aes(
      x = Response,
      y = Predicted,
      color = as.factor(Line),
      shape = as.factor(Ratio)
    ),
    alpha = 0.5,
    size = 1.5
  ) +
  geom_line(
    data = df_line,
    mapping = aes(x = x1, y = y1),
    color = col_line1
  ) +
  geom_line(
    data = df_line,
    mapping = aes(x = x_1, y = y_1),
    color = col_line1
  ) +
  geom_line(
    data = df_line,
    mapping = aes(x = x2, y = y2),
    color = col_line2
  ) +
  geom_line(
    data = df_line,
    mapping = aes(x = x_2, y = y_2),
    color = col_line2
  ) +
  geom_abline(
    slope = 1,
    intercept = 0,
    color = col_line0,
    linewidth = 1
  ) +
  scale_color_manual(
    name = "Isobole",
    values = c(Nord_aurora, Nord_frost)
  ) +
  scale_x_log10(
    # limits = c(0.15, 1.5)
  ) +
  scale_y_log10(
    # limits = c(0.15, 1.5)
  ) +
  # ylim(NA,1.5)+
  labs(
    x = "Observed response",
    y = "Predicted response"
  ) +
  theme_minimal()
p_CASA
```

## DL model (CA ref.)

```{r, warning = F, message = F}
#| fig-cap: Predicted vs observed (DL model with CA as reference).
#| label: fig-CADLpredobs
#| fig-width: 5
#| fig-height: 4

fact_1 <- 2
fact_2 <- 5

col_line0 <- Nord_polar[1]
col_line1 <- Nord_polar[4]
col_line2 <- Nord_snow[1]
seq_line <- seq(xmin, xmax, step)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line * fact_1,
  x_1 = seq_line,
  y_1 = seq_line / fact_1,
  x2  = seq_line,
  y2  = seq_line * fact_2,
  x_2 = seq_line,
  y_2 = seq_line / fact_2
)

p_CADL <- ggplot() +
  geom_point(
    data = df_predobs_CADL,
    mapping = aes(
      x = Response,
      y = Predicted,
      color = as.factor(Line),
      shape = as.factor(Ratio)
    ),
    alpha = 0.5,
    size = 1.5
  ) +
  geom_line(
    data = df_line,
    mapping = aes(x = x1, y = y1),
    color = col_line1
  ) +
  geom_line(
    data = df_line,
    mapping = aes(x = x_1, y = y_1),
    color = col_line1
  ) +
  geom_line(
    data = df_line,
    mapping = aes(x = x2, y = y2),
    color = col_line2
  ) +
  geom_line(
    data = df_line,
    mapping = aes(x = x_2, y = y_2),
    color = col_line2
  ) +
  geom_abline(
    slope = 1,
    intercept = 0,
    color = col_line0,
    linewidth = 1
  ) +
  scale_color_manual(
    name = "Isobole",
    values = c(Nord_aurora, Nord_frost)
  ) +
  scale_x_log10(
    # limits = c(0.15, 1.5)
  ) +
  scale_y_log10(
    # limits = c(0.15, 1.5)
  ) +
  # ylim(NA,1.5)+
  labs(
    x = "Observed response",
    y = "Predicted response"
  ) +
  theme_minimal()
p_CADL
```

## IA model

```{r, warning = F, message = F}
#| fig-cap: Predicted vs observed (IA model).
#| label: fig-IApredobs
#| fig-width: 5
#| fig-height: 4

fact_1 <- 2
fact_2 <- 5

col_line0 <- Nord_polar[1]
col_line1 <- Nord_polar[4]
col_line2 <- Nord_snow[1]
xmin <- 0.1
xmax <- 15
step <- 0.5
seq_line <- seq(xmin, xmax, step)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line * fact_1,
  x_1 = seq_line,
  y_1 = seq_line / fact_1,
  x2  = seq_line,
  y2  = seq_line * fact_2,
  x_2 = seq_line,
  y_2 = seq_line / fact_2
)

p_IA <- ggplot() +
  geom_point(
    data = df_predobs_IA,
    mapping = aes(
      x = Response,
      y = Predicted,
      color = as.factor(Line),
      shape = as.factor(Ratio)
    ),
    alpha = 0.5,
    size = 1.5
  ) +
  geom_line(
    data = df_line,
    mapping = aes(x = x1, y = y1),
    color = col_line1
  ) +
  geom_line(
    data = df_line,
    mapping = aes(x = x_1, y = y_1),
    color = col_line1
  ) +
  geom_line(
    data = df_line,
    mapping = aes(x = x2, y = y2),
    color = col_line2
  ) +
  geom_line(
    data = df_line,
    mapping = aes(x = x_2, y = y_2),
    color = col_line2
  ) +
  geom_abline(
    slope = 1,
    intercept = 0,
    color = col_line0,
    linewidth = 1
  ) +
  scale_color_manual(
    name = "Isobole",
    values = c(Nord_aurora, Nord_frost)
  ) +
  scale_x_log10(
    # limits = c(0.15, 1.5)
  ) +
  scale_y_log10(
    # limits = c(0.15, 1.5)
  ) +
  # ylim(NA,1.5)+
  labs(
    x = "Observed response",
    y = "Predicted response"
  ) +
  theme_minimal()
p_IA
```

## SA model (IA ref.)

```{r, warning = F, message = F}
#| fig-cap: Predicted vs observed (SA model with IA as reference).
#| label: fig-IASApredobs
#| fig-width: 5
#| fig-height: 4

fact_1 <- 2
fact_2 <- 5

col_line0 <- Nord_polar[1]
col_line1 <- Nord_polar[4]
col_line2 <- Nord_snow[1]
seq_line <- seq(xmin, xmax, step)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line * fact_1,
  x_1 = seq_line,
  y_1 = seq_line / fact_1,
  x2  = seq_line,
  y2  = seq_line * fact_2,
  x_2 = seq_line,
  y_2 = seq_line / fact_2
)

p_IASA <- ggplot() +
  geom_point(
    data = df_predobs_IASA,
    mapping = aes(
      x = Response,
      y = Predicted,
      color = as.factor(Line),
      shape = as.factor(Ratio)
    ),
    alpha = 0.5,
    size = 1.5
  ) +
  geom_line(
    data = df_line,
    mapping = aes(x = x1, y = y1),
    color = col_line1
  ) +
  geom_line(
    data = df_line,
    mapping = aes(x = x_1, y = y_1),
    color = col_line1
  ) +
  geom_line(
    data = df_line,
    mapping = aes(x = x2, y = y2),
    color = col_line2
  ) +
  geom_line(
    data = df_line,
    mapping = aes(x = x_2, y = y_2),
    color = col_line2
  ) +
  geom_abline(
    slope = 1,
    intercept = 0,
    color = col_line0,
    linewidth = 1
  ) +
  scale_color_manual(
    name = "Isobole",
    values = c(Nord_aurora, Nord_frost)
  ) +
  scale_x_log10(
    # limits = c(0.15, 1.5)
  ) +
  scale_y_log10(
    # limits = c(0.15, 1.5)
  ) +
  # ylim(NA,1.5)+
  labs(
    x = "Observed response",
    y = "Predicted response"
  ) +
  theme_minimal()
p_IASA
```

## DL model (IA ref.)

```{r, warning = F, message = F}
#| fig-cap: Predicted vs observed (DL model with IA as reference).
#| label: fig-IADLpredobs
#| fig-width: 5
#| fig-height: 4

fact_1 <- 2
fact_2 <- 5

col_line0 <- Nord_polar[1]
col_line1 <- Nord_polar[4]
col_line2 <- Nord_snow[1]
seq_line <- seq(xmin, xmax, step)

df_line <- data.frame(
  x1  = seq_line,
  y1  = seq_line * fact_1,
  x_1 = seq_line,
  y_1 = seq_line / fact_1,
  x2  = seq_line,
  y2  = seq_line * fact_2,
  x_2 = seq_line,
  y_2 = seq_line / fact_2
)

p_IADL <- ggplot() +
  geom_point(
    data = df_predobs_IADL,
    mapping = aes(
      x = Response,
      y = Predicted,
      color = as.factor(Line),
      shape = as.factor(Ratio)
    ),
    alpha = 0.5,
    size = 1.5
  ) +
  geom_line(
    data = df_line,
    mapping = aes(x = x1, y = y1),
    color = col_line1
  ) +
  geom_line(
    data = df_line,
    mapping = aes(x = x_1, y = y_1),
    color = col_line1
  ) +
  geom_line(
    data = df_line,
    mapping = aes(x = x2, y = y2),
    color = col_line2
  ) +
  geom_line(
    data = df_line,
    mapping = aes(x = x_2, y = y_2),
    color = col_line2
  ) +
  geom_abline(
    slope = 1,
    intercept = 0,
    color = col_line0,
    linewidth = 1
  ) +
  scale_color_manual(
    name = "Isobole",
    values = c(Nord_aurora, Nord_frost)
  ) +
  scale_x_log10(
    # limits = c(0.15, 1.5)
  ) +
  scale_y_log10(
    # limits = c(0.15, 1.5)
  ) +
  # ylim(NA,1.5)+
  labs(
    x = "Observed response",
    y = "Predicted response"
  ) +
  theme_minimal()
p_IADL
```
:::

```{r savepredobs, include=F}
ggsave(
  filename = "ExpB_Jonker_predobs_CA.png",
  plot = p_CA,
  width = 5, height = 4,
  path = path_fig
)
ggsave(
  filename = "ExpB_Jonker_predobs_CA.svg",
  plot = p_CA,
  width = 5, height = 4,
  path = path_fig
)

ggsave(
  filename = "ExpB_Jonker_predobs_CASA.png",
  plot = p_CASA,
  width = 5, height = 4,
  path = path_fig
)
ggsave(
  filename = "ExpB_Jonker_predobs_CASA.svg",
  plot = p_CASA,
  width = 5, height = 4,
  path = path_fig
)

ggsave(
  filename = "ExpB_Jonker_predobs_CADL.png",
  plot = p_CADL,
  width = 5, height = 4,
  path = path_fig
)
ggsave(
  filename = "ExpB_Jonker_predobs_CADL.svg",
  plot = p_CADL,
  width = 5, height = 4,
  path = path_fig
)

ggsave(
  filename = "ExpB_Jonker_predobs_IA.png",
  plot = p_IA,
  width = 5, height = 4,
  path = path_fig
)
ggsave(
  filename = "ExpB_Jonker_predobs_IA.svg",
  plot = p_IA,
  width = 5, height = 4,
  path = path_fig
)

ggsave(
  filename = "ExpB_Jonker_predobs_IASA.png",
  plot = p_IASA,
  width = 5, height = 4,
  path = path_fig
)
ggsave(
  filename = "ExpB_Jonker_predobs_IASA.svg",
  plot = p_IASA,
  width = 5, height = 4,
  path = path_fig
)

ggsave(
  filename = "ExpB_Jonker_predobs_IADL.png",
  plot = p_IADL,
  width = 5, height = 4,
  path = path_fig
)
ggsave(
  filename = "ExpB_Jonker_predobs_IADL.svg",
  plot = p_IADL,
  width = 5, height = 4,
  path = path_fig
)
```

```{r, warning = F, message = F}
#| tbl-cap: Percentage of predictions falling inside fold 2 and fold 5 for each model.
#| label: tbl-MIXpredobsfold

calculate_predobs_stats <- function(df) {
  df <- df |>
    mutate(
      Ratio_predobs = Predicted / Response,
      Residuals = Predicted - Response
    )

  per_fold2 <- round(mean(df$Ratio_predobs >= 0.5 & df$Ratio_predobs <= 2) * 100, 1)
  per_fold5 <- round(mean(df$Ratio_predobs >= 0.2 & df$Ratio_predobs <= 5) * 100, 1)

  list(df = df, per_fold2 = per_fold2, per_fold5 = per_fold5)
}

f_calc_residuals <- function(df) {
  df <- df |>
    mutate(
      Ratio_predobs = Predicted / Response,
      Residuals = Predicted - Response
    )
}

dfs <- list(
  CA = f_calc_residuals(df_predobs_CA), "CA-SA" = f_calc_residuals(df_predobs_CASA), "CA-DL" = f_calc_residuals(df_predobs_CADL), "CA-DR" = f_calc_residuals(df_predobs_CADR),
  IA = f_calc_residuals(df_predobs_IA), "IA-SA" = f_calc_residuals(df_predobs_IASA), "IA-DL" = f_calc_residuals(df_predobs_IADL), "IA-DR" = f_calc_residuals(df_predobs_IADR)
)

results <- lapply(dfs, calculate_predobs_stats)

df_predobs_summary <- data.frame(
  Reference_model = c(rep("CA", 4), rep("IA", 4)),
  Model = names(dfs),
  Per_fold2 = sapply(results, `[[`, "per_fold2"),
  Per_fold5 = sapply(results, `[[`, "per_fold5")
)
df_predobs_summary |> datatable(options = list(dom = "t"), class = "hover")
```

#### Residuals

::: panel-tabset
## CA model

```{r, warning = F, message = F}
#| fig-cap: Residuals (CA model).
#| label: fig-CAresiduals
#| fig-width: 10
#| fig-height: 4

p_CA <- ggplot() +
  geom_dotplot(
    data = dfs$CA,
    aes(
      x = paste0(Line, Ratio),
      y = Residuals,
      color = as.factor(Line),
      fill = as.factor(Line)
    ),
    binaxis = "y",
    stackdir = "center",
    alpha = 0.5,
    dotsize = 0.8
  ) +
  geom_abline(
    slope = 0,
    intercept = 0
  ) +
  scale_color_manual(name = "Line", values = c(Nord_aurora, rev(Nord_frost))) +
  scale_fill_manual(name = "Line", values = c(Nord_aurora, rev(Nord_frost))) +
  theme_minimal()

p_CA
```

## SA model (CA ref.)

```{r, warning = F, message = F}
#| fig-cap: Residuals (SA model with CA as reference).
#| label: fig-CASAresiduals
#| fig-width: 10
#| fig-height: 4

p_CASA <- ggplot() +
  geom_dotplot(
    data = dfs$`CA-SA`,
    aes(
      x = paste0(Line, Ratio),
      y = Residuals,
      color = as.factor(Line),
      fill = as.factor(Line)
    ),
    binaxis = "y",
    stackdir = "center",
    alpha = 0.5,
    dotsize = 0.8
  ) +
  geom_abline(
    slope = 0,
    intercept = 0
  ) +
  scale_color_manual(name = "Line", values = c(Nord_aurora, rev(Nord_frost))) +
  scale_fill_manual(name = "Line", values = c(Nord_aurora, rev(Nord_frost))) +
  # scale_x_log10()+
  theme_minimal()
p_CASA
```

## DL model (CA ref.)

```{r, warning = F, message = F}
#| fig-cap: Residuals (DL model with CA as reference).
#| label: fig-CADLresiduals
#| fig-width: 10
#| fig-height: 4

p_CADL <- ggplot() +
  geom_dotplot(
    data = dfs$`CA-DL`,
    aes(
      x = paste0(Line, Ratio),
      y = Residuals,
      color = as.factor(Line),
      fill = as.factor(Line)
    ),
    binaxis = "y",
    stackdir = "center",
    alpha = 0.5,
    dotsize = 0.8
  ) +
  geom_abline(
    slope = 0,
    intercept = 0
  ) +
  scale_color_manual(name = "Line", values = c(Nord_aurora, rev(Nord_frost))) +
  scale_fill_manual(name = "Line", values = c(Nord_aurora, rev(Nord_frost))) +
  # scale_x_log10()+
  theme_minimal()
p_CADL
```

## IA model

```{r, warning = F, message = F}
#| fig-cap: Residuals (IA model).
#| label: fig-IAresiduals
#| fig-width: 10
#| fig-height: 4

p_IA <- ggplot() +
  geom_dotplot(
    data = dfs$IA,
    aes(
      x = paste0(Line, Ratio),
      y = Residuals,
      color = as.factor(Line),
      fill = as.factor(Line)
    ),
    binaxis = "y",
    stackdir = "center",
    alpha = 0.5,
    dotsize = 0.8
  ) +
  geom_abline(
    slope = 0,
    intercept = 0
  ) +
  scale_color_manual(name = "Line", values = c(Nord_aurora, rev(Nord_frost))) +
  scale_fill_manual(name = "Line", values = c(Nord_aurora, rev(Nord_frost))) +
  # scale_x_log10()+
  theme_minimal()
p_IA
```

## SA model (IA ref.)

```{r, warning = F, message = F}
#| fig-cap: Residuals (SA model with IA as reference).
#| label: fig-IASAresiduals
#| fig-width: 10
#| fig-height: 4

p_IASA <- ggplot() +
  geom_dotplot(
    data = dfs$`IA-SA`,
    aes(
      x = paste0(Line, Ratio),
      y = Residuals,
      color = as.factor(Line),
      fill = as.factor(Line)
    ),
    binaxis = "y",
    stackdir = "center",
    alpha = 0.5,
    dotsize = 0.8
  ) +
  geom_abline(
    slope = 0,
    intercept = 0
  ) +
  scale_color_manual(name = "Line", values = c(Nord_aurora, rev(Nord_frost))) +
  scale_fill_manual(name = "Line", values = c(Nord_aurora, rev(Nord_frost))) +
  # scale_x_log10()+
  theme_minimal()
p_IASA
```

## DL model (IA ref.)

```{r, warning = F, message = F}
#| fig-cap: Residuals (DL model with IA as reference).
#| label: fig-IADLresiduals
#| fig-width: 10
#| fig-height: 4

p_IADL <- ggplot() +
  geom_dotplot(
    data = dfs$`IA-DL`,
    aes(
      x = paste0(Line, Ratio),
      y = Residuals,
      color = as.factor(Line),
      fill = as.factor(Line)
    ),
    binaxis = "y",
    stackdir = "center",
    alpha = 0.5,
    dotsize = 0.8
  ) +
  geom_abline(
    slope = 0,
    intercept = 0
  ) +
  scale_color_manual(name = "Line", values = c(Nord_aurora, rev(Nord_frost))) +
  scale_fill_manual(name = "Line", values = c(Nord_aurora, rev(Nord_frost))) +
  # scale_x_log10()+
  theme_minimal()
p_IADL
```
:::

```{r, include=F}
ggsave(
  filename = "ExpB_Jonker_residuals_CA.png",
  plot = p_CA,
  width = 10, height = 4,
  path = path_fig
)
ggsave(
  filename = "ExpB_Jonker_residuals_CA.svg",
  plot = p_CA,
  width = 10, height = 5,
  path = path_fig
)

ggsave(
  filename = "ExpB_Jonker_residuals_CASA.png",
  plot = p_CASA,
  width = 10, height = 4,
  path = path_fig
)
ggsave(
  filename = "ExpB_Jonker_residuals_CASA.svg",
  plot = p_CASA,
  width = 10, height = 4,
  path = path_fig
)

ggsave(
  filename = "ExpB_Jonker_residuals_CADL.png",
  plot = p_CADL,
  width = 10, height = 4,
  path = path_fig
)
ggsave(
  filename = "ExpB_Jonker_residuals_CADL.svg",
  plot = p_CADL,
  width = 10, height = 4,
  path = path_fig
)

ggsave(
  filename = "ExpB_Jonker_residuals_IA.png",
  plot = p_IA,
  width = 10, height = 4,
  path = path_fig
)
ggsave(
  filename = "ExpB_Jonker_residuals_IA.svg",
  plot = p_IA,
  width = 10, height = 4,
  path = path_fig
)

ggsave(
  filename = "ExpB_Jonker_residuals_IASA.png",
  plot = p_IASA,
  width = 10, height = 4,
  path = path_fig
)
ggsave(
  filename = "ExpB_Jonker_residuals_IASA.svg",
  plot = p_IASA,
  width = 10, height = 4,
  path = path_fig
)

ggsave(
  filename = "ExpB_Jonker_residuals_IADL.png",
  plot = p_IADL,
  width = 10, height = 4,
  path = path_fig
)
ggsave(
  filename = "ExpB_Jonker_residuals_IADL.svg",
  plot = p_IADL,
  width = 10, height = 4,
  path = path_fig
)
```

## Summary

```{r, message=F, warning=F}
#| fig-cap: Estimated surface (IA-SA model). Small grey dots represents the measurements at the replicate level while the bigger black dots represent the mean per condition.
#| label: fig-SurfCAres
#| fig-width: 6
#| fig-height: 6

df_expB_repro_plot_f <- df_expB_repro %>%
  group_by(Condition) %>%
  summarise(
    mean = mean(Nb_cocoons),
    sd = sd(Nb_cocoons),
    q2.5 = quantile(Nb_cocoons, 0.025),
    q97.5 = quantile(Nb_cocoons, 0.975),
    Dose_IMD = Dose_IMD,
    Dose_EPX = Dose_EPX,
    .groups = "drop"
  ) |>
  mutate(
    zmin = mean - sd,
    zmax = mean + sd
  )

p_IASA <- plot_ly(
  x = grid_C2,
  y = grid_C1,
  z = ~z_IASA,
  colors = Nord_frost
) %>%
  add_surface(showlegend = FALSE, showscale = FALSE, opacity = .7) %>%
  layout(
    scene = list(
      xaxis = list(title = "[IMD] (mg/kg)"),
      yaxis = list(title = "[EPX] (mg/kg)"),
      zaxis = list(title = "Cocoon production"),
      camera = list(eye = list(x = 2.5, y = -1.2, z = 1))
    ),
    paper_bgcolor = "rgba(0, 0, 0, 0)",
    plot_bgcolor = "rgba(0, 0, 0, 0)"
  ) %>%
  colorbar(title = list(text = "Production of cocoons per cosm")) %>%
  add_markers(
    y = df_expB_repro_mean$Dose_EPX,
    x = df_expB_repro_mean$Dose_IMD,
    z = df_expB_repro_mean$Nb_cocoons,
    type = "scatter3d",
    mode = "markers",
    marker = list(size = 7, color = Nord_polar[1], symbol = 104),
    showlegend = FALSE, opacity = 1
  )

# add error bars
for (i in seq_len(nrow(df_expB_repro_plot_f))) {
  p_IASA <- p_IASA %>%
    add_trace(
      x = df_expB_repro_plot_f$Dose_IMD[i],
      y = df_expB_repro_plot_f$Dose_EPX[i],
      z = c(df_expB_repro_plot_f$zmin[i], df_expB_repro_plot_f$zmax[i]),
      type = "scatter3d",
      mode = "lines",
      line = list(color = Nord_polar[1], width = 2),
      showlegend = FALSE
    )
}

p_IASA
```

```{r savesummary, warning=F}
orca(p_IASA,
  file = "../../fig/Mixture/Spring/ExpB_3DsurfaceJonkerIASA_errorbar.png",
  width = 800,
  height = 600,
  scale = 2,
  format = "png",
  mathjax = "local"
)
```

A significant synergistic interaction in the epoxiconazole–imidacloprid mixture was detected relatively to the IA reference model (IA-SA model, $a$ = -1.5), whereas the CA-SA model did not identify a departure from additivity, which is consistent with the more conservative nature of the CA reference. Power analysis confirmed that interactions of this magnitude (-1.5 or lower) were reliably detectable with the IA-SA model. This synergy suggested by the IA-SA model aligns with theoretical expectations based on toxicokinetic mechanisms described in the literature. Importantly, retesting the single substances in the MIX experiment proved essential to avoid bias in the estimation of mixture effects. Although the dose-response curves from the UNI experiment were not statistically different, their estimated EC$_{50}$ values differed substantially. Without retesting, this discrepancy could have generated an artificially strong synergistic signal (false positive), driven solely by the higher sensitivity of earthworms to imidacloprid in the second experiment rather than by a true mixture interaction.

However, a statistical limitation must be acknowledged: all lack-of-fit tests for the CA and IA reference models, as well as for their associated interaction models, showed significant lack-of-fit. Strictly speaking, this indicates that none of the fitted dose–response surfaces fully captured the variability in the data. While part of this lack-of-fit may be influenced by heterogeneous variance in the response, it cannot be fully attributed to the choice of error distribution, as alternative formulations (e.g., negative-binomial or quasi-Poisson) did not resolve the lack-of-fit. Significant deviations may therefore also reflect limitations in the mean structure of the fitted surfaces or biological processes not explicitly represented in the Jonker framework, such as nonlinear or context-dependent interactions. Consequently, interaction estimates derived from these models should be interpreted with caution. Additional replication or refined experimental designs would be required to more robustly characterize the magnitude and consistency of the observed synergistic pattern.

Nevertheless, the observed synergistic interaction is in accordance with the hypothesized toxicokinetic mechanism with distinct modes of action but with a metabolic inhibition of imidacloprid biotransformation by epoxiconazole through cytochrome P450 interference [@bass_2015; @cedergreen_2006; @puinean_2010]. Such metabolic interactions have been demonstrated in aquatic invertebrates such as Daphnia magna, where triazole co-exposure enhanced esfenvalerate toxicity up to fourfold [@cedergreen_2006] and increased α-cypermethrin toxicity threefold [@gottardi_2017]. Similar synergistic interactions between atrazine and chlorpyrifos have also been reported in invertebrates, consistent with metabolic inhibition mechanisms. Additionally, the moderate hydrophilicity of imidacloprid (log K$_{ow}$ ≈ 0.57) suggests that direct excretion pathways may predominate over metabolic transformation in earthworms, reducing the potential for metabolic interference which could explain the absence of strong interaction. Importantly, this metabolic mechanism remains unconfirmed in earthworms. Earthworms possess unique physiological adaptations for soil environments, including specialized detoxification mechanisms that may not rely heavily on cytochrome P450-mediated metabolism of imidacloprid. Earthworms possess detoxification strategies that rely on glutathione-S-transferases, carboxylesterases, antioxidant enzymes, and gut microbiota metabolism [@katagi_2015; @wang_2019]. Evidence for imidacloprid metabolism via cytochrome P450 enzymes comes primarily from insect species [@chen_2018; @chen_2019], where cytochrome P450 overexpression has been linked to imidacloprid resistance [@elzaki_2017; @kaplanoglu_2017; @liang_2015]. However, the extent to which these metabolic pathways operate in earthworms remains largely unexplored, and extrapolation across taxonomically distant invertebrate groups may not be justified. Therefore, while the statistical signal points toward a small synergistic interaction, biological confirmation of the underlying mechanism is currently lacking.

These findings illustrate the difficulty of extrapolating both mechanisms and magnitudes of interaction across taxa, and emphasize the need for species-specific validation. Future work, including toxicokinetic measurements, or the integration of biochemical biomarkers such as catalase and glutathione-S-transferases as phase II detoxification enzymes [@givaudan_2014; @pelosi_2016], would be necessary to confirm whether the interaction detected here reflects a true synergistic process or arises from statistical noise due to overdispersion. Such complementary data would greatly strengthen mechanistic interpretation of mixture effects in earthworms.

Additionaly, our results suggest that the combined effect of the two compounds could exceed what would be expected from the IA model. In this context, concentration addition (CA) remains a useful and precautionary reference, but it may still underestimate mixture toxicity when synergism occurs. The possibility of such synergistic deviation highlights that mixture exposures could pose greater risks than predicted from single-compound assessments alone. Consequently, our findings reinforce the importance of explicitly accounting for mixture effects and potential synergistic interactions in environmental risk assessment frameworks, especially for pesticide combinations that are likely to co-occur in soils.
