```{r, include=F}
library(tidyverse); library(here); library(ggthemes)
library(viridis); library(tidybayes); library(wesanderson)
library(ggdist); library(patchwork); library(extrafont)
library(scales); library(ggdist); library(ggsci)
library(parallel); library(deSolve); library(tmvtnorm)
library(fdrtool); library(readxl); library(here); library(car)
library(RColorBrewer); library(devtools) ; library(drc)
library(knitr); library(Hmisc); library(nlstools); library(lsmeans)
library(ggpubr);library(brglm2);library(marginaleffects)
library(performance);library(rethinking); library(ggiraph)
library(nord); library(plotly); library(DT)

Nord_frost <- nord(palette = "frost")
Nord_aurora <- nord(palette = "aurora")
Nord_polar <- nord(palette = "polarnight")

pal_col <- c(Nord_aurora[1], Nord_frost[4])
col_EPX <- Nord_frost[2]
col_IMD <- Nord_frost[4]
shape_IMD <- 16
shape_EPX <- 15
col_molec <- c(col_EPX, col_IMD)
sizetitle <- 12

shape_molec <- c(shape_EPX, shape_IMD)

set.seed(121212)

```

# Effect of the mixture on cocoons production

## Data importation

```{r}
df_mix <- read_excel(here::here("data/Data_Mix.xlsx"), sheet="Repro") |>                       # <1>
  mutate(Dose_EPX = as.numeric(Dose_EPX)) |>                                             # <1>
  mutate(Dose_EPX_f = as.factor(round(Dose_EPX, 4))) |>                                  # <1>
  mutate(Dose_IMD = as.numeric(Dose_IMD)) |>                                             # <1>
  mutate(Dose_IMD_f = as.factor(round(Dose_IMD, 4))) |>                                  # <1>
  mutate(Condition = paste(Ratio, Line, sep="")) |> # <1>
  mutate(w=w_tot/Nb_ind) |>                                                              # <1>
  mutate(L=w^(1/3))  
```

1.  Raw data importation and calculation of the mean individual weight and the corresponding structural weight.

```{r}

col_box <- Nord_polar[4]
plot_D0 <- ggplot()+
  geom_boxplot(data=subset(df_mix,t==0), aes(x=Condition, y=w), alpha=0.2, color=col_box)+
  geom_dotplot(data=subset(df_mix,t==0), aes(x=Condition, y=w, color = ID_camp, fill=ID_camp), binaxis='y', stackdir='center', dotsize=0.7, 
                alpha=0.7)+
  labs(x="Dose (mg/kg)", y="Weight (mg)")+
  scale_color_manual(values=c(Nord_aurora, Nord_frost))+
  scale_fill_manual(values=c(Nord_aurora, Nord_frost))+
  theme_classic(14)+
  theme(legend.position = "right", 
        legend.title=element_text(size=sizetitle-2,face="bold"),
        legend.text = element_text(size=sizetitle-2,face="plain"),
        title=element_text(size=sizetitle, face="bold"), 
        axis.title.x = element_blank(),
        axis.line.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y = element_text(size=sizetitle,face="plain"))
plot_D0 
```

## Dose response curves of the single exposures

```{r}
df_mix_E <- subset(df_mix, Ratio == "E" | Ratio == "N") |> 
  mutate(Molecule = "EPX") |> 
  mutate(Dose = Dose_EPX)
df_mix_F <- subset(df_mix, Ratio == "F" | Ratio == "N")
df_mix_G <- subset(df_mix, Ratio == "G" | Ratio == "N")
df_mix_H <- subset(df_mix, Ratio == "H" | Ratio == "N")
df_mix_I <- subset(df_mix, Ratio == "I" | Ratio == "N") |> 
  mutate(Molecule = "IMD") |> 
  mutate(Dose = Dose_EPX)

df_mix_single <- rbind(df_mix_E, df_mix_I)

drc.single.1<- drm(
                Nb_cocoons~Dose,
                data = df_mix_single,
                type="Poisson",
                fct=LL.4(
                  names = c("slope", "Ymin", "Ymax", "EC50"), 
                          fixed=c(NA, 0, NA, NA)
                  ),
                pmodels=data.frame(Molecule, Molecule, Molecule)
              )

Dose_x <- expand.grid(exp(seq(log(0.000001),log(5000), by=(log(5000)-log(0.000001))/100)))
CI.1 <- data.frame(Dose=c(Dose_x$Var1, Dose_x$Var1),
                   Molecule = c(rep("EPX", length(Dose_x$Var1)), rep("IMD", length(Dose_x$Var1))))
pm.1 <- predict(drc.single.1, newdata=CI.1, interval="confidence")
CI.1$p <- pm.1[,1]
CI.1$pmin <- pm.1[,2]
CI.1$pmax <- pm.1[,3]

drc.single.2<- drm(
                Nb_cocoons~Dose,
                data = df_mix_single,
                type="Poisson",
                fct=LL.4(
                  names = c("slope", "Ymin", "Ymax", "EC50"), 
                          fixed=c(NA, 0, NA, NA)
                  ),
                pmodels=data.frame(1, 1, Molecule)
              )

CI.2 <- data.frame(Dose=c(Dose_x$Var1, Dose_x$Var1),
                   Molecule = c(rep("EPX", length(Dose_x$Var1)), rep("IMD", length(Dose_x$Var1))))
pm.2 <- predict(drc.single.2, newdata=CI.2, interval="confidence")
CI.2$p <- pm.2[,1]
CI.2$pmin <- pm.2[,2]
CI.2$pmax <- pm.2[,3]

```

```{r}
line_width <- 1.2

x <- seq(0.000001, 5000, 0.01)

Hill.1 <- function(Dose, Molecule){
  
  i <- 0
  if(Molecule == "IMD"){i <- 1}
  
  Y_min <- 0
  slope <- coef(drc.single.1)[1+i]
  Y_max <- coef(drc.single.1)[3+i]
  EC50 <- coef(drc.single.1)[5+i]
  
  return(Y_min+(Y_max-Y_min)/(1+exp(slope*(log(Dose)-log(EC50)))))
}

plot_drc.single.1 <- ggplot()+
  geom_ribbon(data=CI.1, aes(x=Dose, y=p, ymin=pmin, ymax=pmax, group=Molecule, fill=Molecule), alpha=0.2)+
  geom_line(aes(x=x, y=Hill.1(Dose=x, Molecule="EPX")), 
            color=col_EPX, linewidth=line_width)+
  geom_line(aes(x=x, y=Hill.1(Dose=x, Molecule="IMD")), 
            color=col_IMD, linewidth=line_width)+
  geom_point(data=df_mix_single, 
             aes(x=Dose, y=Nb_cocoons, color=Molecule, shape=Molecule), 
             cex=2, alpha=0.4)+
  #geom_ribbon(data=CI.1, aes(x=x, y=p, ymin=pmin, ymax=pmax), alpha=0.2)+
  scale_color_manual(name="Dose (mg/kg)",values=col_molec)+
  scale_shape_manual(values=shape_molec)+
  scale_fill_manual(name="Dose (mg/kg)",values=col_molec)+
  theme_minimal()+
  scale_x_log10()+
  labs(x="Dose (mg/kg)", 
       y=expression(paste("Number of cocoons produced per cosm")), 
       title = "No common parameter")+
  theme(legend.position = "right", 
        legend.title=element_text(size=sizetitle-2,face="bold"), 
        title=element_text(size=sizetitle, face="bold"), 
        axis.title.x = element_text(size=sizetitle,face="plain"), 
        axis.title.y = element_text(size=sizetitle,face="plain"))

Hill.2 <- function(Dose, Molecule){
  
  i <- 0
  if(Molecule == "IMD"){i <- 1}
  
  Y_min <- 0
  slope <- coef(drc.single.2)[1]
  Y_max <- coef(drc.single.2)[2]
  EC50 <- coef(drc.single.2)[3+i]
  
  return(Y_min+(Y_max-Y_min)/(1+exp(slope*(log(Dose)-log(EC50)))))
}

plot_drc.single.2 <- ggplot()+
  geom_ribbon(data=CI.2, aes(x=Dose, y=p, ymin=pmin, ymax=pmax, group=Molecule, fill=Molecule), alpha=0.2)+
  geom_line(aes(x=x, y=Hill.2(Dose=x, Molecule="EPX")), 
            color=col_EPX, linewidth=line_width)+
  geom_line(aes(x=x, y=Hill.2(Dose=x, Molecule="IMD")), 
            color=col_IMD, linewidth=line_width)+
  geom_point(data=df_mix_single, 
             aes(x=Dose, y=Nb_cocoons, color=Molecule, shape=Molecule), 
             cex=2, alpha=0.4)+
  scale_color_manual(name="Dose (mg/kg)",values=col_molec)+
  scale_shape_manual(values=shape_molec)+
  scale_fill_manual(name="Dose (mg/kg)",values=col_molec)+
  theme_minimal()+
  scale_x_log10()+
  labs(x="Dose (mg/kg)", 
       y=expression(paste("Number of cocoons produced per cosm")), 
       title = "Common Ymax and Slope")+
  theme(legend.position = "right", 
        legend.title=element_text(size=sizetitle-2,face="bold"), 
        title=element_text(size=sizetitle, face="bold"), 
        axis.title.x = element_text(size=sizetitle,face="plain"), 
        axis.title.y = element_text(size=sizetitle,face="plain"))
```

```{r}
df_design <- read.csv(here::here("data/Design_mixture.csv"))[,c(2,3,4)]
C_mat=cbind(df_design$EPX,df_design$IMD)
Max=coef(drc.single.2)[2]
Slopes=c(coef(drc.single.2)[1], coef(drc.single.2)[1])
Ec50s=c(coef(drc.single.1)[5], coef(drc.single.1)[6])
```

## Surface dose-response curve

Step 1 - Function allowing to fit the different Jonker models to our simulated data

```{r, message=F, warning=F}
CA_complete2_fit_speed<-function(C_mat, Response, param=NULL, upper=NULL, lower=NULL, start=NULL, interact="none", identical_slopes=FALSE, iter=500, multicore=FALSE, mc.cores=4){
  
  if (!is.null(param)){
    
    if ((is.null(param$Max))|(is.null(param$Slopes))|(is.null(param$Ec50s)))
      stop("param misspecification")
    
    if (interact=="none")
      stop("please specify interaction")
    
    if (interact=="SA"){ 
      if (missing(upper))
        upper=20 # the intervals for a and b must be larger because they can compensate each other
      if (missing(lower))
        lower=-20
      
      # fit 
      res_CA_optim<-optimize(f=function(x){ 
        CA_complete2_RSS(C_mat=C_mat, 
                        Response=Response, 
                        Max=param$Max, 
                        Slopes=param$Slopes, 
                        Ec50s=param$Ec50s, 
                        a=x, 
                        interact=interact, 
                        multicore=multicore, 
                        mc.cores=mc.cores)}, 
                             upper=upper, 
                             lower=lower)
      
      return(list(a=res_CA_optim$minimum, 
                  RSS=res_CA_optim$objective))
    }
  }
  if (is.null(param)){
    
    require(dfoptim)
    
    if (any(C_mat==0))
      mean_C_mat<-exp(apply(log(C_mat[-which(C_mat==0, arr.ind=TRUE)[,1],]),2,mean))
    
    else
      mean_C_mat<-exp(apply(log(C_mat),2,mean))
    
    if (!identical_slopes){
      
      if (interact=="none"){
        
        if (missing(upper))
          upper=c(max(Response)*5, 0,0, mean_C_mat*10)
        
        if (missing(lower))
          lower=c(0,-100,-100,0,0)
        
        if (missing(start))
          start=c(max(Response),-1,-1,mean_C_mat)
        
        res_CA_nmk<-nmkb(par=start, 
                         fn=function(x){CA_complete2_RSS(C_mat=C_mat, 
                                                         Response=Response, 
                                                         Max=x[1], 
                                                         Slopes=c(x[2], x[3]), 
                                                         Ec50s=c(x[4], x[5]), 
                                                         interact=interact, 
                                                         multicore=multicore, 
                                                         mc.cores=mc.cores)}, 
                         upper=upper, 
                         lower=lower, 
                         control=list(tol=10^-6))
        
        return(list(Max=res_CA_nmk$par[1],
                    Slopes=c(res_CA_nmk$par[2:3]), 
                    Ec50s=c(res_CA_nmk$par[4:5]), 
                    RSS=res_CA_nmk$value))
      }
      
      if (interact=="SA"){
        
        if (missing(upper))
          upper=c(max(Response)*5, 0,0, mean_C_mat*10, 20)  # the intervals for a and b must be larger beacuse they can compensate each other
        
        if (missing(lower))
          lower=c(0,-100,-100,0,0, -20)
        
        if (missing(start))
          start=c(max(Response),-1,-1,mean_C_mat,0)
        
        res_CA_nmk<-nmkb(par=start, 
                         fn=function(x){CA_complete2_RSS(C_mat=C_mat, 
                                                         Response=Response, 
                                                         Max=x[1], 
                                                         Slopes=c(x[2], x[3]), 
                                                         Ec50s=c(x[4], x[5]), 
                                                         a=x[6], 
                                                         interact=interact, 
                                                         multicore=multicore, 
                                                         mc.cores=mc.cores)}, 
                         upper=upper, 
                         lower=lower, 
                         control=list(tol=10^-6))
        
        return(list(Max=res_CA_nmk$par[1], 
                    Slopes=c(res_CA_nmk$par[2:3]), 
                    Ec50s=c(res_CA_nmk$par[4:5]), 
                    a=res_CA_nmk$par[6], 
                    RSS=res_CA_nmk$value))
      }
    }
    
    else {
      
      if (interact=="none"){
        
        if (missing(upper))
          upper=c(max(Response)*5, 0, mean_C_mat*10)
        
        if (missing(lower))
          lower=c(0,-100,0,0)
        
        if (missing(start))
          start=c(max(Response),-1,mean_C_mat)
        
        res_CA_nmk<-nmkb(par=start, 
                         fn=function(x){CA_complete2_RSS(C_mat=C_mat, 
                                                         Response=Response, 
                                                         Max=x[1], 
                                                         Slopes=c(x[2], x[2]), 
                                                         Ec50s=c(x[3], x[4]), 
                                                         interact=interact, 
                                                         multicore=multicore, 
                                                         mc.cores=mc.cores)}, 
                         upper=upper, 
                         lower=lower, 
                         control=list(tol=10^-6))
        
        return(list(Max=res_CA_nmk$par[1], 
                    Slopes=c(res_CA_nmk$par[2], res_CA_nmk$par[2]), 
                    Ec50s=c(res_CA_nmk$par[3:4]), 
                    RSS=res_CA_nmk$value))
      }
      
      if (interact=="SA"){
        
        if (missing(upper))
          upper=c(max(Response)*5, 0, mean_C_mat*10, 20)  # the intervals for a and b must be larger beacuse they can compensate each other
        
        if (missing(lower))
          lower=c(0,-100,0,0, -20)
        
        if (missing(start))
          start=c(max(Response),-1,mean_C_mat,0)
        
        # fit
        res_CA_nmk<-nmkb(par=start, 
                         fn=function(x){CA_complete2_RSS(C_mat=C_mat, 
                                                         Response=Response, 
                                                         Max=x[1], 
                                                         Slopes=c(x[2], x[2]), 
                                                         Ec50s=c(x[3], x[4]), 
                                                         a=x[5], 
                                                         interact=interact, 
                                                         multicore=multicore, 
                                                         mc.cores=mc.cores)}, 
                         upper=upper, 
                         lower=lower, 
                         control=list(tol=10^-6))
        
        return(list(Max=res_CA_nmk$par[1], 
                    Slopes=c(res_CA_nmk$par[2], res_CA_nmk$par[2]), 
                    Ec50s=c(res_CA_nmk$par[3:4]), 
                    a=res_CA_nmk$par[5], 
                    RSS=res_CA_nmk$value))
      }
    }
  }
}


CA_complete2_RSS<-function(C_mat, Response, Max, Slopes, Ec50s, a=0, b=0, interact="none", multicore=FALSE, mc.cores=4){
  
  if (length(Response)!=(dim(C_mat)[1]))
    stop("Should be as many responses as there are conditions")
  
  res_CA<-CA_complete2(C_mat=C_mat, Max=Max, Slopes=Slopes, Ec50s=Ec50s, a=a, b=b, interact=interact, multicore=multicore,
                       mc.cores=mc.cores)
  res_CA_RSS<-sum((res_CA-Response)^2)
  
  return(res_CA_RSS)
}
```

Step 2 : Fit on our data.

```{r, message=F, warning=F}
param <- data.frame(Slopes=Slopes, Max=Max, Ec50s=Ec50s)

res_CA_SA_fit<-CA_complete2_fit_speed(C_mat=cbind(df_mix$Dose_EPX, # <1>
                                                  df_mix$Dose_IMD),# <1>
                                      Response=df_mix$Nb_cocoons,  # <1>
                                      interact="SA",               # <1>
                                      param=param)                 # <1>

res_CA_RSS <- CA_complete2_RSS(C_mat=cbind(df_mix$Dose_EPX,df_mix$Dose_IMD),   # <2>
                               Response=df_mix$Nb_cocoons, Max, Slopes, Ec50s, # <2>
                               interact="SA", a=res_CA_SA_fit$a, b=0)# <2>
```

1.  Fit of the SA model to the simulated value and estimation of the interaction parameter $a$
2.  Calculation of the RSS of the model fit

```{r, message=F, warning=F}
res_a <- round(res_CA_SA_fit$a, 3)                          # <1>
ratio_interaction_a=round(res_CA_SA_fit$a/interaction_a, 3) # <2>
```

1.  Estimated value of $a$
2.  Ratio between the estimated and simulated value of $a$

The estimated interaction parameter $a$ is `r res_a`.

Step 3 - Graphical representation

```{r, message=F, warning=F}
# Graphic preparation

# Construction of the surface mesh

min_dose_EPX <- min(subset(df_design, !EPX==0)$EPX)
max_dose_EPX <- max(subset(df_design, !EPX==0)$EPX)

min_dose_IMD <- min(subset(df_design, !IMD==0)$IMD)
max_dose_IMD <- max(subset(df_design, !IMD==0)$IMD)

by_EPX <- (log(max_dose_EPX)-log(min_dose_EPX))/100
by_IMD <- (log(max_dose_IMD)-log(min_dose_IMD))/100

grid_C1_not_log<-c(0,exp(seq(log(min_dose_EPX),log(max_dose_EPX), by=by_EPX)))
grid_C2_not_log<-c(0,exp(seq(log(min_dose_IMD),log(max_dose_IMD), by=by_IMD)))

grid_C_not_log<-expand.grid(grid_C1_not_log, grid_C2_not_log)

df_mix_data_solved_surf <- CA_complete2(C_mat=grid_C_not_log,            # <1> 
                                        Max=Max,                         # <1> 
                                        Slopes=Slopes,                   # <1> 
                                        Ec50s=Ec50s,                     # <1> 
                                        a=res_CA_SA_fit$a, interact="SA")# <1> 

df_mix_data_solved_surf_ordered <- df_mix_data_solved_surf[order(grid_C_not_log[,2])]

z <- matrix(df_mix_data_solved_surf_ordered,
                    nrow=length(grid_C1_not_log),
                    ncol=length(grid_C2_not_log),
                    byrow=FALSE)
```

1.  Modeling of the dose-response surface with the estimated value of $a$

```{r, message=F, warning=F}
#| fig-cap: Estimated surface isobols (SA model). 
#| label: fig-SurfSAiso
#| fig-width: 5
#| fig-height: 4

contour(x=grid_C1_not_log, y=grid_C2_not_log, 
        z=z, col=Nord_polar[1], xlab="[EPX] (mg/kg)", ylab="[IMD] (mg/kg)")
```

```{r, message=F, warning=F}
#| fig-cap: Estimated surface (SA model). 
#| label: fig-SurfSAdyn
#| fig-width: 5
#| fig-height: 4

figSA <- plotly::plot_ly(x=grid_C2_not_log, y=grid_C1_not_log, z=~z, colors=Nord_frost)%>%
  add_surface()%>%
  layout(scene = list(xaxis = list(title = '[IMD] (mg/kg)'),
                      yaxis = list(title = '[EPX] (mg/kg)'),
                      zaxis = list(title = 'Cocoon production'),
                      camera = list(eye = list(x = -1.8, y = 1.8, z = 1))))%>%
  colorbar(title=list(text="Production of cocoons"))%>%
  add_markers(y=df_sim_data$EPX,
            x=df_sim_data$IMD,
            z=df_sim_data$Y_sim,
            type = "scatter3d",
            mode="markers",
            marker = list(size = 5, color = "black", symbol = 104))


figSA
```

## Dose-response curves per ratio
