# Information about this project

## How to use this repository ?

### Repository organisation

The git repository linked to this website is available [here](https://github.com/LisaGllt/Ew-Mix-TD) and is saved via [SoftwareHeritage](https://archive.softwareheritage.org) on this [page](https://archive.softwareheritage.org/browse/origin/https://github.com/LisaGllt/Ew-Mix-TD).

Folders containing files concerning directly the study :

-   `data` folder : Contains the raw data files with direct notations from the experiments
-   `functions` folder : Contains R scripts with general functions used throughout different scripts
-   `quarto` folder : Contains all the `.qmd` files that generate the html pages, and their associated cache and files which cannot be moved to another folder.
-   `mod` folder : Contain all the models generated in `.rds` files
-   `bootstrap` folder : Contain the R script and its results concerning the bootstrap.
-   `photos` folder : Contains all photos used in html pages
-   `fig` folder : Contains all figure generated by quarto documents
-   `references` folder
    -   `apa.csl` : File of the reference style used for the website
    -   `reference.bib` : File containing all references from a zotero library

Folders concerning the setup of the git repository and the web pages :

-   `_book` : Where the final html pages are created
-   `index.qmd` : Home page of the web site (cannot be put in the `quarto` folder)
-   `_quarto.yaml` : YAML file that setup the structure of the website from the quarto (`.qmd`) documents
-   `_freeze` folder : Cache the results of code blocks (code cells) to avoid recalculating them on each execution
-   `.git`, `.gitignore` & `.github` : Git related folders
-   `.quarto` : Store configuration files, metadata, and intermediate files related to a Quarto project
-   `.Rproj.user` & `Ew-Mix-TD.Rproj` : R project related files
-   `appearance` folder :
    -   `html_css.scss` : CSS file to modify the look of the html pages
    -   `lightnord.theme` : Theme to use for code blocks displayed in the html pages

### How to reproduce everything

If you wish to reproduce the results of this study, all you need are available in the `quarto` folder and the `mod` folder.

Instructions :

-   Whether or not you want to run the models again, please delete the folders from the `quarto` folder that end by `_cache` or `_files` and delete all the figures present in the `fig` folder.
    -   If you do not want to run the models again, move on to the next step
    -   If you wish to run the models again, please delete the files in `mod` but the `.model` files and keep the arborescence)
-   Then, you can render again all .qmd files from the `quarto` folder in the alphabetical order of their name. Some code line will have to be de-commented for some figures to be rendered again.

## Preliminary information about this study

People that have contributed to this study :

-   Laura Frattaroli (research technician) : Earthworms breeding & Mixture tests (October 2024 - August 2025)
-   Julien Rouyer (Gap year intership of engineering school) : Earthworms breeding & Mixture tests (October - December 2024)
-   Cheikh Ahmed Tidane Sarr (M2 intership) : Mixture tests (March - August 2025)

### Abstract

### GANTT {#sec-GANTT}

```{r,, include=F}
# Load necessary libraries
library(ggplot2)
library(dplyr)
library(lubridate)
library(forcats)
library(nord)

Nord_frost <- nord(palette = "frost")
Nord_aurora <- nord(palette = "aurora")
Nord_polar <- nord(palette = "polarnight")
```

```{r, echo=F, warning=F}
#| fig-cap: GANTT
#| label: fig-GANTT
#| fig-width: 10
#| fig-height: 4

# Sample data
data_gantt <- data.frame(
  task = c(
    "1. Preliminary tests",                      # 1
    "2.1. EC50 tests for IMD",                   # 2
    "2.2. EC50 tests for EPX",                   # 3
    "3.1. Mixture tests - Autumn 2024",          # 4
    "3.2. Mixture tests - Small test with IMD",  # 5
    "3.3. Mixture tests - Spring 2025",          # 6
    "3.3. Mixture tests - Hatchling monitoring"  # 7
  ),
  start_date = as.Date(
    c(
      "2024-03-05",                              # 1
      "2024-04-01",                              # 2
      "2024-05-03",                              # 3
      "2024-10-14",                              # 4
      "2025-01-07",                              # 5
      "2025-03-25",                              # 6
      "2025-04-30"                               # 7
    )
  ),
  end_date = as.Date(
    c
    ("2024-04-19",                               # 1
      "2024-07-08",                              # 2
      "2024-07-08",                              # 3
      "2024-12-18",                              # 4
      "2025-02-05",                              # 5
      "2025-04-30",                              # 6
      "2025-06-10"                               # 7
    )
  ),
  status = c(
    "Completed",                                 # 1
    "Completed",                                 # 2
    "Completed",                                 # 3
    "Completed",                                 # 4
    "Completed",                                 # 5
    "Completed",                                 # 6
    "Completed"                                  # 7
  )
)

# Custom color palette for the statuses

status_colors <- c("In Progress" = Nord_frost[1], "Completed" = Nord_frost[4])

# Creating the Gantt chart
ggplot(
  data_gantt, 
  aes(
    x = start_date, 
    # y = reorder(task, -as.numeric(start_date))
    y = fct_rev(task)
  )
) +  # Reorder tasks
  
  geom_segment(
    aes(
      xend = end_date, 
      yend = task, 
      color = status
    ), 
    size = 6, 
    lineend = "round",
    alpha = 0.7
  ) +  # Rounded bars
  
  geom_text(
    aes(
      x = ymd(start_date) + (ymd(end_date)-ymd(start_date))/2, 
      label = task,
    ),
    hjust = 0.5,
    vjust = -1.2,
    size = 4, 
    color = "black",
    fontface = "bold"
  )+
  
  scale_color_manual(values = status_colors) +  # Apply custom colors
  
  labs(
    title = "Project Timeline",
    x = NULL,  # Remove axis title for x
    y = NULL,  # Remove axis title for y
    color = "Status"
  ) +
  
  theme_minimal(base_family = "Arial") +                                          # Use a clean, sans-serif font
  theme(
    plot.title = element_text(size = 18, face = "bold", hjust = 0.5),             # Title style
    legend.position = "right",
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10),
    # axis.text.y = element_text(size = 12, hjust = 0, face = "bold"),                                        # Make task labels bold
    axis.text.y = element_blank(),
    axis.text.x = element_text(size = 10, color = "grey40"),                      # Date labels in grey
    panel.grid.minor = element_blank(),                                           # Remove minor grid lines
    panel.grid.major.y = element_blank(),                                         # Remove horizontal grid lines
    panel.grid.major.x = element_line(color = "grey85", linetype = "dashed")      # Subtle dashed vertical grid
  ) +
  scale_x_date(
    date_labels = "%b %Y", 
    date_breaks = "2 month", 
    expand = c(0, 0),
    limits = c(ymd("2024-02-01"), ymd("2025-10-31"))
    )  # Custom date formatting


```
