```{r, include=F}
library(here)
source(file = here::here("functions/fun.R"))
f_load_libraries_colors()
```

# Preliminary tests {#sec-CAPrelim}

Preliminary tests were performed to identify the concentration range capturing the whole range of effect of each substance. This would allow us to choose more carrefully the tested concentrations for each substance.

### Method

At the time of these preliminary tests, our new lab culture had just started and thus we could not use *A. caliginosa* from our lab. In the Closeaux meadow, *A. icterica* were easy to find so we chose to performed the test with these collected individuals.

These tests were performed as described by @sec-methodtests with the difference being that juveniles were put by 2 instead of 1 in cosms. Growth tests were performed in 1 replicate and reproduction tests were performed in 2 replicates.

The tested concentrations are the following :

-   IMD : 0.001, 0.01, 0.1, 1, 10 mg/kg
-   EPX : 0.01, 0.1, 1, 10, 100 mg/kg

### Results

#### Variables names

-   `Date` : Date of the measurement
-   `ID` : Identification number of the earthworm
-   `ID_cosm` : Identification number of the cosm
-   `t` : Number of days since the start of the exposition
-   `w` : Fresh weight of the earthworm (mg)
-   `w_tot` : Fresh weight of the earthworms in one cosm (mg)
-   `nb_ind` : Number of individuals in one cosm (#)
-   `Dose` : concentration in the soil (mg/kg)
-   `Status` :
    -   "J" : Juvenile
    -   "A" : Adulte
    -   "D" : Dead

#### Effects on juveniles growth

```{r datagrowth, include=F, message=F}
df_growth_full <- read_excel(here::here("data/Data_preliminary_tests.xlsx"), sheet="Growth") |> 
  mutate(L=w^(1/3))

df_growth_EPX <- subset(df_growth_full, Molecule %in% c("Ctrl", "EPX")) |> 
  mutate(Molecule = "EPX")
df_growth_IMD <- subset(df_growth_full, Molecule %in% c("Ctrl", "IMD")) |> 
  mutate(Molecule = "IMD")

df_growth <- rbind(df_growth_EPX, df_growth_IMD)

```

```{r, messsage=F, warning=F}
#| fig-cap: Juvenile earthworms growth. 
#| label: fig-growthJ
#| fig-width: 8
#| fig-height: 4


p <- ggplot(
  data = df_growth,
  aes(
    x = t,
    y = w,
    group = ID,
    color = Molecule
    )
  )+
  geom_point(
    alpha = 0.5
  )+
  geom_line()+
  facet_wrap(
    ~Molecule+Dose,
    ncol = 6
    )+
  
  scale_color_manual(values=col_molec)+
  scale_fill_manual(values=col_molec)+
  
  labs(
    y = "Fresh body weight (mg)",
    x = "Time (days)"
  )+
  
  theme_minimal()

p

```

Earthworms growth can be modeled thanks to @eq-growth.

$$\frac{dL}{dt}=a \Rightarrow L(t)=L_0 = a\times t$$ {#eq-growth}

With :

-   L : The structural volumetric length of the earthworm ($= \sqrt[3]{w}$) (mg$^{1/3}$)
-   a : Growth rate (mg$^{1/3}$/d)

For each earthworm, the growth rate is estimated using the "deSolve" package.

```{r, messsage=F, warning=F, results="hide"}
a_init <- 0.1

df_rates <- data.frame(
  ID = df_growth[df_growth$t==0,]$ID,
  Dose = df_growth[df_growth$t==0,]$Dose,
  Molecule = df_growth[df_growth$t==0,]$Molecule
  )
a_i <- c()

for(i in df_growth[df_growth$t==0,]$ID){
  
  data_i <- data.frame(
    L=df_growth[df_growth$ID==i,]$L,
    t=df_growth[df_growth$ID==i,]$t
    )
  L0_i <- df_growth[df_growth$ID==i & df_growth$t==0,]$L
  
  mod.nlsHill=nls(
    L ~ L0_i+t*a,
    start = list(a=a_init), 
    trace=T, 
    data=data_i
    ) 
  
  a.Est=mod.nlsHill$m$getPars()[1]
  a_i <- c(a_i, a.Est)
}

df_rates <- df_rates%>%
  mutate(a_i=a_i)%>%
  mutate(Status=df_growth[df_growth$t>=28,]$Status)

df_rates$a_i <- replace_na(df_rates$a_i, 0)

df_rates_alive <- df_rates[!df_rates$Status=="D",]

df_rates_alive_mean <- df_rates_alive |> 
  aggregate(a_i ~ Dose + Molecule, FUN=mean)

```

```{r, messsage=F, warning=F}
#| fig-cap: Juvenile earthworms growth rates. 
#| label: fig-growthratesJ
#| fig-width: 6
#| fig-height: 4

p <- ggplot()+
  geom_point(
    data = df_rates_alive_mean,
    aes(
      x = Dose,
      y = a_i,
      color = Molecule
    ),
    alpha = 1,
    size = 3
  )+
  geom_point(
    data = df_rates_alive,
    aes(
      x = Dose,
      y = a_i,
      color = Molecule
    ),
    alpha = 0.5
  )+
  geom_line(
    data = df_rates_alive_mean,
    aes(
      x = Dose,
      y = a_i,
      color = Molecule
    ),
    alpha = 1
  )+
  
  scale_color_manual(values=col_molec)+
  scale_fill_manual(values=col_molec)+
  
  scale_x_log10()+
  
  labs(
    y = expression(paste("Growth rate (", mg^{1/3}, ")")),
    x = "Dose (mg/kg)"
  )+
  
  theme_minimal()
p

```

```{r, include=F}
ggsave(
  filename="Pretest_juv_growth.png", 
  plot=p, 
  width=6, 
  height = 4, 
  path=here::here("fig/Single_expo")
  )
```

#### Effects on adult growth

Data on adult growth is taken from the reproduction tests.

```{r datarepro, include=F, message=F}
df_repro_full <- read_excel(here::here("data/Data_preliminary_tests.xlsx"), sheet="Repro") |> 
  mutate(
    w = w_tot/nb_ind,
    L=w^(1/3)
    ) |> 
  filter(!t == 14)

df_repro_EPX <- subset(df_repro_full, Molecule %in% c("Ctrl", "EPX")) |> 
  mutate(Molecule = "EPX")
df_repro_IMD <- subset(df_repro_full, Molecule %in% c("Ctrl", "IMD")) |> 
  mutate(Molecule = "IMD")

df_repro <- rbind(df_repro_EPX, df_repro_IMD)

```

```{r, messsage=F, warning=F}
#| fig-cap: Adult earthworms growth. 
#| label: fig-growthA
#| fig-width: 8
#| fig-height: 4


p <- ggplot(
  data = df_repro,
  aes(
    x = t,
    y = w,
    group = ID_cosm,
    color = Molecule
    )
  )+
  geom_point(
    alpha = 0.5
  )+
  geom_line()+
  facet_wrap(
    ~Molecule+Dose,
    ncol = 6
    )+
  
  scale_color_manual(values=col_molec)+
  scale_fill_manual(values=col_molec)+
  
  labs(
    y = "Fresh body weight (mg)",
    x = "Time (days)"
  )+
  
  theme_minimal()

p

```

Next we calculate growth rates again per cosm.

```{r, messsage=F, warning=F}
df_rates_A <- data.frame(
  ID=df_repro[df_repro$t==0,]$ID_cosm,
  Dose=df_repro[df_repro$t==0,]$Dose,
  Molecule=df_repro[df_repro$t==0,]$Molecule
  )

a_i <- c()

for(i in df_repro[df_repro$t==0,]$ID_cosm){
  a_i_i <- (df_repro[df_repro$ID_cosm==i & df_repro$t==28,]$L[1]-df_repro[df_repro$ID_cosm==i & df_repro$t==0,]$L[1])/28
  a_i <- c(a_i, a_i_i)
}

df_rates_A <- df_rates_A%>%
  mutate(Dose=df_repro[df_repro$t==0,]$Dose)%>%
  mutate(L0_i=L0_i)%>%
  mutate(a_i=a_i)%>%
  mutate(Status=df_repro[df_repro$t>=28,]$Status)

df_rates_A$a_i <- replace_na(df_rates_A$a_i, 0)

df_rates_A_alive <- df_rates_A[!df_rates_A$Status=="D",]

df_rates_A_alive_mean <- df_rates_A_alive |> 
  aggregate(a_i ~ Dose + Molecule, FUN=mean)

```

```{r, messsage=F, warning=F}
#| fig-cap: Adult earthworms growth rates. 
#| label: fig-growthratesA
#| fig-width: 6
#| fig-height: 4

p <- ggplot()+
  geom_point(
    data = df_rates_A_alive_mean,
    aes(
      x = Dose,
      y = a_i,
      color = Molecule
    ),
    alpha = 1,
    size = 3
  )+
  geom_point(
    data = df_rates_A_alive,
    aes(
      x = Dose,
      y = a_i,
      color = Molecule
    ),
    alpha = 0.5
  )+
  geom_line(
    data = df_rates_A_alive_mean,
    aes(
      x = Dose,
      y = a_i,
      color = Molecule
    ),
    alpha = 1
  )+
  
  scale_color_manual(values=col_molec)+
  scale_fill_manual(values=col_molec)+
  
  scale_x_log10()+
  
  labs(
    y = expression(paste("Growth rate (", mg^{1/3}, ")")),
    x = "Dose (mg/kg)"
  )+
  
  theme_minimal()
p

```

```{r, include=F}
ggsave(
  filename="Pretest_adults_growth.png", 
  plot=p, 
  width=6, 
  height = 4, 
  path=here::here("fig/Single_expo")
  )
```

#### Effects on reproduction

Unfortunately, conditions were not met for *A. icterica* reproduction. No cocoons were collected in controls and the first concentrations.
