```{r, include=F}
library(here)
source(file = here::here("functions/fun.R"))
f_load_libraries_colors()

path_repro <- here::here("fig/Single_expo/Reproduction")
path_growth <- here::here("fig/Single_expo/Growth")
```

# Effects of single exposures of imidacloprid and epoxiconazole on earthworms {#sec-expUNI}

## Methodology

The first step of our study involved evaluating each substance individually on each endpoint, as characterizing single-substance effects is a prerequisite for understanding mixture interactions. We assessed both reproductive endpoints through cocoon production in adult earthworms and developmental endpoints through juvenile growth rates, providing a first evaluation of each compound's toxicological profile before proceeding to mixture testing (UNI experiment).

To study the effects of individual pesticides, tested concentrations were selected based on the ecotoxicological data from Lewis et al. (2006) and pre-tests presented @sec-CAPrelim. For Eisenia fetida, the reported acute 14-day LC50 ranged from 10.7 mg/kg for imidacloprid to \>500 mg/kg for epoxiconazole, while the chronic reproduction NOEC values were ≥ 3.24 mg/kg and ≥ 0.178 mg/kg, respectively. An initial set of eight concentrations was selected for each pesticide, arranged in a geometric sequence to cover the full response range (@tbl-concentrations). For imidacloprid, an additional set of two concentrations (C6 and C8) with an additional concentration already tested in the initial set (C7), was added to refine the dose-response curve. Each concentration was tested in five replicates.

|                 | C1     | C2     | C3    | C4    | C5   | C6   | C7   | C8   | C9   | C10 |
|-----------------|--------|--------|-------|-------|------|------|------|------|------|-----|
| **IMD (mg/kg)** | 0.0016 | 0.0050 | 0.016 | 0.050 | 0.16 | 0.28 | 0.50 | 0.89 | 1.6  | 5.0 |
| **EPX (mg/kg)** | 0.9    | 2.0    | 4.3   | 9.3   | 20.0 | \-   | 43.1 | \-   | 92.8 | 200 |

: Tested concentrations of epoxiconazole and imidacloprid during the UNI experiment. {#tbl-concentrations}

Dose-response curves are modeled with the Hill model (@eq-Hill, @fig-drcscheme).

$$
Y=Y_{min}+\frac{Y_{max}-Y_{min}}{1+\text{exp}(Slope\times [\text{Ln}(Dose)-\text{Ln}(EC_{50})])}
$$ {#eq-Hill}

With :

-   $Y$ : Response for a given dose,
-   $Y_{min}$ : Minimal response,
-   $Y_{max}$ : Maximal response,
-   $EC_{50}$ : Dose for which the response equals $(Y_{max}-Y_{min})/2$,
-   $Slope$ : Slope when the dose equals the EC$_{50}$.

```{r, echo=F, message=F, warning=F}
#| fig-cap: Schematic representation of a dose-response curve with the Hill model
#| label: fig-drcscheme
#| fig-width: 4
#| fig-height: 3

f_Hill <- function(Dose) {
  Y_min <- 0.0
  slope <- 2.0
  Y_max <- 20.0
  EC50 <- 0.5
  return(Y_min + (Y_max - Y_min) / (1 + exp(slope * (log(Dose) - log(EC50)))))
}

dose_vec <- exp(seq(log(0.001), log(100.0), length.out = 101))

df_drc <- data.frame(
  Dose = dose_vec,
  Response = f_Hill(dose_vec)
)

plot_drc <- 

plot_drc <- ggplot(
  data = df_drc, 
  aes(
    x = Dose, 
    y = Response
    )
  ) +
  geom_line(
    color = Nord_polar[1],
    linewidth = 1.1
  )+

  annotate(
    geom = "segment",
    x = 0,
    xend = 0.5,
    y = 10,
    yend = 10,
    color = Nord_frost[3],
    alpha = 1,
    size = 1
  ) +
  annotate(
    geom = "segment",
    y = 0,
    yend = 10,
    x = 0.5,
    xend = 0.5,
    color = Nord_aurora[1],
    alpha = 1,
    size = 1
  ) +
  annotate(
    geom = "text",
    x = 0.5,
    y = -0.8,
    fontface = "bold",
    label = expression(paste(EC[50])),
    color = Nord_aurora[1],
    size = 5
  ) +
  annotate(
    geom = "text",
    x = 0.002,
    y = 18,
    fontface = "bold",
    label = expression(paste(Y[max])),
    color = Nord_polar[3],
    size = 5
  ) +
  annotate(
    geom = "text",
    x = 0.002, y = 0, fontface = "bold",
    label = expression(paste(Y[min])),
    color = Nord_polar[3],
    size = 5
  ) +
  annotate(
    geom = "text",
    x = 0.006,
    y = 8.5,
    fontface = "bold",
    label = expression(paste(1 / 2(Y[max] - Y[min]))),
    color = Nord_frost[3],
    size = 4
  ) +
  annotate(
    geom = "text",
    x = 1.1,
    y = 10,
    label = expression(paste(alpha)),
    color = Nord_frost[2],
    size = 10
  ) +
  annotate(
    geom = "segment",
    x = 0.4,
    xend = 0.6,
    y = 12,
    yend = 8,
    color = Nord_frost[2],
    arrow = arrow(
      ends = "both",
      length = unit(0.1, "inches"),
      angle = 30
    ),
    size = 1.2
  ) +
  geom_point(
    aes(
      x = 0.5,
      y = 10
    ),
    color = Nord_polar[3],
    size = 4
  ) +
  scale_x_log10() +
  labs(
    x = "Dose",
    y = "Response"
  ) +
  theme_minimal(14) +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank()
  )
plot_drc
```

Growth rate and cocoon production dose-response curves were modeled using Normal and Poisson error distributions, respectively. The model fit of all dose-response models was evaluated using lack-of-fit tests compared to Anova models.

## Effect on reproduction

### Reproduction experiments

The soil used for all experiments is the same as the culture to be as close as possible to the conditions of the natural population.

Reproduction tests were conducted following an adaptation of the OECD Technical Guideline 222 [@oecd_2016] (more details @sec-methodtests) in a two-stage experiment. Each pesticide was first tested individually (Experiment A) before assessing the mixture (Experiment B).

To study the effects of individual pesticides, tested concentrations were selected based on the ecotoxicological data from @lewis_2006. For Eisenia fetida, the reported acute 14-day LC50 values were 10.7 mg/kg for imidacloprid and \>500 mg/kg for epoxiconazole, while the chronic reproduction NOEC values were ≥3.24 mg/kg and ≥0.178 mg/kg, respectively. An initial set of eight concentrations was selected for each pesticide, arranged in a geometric sequence to cover the full response range. For imidacloprid, an additional set of three concentrations, including one already tested, was added to refine the dose-response curve. Each concentration was tested in five replicates.

### Experimental results

Variables names :

-   `Date` : Date of the measurement
-   `ID_cosm` : Identification number of the cosm
-   `t` : Number of days since the start of the exposition (d)
-   `w_tot` : Fresh weight of the earthworms in one cosm (mg)
-   `Nb_ind` : Number of alive individuals in a cosm (#)
-   `Dose` : concentration in the soil (mg/kg)
-   `Status` :
    -   "J" : Juvenile
    -   "A" : Adulte
    -   "D" : Dead

```{r datar, warning=F, message=F}
data_expA_repro <- f_read_data_expA_repro()
df_expA_repro_tot <- data_expA_repro$df_expA_repro
df_expA_repro <- data_expA_repro$df_expA_repro_alive
df_expA_repro_mean <- data_expA_repro$df_expA_repro_alive_mean

Val_Ctrl <- 1e-4
Label_Ctrl <- "0 (Ctrl)"
```

#### Initial conditions

We can first take a look at the initial weights of individuals (@fig-initExpARepro).

```{r, warning=F, message=F}
#| fig-cap: Initial weights of adult earthworms in experiment A.
#| label: fig-initExpARepro
#| fig-width: 6
#| fig-height: 6

# Weights at t=0
plot_D0 <- ggplot(
  data = subset(df_expA_repro_tot, t == 0),
  aes(
    x = Dose_f,
    y = w,
    color = Molecule,
    fill = Molecule,
    shape = Molecule
  )
) +
  geom_boxplot(alpha = 0.2) +
  geom_dotplot(
    binaxis = "y",
    stackdir = "center",
    dotsize = 0.7,
    alpha = 0.7
  ) +
  facet_wrap(
    ~Molecule,
    ncol = 1,
    scales = "free"
  ) +
  scale_color_manual(values = col_molec) +
  scale_fill_manual(values = col_molec) +
  scale_shape_manual(values = shape_molec) +
  labs(x = "Dose (mg/kg)", y = "Weight (mg)") +
  theme_classic(14) +
  theme(
    legend.position = "none",
    legend.title = element_text(
      size = sizetitle - 2,
      face = "bold"
    ),
    legend.text = element_text(
      size = sizetitle - 2,
      face = "plain"
    ),
    title = element_text(
      size = sizetitle,
      face = "bold"
    ),
    axis.title.x = element_text(
      size = sizetitle,
      face = "plain"
    ),
    axis.title.y = element_text(
      size = sizetitle,
      face = "plain"
    ),
    strip.background = element_rect(
      color = "black",
      fill = Nord_snow[3],
      size = 0,
      linetype = "solid"
    )
  )
plot_D0
```

```{r, include=F}
ggsave(
  filename = "ExpA_repro_initial_weights.png",
  plot = plot_D0,
  width = 6,
  height = 5,
  path = path_repro
)

ggsave(
  filename = "ExpA_repro_initial_weights.jpg",
  plot = plot_D0,
  width = 6,
  height = 5,
  path = path_repro
)

ggsave(
  filename = "ExpA_repro_initial_weights.svg",
  plot = plot_D0,
  width = 6,
  height = 5,
  path = path_repro
)
```

We can easily see that earthworms exposed to IMD from the second experiment have a slightly lower initial weight than individuals from the first experiment.

We look at if there is an effect of the dose on the inital weights with an ANOVA and a Dunett test.

```{r lmD0EPXr, warning=F, message=F}
# ANOVA
mod_aov <- aov(w ~ Dose_f, data = subset(df_expA_repro_tot, Molecule == "EPX" & t == 0))
summary(mod_aov)

dunnett_test <- glht(mod_aov, linfct = mcp(Dose_f = "Dunnett"))
summary(dunnett_test)
```

```{r lmD0IMDr, warning=F, message=F}
# ANOVA
mod_aov <- aov(w ~ Dose_f, data = subset(df_expA_repro_tot, Molecule == "IMD" & t == 0))
summary(mod_aov)

dunnett_test <- glht(mod_aov, linfct = mcp(Dose_f = "Dunnett"))
summary(dunnett_test)
```

There is no effect of the dose on the initial mean weight of earthworms for both pesticides.

#### Effect on cocoon production

For reproduction, we have count data and therefor the error model is a Poisson distribution. Additionaly, the minimal response is obviously 0 thus we set $Y_{min}$ to 0 in our model.

```{r drcr, warning=F, message=F}
drc.mod.r <- drm(
  Nb_cocoons ~ Dose,
  curveid = Molecule, # <1>
  data = df_expA_repro, # <2>
  type = "Poisson", # <3>
  fct = LL.4(
    names = c("slope", "Ymin", "Ymax", "EC50"), # <4>
    fixed = c(NA, 0, NA, NA) # <5>
  ),
  pmodels = data.frame(Molecule, Molecule, Molecule), # <6>
)

summary(drc.mod.r)

# Confidence interval

Dose_x <- expand.grid(
  exp(
    seq(
      log(Val_Ctrl), log(5000),
      by = (log(5000) - log(Val_Ctrl)) / 100
    )
  )
)

CI.r <- data.frame(
  Dose = c(Dose_x$Var1, Dose_x$Var1),
  Molecule = c(rep("EPX", length(Dose_x$Var1)), rep("IMD", length(Dose_x$Var1)))
)

pm.r <- predict(drc.mod.r, newdata = CI.r, interval = "confidence")
CI.r$p <- pm.r[, 1]
CI.r$pmin <- pm.r[, 2]
CI.r$pmax <- pm.r[, 3]
```

1.  Dose-response relationship and grouping variable
2.  Data to be used
3.  Error distribution type
4.  Setting up the parameters names
5.  $Y_{min}$ is fixed to 0
6.  All parameters depend on the molecule but $Y_{max}$

```{r drcrCI, warning=F, message=F}
est <- coef(drc.mod.r)
ci <- confint(drc.mod.r)
params_tab <- data.frame(
  estimate  = unname(est),
  CI_lower  = ci[, 1],
  CI_upper  = ci[, 2]
)

params_tab |>
  datatable(
    options = list(
      dom = "t",
      autoWidth = TRUE,
      columnDefs = list(
        list(className = "dt-left", targets = "_all")
      )
    ),
    class = "hover"
  ) |>
  formatSignif(columns = c("estimate", "CI_lower", "CI_upper"), c(3, 3, 3))
```

```{r, warning=F, message=F}
#| fig-cap: Dose-response curves for cocoon production
#| label: fig-reprodrc
#| fig-width: 6
#| fig-height: 5

plot_drc_r <- ggplot() +
  geom_ribbon_interactive(
    data = CI.r,
    aes(
      x = Dose,
      y = p,
      ymin = pmin, ymax = pmax,
      group = Molecule,
      fill = Molecule,
      tooltip = Molecule,
      data_id = Molecule,
    ),
    alpha = 0.2
  ) +
  geom_line_interactive(
    data = CI.r,
    aes(
      x = Dose,
      y = p,
      color = Molecule,
      tooltip = Molecule,
      data_id = Molecule,
      color = Molecule,
      shape = Molecule
    ),
    linewidth = 1.2
  ) +
  geom_point_interactive(
    data = df_expA_repro,
    aes(
      x = Dose_plot,
      y = Nb_cocoons,
      shape = Molecule,
      tooltip = Molecule,
      data_id = Molecule,
      color = Molecule,
      shape = Molecule
    ),
    cex = 2,
    alpha = 0.4
  ) +
  geom_point_interactive(
    data = df_expA_repro_mean,
    aes(
      x = Dose_plot,
      y = Nb_cocoons,
      shape = Molecule,
      tooltip = Molecule,
      data_id = Molecule,
      color = Molecule,
      shape = Molecule
    ),
    alpha = 1,
    size = 3
  ) +
  scale_color_manual(name = "", values = col_molec) +
  scale_shape_manual(name = "", values = shape_molec) +
  scale_fill_manual(name = "", values = col_molec) +
  theme_minimal() +
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.001, 0.01, 0.1, 1, 10, 100, 1000),
    labels = c(Label_Ctrl, "0.001", "0.01", "0.1", "1", "10", "100", "1000")
  ) +
  labs(
    x = "Dose (mg/kg)",
    y = "Number of cocoons produced per cosm (#)",
  ) +
  theme(
    legend.position = "right",
    legend.title = element_text(
      size = sizetitle - 2,
      face = "bold"
    ),
    title = element_text(
      size = sizetitle,
      face = "bold"
    ),
    axis.title.x = element_text(
      size = sizetitle,
      face = "plain"
    ),
    axis.title.y = element_text(
      size = sizetitle,
      face = "plain"
    )
  )

tooltip_css <- "
  border-radius: 12px;
  color: #333;
  background-color: white;
  padding: 10px;
  font-size: 14px;
  transition: all 0.5s ease-out;
"

hover_css <- "
  filter: brightness(75%);
  cursor: pointer;
  transition: all 0.5s ease-out;
  filter: brightness(1.15);
"

interactive_plot <- girafe(ggobj = plot_drc_r) %>%
  girafe_options(opts_sizing(rescale = FALSE))

# Add interactivity
interactive_plot <- interactive_plot %>%
  girafe_options(
    opts_hover(css = hover_css),
    opts_tooltip(css = tooltip_css),
    opts_hover_inv(css = "opacity:0.3; transition: all 0.2s ease-out;")
  )

interactive_plot

plot_drc_r_f <- plot_drc_r +
  labs(title = "A. Effects on cocoon production")
```

```{r, include=F}
ggsave(
  filename = "ExpA_repro_drc_single.png",
  plot = plot_drc,
  width = 6,
  height = 4,
  path = path_repro
)
ggsave(
  filename = "ExpA_repro_drc_single.jpg",
  plot = plot_drc,
  width = 6,
  height = 4,
  path = path_repro
)
ggsave(
  filename = "ExpA_repro_drc_single.svg",
  plot = plot_drc,
  width = 6,
  height = 4,
  path = path_repro
)
```

```{r}
# Anova model
df_expA_repro_anova <- df_expA_repro |>
  mutate(
    Condition_f = as.factor(paste0(Molecule, Dose_plot)),
    Molecule = as.factor(Molecule)
  )

anova.drc.r <- glm(
  Nb_cocoons ~ Condition_f,
  family = poisson(link = "log"),
  data = df_expA_repro_anova
)
# check_model(glm_anova)
# predict(glm_anova)

# Log-Likelihood
LL_drc <- as.numeric(logLik(drc.mod.r))
LL_anova <- as.numeric(logLik(anova.drc.r))

# Number of parameters
k_drc <- 6
k_anova <- attr(logLik(anova.drc.r), "df")

# Log-Likelihood ratio test
# H0 : the drc is OK
# H1 : the ANOVA modèle (saturated) is better
D <- -2 * (LL_drc - LL_anova)
df_test <- k_anova - k_drc

# Verification
p_val <- pchisq(D, df = df_test, lower.tail = FALSE)
cat("Lack-of-fit test: D =", round(D, 3), ", df =", df_test, ", p =", round(p_val, 4), "\n")
```

```{r, warning=F, message=F}
#| fig-cap: Diagnostic graphs of the dose-response model for reproduction
#| label: fig-drcdiagr
#| fig-width: 8
#| fig-height: 4

col_diag <- Nord_polar[4]

plot_QQ <- ggplot(mapping = aes(sample = residuals(drc.mod.r))) +
  stat_qq(alpha = 0.3) +
  stat_qq_line(color = col_diag) +
  labs(
    x = "Normal quantiles",
    y = "Residuals"
  ) +
  theme_bw()

plot_resfit <- ggplot() +
  geom_point(
    mapping = aes(
      x = fitted(drc.mod.r),
      y = residuals(drc.mod.r)
    ),
    color = col_diag,
    alpha = 0.3
  ) +
  scale_x_log10() +
  labs(
    x = "Fitted",
    y = "Residuals"
  ) +
  theme_bw()

plot <- plot_resfit + plot_QQ + plot_layout(ncol = 2)
plot
```

NOEC determination :

```{r, warning=F, message=F}
df_expA_repro$Dose_f <- as.factor(df_expA_repro$Dose)
df_expA_repro$Dose_f <- relevel(df_expA_repro$Dose_f, ref = "0")

cat("IMD - Determination of NOEC and LOEC\n")
mod_aov <- aov(Nb_cocoons ~ Dose_f, data = subset(df_expA_repro, Molecule == "IMD"))
summary(mod_aov)
dunnett_test <- glht(mod_aov, linfct = mcp(Dose_f = "Dunnett"))
summary(dunnett_test)

cat("EPX - Determination of NOEC and LOEC\n")
mod_aov <- aov(Nb_cocoons ~ Dose_f, data = subset(df_expA_repro, Molecule == "EPX"))
summary(mod_aov)
dunnett_test <- glht(mod_aov, linfct = mcp(Dose_f = "Dunnett"))
summary(dunnett_test)
```

#### Effect on hatchlings

```{r}
df_expA_hatchlings <- f_read_data_expA_hatchlings()
```

```{r, warning = F, message = F}
#| fig-cap: Mean cumulated number of juveniles produced determined with the monitoring of hatchlings (after 69 days of incubation for IMD and after 55 days for EPX)
#| label: fig-hatchlings
#| fig-width: 8
#| fig-height: 4

p <- ggplot(data = df_expA_hatchlings) +
  geom_col(
    aes(
      x = as.factor(Dose),
      y = Nb_juv_cum,
      color = Molecule,
      fill = Molecule
    ),
    alpha = 0.5
  ) +
  labs(
    x = "Concentration (mg/kg)",
    y = "Mean cumulated number of juveniles produced (#)"
  ) +
  facet_wrap(~Molec, scales = "free") +
  scale_color_manual(values = col_molec) +
  scale_fill_manual(values = col_molec) +
  theme_minimal()
p
```

#### Effect on adult growth

```{r, warning=F, message=F}
#| fig-cap: Earthworms growth according to their exposition.
#| label: fig-growthplotadults
#| fig-width: 6
#| fig-height: 10

nb_dose_EPX <- n_distinct(subset(df_expA_repro, Molecule == "EPX")$Dose)
nb_dose_IMD <- n_distinct(subset(df_expA_repro, Molecule == "IMD")$Dose)

pal_dose_EPX <- nord(
  palette = "aurora", nb_dose_EPX + 2,
  alpha = 1, reverse = T
)[-c(1, 2)]
pal_dose_IMD <- nord(
  palette = "aurora", nb_dose_IMD + 2,
  alpha = 1, reverse = T
)[-c(1, 2)]

plot_growth_EPX <- ggplot(
  data = subset(df_expA_repro, Molecule == "EPX"),
  aes(
    x = t,
    y = w,
    group = ID_cosm,
    color = as.factor(Dose)
  )
) +
  geom_point(shape = shape_EPX) +
  scale_color_manual(
    name = "Dose (mg/kg)",
    values = pal_dose_EPX
  ) +
  geom_line() +
  facet_wrap(~Dose, ncol = 3) +
  labs(
    x = "Time (d)",
    y = "Weight (mg)",
    title = "Growth of earthworms exposed to epoxiconazole"
  ) +
  theme_bw() +
  theme(
    legend.position = "right",
    legend.title = element_text(size = sizetitle - 2, face = "bold"),
    strip.background = element_rect(
      colour = "black", fill = "white",
      linetype = "solid"
    ),
    title = element_text(size = sizetitle, face = "bold"),
    axis.title.x = element_text(size = sizetitle, face = "plain"),
    axis.title.y = element_text(size = sizetitle, face = "plain")
  )

plot_growth_IMD <- ggplot(
  data = subset(df_expA_repro, Molecule == "IMD"),
  aes(
    x = t,
    y = w,
    group = ID_cosm,
    color = as.factor(Dose)
  )
) +
  geom_point(shape = shape_IMD) +
  geom_line() +
  facet_wrap(~Dose, ncol = 3) +
  scale_color_manual(
    name = "Dose (mg/kg)",
    values = pal_dose_IMD
  ) +
  labs(
    x = "Time (d)",
    y = "Weight (mg)",
    title = "Growth of earthworms exposed to imidacloprid"
  ) +
  theme_bw() +
  theme(
    legend.position = "right",
    legend.title = element_text(size = sizetitle - 2, face = "bold"),
    strip.background = element_rect(
      colour = "black", fill = "white",
      linetype = "solid"
    ),
    title = element_text(size = sizetitle, face = "bold"),
    axis.title.x = element_text(size = sizetitle, face = "plain"),
    axis.title.y = element_text(size = sizetitle, face = "plain")
  )

plot <- plot_growth_EPX + plot_growth_IMD + plot_layout(ncol = 1, heights = c(1, 4 / 3))
plot
```

```{r, include=F}
ggsave(
  filename = "ExpA_repro_growth_curves.png",
  plot = plot,
  width = 8,
  height = 4,
  path = path_repro
)

ggsave(
  filename = "ExpA_repro_growth_curves.jpg",
  plot = plot,
  width = 8,
  height = 4,
  path = path_repro
)

ggsave(
  filename = "ExpA_repro_growth_curves.svg",
  plot = plot,
  width = 8,
  height = 4,
  path = path_repro
)
```

```{r growthratesfuncr}
df_expA_repro_grate <- df_expA_repro |>
  dplyr::select(ID_cosm, t, L, Dose, Dose_plot, Molecule) |>
  pivot_wider(names_from = t, values_from = L, names_prefix = "L_t") |>
  mutate(a_i = (L_t28 - L_t0) / 28)

df_expA_repro_grate_mean <- df_expA_repro_grate |>
  aggregate(a_i ~ Molecule + Dose + Dose_plot, FUN = "mean")
```

```{r, warning=F, message=F}
#| fig-cap: Effect of the pesticides on growth rates.
#| label: fig-growthrates
#| fig-width: 8
#| fig-height: 4


p <- ggplot() +
  geom_point(
    data = df_expA_repro_grate,
    aes(
      x = Dose_plot,
      y = a_i,
      color = Molecule,
      shape = Molecule
    ),
    alpha = 0.5,
  ) +
  geom_point(
    data = df_expA_repro_grate_mean,
    aes(
      x = Dose_plot,
      y = a_i,
      color = Molecule,
      shape = Molecule
    ),
    alpha = 1,
    size = 3
  ) +
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100), # inclure la valeur fictive
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100")
  ) +
  facet_wrap(~Molecule, scales = "free_x") +
  scale_color_manual(values = col_molec) +
  scale_fill_manual(values = col_molec) +
  scale_shape_manual(values = shape_molec) +
  labs(
    x = "Dose (mg/kg)",
    y = "Growth rate" # ,
    # title = "Effect of the pesticides on adult growth rates"
  ) +
  ylim(NA, 0.05) +
  theme_minimal(base_size = 15) + # Thème minimaliste
  theme(
    plot.title = element_text(
      # hjust = 0.5,
      face = "bold"
    ),
    legend.position = "none",
    strip.background = element_rect(
      color = "black",
      fill = Nord_snow[3],
      size = 0,
      linetype = "solid"
    ),
    strip.text = element_text(face = "bold")
  )
p
```

```{r, include=F}
ggsave(
  filename = "ExpA_repro_growth_rates.png",
  plot = p,
  width = 8,
  height = 4,
  path = path_repro
)

ggsave(
  filename = "ExpA_repro_growth_rates.jpg",
  plot = p,
  width = 8,
  height = 4,
  path = path_repro
)

ggsave(
  filename = "ExpA_repro_growth_rates.svg",
  plot = p,
  width = 8,
  height = 4,
  path = path_repro
)
```

NOEC determination for adult growth :

```{r, warning=F, message=F}
df_expA_repro_grate$Dose_f <- as.factor(df_expA_repro_grate$Dose)
df_expA_repro_grate$Dose_f <- relevel(df_expA_repro_grate$Dose_f, ref = "0")

cat("IMD - Determination of NOEC and LOEC\n")
mod_aov <- aov(a_i ~ Dose_f, data = subset(df_expA_repro_grate, Molecule == "IMD"))
summary(mod_aov)
dunnett_test <- glht(mod_aov, linfct = mcp(Dose_f = "Dunnett"))
summary(dunnett_test)

cat("EPX - Determination of NOEC and LOEC\n")
mod_aov <- aov(a_i ~ Dose_f, data = subset(df_expA_repro_grate, Molecule == "EPX"))
summary(mod_aov)
dunnett_test <- glht(mod_aov, linfct = mcp(Dose_f = "Dunnett"))
summary(dunnett_test)
```

### Comparison to environmental concentrations

```{r envconc}
# Environmental concentrations (Froger et al. 2023)
EPX_Cmin <- 1.1 / 1000
EPX_Cmax <- 23.6 / 1000
EPX_median <- 5.8 / 1000
EPX_Q25 <- 2.8 / 1000
EPX_Q75 <- 10.9 / 1000

EPX_Cmax_pelosi <- 283 / 1000

IMD_Cmin <- 2 / 1000
IMD_Cmax <- 13.8 / 1000
IMD_median <- 2.9 / 1000
IMD_Q25 <- 2.5 / 1000
IMD_Q75 <- 5.8 / 1000

IMD_Cmax_pelosi <- 283 / 1000
```

```{r, warning=F, message=F}
#| fig-cap: Estimated effect on cocoon production for environmental concentrations
#| label: fig-reprodrcenv
#| fig-width: 6
#| fig-height: 6


p_IMD <- ggplot() +
  annotate(
    "rect",
    xmin = IMD_Cmin, xmax = IMD_Cmax,
    ymin = -Inf, ymax = Inf,
    alpha = 0.2,
    fill = col_IMD,
    color = col_IMD
  ) +
  annotate(
    "rect",
    xmin = IMD_Q25, xmax = IMD_Q75,
    ymin = -Inf, ymax = Inf,
    color = col_IMD,
    fill = col_IMD,
    alpha = 0.1
  ) +
  geom_vline(
    xintercept = IMD_median,
    color = col_IMD,
    linetype = "dotted",
    linewidth = 1.2
  ) +
  geom_vline(
    xintercept = IMD_Cmax_pelosi,
    color = col_red,
    linetype = "dashed",
    linewidth = 1.2
  ) +
  geom_ribbon(
    data = subset(CI.r, Molecule == "IMD"),
    aes(
      x = Dose,
      y = p,
      ymin = pmin, ymax = pmax,
      group = Molecule,
      fill = Molecule
    ),
    alpha = 0.2
  ) +
  geom_line(
    data = subset(CI.r, Molecule == "IMD"),
    aes(
      x = Dose,
      y = p,
      color = Molecule,
      shape = Molecule
    ),
    linewidth = 1.2
  ) +
  geom_point(
    data = subset(df_expA_repro, Molecule == "IMD"),
    aes(
      x = Dose_plot,
      y = Nb_cocoons,
      color = Molecule,
      shape = Molecule
    ),
    cex = 2,
    alpha = 0.4
  ) +
  geom_point(
    data = subset(df_expA_repro_mean, Molecule == "IMD"),
    aes(
      x = Dose_plot,
      y = Nb_cocoons,
      color = Molecule,
      shape = Molecule
    ),
    alpha = 1,
    size = 3
  ) +
  scale_color_manual(name = "", values = rev(col_molec)) +
  scale_shape_manual(name = "", values = rev(shape_molec)) +
  scale_fill_manual(name = "", values = rev(col_molec)) +
  theme_minimal() +
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.001, 0.01, 0.1, 1, 10, 100, 1000),
    labels = c(Label_Ctrl, "0.001", "0.01", "0.1", "1", "10", "100", "1000")
  ) +
  labs(
    x = "Dose (mg/kg)",
    y = "Number of cocoons produced per cosm (#)"
  ) +
  theme(
    legend.position = "right"
  )

p_EPX <- ggplot() +
  annotate(
    "rect",
    xmin = EPX_Cmin, xmax = EPX_Cmax,
    ymin = -Inf, ymax = Inf,
    alpha = 0.2,
    fill = col_EPX,
    color = col_EPX
  ) +
  annotate(
    "rect",
    xmin = EPX_Q25, xmax = EPX_Q75,
    ymin = -Inf, ymax = Inf,
    color = col_EPX,
    fill = col_EPX,
    alpha = 0.1
  ) +
  geom_vline(
    xintercept = EPX_median,
    color = col_EPX,
    linetype = "dotted",
    linewidth = 1.2
  ) +
  geom_vline(
    xintercept = EPX_Cmax_pelosi,
    color = col_red,
    linetype = "dashed",
    linewidth = 1.2
  ) +
  geom_ribbon(
    data = subset(CI.r, Molecule == "EPX"),
    aes(
      x = Dose,
      y = p,
      ymin = pmin, ymax = pmax,
      group = Molecule,
      fill = Molecule
    ),
    alpha = 0.2
  ) +
  geom_line(
    data = subset(CI.r, Molecule == "EPX"),
    aes(
      x = Dose,
      y = p,
      color = Molecule,
      shape = Molecule
    ),
    linewidth = 1.2
  ) +
  geom_point(
    data = subset(df_expA_repro, Molecule == "EPX"),
    aes(
      x = Dose_plot,
      y = Nb_cocoons,
      color = Molecule,
      shape = Molecule
    ),
    cex = 2,
    alpha = 0.4
  ) +
  geom_point(
    data = subset(df_expA_repro_mean, Molecule == "EPX"),
    aes(
      x = Dose_plot,
      y = Nb_cocoons,
      color = Molecule,
      shape = Molecule
    ),
    alpha = 1,
    size = 3
  ) +
  scale_color_manual(name = "", values = col_molec) +
  scale_shape_manual(name = "", values = shape_molec) +
  scale_fill_manual(name = "", values = col_molec) +
  theme_minimal() +
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.001, 0.01, 0.1, 1, 10, 100, 1000),
    labels = c(Label_Ctrl, "0.001", "0.01", "0.1", "1", "10", "100", "1000")
  ) +
  labs(
    x = "Dose (mg/kg)",
    y = "Number of cocoons produced per cosm (#)"
  ) +
  theme(
    legend.position = "right"
  )

p <- p_EPX / p_IMD
p
```

```{r, include=F}
ggsave(
  filename = "ExpA_repro_drc_single_env_froger.png",
  plot = p,
  width = 6,
  height = 7,
  path = path_repro
)

ggsave(
  filename = "ExpA_repro_drc_single_env_froger.jpg",
  plot = p,
  width = 6,
  height = 7,
  path = path_repro
)

ggsave(
  filename = "ExpA_repro_drc_single_env_froger.svg",
  plot = p,
  width = 6,
  height = 7,
  path = path_repro
)
```

## Effect on juvenile growth

### Experimental results

Variables names :

-   `Date` : Date of the measurement
-   `ID` : Identification number of the earthworm
-   `t` : Number of days since the start of the exposition
-   `w` : Fresh weight of the earthworm (mg)
-   `Dose` : concentration in the soil (mg/kg)
-   `status` :
    -   "J" : Juvenile
    -   "A" : Adulte
    -   "D" : Dead

```{r datag, warning=F, message=F}
data_expA_growth <- f_read_data_expA_growth()
df_expA_growth_tot <- data_expA_growth$df_expA_growth_tot
df_expA_growth <- data_expA_growth$df_expA_growth
```

##### Initial state

We can first take a look at the initial weights of individuals (@fig-initGrowth).

```{r, warning=F, message=F}
#| fig-cap: Initial weights of juvenile earthworms in experiment A.
#| label: fig-initGrowth
#| fig-width: 6
#| fig-height: 6

plot_D0 <- ggplot(
  data = subset(df_expA_growth_tot, t == 0),
  aes(
    x = Dose_f,
    y = w,
    color = Molecule,
    fill = Molecule
  )
) +
  geom_boxplot(alpha = 0.2) +
  geom_dotplot(
    binaxis = "y",
    stackdir = "center",
    dotsize = 0.7,
    alpha = 0.7
  ) +
  labs(
    x = "Dose (mg/kg)",
    y = "Weight (mg)"
  ) +
  facet_wrap(
    ~Molecule,
    ncol = 1,
    scales = "free"
  ) +
  scale_color_manual(values = col_molec) +
  scale_fill_manual(values = col_molec) +
  theme_classic(14) +
  theme(
    legend.position = "none",
    legend.title = element_text(
      size = sizetitle - 2,
      face = "bold"
    ),
    legend.text = element_text(
      size = sizetitle - 2,
      face = "plain"
    ),
    title = element_text(
      size = sizetitle,
      face = "bold"
    ),
    axis.title.x = element_text(
      size = sizetitle,
      face = "plain"
    ),
    axis.title.y = element_text(
      size = sizetitle,
      face = "plain"
    ),
    strip.background = element_rect(
      color = "black",
      fill = "grey95",
      size = 0,
      linetype = "solid"
    )
  )
plot_D0
```

```{r, include=F}
ggsave(
  filename = "ExpA_growth_initial_weights.png",
  plot = plot_D0,
  width = 6,
  height = 5,
  path = path_growth
)
ggsave(
  filename = "ExpA_growth_initial_weights.jpg",
  plot = plot_D0,
  width = 6,
  height = 5,
  path = path_growth
)
```

We can easily see that earthworms exposed to IMD from the second experiment have a slightly lower initial weight than individuals from the first experiment.

We look at if there is an effect of the dose on the inital weights with an ANOVA and a Dunett test.

```{r lmD0EPXgr, warning=F, message=F}
# ANOVA
mod_aov <- aov(w ~ Dose_f, data = subset(df_expA_growth_tot, Molecule == "EPX" & t == 0))
summary(mod_aov)

dunnett_test <- glht(mod_aov, linfct = mcp(Dose_f = "Dunnett"))
summary(dunnett_test)
```

For EPX, there is no significant effect of the dose on the initial weight of earthworms (Student test : pval(IMD) = 0.125).

```{r lmD0IMDgr, warning=F, message=F}
# ANOVA
mod_aov <- aov(w ~ Dose_f, data = subset(df_expA_growth_tot, Molecule == "IMD" & t == 0))
summary(mod_aov)

dunnett_test <- glht(mod_aov, linfct = mcp(Dose_f = "Dunnett"))
summary(dunnett_test)
```

For IMD, there is a significant effect of the dose on earthworm initial weights.

-   ANOVA : pval(IMD) = 9.66e-05,
-   All concentrations are not significatively different from the control (post hoc Dunett test).

However, earthworms were non the less randomly attributed to conditions and the growth model allows to take the differences in initial weight into account.

##### Earthworms growth

```{r, warning=F, message=F}
#| fig-cap: Earthworms growth according to their exposition.
#| label: fig-growthplotjuv
#| fig-width: 6
#| fig-height: 10

nb_dose_EPX <- n_distinct(subset(df_expA_growth_tot, Molecule == "EPX")$Dose)
nb_dose_IMD <- n_distinct(subset(df_expA_growth_tot, Molecule == "IMD")$Dose)

pal_dose_EPX <- nord(
  palette = "aurora",
  nb_dose_EPX + 2,
  alpha = 1,
  reverse = T
)[-c(1, 2)]
pal_dose_IMD <- nord(
  palette = "aurora",
  nb_dose_IMD + 2,
  alpha = 1,
  reverse = T
)[-c(1, 2)]

plot_growth_EPX <- ggplot(
  data = subset(df_expA_growth_tot, Molecule == "EPX"),
  aes(
    x = t,
    y = w,
    group = ID,
    color = as.factor(Dose)
  ),
  shape = shape_EPX
) +
  geom_point() +
  scale_color_manual(
    name = "Dose (mg/kg)",
    values = pal_dose_EPX
  ) +
  geom_line() +
  facet_wrap(
    ~Dose,
    ncol = 3
  ) +
  labs(
    x = "Time (d)",
    y = "Weight (mg)",
    title = "Epoxiconazole"
  ) +
  theme_bw() +
  theme(
    legend.position = "right",
    legend.title = element_text(
      size = sizetitle - 2,
      face = "bold"
    ),
    strip.background = element_rect(
      colour = "black",
      fill = "white",
      linetype = "solid"
    ),
    title = element_text(
      size = sizetitle,
      face = "bold"
    ),
    axis.title.x = element_text(
      size = sizetitle,
      face = "plain"
    ),
    axis.title.y = element_text(
      size = sizetitle,
      face = "plain"
    )
  )

plot_growth_IMD <- ggplot(
  data = subset(df_expA_growth_tot, Molecule == "IMD"),
  aes(
    x = t,
    y = w,
    group = ID,
    color = as.factor(Dose)
  ),
  shape = shape_IMD
) +
  geom_point() +
  geom_line() +
  facet_wrap(
    ~Dose,
    ncol = 3
  ) +
  scale_color_manual(name = "Dose (mg/kg)", values = pal_dose_IMD) +
  labs(
    x = "Time (d)",
    y = "Weight (mg)",
    title = "Imidacloprid"
  ) +
  theme_bw() +
  theme(
    legend.position = "right",
    legend.title = element_text(
      size = sizetitle - 2,
      face = "bold"
    ),
    strip.background = element_rect(
      colour = "black",
      fill = "white",
      linetype = "solid"
    ),
    title = element_text(
      size = sizetitle,
      face = "bold"
    ),
    axis.title.x = element_text(
      size = sizetitle,
      face = "plain"
    ),
    axis.title.y = element_text(
      size = sizetitle,
      face = "plain"
    )
  )

plot <- plot_growth_EPX + plot_growth_IMD + plot_layout(ncol = 1, heights = c(1, 4 / 3))
plot
```

```{r, include=F}
ggsave(
  filename = "ExpA_growth_curves_juveniles_IMD.png",
  plot = plot_growth_IMD,
  width = 6,
  height = 6.6,
  path = path_growth
)

ggsave(
  filename = "ExpA_growth_curves_juveniles_EPX.png",
  plot = plot_growth_EPX,
  width = 6,
  height = 5,
  path = path_growth
)
```

### Growth model - Growth rates calculation

The growth model is the following :

$$
\frac{dL}{dt}=a \Rightarrow L(t)=L_0 + a\times t
$$

With :

-   L : The structural volumetric length of the earthworm ($= \sqrt[3]{w}$) (mg$^{1/3}$)
-   a : Growth rate (mg$^{1/3}$/d)

For each earthworm, the growth rate is estimated using `nls` from the "stats" package.

```{r growthratesfuncg}
f_growth_rate <- function(data) {
  a_init <- 0.1
  a_i <- c()

  # Calculation of the growth rate for each individual
  for (i in subset(data, t == 0)$ID) {
    data_i <- data.frame(
      L = subset(data, ID == i)$L,
      t = subset(data, ID == i)$t
    )
    L0_i <- subset(data, ID == i & t == 0)$L

    if (length(na.omit(data_i$L)) == 2) { # If only 2 data points
      a.Est <- (subset(data_i, !t == 0)$L - subset(data_i, t == 0)$L) /
        subset(data_i, !t == 0)$t
    } else { # If 3 data points (or more)
      EPX.nlsHill <- nls(
        L ~ L0_i + t * a,
        start = list(a = a_init),
        trace = T,
        data = data_i
      )
      a.Est <- EPX.nlsHill$m$getPars()[1]
    }
    a_i <- rbind(a_i, a.Est)
  }

  return(a_i)
}
```

```{r growthratescalc, warning=F, message=F, output=F}
# Growth rate calculation for individuals alive at the end of the experiment
a_i <- f_growth_rate(df_expA_growth) |> as.data.frame()

df_rates_alive <- cbind(subset(df_expA_growth, t == 0), a_i) |>
  as.data.frame()

df_rates_controls <- subset(df_rates_alive, Molec %in% c("Ctrl_1", "Ctrl_2")) |>
  aggregate(a ~ Molec, FUN = mean)

df_rates_alive <- df_rates_alive |>
  mutate(
    r_a = case_when(
      Lot == "A" ~ a / subset(df_rates_controls, Molec == "Ctrl_1")$a,
      Lot == "B" ~ a / subset(df_rates_controls, Molec == "Ctrl_2")$a
    ) * 100
  )

df_rates_alive_mean <- df_rates_alive |>
  group_by(Dose, Molecule, Dose_plot) |>
  summarise(
    r_a = mean(r_a, na.rm = TRUE),
    a = mean(a, na.rm = TRUE),
    .groups = "drop"
  )
```

### Dose-response curve for juvenile growth

```{r drcg, warning=F, message=F}
drc.mod.g <- drm(
  a ~ Dose, Molecule,
  data = df_rates_alive,
  fct = LL.4(
    names = c("slope", "Ymin", "Ymax", "EC50"),
    fixed = c(NA, NA, NA, NA)
  ),
  pmodels = data.frame(Molecule, 1, 1, Molecule),
  lowerl = c(-Inf, -Inf, -Inf, 1e-4)
)
summary(drc.mod.g)

Dose_x <- expand.grid(
  exp(
    seq(
      log(0.000001), log(5000),
      by = (log(5000) - log(0.000001)) / 100
    )
  )
)

CI.g <- data.frame(
  Dose = c(Dose_x$Var1, Dose_x$Var1),
  Molecule = c(rep("EPX", length(Dose_x$Var1)), rep("IMD", length(Dose_x$Var1)))
)

pm.g <- predict(drc.mod.g, newdata = CI.g, interval = "confidence")
CI.g$p <- pm.g[, 1]
CI.g$pmin <- pm.g[, 2]
CI.g$pmax <- pm.g[, 3]
```

```{r, warning=F, message=F}
plot_drc_g <- ggplot() +
  # geom_ribbon_interactive(
  #   data=CI.g,
  #   aes(
  #     x=Dose,
  #     y=p,
  #     ymin=pmin, ymax=pmax,
  #     group=Molecule,
  #     fill=Molecule,
  #     tooltip = Molecule,
  #     data_id = Molecule,
  #     ),
  #   alpha=0.2)+
  # geom_line_interactive(
  #   data = CI.g,
  #   aes(
  #     x=Dose,
  #     y=p,
  #     color=Molecule,
  #     tooltip = Molecule,
  #     data_id = Molecule,
  #     color=Molecule,
  #     shape = Molecule
  #     ),
  #   linewidth = 1.2
  #   )+
  geom_point_interactive(
    data = df_rates_alive,
    aes(
      x = Dose_plot,
      y = a,
      shape = Molecule,
      tooltip = Molecule,
      data_id = Molecule,
      color = Molecule,
      shape = Molecule
    ),
    cex = 2,
    alpha = 0.4
  ) +
  geom_point_interactive(
    data = df_rates_alive_mean,
    aes(
      x = Dose_plot,
      y = a,
      shape = Molecule,
      tooltip = Molecule,
      data_id = Molecule,
      color = Molecule,
      shape = Molecule
    ),
    alpha = 1,
    size = 3
  ) +
  scale_color_manual(name = "", values = col_molec) +
  scale_shape_manual(name = "", values = shape_molec) +
  scale_fill_manual(name = "", values = col_molec) +
  theme_minimal() +
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.001, 0.01, 0.1, 1, 10, 100, 1000),
    labels = c(Label_Ctrl, "0.001", "0.01", "0.1", "1", "10", "100", "1000")
  ) +
  labs(
    x = "Dose (mg/kg)",
    y = expression(paste("Growth rate (", mg^{
      1 / 3
    }, "/day)")),
    # y = "Relative growth rate (%)",
    # title = "B. Effects on juvenile growth"
  ) +
  theme(
    legend.position = "none",
    legend.title = element_text(
      size = sizetitle - 2,
      face = "bold"
    ),
    title = element_text(
      size = sizetitle,
      face = "bold"
    ),
    axis.title.x = element_text(
      size = sizetitle,
      face = "plain"
    ),
    axis.title.y = element_text(
      size = sizetitle,
      face = "plain"
    )
  )

tooltip_css <- "
  border-radius: 12px;
  color: #333;
  background-color: white;
  padding: 10px;
  font-size: 14px;
  transition: all 0.5s ease-out;
"

hover_css <- "
  filter: brightness(75%);
  cursor: pointer;
  transition: all 0.5s ease-out;
  filter: brightness(1.15);
"

interactive_plot <- girafe(ggobj = plot_drc_g) %>%
  girafe_options(opts_sizing(rescale = FALSE))

# Add interactivity
interactive_plot <- interactive_plot %>%
  girafe_options(
    opts_hover(css = hover_css),
    opts_tooltip(css = tooltip_css),
    opts_hover_inv(css = "opacity:0.3; transition: all 0.2s ease-out;")
  )

plot_drc_g_f <- plot_drc_g +
  labs(title = "B. Effects on juvenile growth")
```

```{r, warning=F, message=F}
#| fig-cap: Dose-response curves for growth.
#| label: fig-growthdrc
#| fig-width: 8
#| fig-height: 4

p <- ggplot() +
  # geom_ribbon_interactive(
  #   data=CI.g,
  #   aes(
  #     x=Dose,
  #     y=p,
  #     ymin=pmin, ymax=pmax,
  #     group=Molecule,
  #     fill=Molecule,
  #     tooltip = Molecule,
  #     data_id = Molecule,
  #     ),
  #   alpha=0.2)+
  # geom_line_interactive(
  #   data = CI.g,
  #   aes(
  #     x=Dose,
  #     y=p,
  #     color=Molecule,
  #     tooltip = Molecule,
  #     data_id = Molecule,
  #     color=Molecule,
  #     shape = Molecule
  #     ),
  #   linewidth = 1.2
  #   )+
  geom_point(
    data = df_rates_alive,
    aes(
      x = Dose_plot,
      y = a,
      color = Molecule,
      shape = Molecule
    ),
    alpha = 0.5,
  ) +
  geom_point(
    data = df_rates_alive_mean,
    aes(
      x = Dose_plot,
      y = a,
      color = Molecule,
      shape = Molecule
    ),
    alpha = 1,
    size = 3
  ) +
  scale_x_log10(
    breaks = c(Val_Ctrl, 0.01, 0.1, 1, 10, 100), # inclure la valeur fictive
    labels = c(Label_Ctrl, "0.01", "0.1", "1", "10", "100")
  ) +
  facet_wrap(~Molecule, scales = "free_x") +
  scale_color_manual(values = col_molec) +
  scale_fill_manual(values = col_molec) +
  scale_shape_manual(values = shape_molec) +
  labs(
    x = "Dose (mg/kg)",
    y = expression(paste("Growth rate (", mg^{
      1 / 3
    }, "/day)")) # ,
    # title = "Effect of the pesticides on juvenile growth rates"
  ) +
  ylim(NA, 0.15) +
  theme_minimal(base_size = 15) + # Thème minimaliste
  theme(
    plot.title = element_text(
      # hjust = 0.5,
      face = "bold"
    ),
    legend.position = "none",
    strip.background = element_rect(
      color = "black",
      fill = Nord_snow[3],
      size = 0,
      linetype = "solid"
    ),
    strip.text = element_text(face = "bold")
  )
p
```

```{r, include=F}
ggsave(
  filename = "ExpA_growth_drc_single.png",
  plot = p,
  width = 8,
  height = 4,
  path = path_growth
)
ggsave(
  filename = "ExpA_growth_drc_single.svg",
  plot = p,
  width = 8,
  height = 4,
  path = path_growth
)
```

```{r}
# Anova model
df_rates_alive <- df_rates_alive |>
  mutate(
    Condition_f = as.factor(paste0(Molecule, Dose_plot)),
    Molecule = as.factor(Molecule)
  )

anova.drc.g <- glm(
  a ~ Condition_f,
  data = df_rates_alive
)
# check_model(glm_anova)
# predict(glm_anova)

# Log-likelihood
LL_drc <- as.numeric(logLik(drc.mod.g))
LL_anova <- as.numeric(logLik(anova.drc.g))

# Number of parameters
k_drc <- 6
k_anova <- attr(logLik(anova.drc.g), "df")

# Log-likelihood ratio test
# H0 : the drc model is OK
# H1 : the ANOVA model (saturated) is better
D <- -2 * (LL_drc - LL_anova)
df_test <- k_anova - k_drc

# Vérification

p_val <- pchisq(D, df = df_test, lower.tail = FALSE)
cat("Lack-of-fit test: D =", round(D, 3), ", df =", df_test, ", p =", round(p_val, 4), "\n")
```

This drc model logically does not pass the lake-of-fit test.

```{r, warning=F, message=F}
#| fig-cap: Diagnostic graphs
#| label: fig-drcdiagg
#| fig-width: 8
#| fig-height: 4

col_diag <- Nord_polar[4]

plot_QQ <- ggplot(
  mapping = aes(
    sample = residuals(drc.mod.g)
  )
) +
  stat_qq(alpha = 0.3) +
  stat_qq_line(color = col_diag) +
  labs(
    x = "Normal quantiles",
    y = "Residuals"
  ) +
  theme_minimal()

plot_resfit <- ggplot() +
  geom_point(
    mapping = aes(
      x = fitted(drc.mod.g),
      y = residuals(drc.mod.g)
    ),
    color = col_diag,
    alpha = 0.3
  ) +
  labs(
    x = "Fitted",
    y = "Residuals"
  ) +
  scale_x_log10() +
  theme_minimal()

plot <- plot_resfit + plot_QQ + plot_layout(ncol = 2)
plot
```

NOEC determination for juvenile growth :

```{r, warning=F, message=F}
# ANOVA
cat("IMD - Determination of NOEC and LOEC\n")
mod_aov <- aov(a ~ Dose_f, data = subset(df_rates_alive, Molecule == "IMD"))
summary(mod_aov)

dunnett_test <- glht(mod_aov, linfct = mcp(Dose_f = "Dunnett"))
summary(dunnett_test)

cat("EPX - Determination of NOEC and LOEC\n")
mod_aov <- aov(a ~ Dose_f, data = subset(df_rates_alive, Molecule == "EPX"))
summary(mod_aov)

dunnett_test <- glht(mod_aov, linfct = mcp(Dose_f = "Dunnett"))
summary(dunnett_test)
```

We can also say that there is an effect of the dose on juveniles growth.

### Observed mortality

```{r, warning=F, message=F}
#| fig-cap: Mortality observed in each condition.
#| label: fig-growthdrcmortality
#| fig-width: 6
#| fig-height: 5

df_dead_g <- df_expA_growth_tot |>
  filter(t == 28) |>
  group_by(Dose_f, Molecule) |>
  summarise(
    n_D = sum(Status == "D", na.rm = TRUE), # compte lignes avec Status "D"
    n_total = n(), # total lignes par condition
    .groups = "drop"
  )

p <- ggplot(
  data = df_dead_g,
  aes(
    x = Dose_f,
    y = n_D,
    color = Molecule,
    fill = Molecule
  )
) +
  geom_col(
    alpha = 0.5
  ) +
  geom_text(
    aes(label = round(n_D)),
    vjust = -0.5,
    size = 4
  ) +
  labs(
    x = "Dose (mg/kg)",
    y = "Number of dead individuals (#)"
  ) +
  facet_wrap(
    ~Molecule,
    ncol = 1,
    scales = "free"
  ) +
  scale_color_manual(values = col_molec) +
  scale_fill_manual(values = col_molec) +
  lims(y = c(0, 4.5)) +
  theme_classic(12) +
  theme(
    legend.position = "none",
    legend.title = element_text(
      size = sizetitle - 2,
      face = "bold"
    ),
    legend.text = element_text(
      size = sizetitle - 2,
      face = "plain"
    ),
    title = element_text(
      size = sizetitle,
      face = "bold"
    ),
    strip.background = element_rect(
      color = "black",
      fill = "grey95",
      size = 0,
      linetype = "solid"
    )
  )
p
```

```{r, include=F}
ggsave(
  filename = "ExpA_growth_single_dead.png",
  plot = p,
  width = 5,
  height = 5,
  path = path_growth
)
ggsave(
  filename = "Growth_single_dead.svg",
  plot = p,
  width = 5,
  height = 5,
  path = path_growth
)
```

## Conclusion

```{r, warning=F, message=F}
#| fig-cap: Estimated effect on cocoon production for environmental concentrations
#| label: fig-drcccl
#| fig-width: 8
#| fig-height: 4

p <- plot_drc_r_f + plot_drc_g_f +
  plot_layout(ncol = 2, guides = "collect")
p
```

```{r, include=F}
ggsave(
  filename = "Article_drc.png",
  plot = p,
  width = 8,
  height = 4,
  path = here::here("fig/")
)
ggsave(
  filename = "Article_drc.svg",
  plot = p,
  width = 8,
  height = 4,
  path = here::here("fig/")
)
```

The individual toxicity profiles of epoxiconazole and imidacloprid in earthworms confirm both compounds as environmentally relevant stressors, albeit with markedly different potencies.

Imidacloprid demonstrated high toxicity to earthworms with pronounced effects on both growth (NOECjuvenile = 0.28 mg/kg; NOECadult = 0.5 mg/kg) and reproduction (EC50 = 0.55 mg/kg; NOEC = 0.28 mg/kg). These findings align closely with published literature, where imidacloprid EC50 values for reproduction in Eisenia species have been reported at 0.87 mg/kg (Wang et al., 2019), and chronic assays showed EC50 values ranging from 0.21 to 1.89 mg/kg depending on soil type (Bandeira et al., 2020).

In contrast, epoxiconazole exhibited substantially lower toxicity, with moderate effects on growth (NOECjuvenile = 9.3 mg/kg; NOECadult = 92.8 mg/kg) and reproduction (EC50 = 126.8 mg/kg; NOEC \>= 200 mg/kg). The literature on epoxiconazole toxicity to earthworms remains more limited compared to imidacloprid, reflecting the generally lower concern for triazole fungicides in soil invertebrate risk assessment. The reduced potency measured in our study is consistent with reported data for Aporrectodea icterica exposed to a formulated version of epoxiconazole (OPUS®) in Pelosi et al. (2016), however the LC50 values of 45.5 mg/kg indicates a higher sensitivity of this species. Across both compounds, a consistent pattern emerged: reproductive effects occurred at lower concentrations than adult growth effects, indicating that reproduction is a more sensitive endpoint for detecting pesticide impacts in adult earthworms. This sensitivity hierarchy aligns with established ecotoxicological principles and regulatory testing frameworks. However, juvenile growth was more sensitive than adult growth and at least as sensitive as reproduction, highlighting the particular vulnerability of early life stages.

The toxicity ratio between these compounds (EC50(IMD)/EC50(EPX) ≈ 230-fold difference) demonstrates the substantially higher potency of the neonicotinoid insecticide compared to the triazole fungicide, a pattern consistent with their respective modes of action and target specificity. This differential potency has important implications for mixture risk assessment, as the more toxic component (imidacloprid) would be expected to drive mixture effects under concentration addition assumptions.

Comparison of environmental concentrations with observed effect thresholds reveals important risk assessment insights. For imidacloprid, the reproduction EC50 of 0.55 mg/kg represents concentrations 36.4 to 189.6-fold higher than typical median environmental levels (0.0029-0.0151 mg/kg), but only 3.4-fold higher than maximum detected concentrations (0.16 mg/kg) (@tbl-concenv). The growth NOEC of 0.28 mg/kg similarly falls within 1.8-fold of maximum environmental concentrations. This suggests that while effects are unlikely under typical exposure scenarios, peak contamination events could approach concentrations of ecological concern. For epoxiconazole, the reproductive EC50 of 126.8 mg/kg provides larger safety margins, being 448-fold higher than maximum detected environmental concentrations (0.283 mg/kg) and over 3,000-fold higher than median concentrations (@tbl-concenv). The growth NOEC of 9.3 mg/kg maintains a 33-fold safety margin even against maximum environmental levels.

| Compound | Source | Median | Q75% | Maximum | Former application dose (EU) |
|----|----|----|----|----|----|
| IMD | Froger et al. (2023) | 2.9 | 5.8 | 13.8 |  |
| IMD | Pelosi et al. (2021) | 15.1 | – | 160 | 168 |
| EPX | Froger et al. (2023) | 5.8 | 10.9 | 23.6 |  |
| EPX | Pelosi et al. (2021) | 34.6 | – | 283 | 153 |

: Summary of results for the detected imidacloprid and epoxiconazole residues in the Froger et al. (2023) and Pelosi et al. (2021) studies. {#tbl-concenv}

These findings indicate that imidacloprid poses greater environmental risk than epoxiconazole under current contamination scenarios, particularly in intensive agricultural systems where maximum concentrations approach effect thresholds. The narrow safety margin for imidacloprid (1.8-3.4 fold) falls below typical regulatory safety factors of 10-100, suggesting potential for ecological impacts during peak exposure periods or in highly contaminated sites. Although both imidacloprid and epoxiconazole are now restricted, these substances are persistent in soils, with imidacloprid concentrations in some locations exceeding safety margins. Moreover, even though epoxiconazole alone exhibits limited toxicity, additive effects with imidacloprid residues could increase the overall risk to soil organisms.

<button class="accordion-button" type="button" data-bs-toggle="collapse" data-bs-target="#collapseOne">

<b> Session Information </b>

</button>

:::: {#collapseOne .accordion-collapse .collapse}
<div>

```{r}
sessionInfo()
```

</div>
::::
